### 2019-12-16 main.tex
Initial Overleaf Import

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ruled,vlined, linesnumbered]{algorithm2e}
\usepackage[english]{babel}
\usepackage[nottoc]{tocbibind}
\usepackage{color}
\usepackage{natbib}
\providecommand{\note}[1]{\textcolor{red}{#1}}

\title{Efficient Feature Screening for Lasso-Type
Problems via Batched Safe-Strong Rules}
\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
  \and
  Patrick Breheny\\Department of Biostatistics\\University of Iowa}
\date{}

\begin{document}

\maketitle

\section{Introduction}

The lasso (least absolute shrinkage and selection operator) model\citep{tibshirani1996regression}, is a popular model in statistics and machine learning, especially in high-dimensional problems. The model can be defined as the following modification of the least squares optimization problem:
\begin{equation}
    \hat{\beta}(\lambda)=\underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}||y-X\beta||_2^2+\lambda||\beta||_1,
\end{equation}
where $y$ is the $n\times 1$ response vector correspond to $n$ observations, $X=(x_1,x_2,...,x_p)$ is the $n\times p$ feature matrix correspond to $p$ features, $\beta\in \mathbb{R}^p$ is the $p\times 1$ coefficient vector and $\lambda$ is the regularization tuning parameter. $||\cdot||_2$ denotes the $l_2$ (Euclidean) norm and $||\cdot||_1$ denotes the $l_1$ norm.

The lasso model has several attractive properties compared to least squares regression, including increased stability of estimation, increased prediction accuracy, and automatic variable selection arising from the fact that it yields sparse estimates of $\beta$.  As a result, it is widely applied in different fields, such as gene expression data analysis, image recognition and text mining, and has been extended in several ways, such as group lasso\cite{yuan2006model}, elastic net\cite{zou2005regularization} and sparse generalized linear models. Because of its wide popularity, solving the lasso model efficiently is an important topic in statistics and machine learning.

Because the optimal value of $\lambda$ is not known in advance, typical practice is to solve for $\beta$ along a sequence of values of the tuning parameter $\lambda$, known as the solution path.  Pathwise algorithms can be efficiently implemented by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.  In particular, the pathwise coordinate descent algorithm\cite{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS (least angle regression)\cite{efron2004least}, especially in high dimensional settings where $p$ is large. In sparse settings, it scales up very well with a computational cost of approximately $O(np)$. As a result, it is widely used to fit the lasso and other penalized regression models.

However, modern data collection and storage techniques allow researchers to measure an increasingly large number of features, which introduce additional computational challenges. In particular, it may not be possible to store the feature matrix, which can require many GBs of memory to store, in memory. One can resolve this problem by using a memory mapping package such as \textbf{bigmemory}, which allows us to store the feature matrix on disk and read it portions of it as needed; however, this results in frequent reading from disk, which is extremely slow compared to other parts of the algorithm and becomes a bottleneck with respect to the computational burden of fitting lasso models on very large data sets.

One promising technique to address this challenge is feature screening. The lasso model solution is sparse in the sense that most coefficients will be exactly zero; for these ``inactive'' coefficients we do not need their associated features.  In theory, if we knew which coefficients were nonzero, we could read into memory only those features and leave the remaining features on disk. In reality, we cannot know this prior to fitting the model -- however, through the clever use of feature screening rules, we can greatly reduce the number of times inactive features are read into memory, thereby minimizing the computational burden.  In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision: for example, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.

There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}, which occasionally incorrectly discard an active feature, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.  As one might expect, strong rules tend to be easy to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.  This check is not necessary with safe rules.  However, safe rules are considerably less powerful at discarding features than strong rules.  More recently, hybrid approaches \cite{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.

\note{I think we need a better transition here} In this paper, we proposed adaptive batched safe-strong rules. We divided the set of $\lambda$ values into batches and screening within each batch is based on the same solution at one $\lambda$ value at the beginning of the batch. On one hand, basing on the same solution avoids many costly computation and on the other hand, referring to solution at a close $\lambda$ value provides more screening power. An adaptive choice of batches sizes are applied using the screening performance from previous $\lambda$ values to better balance these two effects. It will be shown that our adaptive rule can greatly reduce the computation time and outperform other method under all scenarios. Similar to HSSR, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models. For example we extended the method to work with logistic regression with lasso penalty.

This manuscript provides a brief review of existing feature screening rules in Section\ref{sec:existing} as well as the following novel contributions:

\begin{itemize}
    \item A new feature screening framework (Section ?3.2??), which does screening in batches of $\lambda$ values with any safe screening rules, which can generate a family of more efficient and scalable screening rule, compared to previous screening rules that are either sequential or one-step.
    \item Two specific applications of this framework, Batch-SSR-SEDPP and Batch-SSR-Slores, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section ?3.3??).
    \item An algorithm to adaptively determine efficient batch sizes (Section \ref{sec:batch-size}).
    \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
    \item The Batch-SSR-SEDPP and Batch-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\cite{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
\end{itemize}

\section{Existing feature screening rules}
\label{sec:existing}

% \begin{itemize}
%     \item Active set cycling ?
%     \item Strong rules
%     \item Safe rules:
%     \begin{itemize}
%         \item Sequential EDPP
%         \item Basic EDPP
%     \end{itemize}
%     \item Hybrid Safe-Strong rule
% \end{itemize}

Screening rules are able to discard zero coefficients due to the KKT (Karush-Kuhn-Tucker) conditions of the lasso problem. It states that the solution $\hat{\beta}(\lambda)$ must satisfies the following conditions:

\begin{equation}
    \begin{cases}
    x_j^Tr(\lambda)/n = \lambda sign(\hat{\beta}(\lambda)_j),\qquad if\quad \hat{\beta}(\lambda)_j\neq 0,\\
    |x_j^Tr(\lambda)/n| \leq \lambda,\hfill if\quad \hat{\beta}(\lambda)_j= 0,
    \end{cases}
\end{equation}

where $r(\lambda)$ is the residuals vector at $\lambda$ defined as $y-X\hat{\beta}(\lambda)$. If the residuals are known, we can safely conclude feature $j$ has 0 coefficient if the second condition meets, but residuals cannot be calculated without first solving the coefficients. However, when fitting a solution path, residuals at previous $\lambda$ values can be calculated and provide information about residuals at current $\lambda$ value.

Pathwise coordinate descent is a popular algorithm fitting a solution path for lasso problem using warm start. Given the previous solution $\hat{\beta}(\lambda_0)$ with residuals $r(\lambda_0)$, the solution $\hat{\beta}(\lambda)$ with residuals $r(\lambda)$ can be computed by the following algorithm:
\begin{algorithm}
    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Initialize}{Initialize}
    \SetAlgoLined
    \Input{$\hat{\beta}(\lambda_0), \{x_j\}_{j=1}^p, r(\lambda_0)$}
    \Initialize{ $r = r(\lambda_0),\hat{\beta} = \hat{\beta}(\lambda_0)$}
    \BlankLine
    \While{not converged}{
        \For{$j \xleftarrow{}$ 1 \KwTo p}{
            $z_j\xleftarrow{}\hat{\beta} + x_j^Tr/n$\;
            \uIf{$z_j > \lambda$}{
                $\beta_j^{new}\xleftarrow{} z_j-\lambda$\;
            }\uElseIf{$z_j < -\lambda$}{
                $\beta_j^{new}\xleftarrow{} z_j+\lambda$\;
            }\Else{
                $\beta_j^{new}\xleftarrow{} 0$\;
            }
            $r\xleftarrow{}r-(\beta_j^{new}-\hat{\beta}_j)x_j$\;
            $\hat{\beta}_j\xleftarrow{}\beta_j^{new}$\;
        }

    }
    \Output{$\hat{\beta}(\lambda)\xleftarrow{}\hat{\beta},r(\lambda)\xleftarrow{}r$}
    \caption{Pathwise coordinate descent with warm start $\hat{\beta}(\lambda_0),r(\lambda_0)$}
\end{algorithm}

\noindent In this algorithm, residuals $r$ are computed at each $\lambda$ value for the update of the coefficients and can also be reused conveniently for feature screening purpose.

Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling\cite{lee2007efficient}. When solving the coefficients for current $\lambda$, first consider the model with coefficients that were non-zero at previous $\lambda_0$. After computing the first solution, a post-convergence KKT conditions check is performed and if there is no violation, the solution to the smaller model will be the exact solution to the full model. If there are violations, corresponding features will be added to the model and the procedure will repeat. Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm converges fast.

For the rest of the paper, it will be assumed that $y$ is centered so intercept can be dropped and $\{x_j\}_{j=1}^p$ are centered and standardized. That is:

\begin{equation}
    \sum_{i=1}^ny_i=0, \qquad \sum_{i=1}^n x_{ij}=0, \qquad \sum_{i=1}^n x_{ij}^2=n,\qquad j=1,2,...,p.
\end{equation}
This standardization make it reasonable to apply the same penalty to all features, which are usually measured in different units. It improves the efficiency and stability of the optimization as well. Most importantly for this paper, it greatly helps simplify the forms for screening rules and thus simplify the code for implementation.

\subsection{}

\section{Batched safe-strong rule}
\label{sec:method}

\subsection{Batched EDPP rule}
\begin{itemize}
    \item Validate that given solution at one lambda value, we can safely screen for solutions at a batch of lambda values.
    \item From the simplified notation of the EDPP rule, most quantities need to be calculated once per batch from the given solution.
    \item Propose the new rule.
\end{itemize}

\subsection{Batched strong rule after batched EDPP rule}
\begin{itemize}
    \item Analyse hybrid strong rule in this case and point out calculation that can be avoided (at a small cost of power)
    \item Propose the new combined rule (Batched safe strong rule)
    \item Proof of convergence
\end{itemize}

\subsection{Coordinate descent with Batched safe strong rule}

\begin{itemize}
    \item Quantities that can be shared by batched safe strong rule and coordinate descent
    \item pseudo code
\end{itemize}

\subsection{Adaptive determining batch size}
\label{sec:batch-size}
\begin{itemize}
    \item Analyse computing cost for each part of coordinate descent with Batched safe strong rule.
    \item Analyse pattern of the number of rejections by EDPP rule over the solution path.
    \item Propose a rule for starting a new batch by balancing cost of each part
\end{itemize}

\subsection{Performance analysis}
\begin{itemize}
    \item Screening power
    \item Computational complexity ?
\end{itemize}

\section{Extension to other lasso type problems}
\label{sec:4}

\begin{itemize}
    \item Logistic regression with Slores instead of EDPP
    \item group lasso ?
    \item elastic net ?
\end{itemize}

\section{Experiments}
\label{sec:5}

\subsection{Simulations}
\label{sec:sim}
\begin{itemize}
    \item Introduction to biglasso package
\end{itemize}
\begin{itemize}
    \item Comparing active set cycling, strong rules, SEDPP, Hybrid SSR, and proposed Batched SSR
    \item Varying n, p. Computation time for all methods grow linearly and ratios among them are constant.
    \item Varying signal-noise ratio. As the signal increases, the proposed method has larger advantage over other method.
    \item Varying $||\beta||_0$, number of non-zero coefficients, or sparsity. When the model is sparser, the proposed method has larger advantage over other methods.
\end{itemize}

\subsection{Real data analysis}
\label{sec:real-data}

\subsection{Big data performance}

\begin{itemize}
    \item Analyse and profile different methods. Compare them in big data case ?
\end{itemize}

\section{Conclusion}
\label{sec:6}

\bibliographystyle{unsrt}
\bibliography{ref}

\end{document}

### 2019-12-16 main.tex
Modified last part of section 1 and beginning of section 2.

@@
 The lasso model solution is sparse in the sense that most coefficients will be exactly zero; for these ``inactive'' coefficients we do not need their associated features.
-In theory, if we knew which coefficients were nonzero, we could read into memory only those features and leave the remaining features on disk.
+In theory, if we knew which coefficients were nonzero at each value of $\lambda$, we could read into memory only those features and leave the remaining features on disk.
 In reality, we cannot know this prior to fitting the model -- however, through the clever use of feature screening rules, we can greatly reduce the number of times inactive features are read into memory, thereby minimizing the computational burden.
-In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision: for example, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
+In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision and a decision is made for each $\lambda$ values: for example, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
 
-There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}, which occasionally incorrectly discard an active feature, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
-As one might expect, strong rules tend to be easy to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
+There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}, which occasionally incorrectly discard some active features, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
+As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
 This check is not necessary with safe rules.
@@
 
-\note{I think we need a better transition here} In this paper, we proposed adaptive batched safe-strong rules.
+\note{I think we need a better transition here} In this paper, we proposed an adaptive batched screening scheme that changes how screening is done along the path of $\lambda$ values and implement it into hybrid approaches to form adaptive batched safe-strong rules.
 We divided the set of $\lambda$ values into batches and screening within each batch is based on the same solution at one $\lambda$ value at the beginning of the batch.
@@
 It will be shown that our adaptive rule can greatly reduce the computation time and outperform other method under all scenarios.
-Similar to HSSR, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
+Similar to hybrid approaches, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
 For example we extended the method to work with logistic regression with lasso penalty.
@@
 where $r(\lambda)$ is the residuals vector at $\lambda$ defined as $y-X\hat{\beta}(\lambda)$.
-If the residuals are known, we can safely conclude feature $j$ has 0 coefficient if the second condition meets, but residuals cannot be calculated without first solving the coefficients.
-However, when fitting a solution path, residuals at previous $\lambda$ values can be calculated and provide information about residuals at current $\lambda$ value.
+If the residuals are known, we can safely conclude feature $j$ has 0 coefficient if the second condition holds with "$<$", but residuals cannot be calculated without first solving the coefficients.
+However, when fitting a solution path, residuals at previous $\lambda$ values can be calculated and provide information about residuals at current $\lambda$ value and thus be used for screening.
 
@@
 
-\noindent In this algorithm, residuals $r$ are computed at each $\lambda$ value for the update of the coefficients and can also be reused conveniently for feature screening purpose.
-
-Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling\cite{lee2007efficient}.
-When solving the coefficients for current $\lambda$, first consider the model with coefficients that were non-zero at previous $\lambda_0$.
-After computing the first solution, a post-convergence KKT conditions check is performed and if there is no violation, the solution to the smaller model will be the exact solution to the full model.
-If there are violations, corresponding features will be added to the model and the procedure will repeat.
-Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm converges fast.
+\noindent In this algorithm, residuals $r$ are computed at each $\lambda$ value for the update of the coefficients and can thus be reused conveniently for feature screening purpose.
 
@@
 
-\subsection{}
+It will also be assumed that lasso model is solved along $K+1$ decreasing values of $\lambda$ denoted as $\lambda_0,\lambda_1,...,\lambda_K$.
+
+\subsection{Active-set Cycling}
+
+Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \cite{lee2007efficient}.
+When solving the coefficients for at $\lambda_k$, first consider the model with coefficients that were non-zero at $\lambda_{k-1}$.
+After computing the first solution, a post-convergence KKT conditions check is performed and if there is no violation, the solution to the smaller model will be the exact solution to the full model.
+If there are violations, corresponding features will be added to the model and the procedure will repeat.
+Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm converges fast.
 

### 2019-12-18 main.tex
Add Section 2.

@@
 \providecommand{\note}[1]{\textcolor{red}{#1}}
+\newtheorem{theorem}{Theorem}[section]
 
@@
 
-There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}, which occasionally incorrectly discard some active features, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
+There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}\cite{qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
 As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
@@
 Screening rules are able to discard zero coefficients due to the KKT (Karush-Kuhn-Tucker) conditions of the lasso problem.
-It states that the solution $\hat{\beta}(\lambda)$ must satisfies the following conditions:
+It states that the solution $\hat{\beta}(\lambda)$ is optimal if and only if the following conditions hold:
 
@@
 Given the previous solution $\hat{\beta}(\lambda_0)$ with residuals $r(\lambda_0)$, the solution $\hat{\beta}(\lambda)$ with residuals $r(\lambda)$ can be computed by the following algorithm:
-\begin{algorithm}
+
+\begin{algorithm}[H]
     \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Initialize}{Initialize}
@@
 
-For the rest of the paper, it will be assumed that $y$ is centered so intercept can be dropped and $\{x_j\}_{j=1}^p$ are centered and standardized. That is:
+For the rest of the paper, it will be assumed that $y$ is centered so the intercept can be dropped and $\{x_j\}_{j=1}^p$ are centered and standardized. That is:
 
@@
 It improves the efficiency and stability of the optimization as well.
-Most importantly for this paper, it greatly helps simplify the forms for screening rules and thus simplify the code for implementation.
+Most importantly for this manuscript, it greatly helps simplify the formulas for screening rules and thus simplify the code for implementation.
 
 It will also be assumed that lasso model is solved along $K+1$ decreasing values of $\lambda$ denoted as $\lambda_0,\lambda_1,...,\lambda_K$.
+Solution of $\beta$ at any $\lambda_k$ is denoted as $\hat{\beta}(\lambda_k)$.
+From the KKT conditions (2), when $\lambda>\max_j|x_j^Ty/n|$, $r(\lambda)=y$ and all the coefficients will always be zero.
+As a result, we only need to focus on $\lambda\in (0,\max_j|x_j^Ty/n|]$ and we will set $\lambda_0=\max_j|x_j^Ty/n|$.
 
@@
 Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \cite{lee2007efficient}.
-When solving the coefficients for at $\lambda_k$, first consider the model with coefficients that were non-zero at $\lambda_{k-1}$.
-After computing the first solution, a post-convergence KKT conditions check is performed and if there is no violation, the solution to the smaller model will be the exact solution to the full model.
-If there are violations, corresponding features will be added to the model and the procedure will repeat.
-Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm converges fast.
+When solving the coefficients for at $\lambda_{k+1}$, first only consider features whose coefficients were non-zero at $\lambda_k$ and discard other features with zero coefficients at $\lambda_k$.
+We compute the solution for the smaller model with these reduced number of coefficients.
+
+After computing the solution, a post-convergence KKT conditions check is performed.
+Because the KKT conditions are sufficient for the solution to be optimal, if there is no violation, the solution to the smaller model will be exactly the same as if we solve the model with all features.
+If there are violations, corresponding features will be added to the model and this procedure will repeat.
+Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm provides substantial speed up.
+
+\subsection{Strong rules}
+
+Sequential strong rule (SSR) \cite{tibshirani2011regression} is a fast and powerful feature screening rule.
+Given the solution $\hat{\beta}(\lambda_k)$ at $\lambda_k$, we can compute the residual vector as $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$.
+The SSR discard the $j$-th feature at $\lambda_{k+1}$ if:
+
+\begin{equation}
+    |x_j^Tr(\lambda_k)/n|<2\lambda_{k+1}-\lambda_k.
+\end{equation}
+
+The SSR is derived from the KKT condition and the "unit-slope" assumption.
+In (2), if we denote the left-hand-side as $c_j(\lambda)=x_j^Tr(\lambda)/n$, then the "unit-slope" assumption assumes a unit bound on the slope of $c_j(\lambda)$ over $\lambda$.
+That is:
+
+\begin{equation}
+    |c_j(\lambda)-c_j(\lambda')|\leq |\lambda-\lambda'|,\qquad \forall \lambda,\lambda'\in(0,\lambda_0].
+\end{equation}
+
+Under this condition and (4), using triangle inequality, $c_j(\lambda_k)$ can be bounded as the following:
+
+\begin{equation}
+    \begin{split}
+        |c_j(\lambda_{k+1})| &\leq |c_j(\lambda_{k+1})-c_j(\lambda_k)| + |c_j(\lambda_k)|\\
+    &< \lambda_k - \lambda_{k+1} + (2\lambda_{k+1}-\lambda_k)\\
+    &=\lambda_{k+1},
+    \end{split}
+\end{equation}
+and then KKT conditions (2) guarantees $\hat{\beta}_j(\lambda_{k+1})=0$.
+
+The biggest problem of SSR is that the "unit-slope" condition (5) may not hold and thus discarded features are not guaranteed to have zero coefficients.
+A post-convergence KKT check is needed for the discarded features to make sure their coefficients are truly zero.
+If violations occur, we need to refit the model adding the violating features and repeat the post-convergence check.
+The cost for each post-convergence check is O(np) and especially costly when violations occur.
+However, previous studies have shown that violations are rare and thus additional cost is acceptable.
+
+A nice property about SSR with post-convergence check is that some quantities can be reused.
+When doing post-convergence check at $\lambda_k$, $x_j^Tr(\lambda_k)/n$ is calculated in (2).
+Then in SSR screening at $\lambda_{k+1}$ (4), this quantity is used again.
+In fact, when the quantity $x_j^Tr(\lambda_k)/n$ is already computed, other parts of the computation of (4) have almost zero cost.
+In conclusion, the computation cost of SSR is generally only the cost of the post-convergence check, which is O(npK).
+
+\subsection{Safe rules}
+
+Compared to strong rules, safe rules can discard features safely.
+Those discarded features are guaranteed to have zero coefficients and we do not need an addition check to validate them.
+We will mainly focus on enhanced dual polytope projections (EDPP) rules\cite{wang2013lasso}, because they outperform other current safe rules and are easy to incorporate in our method.
+
+The EDPP rules are derived from the dual formulation of the lasso problem (1):
+
+\begin{equation}
+    \begin{split}
+        \hat{\theta}(\lambda) = \underset{\theta\in \mathbb{R}^n}{\mathrm{argmax}}\frac{1}{2n}||y||_2^2-\frac{n\lambda}{2}||\theta-\frac{y}{n\lambda}||_2^2\\
+        subject\quad to\quad |x_j^T\theta|\leq 1,\quad \forall j=1,2,...,p.
+    \end{split}
+\end{equation}
+This is minimizing the distance between $\theta$ and the rescaled response $\frac{y}{n\lambda}$ subject to the conditions $|x_j^T\theta|\leq 1$.
+Geometrically $\hat{\theta}(\lambda)$ can be viewed as the projection of the rescaled response $\frac{y}{n\lambda}$ onto the polytope defined by $|x_j^T\theta|\leq 1$.
+As $\lambda$ decreases alone the solution path, the rescaled response $\frac{y}{n\lambda}$ moves further away from 0 and the projection $\hat{\theta}(\lambda)$ moves with it.
+Because $\hat{\theta}(\lambda)$ is a projection onto a non-empty closed convex set, the movement of the projection can be bounded and thus $\hat{\theta}(\lambda)$ can be bounded given some previous solution $\hat{\theta}(\lambda')$ at some $\lambda'>\lambda$.
+
+In fact, the solution of the primal problem (1) and the solution of the dual problem (7) can be linked by:
+\begin{equation}
+    \hat{\theta}(\lambda)=\frac{y-X\hat{\beta}(\lambda)}{n\lambda}=\frac{r(\lambda)}{n\lambda},
+\end{equation}
+so bounding $\hat{\theta}(\lambda)$ is essentially bounding the residual vector $r(\lambda)$.
+Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP), were proposed\cite{wang2013lasso} simplified\cite{zeng2017efficient} under the standardization (3) and can be stated in the following theorems:
+
+\begin{theorem}[BEDPP]
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$. Under (3) and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
+    \begin{equation}
+        |(\lambda_0+\lambda)x_j^Ty-(\lambda_0-\lambda)sign(x_*^Ty)\lambda_0x_j^Tx_*|<2n\lambda_0\lambda-(\lambda_0-\lambda)\sqrt{n||y||_2^2-n^2\lambda_0^2}.
+    \end{equation}
+\end{theorem}
+
+\begin{theorem}[SEDPP]
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (3)
+    \begin{enumerate}
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=y-X\hat{\beta}(\lambda_k)$, then $\hat{\beta}_j(\lambda_{k+1})=0$ if
+        \begin{equation}
+            \begin{split}
+                &\left|2\lambda_{k+1}x_j^Tr(\lambda_k)+(\lambda_k-\lambda_{k+1})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_k)x_j^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\\&<2n\lambda_k\lambda_{k+1}-(\lambda_k-\lambda_{k+1})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
+            \end{split}
+        \end{equation}
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, SEDPP rule reduces to BEDPP rule. $\hat{\beta}_j(\lambda_1)=0$ if (9) holds with $\lambda=\lambda_1$.
+    \end{enumerate}
+\end{theorem}
+
+In BEDPP rule (9), the most costly parts of computation that take O(np) time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
+These quantities does not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
+After this step is finished, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with O(np) cost.
+
+In SEDPP rule (10), it requires computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ ($x_j^T\hat{y}(\lambda_k)$ can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$).
+For screening at every $\lambda_{k+1}$, $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ need to be recalculated and this step takes O(np) time.
+Thus SEDPP is a sequential rule and computation of the sequence takes O(npK) time.
+
+BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ by comparing it to $r(\lambda_0)=y$.
+As $\lambda_k$ gets further away from $\lambda_0$, this bound becomes less precise and the screening rule becomes less powerful.
+SEDPP is slower, but at each $\lambda_{k+1}$, it is comparing $r(\lambda_{k+1})$ to $r(\lambda_k)$.
+Because $\lambda_{k+1}$ and $\lambda_k$ are close, the bound will be tight and screening will keep being powerful.
+
+\subsection{Hybrid safe-strong rules}
+
+The hybrid safe-strong rules (HSSR) \cite{zeng2017efficient} was proposed to combine SSR with any member of safe rules to take advantage of both.
+More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments.
+This algorithm discards features that are discarded by either SSR or BEDPP rule.
+Then, when doing post-convergence check, it only checks features that are discarded by SSR but not discarded by BEDPP rule, instead of all features that are discarded by SSR.
+
+BEDPP rule is fast because heavy computation only occurs at the first step.
+SSR only requires heavy computation at the post-convergence check step.
+Now the set of features that need a post-convergence check is narrowed down by BEDPP rule and thus the cost of the post convergence check is reduced directly.
+Combining this two rules lead to a hybrid rule that outperforms using any screening rules alone in experiments.
+
+\subsection{Batch screening iterative lasso}
+
+Batch screening iterative lasso (BASIL) \cite{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches.
+Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+l}\}$ values we are going to solve at.
+First we do the screening for each $\lambda_{k+i}$ value in the batch based on solution at $\lambda_k$ by discarding the $j$-th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+i}-\lambda_k$.
+Then at each $\lambda_{k+i}$ value we solve the lasso problem with only the features that are not discarded.
+Last at post-convergence check, we search for largest $k+i$ in the batch $\{k+1,k+2,...,k+l\}$ such that KKT conditions hold for solution at $\lambda_{k+i}$ and accept only the solution from $\lambda_{k+1}$ to $\lambda_{k+i}$.
+Next, we move to a new batch by replacing the batch head $k$ with $k+i$ and repeat the same procedure again.
+
+The BASIL is most beneficial when the whole $X$ matrix is to large to be fit into the RAM, thus we need to read in a small number of columns $x_j$ from the hard disk at a time.
+In the post-convergence check for every batch, for each $j$, $x_j$ only needs to be read in once and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+l}\}$.
+Moreover, similar to SSR with ordinary post-convergence check, $x_j^Tr(\lambda_{x+i})$ computed at BASIL's post-convergence check step can be reused for screening at next batch.
 

### 2020-01-22 main.tex
Fixed error (missing $ for math); compiles properly now

@@
 
-\note{I think we need a better transition here} In this paper, we proposed an adaptive batched screening scheme that changes how screening is done along the path of $\lambda$ values and implement it into hybrid approaches to form adaptive batched safe-strong rules.
+Previous screening rules can also be divided into two categories, sequential rules and one-step rules, by how the screening is carried out along the path of $\lambda$ values.
+Sequential rules do heavy computation for each $\lambda$ values, so they are slower but relatively powerful at each $\lambda$ values.
+One-step rules only require heavy computation at the beginning and thus are faster but they cannot remain powerful along the path for long.
+
+In this paper, we proposed an adaptive batched screening scheme that changes how screening is done along the path of $\lambda$ values and implement it into hybrid approaches to form adaptive batched safe-strong rules.
 We divided the set of $\lambda$ values into batches and screening within each batch is based on the same solution at one $\lambda$ value at the beginning of the batch.
-On one hand, basing on the same solution avoids many costly computation and on the other hand, referring to solution at a close $\lambda$ value provides more screening power.
+This screening scheme helps avoid disadvantages of both sequential rules and one-step rules.
+On one hand, basing on the same solution avoids many costly computation within a batch and on the other hand, referring to solution at a close $\lambda$ value provides more screening power.
 An adaptive choice of batches sizes are applied using the screening performance from previous $\lambda$ values to better balance these two effects.
-It will be shown that our adaptive rule can greatly reduce the computation time and outperform other method under all scenarios.
+It will be shown that our adaptive rule can greatly reduce the computation time and outperform other methods under all scenarios.
 Similar to hybrid approaches, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP), were proposed\cite{wang2013lasso} simplified\cite{zeng2017efficient} under the standardization (3) and can be stated in the following theorems:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\cite{wang2013lasso}, were proposed and under the standardization (3) can be simplified in the following theorems\cite{zeng2017efficient}:
 
@@
 Batch screening iterative lasso (BASIL) \cite{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches.
-Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+l}\}$ values we are going to solve at.
-First we do the screening for each $\lambda_{k+i}$ value in the batch based on solution at $\lambda_k$ by discarding the $j$-th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+i}-\lambda_k$.
-Then at each $\lambda_{k+i}$ value we solve the lasso problem with only the features that are not discarded.
-Last at post-convergence check, we search for largest $k+i$ in the batch $\{k+1,k+2,...,k+l\}$ such that KKT conditions hold for solution at $\lambda_{k+i}$ and accept only the solution from $\lambda_{k+1}$ to $\lambda_{k+i}$.
-Next, we move to a new batch by replacing the batch head $k$ with $k+i$ and repeat the same procedure again.
+Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at.
+First we do the screening for each $\lambda_{k+b}$ value in the batch based on solution at $\lambda_k$ by discarding the $j$-th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Then at each $\lambda_{k+b}$ value we solve the lasso problem with only the features that are not discarded.
+Last at post-convergence check, we search for largest $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that KKT conditions hold for solution at $\lambda_{k+b}$ and accept only the solution from $\lambda_{k+1}$ to $\lambda_{k+b}$.
+Next, we move to a new batch by replacing the batch head $k$ with $k+b$ and repeat the same procedure again.
 
 The BASIL is most beneficial when the whole $X$ matrix is to large to be fit into the RAM, thus we need to read in a small number of columns $x_j$ from the hard disk at a time.
-In the post-convergence check for every batch, for each $j$, $x_j$ only needs to be read in once and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+l}\}$.
-Moreover, similar to SSR with ordinary post-convergence check, $x_j^Tr(\lambda_{x+i})$ computed at BASIL's post-convergence check step can be reused for screening at next batch.
+In the post-convergence check for every batch, for each $j$, $x_j$ only needs to be read in once and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$.
+Moreover, similar to SSR with ordinary post-convergence check, $x_j^Tr(\lambda_{x+b})$ computed at BASIL's post-convergence check step can be reused for screening at next batch.
 
@@
 
+In this section, we will introduce the batched safe-strong rules, combine them with pathwise coordinate descent algorithm and propose a strategy to adaptively  start new batches.
+
 \subsection{Batched EDPP rule}
-\begin{itemize}
-    \item Validate that given solution at one lambda value, we can safely screen for solutions at a batch of lambda values.
-    \item From the simplified notation of the EDPP rule, most quantities need to be calculated once per batch from the given solution.
-    \item Propose the new rule.
-\end{itemize}
+
+From the SEDPP rule (10) in Theorem 2.2, we can do screening at $\lambda_{k+1}$ given the solution at $\lambda_k$.
+Now consider we are solving the lasso problem along the path $\lambda_0,...,\lambda_k,\lambda_{k+2},...,\lambda_K$ instead.
+Using the SEDPP rule, we can do screening at $\lambda_{k+2}$ as well, given the solution at $\lambda_k$, which is considered the previous solution now.
+Similarly, given the solution at $\lambda_k$, we can do screening for a batch of $B$ $\lambda$-values: $\lambda_{k+1},...,\lambda_{k+B}$ and then all the discarded features are guaranteed to be zero.
+Batched EDPP is still a safe rule, but it is neither sequential nor one-step.
+
+Similar to SEDPP, the batched EDPP rule can be stated in the following theorem:
+
+\begin{theorem}[Batched EDPP]
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (3)
+    \begin{enumerate}
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=y-X\hat{\beta}(\lambda_k)$, then for some $B$ and any $b$ s.t.
+$k<k+b\leq k+B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \begin{equation}
+            \begin{split}
+                &\left|2\lambda_{k+b}x_j^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_k)x_j^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\\&<2n\lambda_k\lambda_{k+b}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
+            \end{split}
+        \end{equation}
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some $B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \begin{equation}
+        |(\lambda_0+\lambda_b)x_j^Ty-(\lambda_0-\lambda_b)sign(x_*^Ty)\lambda_0x_j^Tx_*|<2n\lambda_0\lambda_b-(\lambda_0-\lambda_b)\sqrt{n||y||_2^2-n^2\lambda_0^2}.
+    \end{equation}
+    \end{enumerate}
+\end{theorem}
+
+For each $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (11) or (12) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
+The most expensive computations are $x_j^Tr(\lambda_k)$ and $x_j^Ty$, for $j=1,2,...,p$.
+$x_j^Ty$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the batch and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that batch.
+These two computation take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
+
+Compared to sequential methods like SEDPP, the batched method only requires one $O(np)$ computation in one batch, while SEDPP requires one $O(np)$ computation for each $\lambda$-value.
+Compared to one-step methods like BEDPP, if the batch size is not too large, the solution at the batch head $\lambda_k$ and the solution at some $\lambda_{k+b}$ in the batch are usually relatively close, so screening at $\lambda_{k+b}$ using solution at $\lambda_k$ will remain powerful.
+For one-step method, as $\lambda_k$ gets further away from $\lambda_0$, the screening power can drop drastically and
+may not be any beneficial after that.
 
 \subsection{Batched strong rule after batched EDPP rule}
-\begin{itemize}
-    \item Analyse hybrid strong rule in this case and point out calculation that can be avoided (at a small cost of power)
-    \item Propose the new combined rule (Batched safe strong rule)
-    \item Proof of convergence
-\end{itemize}
+
+Because HSSR \cite{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider to add a strong rule screening after the batched EDPP rule screening.
+The batched SSR and batched EDPP rule combined will form our batched safe strong rule.
+
+For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (2).
+However, combined with safe rules, previous post-convergence check only need to check features that are not discarded at the previous $\lambda$-value.
+Thus, for features that are discarded at the previous $\lambda$-value but not at the current $\lambda$-value, their corresponding $x_j^Tr(\lambda_k)$ have not been computed yet and thus cannot be used without additional cost.
+Similar to the idea of BASIL \cite{qian2019fast}, we can also do the strong rule screening in batches to reduce the number of required computations.
+
+we are going to combine batched EDPP rule and batched SSR to form the batch safe strong rule as following.
+First, we determine a batch $\lambda_{k+1},...,\lambda_{k+B}$, and both batched EDPP rule and batched SSR will be conducted in this batch.
+Second $x_j^Tr(\lambda_k)$ will be computed and stored.
+Then for each $\lambda_{k+b}$ in the batch, after doing batched EDPP rule screening, a batched SSR screening is carried out on the features have not been discarded by batched EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Last, a post-convergence check is conducted on the features that were discarded by batched SSR but not discarded by batched EDPP rule.
+
+By choosing the same batch for batched EDPP rule and batched SSR, the quantity $x_j^Tr(\lambda_k)$ only needs to be computed once and can be used by both rules.
+Also, because batched EDPP rule can stay powerful, it keeps the set of features that require post-convergence check small, while because basic EDPP loses power for $\lambda$-values that are far away from $\lambda_0$, post-convergence check for HSSR will be more expensive.
 
@@
 
-\begin{itemize}
-    \item Quantities that can be shared by batched safe strong rule and coordinate descent
-    \item pseudo code
-\end{itemize}
+In this section, we will show the algorithm to do pathwise coordinate descent with our batched safe strong rule screening.
+We will only show the algorithm for solving one batch $\lambda_{k+1},...,\lambda_{k+B}$.
+To solve the next batch, we just need to apply the same algorithm using the output from last batch as input.
+Note here for the first batch with batch head $\lambda_0$, the residuals vector $r(\lambda_0)$ is just the response $y$, because all the $\hat{\beta}(\lambda_0)$ are zero.
+$\{x_j^Ty\}_{j=1}^p$ need to be computed at the beginning and stored for the whole path.
+
+\begin{algorithm}[H]
+    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Pre}{Pre-compute}\SetKwInOut{Initialize}{Initialize}
+    \SetAlgoLined
+    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p, \hat{\beta}(\lambda_k), r(\lambda_k), \lambda_{k+1},...,\lambda_{k+B}$}
+    \Pre{ $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$}
+    \BlankLine
+    \For{$b\xleftarrow{}$ 1 \KwTo B}{
+        Safe Screening: $\mathcal{S}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
+
+        Strong Screening: $\mathcal{R}\xleftarrow{}\{j\in \mathcal{S}:x_j$ not discarded by batched SSR$\}$.
+
+        \Initialize{$\hat{\beta}(\lambda_{k+b})=\hat{\beta}(\lambda_{k+b-1}), r(\lambda_{k+b})=r(\lambda_{k+b-1})$}
+
+        \Repeat{Post-convergence check passes for all $j\in \mathcal{S}\setminus\mathcal{R}$}{
+            Conduct pathwise coordinate descent in Algorithm 1 with warm start $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$, until converge.
+Save the outputs as $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$.
+        }
+    }
+    \Output{$\{\hat{\beta}(\lambda_{k+b})\}_{b=1}^B, r(\lambda_{k+B})$}
+    \caption{Pathwise coordinate descent with batched safe strong rule screening}
+\end{algorithm}
 

### 2020-01-22 main.tex
Edits to Section 2

@@
 \usepackage{natbib}
+\newtheorem{theorem}{Theorem}[section]
+
+% Custom commands / shortcuts
+\providecommand{\sign}{\textrm{sign}}
 \providecommand{\note}[1]{\textcolor{red}{#1}}
-\newtheorem{theorem}{Theorem}[section]
+\providecommand{\lam}{\lambda}
 
@@
 
-% \begin{itemize}
-%     \item Active set cycling ?
-%     \item Strong rules
-%     \item Safe rules:
-%     \begin{itemize}
-%         \item Sequential EDPP
-%         \item Basic EDPP
-%     \end{itemize}
-%     \item Hybrid Safe-Strong rule
-% \end{itemize}
+Throughout this paper, it will be assumed that $y$ is centeredand $\{x_j\}_{j=1}^p$ are centered and standardized:
+\begin{equation}
+    \sum_{i=1}^ny_i=0, \qquad \sum_{i=1}^n x_{ij}=0, \qquad \sum_{i=1}^n x_{ij}^2=n,\qquad j=1,2,...,p.
+\end{equation}
+This standardization make it reasonable to apply the same penalty to all features, even if originally measured in different units.
+It also improves the efficiency and stability of the optimization, and helps to simplify optimization.
+For example, under this standardization, the intercept is exactly 0 and thus may be ignored.
+Standardization also simplifies the formulas for screening rules and thus allows for more efficient implementation.
 
-Screening rules are able to discard zero coefficients due to the KKT (Karush-Kuhn-Tucker) conditions of the lasso problem.
-It states that the solution $\hat{\beta}(\lambda)$ is optimal if and only if the following conditions hold:
+Typical practice when fitting lasso models is to solve for $\hat{\beta}(\lambda)$ along a decreasing sequence of $K+1$ values of $\lambda$: $\lambda_0 > \lambda_1 > \cdots > \lambda_K$.
+As we will discuss shortly, we set $\lambda_0=\max_j|x_j^Ty/n|$ throughout; this ensures that $\hat{\beta}(\lambda_0)=0$, making it a natural point from which to start.
 
-\begin{equation}
-    \begin{cases}
-    x_j^Tr(\lambda)/n = \lambda sign(\hat{\beta}(\lambda)_j),\qquad if\quad \hat{\beta}(\lambda)_j\neq 0,\\
-    |x_j^Tr(\lambda)/n| \leq \lambda,\hfill if\quad \hat{\beta}(\lambda)_j= 0,
-    \end{cases}
-\end{equation}
+\note{I think we need to fix notation here -- you're using $\lam_0$ to represent both $\lam_{\max}$ and the previous value of $\lam$ in a pathwise algorithm.}
 
-where $r(\lambda)$ is the residuals vector at $\lambda$ defined as $y-X\hat{\beta}(\lambda)$.
-If the residuals are known, we can safely conclude feature $j$ has 0 coefficient if the second condition holds with "$<$", but residuals cannot be calculated without first solving the coefficients.
-However, when fitting a solution path, residuals at previous $\lambda$ values can be calculated and provide information about residuals at current $\lambda$ value and thus be used for screening.
+Pathwise coordinate descent is a popular algorithm fitting a solution path for lasso problem.
+Letting $r(\lambda) \equiv y-X\hat{\beta}(\lambda)$ denote the vector of residuals, the solution $\hat{\beta}(\lambda)$ can be computed using Algorithm~\ref{Alg:pathwise-coordinate-descent}.
+Note that the algorithm uses the previous solution $\hat{\beta}(\lambda_0)$ as the initial value in obtaining the next solution along the path, a strategy known as a ``warm start''.
 
-Pathwise coordinate descent is a popular algorithm fitting a solution path for lasso problem using warm start.
-Given the previous solution $\hat{\beta}(\lambda_0)$ with residuals $r(\lambda_0)$, the solution $\hat{\beta}(\lambda)$ with residuals $r(\lambda)$ can be computed by the following algorithm:
-
-\begin{algorithm}[H]
+\begin{algorithm}[H]\label{Alg:pathwise-coordinate-descent}
     \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Initialize}{Initialize}
@@
         }
-
     }
@@
 
-\noindent In this algorithm, residuals $r$ are computed at each $\lambda$ value for the update of the coefficients and can thus be reused conveniently for feature screening purpose.
-
-For the rest of the paper, it will be assumed that $y$ is centered so the intercept can be dropped and $\{x_j\}_{j=1}^p$ are centered and standardized. That is:
-
+In convex optimization, the Karush-Kuhn-Tucker (KKT) conditions are both necessary and sufficient for any optimal solution.
+Screening rules take advantage of these KKT conditions in order to discard inactive coefficients.
+For the lasso, the KKT conditions governing the optimal solution $\hat{\beta}(\lambda)$ are given by
 \begin{equation}
-    \sum_{i=1}^ny_i=0, \qquad \sum_{i=1}^n x_{ij}=0, \qquad \sum_{i=1}^n x_{ij}^2=n,\qquad j=1,2,...,p.
+  \begin{aligned}
+    x_j^Tr(\lambda)/n &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if} \quad \hat{\beta}(\lambda)_j\neq 0,\\
+    |x_j^Tr(\lambda)/n| &\leq \lambda & & \textrm{if} \quad \hat{\beta}(\lambda)_j= 0.
+  \end{aligned}
 \end{equation}
-This standardization make it reasonable to apply the same penalty to all features, which are usually measured in different units.
-It improves the efficiency and stability of the optimization as well.
-Most importantly for this manuscript, it greatly helps simplify the formulas for screening rules and thus simplify the code for implementation.
-
-It will also be assumed that lasso model is solved along $K+1$ decreasing values of $\lambda$ denoted as $\lambda_0,\lambda_1,...,\lambda_K$.
-Solution of $\beta$ at any $\lambda_k$ is denoted as $\hat{\beta}(\lambda_k)$.
-From the KKT conditions (2), when $\lambda>\max_j|x_j^Ty/n|$, $r(\lambda)=y$ and all the coefficients will always be zero.
-As a result, we only need to focus on $\lambda\in (0,\max_j|x_j^Ty/n|]$ and we will set $\lambda_0=\max_j|x_j^Ty/n|$.
+If the residuals were known, we could safely conclude that $\hat{\beta}(\lambda)_j=0$ by checking the second condition holds as a strict inequality.
+The complication, of course, is that the residuals are not known until after we have solved for all the coefficients.
+However, when fitting a solution path, residuals at previous $\lambda$ values provide information about residuals at the next $\lambda$ value and thus be used for screening.
+Note that in Algorithm~\ref{Alg:pathwise-coordinate-descent}, the residuals $r$ are computed at each $\lambda$ value and can thus be conveniently reused for the purpose of feature screening.
 

### 2020-02-06 main.tex
Add section 3. Fix previous sections.

@@
 \usepackage{natbib}
+\usepackage{graphicx}
 \newtheorem{theorem}{Theorem}[section]
@@
 
-\note{I think we need to fix notation here -- you're using $\lam_0$ to represent both $\lam_{\max}$ and the previous value of $\lam$ in a pathwise algorithm.}
-
 Pathwise coordinate descent is a popular algorithm fitting a solution path for lasso problem.
-Letting $r(\lambda) \equiv y-X\hat{\beta}(\lambda)$ denote the vector of residuals, the solution $\hat{\beta}(\lambda)$ can be computed using Algorithm~\ref{Alg:pathwise-coordinate-descent}.
-Note that the algorithm uses the previous solution $\hat{\beta}(\lambda_0)$ as the initial value in obtaining the next solution along the path, a strategy known as a ``warm start''.
+For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using Algorithm~\ref{Alg:pathwise-coordinate-descent}.
+Note that the algorithm uses the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in obtaining the next solution along the path, a strategy known as a ``warm start''.
 
@@
     \SetAlgoLined
-    \Input{$\hat{\beta}(\lambda_0), \{x_j\}_{j=1}^p, r(\lambda_0)$}
-    \Initialize{ $r = r(\lambda_0),\hat{\beta} = \hat{\beta}(\lambda_0)$}
+    \Input{$\hat{\beta}(\lambda_k), \{x_j\}_{j=1}^p, r(\lambda_k)$}
+    \Initialize{ $r = r(\lambda_k),\hat{\beta} = \hat{\beta}(\lambda_k)$}
     \BlankLine
@@
     }
-    \Output{$\hat{\beta}(\lambda)\xleftarrow{}\hat{\beta},r(\lambda)\xleftarrow{}r$}
-    \caption{Pathwise coordinate descent with warm start $\hat{\beta}(\lambda_0),r(\lambda_0)$}
+    \Output{$\hat{\beta}(\lambda_{k+1})\xleftarrow{}\hat{\beta},r(\lambda_{k+1})\xleftarrow{}r$}
+    \caption{Pathwise coordinate descent with warm start $\hat{\beta}(\lambda_k),r(\lambda_k)$}
 \end{algorithm}
@@
   \begin{aligned}
-    x_j^Tr(\lambda)/n &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if} \quad \hat{\beta}(\lambda)_j\neq 0,\\
-    |x_j^Tr(\lambda)/n| &\leq \lambda & & \textrm{if} \quad \hat{\beta}(\lambda)_j= 0.
+    &x_j^Tr(\lambda)/n& &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if} \quad \hat{\beta}(\lambda)_j\neq 0,\\
+    |&x_j^Tr(\lambda)/n|& &\leq \lambda & & \textrm{if} \quad \hat{\beta}(\lambda)_j= 0.
   \end{aligned}
@@
 The complication, of course, is that the residuals are not known until after we have solved for all the coefficients.
-However, when fitting a solution path, residuals at previous $\lambda$ values provide information about residuals at the next $\lambda$ value and thus be used for screening.
-Note that in Algorithm~\ref{Alg:pathwise-coordinate-descent}, the residuals $r$ are computed at each $\lambda$ value and can thus be conveniently reused for the purpose of feature screening.
+However, when fitting a solution path, residuals at previous $\lambda$-values provide information about residuals at the next $\lambda$-value and thus be used for screening.
+Note that in Algorithm~\ref{Alg:pathwise-coordinate-descent}, the residuals $r$ are computed at each $\lambda$-value and can thus be conveniently reused for the purpose of feature screening.
 
@@
         \hat{\theta}(\lambda) = \underset{\theta\in \mathbb{R}^n}{\mathrm{argmax}}\frac{1}{2n}||y||_2^2-\frac{n\lambda}{2}||\theta-\frac{y}{n\lambda}||_2^2\\
-        subject\quad to\quad |x_j^T\theta|\leq 1,\quad \forall j=1,2,...,p.
+        \textrm{subject to } |x_j^T\theta|\leq 1,\quad \forall j=1,2,...,p.
     \end{split}
@@
 $x_j^Ty$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the batch and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that batch.
-These two computation take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
+These two computations take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
 
@@
 
-Because HSSR \cite{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider to add a strong rule screening after the batched EDPP rule screening.
+Because HSSR \cite{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the batched EDPP rule screening.
 The batched SSR and batched EDPP rule combined will form our batched safe strong rule.
@@
 For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (2).
-However, combined with safe rules, previous post-convergence check only need to check features that are not discarded at the previous $\lambda$-value.
+However, combined with safe rules, previous post-convergence check only needs to check features that are not discarded at the previous $\lambda$-value.
 Thus, for features that are discarded at the previous $\lambda$-value but not at the current $\lambda$-value, their corresponding $x_j^Tr(\lambda_k)$ have not been computed yet and thus cannot be used without additional cost.
@@
 
-we are going to combine batched EDPP rule and batched SSR to form the batch safe strong rule as following.
+We are going to combine batched EDPP rule and batched SSR to form the batch safe strong rule as following.
 First, we determine a batch $\lambda_{k+1},...,\lambda_{k+B}$, and both batched EDPP rule and batched SSR will be conducted in this batch.
 Second $x_j^Tr(\lambda_k)$ will be computed and stored.
-Then for each $\lambda_{k+b}$ in the batch, after doing batched EDPP rule screening, a batched SSR screening is carried out on the features have not been discarded by batched EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Then for each $\lambda_{k+b}$ in the batch, after doing batched EDPP rule screening, a batched SSR screening is carried out on the features that have not been discarded by batched EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
 Last, a post-convergence check is conducted on the features that were discarded by batched SSR but not discarded by batched EDPP rule.
@@
 
-\subsection{Coordinate descent with Batched safe strong rule}
+\subsection{Coordinate descent with batched safe strong rule}
 
@@
 We will only show the algorithm for solving one batch $\lambda_{k+1},...,\lambda_{k+B}$.
-To solve the next batch, we just need to apply the same algorithm using the output from last batch as input.
+After finishing this batch, we just need to start a new batch and apply the same algorithm using the output from last batch as input.
 Note here for the first batch with batch head $\lambda_0$, the residuals vector $r(\lambda_0)$ is just the response $y$, because all the $\hat{\beta}(\lambda_0)$ are zero.
@@
     \For{$b\xleftarrow{}$ 1 \KwTo B}{
-        Safe Screening: $\mathcal{S}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
+        Safe Screening: $\mathcal{S}_{k+b}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
 
-        Strong Screening: $\mathcal{R}\xleftarrow{}\{j\in \mathcal{S}:x_j$ not discarded by batched SSR$\}$.
+        Strong Screening: $\mathcal{R}_{k+b}\xleftarrow{}\{j\in \mathcal{S}_{k+b}:x_j$ not discarded by batched SSR$\}$.
 
@@
 
-        \Repeat{Post-convergence check passes for all $j\in \mathcal{S}\setminus\mathcal{R}$}{
-            Conduct pathwise coordinate descent in Algorithm 1 with warm start $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$, until converge.
-Save the outputs as $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$.
+        \Repeat{Post-convergence check passes}{
+            Pathwise coordinate descent in Algorithm 1 with only features in $\mathcal{R}_{k+b}$ and with warm start $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$, until converge.
+Save the outputs in $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$.
+
+            Post-convergence check for all $j\in \mathcal{S}_{k+b}\setminus\mathcal{R}_{k+b}$,
+
+            \uIf{Post-convergence check does not pass}{
+                Add violating features to $\mathcal{R}_{k+b}$\;
+            }
         }
@@
 
-\subsection{Adaptive determining batch size}
-\label{sec:batch-size}
-\begin{itemize}
-    \item Analyse computing cost for each part of coordinate descent with Batched safe strong rule.
-    \item Analyse pattern of the number of rejections by EDPP rule over the solution path.
-    \item Propose a rule for starting a new batch by balancing cost of each part
-\end{itemize}
+\subsection{Adaptive batched safe strong rule}
 
-\subsection{Performance analysis}
-\begin{itemize}
-    \item Screening power
-    \item Computational complexity ?
-\end{itemize}
+In this section we will develop an algorithm to adaptively determining when to end the current batch and start a new batch, by evaluating screening power at previous $\lambda$-values in current batch.
+Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 2.
+Then we will propose an adaptive algorithm that can minimize the entire computation cost.
+
+\subsubsection{Complexity analysis}
+
+This complexity analysis will only consider calculations with $O(np)$ complexity.
+The rest calculations, those with $O(p)$ complexity for example, are not only faster in order, but also require no out-of-core computing.
+Calculation of ${x_j^Ty}_{j=1}^p$ is needed for pathwise coordinate descent in algorithm 1 and is not additional cost for screening, so it would not be considered either.
+We will assume that strong rule screening is always powerful in the sense that $|\mathcal{R}_b|=o(p)\approx0$, but safe rule screening may not.
+We also assume that post-convergence check will mostly pass in the first iteration and thus is only needed approximately once per $\lambda$-value.
+
+Under these assumptions, there are two dominating parts in the algorithm for each batch.
+First, the computation of $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ at the beginning of the batch, which requires $np$ multiplications.
+Then, for each $\lambda$-value $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_b\setminus\mathcal{R}_b|\approx|\mathcal{S}_b|$ KKT condition checks and each KKT condition check requires $n$ multiplications.
+These sum up to $n\sum_{b=1}^B|\mathcal{S}_b|$ multiplications.
+Combining these two parts, we will have the average cost per $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$ to be
+
+\begin{equation}
+    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_b|}{B}.
+\end{equation}
+
+The first term is the average cost for safe screening.
+Increasing batch size $B$ means reusing calculation at the batch head more times for the safe screening and thus reducing the average cost.
+The second term is the average cost for KKT condition checking.
+As the batch size $B$ increases, safe rule screening becomes less powerful and the number of KKT condition checks required ($|\mathcal{S}_b|$) increases.
+The following plot illustrates the effect of $B$ on $|\mathcal{S}_b|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
+The y axis is the proportion of discarded features, calculated as $1-|\mathcal{S}_b|/p$.
+
+\begin{center}
+    \includegraphics[scale = 0.5]{plots/batchsizes.png}
+\end{center}
+
+BEDPP (Basic EDPP) rule is the special case of batched EDPP with only one batch of the largest possible size $B=K=100$.
+When the batch is large, the safe rule screening will eventually fail to discard any features and make the KKT condition checking cost increase to its maximum $np$.
+SEDPP rule is the special case where all batches have the smallest possible batch size $B=1$.
+It remains very powerful along the path, making the KKT condition checking cost almost 0, but the safe screening itself is costly and takes $np$ time per $\lambda$-value.
+Batched EDPP can strike a balance between BEDPP and SEDPP.
+In this example, using batches with fixed sizes $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
+
+This example also shows the performance of batch EDPP rule changes along the path of $\lambda$-values.
+Take the batched EDPP with $B=10$ as an example.
+For the first batch of 10 $\lambda$-values, the batched EDPP stays powerful even at the end, which means this batch is still exploitable.
+We may want to extend this batch to reduce average safe screening cost without harming the KKT condition checking cost much.
+For the last batch however, the screening power is close to 0 for the last few $\lambda$-values, which means this batch becomes useless at this point.
+Starting a new batch earlier can greatly reduce the KKT condition checking cost with relatively small increase in safe screening cost.
+Also, the performance of batch EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
+These suggest that starting a new batch after every fixed number of $\lambda$-values cannot not be consistently efficient and we want a method that can automatically determine whether to start a new batch given current performance.
+
+\subsubsection{Adaptive batch starting algorithm}
+
+From previous example, we assume the average cost is a convex function of batch size $B$ which decreases first and then after some optimal value increases again.
+If we want to minimize the average cost per $\lambda$-value, we need to end the current batch when extending the current batch by 1 $\lambda$-value will increase the average cost.
+That is, end the current batch at $\lambda_{B-1}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$.
+From (13), this condition will be:
+
+\begin{equation}
+    (B-1)|\mathcal{S}_B|-\sum_{b=1}^{B-1}|\mathcal{S}_b|>p.
+\end{equation}
+In practice, we will end the batch at $\lambda_B$ and start at $\lambda_{B+1}$ instead, because evaluating $\mathcal{S}_B$ needs screening at $\lambda_B$ and if we have already done the screening, it would be a waste not to use the screening result.
+
+This batch restarting condition is a greedy condition that only considers the current batch cost.
+In practice, we cannot know about future batches so this is the most reasonable condition.
+In fact, it can handle the three most common scenarios well.
+First, if the screening power stays high, meaning $\mathcal{S}_b$ is small for all $b$, then the left-hand-side of (14) will be small and thus at this point we will extend the current batch to further exploit it.
+Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_B$ is large but $\mathcal{S}_b$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (14) will be large and we will end the useless current batch and start a new batch.
+Last, if the screening power drops dramatically right after the beginning of the current batch, meaning $\mathcal{S}_b$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (14) will be approximately $p-|\mathcal{S}_1|<p$.
+We will not end the current batch although it becomes useless, because if we did, the next batch would be useless as well.
+
+Combined with Algorithm 2, we will propose the pathwise coordinate descent with adaptive batched safe strong rule screening.
+After ending a batch, if there are still unsolved $\lambda$-values in the path $\lambda_0,\lambda_1,...,\lambda_K$, we can just start a new batch with the rest unsolved $\lambda$-values and apply the same algorithm.
+
+\begin{algorithm}[H]
+    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Pre}{Pre-compute}\SetKwInOut{Initialize}{Initialize}
+    \SetAlgoLined
+    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p, \hat{\beta}(\lambda_k), r(\lambda_k), \lambda_{k+1},...,\lambda_{K}$}
+    \Pre{ $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$}
+    \BlankLine
+    $B\xleftarrow{}1$
+
+    \Repeat{$(B-1)|\mathcal{S}_B|-\sum_{b=1}^{B-1}|\mathcal{S}_{b}|>p$ or $B>K$}{
+        Safe Screening: $\mathcal{S}_{k+B}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
+
+        Strong Screening: $\mathcal{R}_{k+B}\xleftarrow{}\{j\in \mathcal{S}_{k+B}:x_j$ not discarded by batched SSR$\}$.
+
+        \Initialize{$\hat{\beta}(\lambda_{k+B})=\hat{\beta}(\lambda_{k+B-1}), r(\lambda_{k+B})=r(\lambda_{k+B-1})$}
+
+        \Repeat{Post-convergence check passes}{
+            Pathwise coordinate descent in Algorithm 1 with only features in $\mathcal{R}_{k+B}$ and with warm start $\hat{\beta}(\lambda_{k+B}), r(\lambda_{k+B})$, until converge.
+Save the outputs in $\hat{\beta}(\lambda_{k+B}), r(\lambda_{k+B})$.
+
+            Post-convergence check for all $j\in \mathcal{S}_{k+B}\setminus\mathcal{R}_{k+B}$,
+
+            \uIf{Post-convergence check does not pass}{
+                Add violating features to $\mathcal{R}_{k+B}$\;
+            }
+        }
+        $B\xleftarrow{}B+1$
+    }
+    \Output{$\{\hat{\beta}(\lambda_{k+b})\}_{b=1}^B, r(\lambda_{k+B}),\lambda_{k+B+1},...,\lambda_K$}
+    \caption{Pathwise coordinate descent with adaptive batched safe strong rule screening}
+\end{algorithm}
 

### 2020-02-16 main.tex
Add section 4.1

@@
 Given the solution $\hat{\beta}(\lambda_k)$ at $\lambda_k$, we can compute the residual vector as $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$.
-The SSR discard the $j$-th feature at $\lambda_{k+1}$ if:
+The SSR discards the $j$-th feature at $\lambda_{k+1}$ if:
 
@@
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=y-X\hat{\beta}(\lambda_k)$, then $\hat{\beta}_j(\lambda_{k+1})=0$ if
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then $\hat{\beta}_j(\lambda_{k+1})=0$ if
         \begin{equation}
@@
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=y-X\hat{\beta}(\lambda_k)$, then for some $B$ and any $b$ s.t.
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some $B$ and any $b$ s.t.
 $k<k+b\leq k+B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
@@
 
+\subsection{Batched safe strong rule for sparse logistic regression}
+
+The sparse logistic regression model can be defined as:
+
+\begin{equation}
+    \hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}-\frac{1}{n}\sum_{i=1}^n\{y_i\log\pi_i(\beta)+(1-y_i)\log(1-\pi_i(\beta))\}+\lambda||\beta||_1,
+\end{equation}
+where $\pi(\beta)=\{\pi_i(\beta)\}_{i=1}^n=\{p(y_i=1|x_{i1},x_{i2},...,x_{ip})\}_{i=1}^n=\{e^{\eta_i(\beta)}/(1+e^{\eta_i(\beta)})\}_{i=1}^n$ is the predicted value vector and $\eta(\beta)=X\beta$ is the linear function.
+$X$ are still the $n\times p$ standardized feature matrix  but in this model the $y\in\{0,1\}^n$ is a binary response vector.
+$\beta$ is still the $p\times1$ coefficient vector but we also need a $\beta_0$ as the intercept.
+
+We can use SSR to do the strong rule screening with a small change according to the KKT condition.
+The residual vector now is $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
+Then the SSR discards the $j$-th feature at $\lambda_{k+1}$ if (4) holds.
+
+For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\cite{wang2014safe} is used.
+It was proposed as an one-step rule but we will extend it to a batched rule.
+Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$
+
+\begin{theorem}[Batched Slores]
+For the sparse logistic regression model (15), let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$.
+Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
+$\forall\theta\in(0,1)^n$, let $x_*=argmax_{x_j}|x_j^Ty/n|$ and
+
+\begin{equation}
+    \begin{split}
+        g(\theta)&=\frac{1}{n}\sum_{i=1}^n\{\theta_i\log \theta_i+(1-\theta_i)\log(1-\theta_i)\},\\
+    \nabla g_i(\theta) &= \frac{1}{n}\log\frac{\theta_i}{1-\theta_i}.
+    \end{split}
+\end{equation}
+
+Under condition (3), for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
+For some $B$ and any $b$ s.t.
+$k<k+b\leq k+B\leq K$, let
+
+\begin{equation}
+    R(\lambda_{k+b})=\sqrt{\frac{n}{2}\bigg[g\bigg(\frac{\lambda_{k+b}}{\lambda_k}\theta(\lambda_k)\bigg)-g\bigg(\theta(\lambda_k)\bigg)+\bigg(1-\frac{\lambda_{k+b}}{\lambda_k}\bigg)\bigg(\nabla g\big(\theta(\lambda_k)\big)\bigg)^T\theta(\lambda_k)\bigg]},
+\end{equation}
+
+$d(\lambda_{k+b})=\sqrt{n}(\lambda_k-\lambda_{k+b})/R(\lambda_{k+b})$. For $\xi = -1,1$ and $j=1,2,...,p$,
+
+\begin{enumerate}
+    \item If $-\xi sign(x_*^Ty)x_j^Tx_*\geq nd(\lambda_{k+b})$, then
+
+    \begin{equation}
+        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=\sqrt{n}R(\lambda_{k+b})-\xi x_j^Tr(\lambda_k);
+    \end{equation}
+
+    \item If $-\xi sign(x_*^Ty)x_j^Tx_*< nd(\lambda_{k+b})$, then
+
+    \begin{equation}
+        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=R(\lambda_{k+b})\sqrt{n+nu_\xi^2-2\xi u_\xi sign(x_*^Ty)x_j^Tx_*}-nu_\xi(\lambda_k-\lambda_{k+b})-\xi x_j^Tr(\lambda_k),
+    \end{equation}
+    where
+    \begin{align}
+        u_\xi&=\frac{-\xi a_1+\sqrt{\Delta}}{2a_2},\\
+        a_0&=(x_j^Tx_*)^2-n^2d^2(\lambda_{k+b}),\nonumber\\
+        a_1&=-2n\,sign(x_*^Ty)x_j^Tx_*\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
+        a_2&=n^2\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
+        \Delta&=a_1^2-4a_0a_1.\nonumber
+    \end{align}
+\end{enumerate}
+
+Then $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \begin{equation}
+            \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))
+        \end{equation}
+\end{theorem}
+
+When computing the batched Slores, $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ need to be computed only once, stored and reused for the whole solution path $\lambda_0>\lambda_1>...>\lambda_K$.
+Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed once for each batch.
+Thus algorithm 3 for adaptive batched safe strong rule can be done with Slores rule instead of EDPP rule to do screening for sparse logistic regression model.
+
 \begin{itemize}

### 2020-02-17 main.tex
Add section 4.2

@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\cite{wang2013lasso}, were proposed and under the standardization (3) can be simplified in the following theorems\cite{zeng2017efficient}:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\cite{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\cite{zeng2017efficient}:
 
 \begin{theorem}[BEDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$. Under (3) and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$. Under (2) and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
     \begin{equation}
@@
 \begin{theorem}[SEDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (3)
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
     \begin{enumerate}
@@
 \begin{theorem}[Batched EDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (3)
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
     \begin{enumerate}
@@
 For each $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (11) or (12) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
-The most expensive computations are $x_j^Tr(\lambda_k)$ and $x_j^Ty$, for $j=1,2,...,p$.
-$x_j^Ty$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the batch and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that batch.
+The most expensive computations are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, for $j=1,2,...,p$.
+$x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the batch and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that batch.
 These two computations take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
@@
 
+The structure of the batched safe strong rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
+We are going to derive the extensions to two lasso type problems and show these extensions improve computation efficiency.
+
 \subsection{Batched safe strong rule for sparse logistic regression}
@@
 where $\pi(\beta)=\{\pi_i(\beta)\}_{i=1}^n=\{p(y_i=1|x_{i1},x_{i2},...,x_{ip})\}_{i=1}^n=\{e^{\eta_i(\beta)}/(1+e^{\eta_i(\beta)})\}_{i=1}^n$ is the predicted value vector and $\eta(\beta)=X\beta$ is the linear function.
-$X$ are still the $n\times p$ standardized feature matrix  but in this model the $y\in\{0,1\}^n$ is a binary response vector.
+$X$ are still the $n\times p$ standardized feature matrix but in this model the $y\in\{0,1\}^n$ is an unstandardized binary response vector.
 $\beta$ is still the $p\times1$ coefficient vector but we also need a $\beta_0$ as the intercept.
@@
 For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\cite{wang2014safe} is used.
-It was proposed as an one-step rule but we will extend it to a batched rule.
-Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$
+It was proposed as a one-step rule but we will extend it to a batched rule.
+Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
 
@@
 
-Under condition (3), for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
+Under condition (2) except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
 For some $B$ and any $b$ s.t.
@@
 
-\begin{itemize}
-    \item Logistic regression with Slores instead of EDPP
-    \item group lasso ?
-    \item elastic net ?
-\end{itemize}
+\subsection{Batched safe strong rule for group lasso}
+
+The group lasso problem \cite{yuan2006model} can be defined as:
+
+\begin{equation}
+    \hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}\bigg|\bigg|y-\sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2+\lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_1,
+\end{equation}
+where $\beta=(\beta_1^T,...,\beta_G^T)^T$, $X_g$ is a $n\times p_g$ sub-matrix consisting of columns of $X$ corresponding to features in group $g$, $g=1,2,...,G$.
+Besides standardization in (2), we apply an addition level of standardization at the group level\cite{breheny2015group}:
+
+\begin{equation}
+    X_g^TX_g=nI_{p_g\times p_g},\qquad g=1,2,...,G.
+\end{equation}
+
+According to the KKT condition, we can use SSR to do strong rule screening.
+Given $r(\lambda_k)=y-\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, we discard features in the $g$-th group at $\lambda_{k+1}$ if:
+
+\begin{equation}
+    \bigg|\bigg|\frac{1}{n}X_g^Tr(\lambda_k)\bigg|\bigg|_2<\sqrt{p_g}(2\lambda_{k+1}-\lambda_k).
+\end{equation}
+
+For safe rule screening, we have SEDPP for group lasso\cite{wang2013lasso} and we can extend it the batched EDPP rule for group lasso.
+
+\begin{theorem}[Batched EDPP for group lasso]
+For the group lasso problem (22), let $\lambda_0:=\max_j\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$.
+Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
+Under condition (2) and (23)
+    \begin{enumerate}
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for some $B$ and any $b$ s.t.
+$k<k+b\leq k+B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \begin{equation}
+            \begin{split}
+                &\left|\left|2\lambda_{k+b}X_g^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( X_g^Ty-\frac{y^T\hat{y}(\lambda_k)X_g^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\right|_2\\
+                &<2n\lambda_k\lambda_{k+b}\sqrt{p_g}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
+            \end{split}
+        \end{equation}
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for some $B$ and any $b$ s.t.
+$0<b\leq B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \begin{equation}
+        \left|\left|(\lambda_0+\lambda_b)X_g^Ty-(\lambda_0-\lambda_b)X_g^TX_*X_*^Ty\right|\right|_2<2n\lambda_0\lambda_b\sqrt{p_g}-(\lambda_0-\lambda_b)\sqrt{n||y||_2^2-n^2\lambda_0^2p_*}.
+    \end{equation}
+    \end{enumerate}
+\end{theorem}
+
+Similar to Batched EDPP rule, three expensive computations are $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$ and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
+The first and second only need to be computed once for the whole solution path.
+The last only needs to be computed once per batch with cost $O(np)$.
 

### 2020-05-15 main.tex
Add 5.1 simulation and  5.2 real data analysis

@@
 \usepackage{graphicx}
+\usepackage{float}
 \newtheorem{theorem}{Theorem}[section]
-
+\bibliographystyle{abbrvnat}
 % Custom commands / shortcuts
@@
 The lasso model has several attractive properties compared to least squares regression, including increased stability of estimation, increased prediction accuracy, and automatic variable selection arising from the fact that it yields sparse estimates of $\beta$.
-As a result, it is widely applied in different fields, such as gene expression data analysis, image recognition and text mining, and has been extended in several ways, such as group lasso\cite{yuan2006model}, elastic net\cite{zou2005regularization} and sparse generalized linear models.
+As a result, it is widely applied in different fields, such as gene expression data analysis, image recognition and text mining, and has been extended in several ways, such as group lasso\citep{yuan2006model}, elastic net\citep{zou2005regularization} and sparse generalized linear models.
 Because of its wide popularity, solving the lasso model efficiently is an important topic in statistics and machine learning.
@@
 Pathwise algorithms can be efficiently implemented by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.
-In particular, the pathwise coordinate descent algorithm\cite{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS (least angle regression)\cite{efron2004least}, especially in high dimensional settings where $p$ is large.
+In particular, the pathwise coordinate descent algorithm\citep{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS (least angle regression)\citep{efron2004least}, especially in high dimensional settings where $p$ is large.
 In sparse settings, it scales up very well with a computational cost of approximately $O(np)$.
@@
 
-There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}\cite{qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
+There are two important categories of features screening rules: ``strong'' rules\citep{tibshirani2011regression}\citep{qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules\citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
 As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
@@
 However, safe rules are considerably less powerful at discarding features than strong rules.
-More recently, hybrid approaches \cite{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.
+More recently, hybrid approaches \citep{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.
 
@@
     \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
-    \item The Batch-SSR-SEDPP and Batch-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\cite{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
+    \item The Batch-SSR-SEDPP and Batch-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
 \end{itemize}
@@
 \subsection{Active-set Cycling}
+\label{sec:active}
 
-Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \cite{lee2007efficient}.
+Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \citep{lee2007efficient}.
 When solving the coefficients for at $\lambda_{k+1}$, first only consider features whose coefficients were non-zero at $\lambda_k$ and discard other features with zero coefficients at $\lambda_k$.
@@
 
-Sequential strong rule (SSR) \cite{tibshirani2011regression} is a fast and powerful feature screening rule.
+Sequential strong rule (SSR) \citep{tibshirani2011regression} is a fast and powerful feature screening rule.
 Given the solution $\hat{\beta}(\lambda_k)$ at $\lambda_k$, we can compute the residual vector as $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$.
@@
 Those discarded features are guaranteed to have zero coefficients and we do not need an addition check to validate them.
-We will mainly focus on enhanced dual polytope projections (EDPP) rules\cite{wang2013lasso}, because they outperform other current safe rules and are easy to incorporate in our method.
+We will mainly focus on enhanced dual polytope projections (EDPP) rules\citep{wang2013lasso}, because they outperform other current safe rules and are easy to incorporate in our method.
 
@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\cite{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\cite{zeng2017efficient}:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\citep{zeng2017efficient}:
 
@@
 
-The hybrid safe-strong rules (HSSR) \cite{zeng2017efficient} was proposed to combine SSR with any member of safe rules to take advantage of both.
+The hybrid safe-strong rules (HSSR) \citep{zeng2017efficient} was proposed to combine SSR with any member of safe rules to take advantage of both.
 More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments.
@@
 
-Batch screening iterative lasso (BASIL) \cite{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches.
+Batch screening iterative lasso (BASIL) \citep{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches.
 Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at.
@@
 
-Because HSSR \cite{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the batched EDPP rule screening.
+Because HSSR \citep{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the batched EDPP rule screening.
 The batched SSR and batched EDPP rule combined will form our batched safe strong rule.
@@
 Thus, for features that are discarded at the previous $\lambda$-value but not at the current $\lambda$-value, their corresponding $x_j^Tr(\lambda_k)$ have not been computed yet and thus cannot be used without additional cost.
-Similar to the idea of BASIL \cite{qian2019fast}, we can also do the strong rule screening in batches to reduce the number of required computations.
+Similar to the idea of BASIL \citep{qian2019fast}, we can also do the strong rule screening in batches to reduce the number of required computations.
 
@@
 
-\begin{center}
-    \includegraphics[scale = 0.5]{plots/batchsizes.png}
-\end{center}
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 0.5]{plots/batchsizes.png}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different batch sizes.}
+    \label{fig:3.4.1}
+\end{figure}
 
@@
 The structure of the batched safe strong rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
+After a batched safe strong rule is built, we can automatically apply the adaptive batch starting algorithm to make it an adaptive batched safe strong rule.
 We are going to derive the extensions to two lasso type problems and show these extensions improve computation efficiency.
@@
 
-For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\cite{wang2014safe} is used.
+For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\citep{wang2014safe} is used.
 It was proposed as a one-step rule but we will extend it to a batched rule.
@@
 
-The group lasso problem \cite{yuan2006model} can be defined as:
+The group lasso problem \citep{yuan2006model} can be defined as:
 
@@
 where $\beta=(\beta_1^T,...,\beta_G^T)^T$, $X_g$ is a $n\times p_g$ sub-matrix consisting of columns of $X$ corresponding to features in group $g$, $g=1,2,...,G$.
-Besides standardization in (2), we apply an addition level of standardization at the group level\cite{breheny2015group}:
+Besides standardization in (2), we apply an addition level of standardization at the group level\citep{breheny2015group}:
 
@@
 
-For safe rule screening, we have SEDPP for group lasso\cite{wang2013lasso} and we can extend it the batched EDPP rule for group lasso.
+For safe rule screening, we have SEDPP for group lasso\citep{wang2013lasso} and we can extend it the batched EDPP rule for group lasso.
 
@@
 
-\subsection{Simulations}
+In this section conduct experiments solving lasso model on both simulated data sets and real data sets, to show our proposed adaptive batched safe strong rule screening method outperforms previous screening method such as SSR, SEDPP, HSSR and Slores.
+Active-set cycling in \ref{sec:active} is always used with all screening methods because it can be easily combined with any screening methods with on extra cost.
+
+The adaptive batched safe strong rule screening is implemented in the \textbf{R} package \textbf{biglasso} and we will use this package for our experiment.
+Compared to traditional packages that solve lasso problem, such as \textbf{glmnet}, \textbf{biglasso} focuses on efficiently solving lasso problem with high-dimensional data sets that have a large number of features.
+First, it utilized the memory-mapping techniques that stores the data set on the disk and reads in only the part of the data necessary for model solving.
+Second, it applied screening rules to reduce both the computation cost and memory cost as we have discussed.
+These two features together help \textbf{biglasso} to outperform other packages.
+We will show that our new screening method will result in a new version of the package that shows significant improvement compared to previous version.
+
+For all the following experiments, we will solve the lasso model along a path of $100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_K=0.05\lambda_0$ and the rest $\lambda$-values equally spaced between them on log scale.
+
+\subsection{Simulation study}
 \label{sec:sim}
-\begin{itemize}
-    \item Introduction to biglasso package
-\end{itemize}
-\begin{itemize}
-    \item Comparing active set cycling, strong rules, SEDPP, Hybrid SSR, and proposed Batched SSR
-    \item Varying n, p. Computation time for all methods grow linearly and ratios among them are constant.
-    \item Varying signal-noise ratio. As the signal increases, the proposed method has larger advantage over other method.
-    \item Varying $||\beta||_0$, number of non-zero coefficients, or sparsity. When the model is sparser, the proposed method has larger advantage over other methods.
-\end{itemize}
+
+\subsubsection{Lasso model}
+
+In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive batched safe strong rule (ABSSR).
+The safe rule used in ABSSR will be batched EDPP rule.
+Note that AC is always incorporated with all other screening rules, so using AC alone can be considered as a baseline for this comparison.
+
+The data will be simulated from the model: $y=X\beta+0.1\epsilon$.
+$X$ and $\epsilon$ are sampled i.i.d from $N(0,1)$.
+$\beta$ will have $s$ randomly selected elements equally spaced between $[-\beta_{max},\beta_{max}]$ and the rest $p-s$ elements are zeros.
+Each setting is replicated $10$ times to calculate the average time cost.
+We consider the following cases:
+
+\begin{enumerate}
+    \item \textbf{Varying number of features $\mathbf{p}$:} we fix $n=1,000$, $s=20$, $\beta_{max}=1$ and vary $p$ from $1,000$ to $100,000$.
+    \item \textbf{Varying sample size $\mathbf{n}$:} we fix $p=10,000$, $s=20$, $\beta_{max}=1$ and vary $n$ from $200$ to $10,000$.
+    \item \textbf{Varying signal strength $\mathbf{\beta_{max}}$:} we fix $p=10,000$, $n=1,000$, $s=20$ and vary $\beta_{max}$ from $0.05$ to $1$.
+    \item \textbf{Varying sparsity $\mathbf{s}$:} we fix $p=10,000$, $n=1,000$, total signal size $\beta_{max}\times s=20$ and vary $s$ from $10$ to $300$.
+\end{enumerate}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 0.59]{plots/gaus1.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+Top row: computation time in second.
+Bottom row: relative computation time compared to AC.
+First column: varying number of features $p$.
+Second column: varying sample size $n$.
+Third column: varying signal strength $\beta_{max}$.
+Fourth column: varying sparsity $s$.}
+    \label{fig:5.1.1}
+\end{figure}
+
+Figure 2 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
+The ABSSR is uniformly the fastest under all settings.
+Most of the time it is 2-4 times faster than any other screening methods.
+It outperforms other methods especially when the data set is large (large $n$ or large $p$) or the active features are sparse among all features (small $s$).
+
+There are several atypical cases when ABSSR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
+This corresponds a small data set and computation will not be challenging.
+(2) $\beta_{max}$ is close to zero.
+This means all the nonzero coefficients are close to zero and are hard to be distinguished from zero coefficients.
+This can cause problem for any statistical learning methods.
+(3) $s$ is large.
+In this case, the underlying model that generate the data set is not sparse in the sense that proportion of nonzero coefficients is not small.
+Lasso model would not be the optimal model to analyse such an data set.
+
+We also tried varying other factors, for example, varying the correlation among features in $X$ or varying the sparsity with fixed signal strength.
+The ABSSR also shows uniform advantage over other method when those factors vary in reasonable ranges.
+
+\subsubsection{Sparse logistic regression model}
+
+In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and ABSSR with Slores as the safe rule (ABSlores).
+SSR is implemented in all of the three screening methods so it will be considered as the baseline.
+
+The data will be simulated from the model: $y=\mathbf{1}\{X\beta+0.1\epsilon >0\}$.
+$X$ and $\epsilon$ are sampled i.i.d from $N(0,1)$.
+$\beta$ will have $s$ randomly selected elements equally spaced between $[-\beta_{max},\beta_{max}]$ and the rest $p-s$ elements are zeros.
+Each setting is replicated $10$ times to calculate the average time cost.
+We consider the same 4 cases we have considered in the previous experiment.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale = 0.59]{plots/bin1.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+Top row: computation time in second.
+Bottom row: relative computation time compared to SSR.
+First column: varying number of features $p$.
+Second column: varying sample size $n$.
+Third column: varying signal strength $\beta_{max}$.
+Fourth column: varying sparsity $s$.}
+    \label{fig:5.1.2}
+\end{figure}
+
+Figure 3 shows the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
+ABSlores is also uniformly faster than other methods and this improvement is significant except for some atypical cases.
 
@@
 \label{sec:real-data}
+
+In previous sections, we used simulation to compare the screening methods under different scenario.
+In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test these screening methods on some real data sets to make sure our comparison conclusion is representative in real world.
+Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2017efficient}, we will test on the following data sets:
+
+\begin{enumerate}
+    \item \textbf{Breast cancer gene expression data
+(GENE):} this data has expression measurements of $p=17,322$ genes from $n=536$ patients.
+The response is the expression measurement of the gene BRCA1, which has been identified to be related to risk of breast cancer.
+    \item \textbf{MNIST handwritten image data
+(MNIST):} this data set has $60,000$ images in the training set and $10,000$ images in the testing set.
+Each image is a $28\times 28=784$ pixels image of handwritten digits.
+We use the training set to form a $n=784\times p=60,000$ feature matrix, treating pixels as samples and images as features.
+Then an image from the testing set is randomly selected as the response.
+    \item \textbf{ Cardiac fibrosis genome-wide association data
+(GWAS):} this data set has $p=660,496$ single nucleotide
+polymorphisms (SNPs) collected from $n=313$ human hearts. The response is the log of the ratio of cardiomyocytes to fibroblasts in the heart tissue, which is associated with heart failure.
+    \item \textbf{Subset of New York Times bag-of-words data
+(NYT):} the raw data set is a $300,000\times 102,660$ matrix, each row being a document and each column being number of occurrence of a specific word in those documents.
+We selected $n=5,500$ documents by removing documents with low word counts.
+Then $55,000$ words are selected as the features and a randomly selected word is the response.
+
+\end{enumerate}
+
+For 1 and 3, we replicate the experiment 10 times to take the average.
+For 2 and 4, since in each experiment the response is randomly selected, we replicate the experiment 50 times to get an accurate estimate.
+The following table compares the average computation time for different screening methods in these data sets.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{l|l|l|l|l}
+\hline
+ & GENE & MNIST & GWAS & NYT \\
+Screening method & n=536 & n=784 & n=313 & n=5,500 \\
+ & p=17,322 & p=60,000 & p=660,496 & p=55,000 \\ \hline
+AC & 2.14 (0.03) & 6.82 (0.07) & 46.67 (0.13) & 59.20 (1.89) \\
+SSR & 1.34 (0.01) & 5.20 (0.01) & 25.34 (0.08) & 35.40 (0.44) \\
+SEDPP & 1.38 (0.01) & 8.40 (0.45) & 25.48 (0.05) & 53.69 (3.81) \\
+HSSR & 1.21 (0.01) & 3.44 (0.07) & 23.85 (0.06) & 31.05 (0.80) \\
+ABSSR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\\hline
+\end{tabular}
+\caption{Average computing time in second (standard error) for solving the lasso model}
+\end{table}
+
+ABSSR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\%.
+Also note that the performance of SEDPP varies a lot in MNIST and NYT data sets, where the response is randomly selected in each replication, suggesting that the speed of SEDPP is sensitive to the data.
+ABSSR is built with SEDPP as the safe rule but does not have the problem of instability, because it can adaptively adjust itself according the performance of the safe rule.
 
@@
 
-\bibliographystyle{unsrt}
 \bibliography{ref}

### 2020-09-15 main.tex
Change name from 'batch' to 'adaptive'

@@
 
-\title{Efficient Feature Screening for Lasso-Type
-Problems via Batched Safe-Strong Rules}
+\title{Adaptive Safe Strong Screening for Efficient Lasso-Type
+Problems Optimization over the Solution Path}
 \author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
@@
 In sparse settings, it scales up very well with a computational cost of approximately $O(np)$.
-As a result, it is widely used to fit the lasso and other penalized regression models.
 
@@
 
-Previous screening rules can also be divided into two categories, sequential rules and one-step rules, by how the screening is carried out along the path of $\lambda$ values.
-Sequential rules do heavy computation for each $\lambda$ values, so they are slower but relatively powerful at each $\lambda$ values.
+Previous safe screening rules can also be divided into two categories, sequential rules and one-step rules, by how the screening is carried out along the path of $\lambda$ values.
+Sequential rules do heavy computation for each $\lambda$ values using solution from its previous $\lambda$ value, so they are slower but relatively powerful at each $\lambda$ values.
 One-step rules only require heavy computation at the beginning and thus are faster but they cannot remain powerful along the path for long.
 
-In this paper, we proposed an adaptive batched screening scheme that changes how screening is done along the path of $\lambda$ values and implement it into hybrid approaches to form adaptive batched safe-strong rules.
-We divided the set of $\lambda$ values into batches and screening within each batch is based on the same solution at one $\lambda$ value at the beginning of the batch.
+In this paper, we proposed an adaptive safe screening scheme that changes how screening is done along the path of $\lambda$ values.
+We do safe screening on $\lambda$ values alone the path referencing to the same solution at the $\lambda$ value in the beginning, as in one-step rules, until it is beneficial to update to a new $\lambda$ value as the reference.
 This screening scheme helps avoid disadvantages of both sequential rules and one-step rules.
-On one hand, basing on the same solution avoids many costly computation within a batch and on the other hand, referring to solution at a close $\lambda$ value provides more screening power.
-An adaptive choice of batches sizes are applied using the screening performance from previous $\lambda$ values to better balance these two effects.
+On one hand, reusing the same solution as reference avoids many costly computation before updating and on the other hand, referring to solution at a closer $\lambda$ value provides more screening power.
+An adaptive scheme determines when to update the reference based on the previous screening performance, to better balance these two effects.
 It will be shown that our adaptive rule can greatly reduce the computation time and outperform other methods under all scenarios.
+Following the hybrid approaches, we also combined our approach with strong rules to form adaptive safe strong rules.
 Similar to hybrid approaches, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
-For example we extended the method to work with logistic regression with lasso penalty.
+For example we extended the method to work with logistic regression with lasso penalty and group lasso.
 
@@
 \begin{itemize}
-    \item A new feature screening framework (Section ?3.2??), which does screening in batches of $\lambda$ values with any safe screening rules, which can generate a family of more efficient and scalable screening rule, compared to previous screening rules that are either sequential or one-step.
-    \item Two specific applications of this framework, Batch-SSR-SEDPP and Batch-SSR-Slores, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section ?3.3??).
-    \item An algorithm to adaptively determine efficient batch sizes (Section \ref{sec:batch-size}).
+    \item A new feature screening framework (Section ?3.2??), which updates the reference for screening alone the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
+    \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section ?3.4,4.1??).
+    \item An algorithm to determine when to update to a new reference $\lambda$ value for best efficiency (Section \ref{sec:adaptive}).
     \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
-    \item The Batch-SSR-SEDPP and Batch-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
+    \item The Ada-SSR-SEDPP and Ada-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
 \end{itemize}
@@
 Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \citep{lee2007efficient}.
+It can be implemented on top of any lasso algorithm with no additional cost.
 When solving the coefficients for at $\lambda_{k+1}$, first only consider features whose coefficients were non-zero at $\lambda_k$ and discard other features with zero coefficients at $\lambda_k$.
@@
 
-BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ by comparing it to $r(\lambda_0)=y$.
+BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ using $r(\lambda_0)=y$ as a reference.
 As $\lambda_k$ gets further away from $\lambda_0$, this bound becomes less precise and the screening rule becomes less powerful.
-SEDPP is slower, but at each $\lambda_{k+1}$, it is comparing $r(\lambda_{k+1})$ to $r(\lambda_k)$.
+SEDPP is slower, but at each $\lambda_{k+1}$, it uses $r(\lambda_{k})$ as the reference.
 Because $\lambda_{k+1}$ and $\lambda_k$ are close, the bound will be tight and screening will keep being powerful.
@@
 
-\section{Batched safe-strong rule}
+\section{Adaptive safe-strong rule}
 \label{sec:method}
 
-In this section, we will introduce the batched safe-strong rules, combine them with pathwise coordinate descent algorithm and propose a strategy to adaptively start new batches.
+In this section, we will introduce the framework of adaptive safe-strong rules, implement them with EDPP as the safe rule to form Ada-SSR-EDPP and propose a strategy to adaptively updating the reference.
 
-\subsection{Batched EDPP rule}
+\subsection{Adaptive EDPP safe rule}
 
@@
 Using the SEDPP rule, we can do screening at $\lambda_{k+2}$ as well, given the solution at $\lambda_k$, which is considered the previous solution now.
-Similarly, given the solution at $\lambda_k$, we can do screening for a batch of $B$ $\lambda$-values: $\lambda_{k+1},...,\lambda_{k+B}$ and then all the discarded features are guaranteed to be zero.
-Batched EDPP is still a safe rule, but it is neither sequential nor one-step.
+Similarly, with solution at $\lambda_k$ as the reference, we can keep screening for a number of $\lambda$-values: $\lambda_{k+1},\lambda_{k+2},...$ until it is beneficial to update the solution at some $\lambda_{K+B}$ as the new reference and in this way all the discarded features are guaranteed to be zero.
+Adaptive EDPP is still a safe rule, but it is neither sequential nor one-step.
 
-Similar to SEDPP, the batched EDPP rule can be stated in the following theorem:
+Similar to SEDPP, the Adaptive EDPP rule can be stated in the following theorem:
 
-\begin{theorem}[Batched EDPP]
+\begin{theorem}[Adaptive EDPP]
     For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
@@
 
-For each $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (11) or (12) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
+For each $\lambda$-value in one update $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (11) or (12) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
 The most expensive computations are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, for $j=1,2,...,p$.
-$x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the batch and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that batch.
+$x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the update and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that update.
 These two computations take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
 
-Compared to sequential methods like SEDPP, the batched method only requires one $O(np)$ computation in one batch, while SEDPP requires one $O(np)$ computation for each $\lambda$-value.
-Compared to one-step methods like BEDPP, if the batch size is not too large, the solution at the batch head $\lambda_k$ and the solution at some $\lambda_{k+b}$ in the batch are usually relatively close, so screening at $\lambda_{k+b}$ using solution at $\lambda_k$ will remain powerful.
+Compared to one-step methods like BEDPP, after updating, the solution as the reference at $\lambda_k$ and the solution at some $\lambda_{k+b}$ in that update are usually relatively close, so screening at $\lambda_{k+b}$ using solution at $\lambda_k$ will remain powerful.
 For one-step method, as $\lambda_k$ gets further away from $\lambda_0$, the screening power can drop drastically and
 may not be any beneficial after that.
+Compared to sequential methods like SEDPP, the adaptive method only requires one $O(np)$ computation in one update, while SEDPP requires one $O(np)$ computation for each $\lambda$-value.
+The framework of adaptive safe screening can also be easily applied to other sequential safe rules, to form a family of adaptive safe rules to achieve the same improvement.
 
-\subsection{Batched strong rule after batched EDPP rule}
+\subsection{Adaptive safe strong rule on top of adaptive EDPP rule}
 
-Because HSSR \citep{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the batched EDPP rule screening.
-The batched SSR and batched EDPP rule combined will form our batched safe strong rule.
+Because HSSR \citep{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
+The SSR and adpative EDPP rule combined will form our adaptive safe strong rule: Ada-SSR-EDPP.
 
+This combination is not trivial.
 For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (2).
@@
 Thus, for features that are discarded at the previous $\lambda$-value but not at the current $\lambda$-value, their corresponding $x_j^Tr(\lambda_k)$ have not been computed yet and thus cannot be used without additional cost.
-Similar to the idea of BASIL \citep{qian2019fast}, we can also do the strong rule screening in batches to reduce the number of required computations.
+Similar to the idea of BASIL \citep{qian2019fast}, we can also do the strong rule screening adaptively by using the latest $x_j^Tr(\lambda_k)$ available, which is computed by adaptive EDPP rule at the latest update, to reduce the number of required computations.
 
-We are going to combine batched EDPP rule and batched SSR to form the batch safe strong rule as following.
-First, we determine a batch $\lambda_{k+1},...,\lambda_{k+B}$, and both batched EDPP rule and batched SSR will be conducted in this batch.
-Second $x_j^Tr(\lambda_k)$ will be computed and stored.
-Then for each $\lambda_{k+b}$ in the batch, after doing batched EDPP rule screening, a batched SSR screening is carried out on the features that have not been discarded by batched EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
-Last, a post-convergence check is conducted on the features that were discarded by batched SSR but not discarded by batched EDPP rule.
+We are going to combine adaptive EDPP rule and SSR to form the Ada-SSR-EDPP as following.
+Suppose we have a latest updated reference $\lambda_k$ with $x_j^Tr(\lambda_k)$ computed and want the solution at some following $\lambda_{k+b}$.
+First, we do adaptive EDPP rule screening.
+Second, an adaptive SSR screening is carried out on the features that have not been discarded by adaptive EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Third, a post-convergence check is conducted on the features that were discarded by adaptive SSR but not discarded by adaptive EDPP rule.
+Then we move on to the next $\lambda_{k+b+1}$ and repeat the same procedure, unless we determine an update is needed.
 
-By choosing the same batch for batched EDPP rule and batched SSR, the quantity $x_j^Tr(\lambda_k)$ only needs to be computed once and can be used by both rules.
-Also, because batched EDPP rule can stay powerful, it keeps the set of features that require post-convergence check small, while because basic EDPP loses power for $\lambda$-values that are far away from $\lambda_0$, post-convergence check for HSSR will be more expensive.
+By choosing the same reference for adaptive EDPP rule and adaptive SSR, the quantity $x_j^Tr(\lambda_k)$ only needs to be computed once and can be used by both rules.
+Also, because adaptive EDPP rule can stay powerful, it keeps the set of features that require post-convergence check small, while because basic EDPP loses power for $\lambda$-values that are far away from $\lambda_0$, post-convergence check for HSSR will be more expensive.
 
-\subsection{Coordinate descent with batched safe strong rule}
+\subsection{Pathwise lasso algorithm with adaptive safe strong rule}
 
-In this section, we will show the algorithm to do pathwise coordinate descent with our batched safe strong rule screening.
-We will only show the algorithm for solving one batch $\lambda_{k+1},...,\lambda_{k+B}$.
-After finishing this batch, we just need to start a new batch and apply the same algorithm using the output from last batch as input.
-Note here for the first batch with batch head $\lambda_0$, the residuals vector $r(\lambda_0)$ is just the response $y$, because all the $\hat{\beta}(\lambda_0)$ are zero.
+In this section, we will show the algorithm to solve the lasso problem over the solution path with pathwise coordinate descent algorithm and our adaptive safe strong screening rule.
+The pathwise coordinate descent algorithm can be substituted by any other pathwise lasso algorithms and the adaptive EDPP can also be substituted by any other adaptive safe rules in our framework.
+Note here the first reference chosen will be $\lambda_0$, where the residuals vector $r(\lambda_0)$ is just the response $y$, because all the $\hat{\beta}(\lambda_0)$ are zero.
 $\{x_j^Ty\}_{j=1}^p$ need to be computed at the beginning and stored for the whole path.
@@
     \SetAlgoLined
-    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p, \hat{\beta}(\lambda_k), r(\lambda_k), \lambda_{k+1},...,\lambda_{k+B}$}
-    \Pre{ $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$}
+    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p,  \lambda_{0},...,\lambda_{K}$}
     \BlankLine
-    \For{$b\xleftarrow{}$ 1 \KwTo B}{
-        Safe Screening: $\mathcal{S}_{k+b}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
+    \Initialize{reference = $\lambda_0$}
 
-        Strong Screening: $\mathcal{R}_{k+b}\xleftarrow{}\{j\in \mathcal{S}_{k+b}:x_j$ not discarded by batched SSR$\}$.
+    \For{$k\xleftarrow{}$ 1 \KwTo K}{
+        Safe Screening: $\mathcal{S}_{k}\xleftarrow{}\{j:x_j$ not discarded by adaptive EDPP rule given the reference$\}$.
 
-        \Initialize{$\hat{\beta}(\lambda_{k+b})=\hat{\beta}(\lambda_{k+b-1}), r(\lambda_{k+b})=r(\lambda_{k+b-1})$}
+        Strong Screening: $\mathcal{R}_{k}\xleftarrow{}\{j\in \mathcal{S}_{k}:x_j$ not discarded by adaptive SSR given the reference$\}$.
+
+        \Initialize{$\hat{\beta}(\lambda_{k})=\hat{\beta}(\lambda_{k-1}), r(\lambda_{k})=r(\lambda_{k-1})$}
 
         \Repeat{Post-convergence check passes}{
-            Pathwise coordinate descent in Algorithm 1 with only features in $\mathcal{R}_{k+b}$ and with warm start $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$, until converge.
-Save the outputs in $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$.
+            Pathwise lasso algorithm with only features in $\mathcal{R}_{k}$ and with warm start $\hat{\beta}(\lambda_{k}), r(\lambda_{k})$, until converge.
 
-            Post-convergence check for all $j\in \mathcal{S}_{k+b}\setminus\mathcal{R}_{k+b}$,
+            Save new $\hat{\beta}(\lambda_{k}), r(\lambda_{k})$.
+
+            Post-convergence check for all $j\in \mathcal{S}_{k}\setminus\mathcal{R}_{k}$,
 
             \uIf{Post-convergence check does not pass}{
-                Add violating features to $\mathcal{R}_{k+b}$\;
+                Add violating features to $\mathcal{R}_{k}$\;
             }
         }
+        \uIf{Update conditions met}{
+            Reference = $\lambda_{k}$
+
+            Compute and save: $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$.}
+
     }
-    \Output{$\{\hat{\beta}(\lambda_{k+b})\}_{b=1}^B, r(\lambda_{k+B})$}
-    \caption{Pathwise coordinate descent with batched safe strong rule screening}
+    \Output{$\{\hat{\beta}(\lambda_{k})\}_{k=1}^K, r(\lambda_{k+B})$}
+    \caption{Pathwise lasso algorithm with adaptive safe strong rule screening}
 \end{algorithm}
 
-\subsection{Adaptive batched safe strong rule}
+\subsection{Adaptive update algorithm}
+\label{sec:adaptive}
 
-In this section we will develop an algorithm to adaptively determining when to end the current batch and start a new batch, by evaluating screening power at previous $\lambda$-values in current batch.
+In this section we will fill in line 11 in Algorithm 2.
+We will develop an algorithm to adaptively determining when update the reference for screening, by evaluating screening power at previous $\lambda$-values since the last update.
 Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 2.
@@
 This complexity analysis will only consider calculations with $O(np)$ complexity.
-The rest calculations, those with $O(p)$ complexity for example, are not only faster in order, but also require no out-of-core computing.
-Calculation of ${x_j^Ty}_{j=1}^p$ is needed for pathwise coordinate descent in algorithm 1 and is not additional cost for screening, so it would not be considered either.
+The rest calculations, those with $O(p)$ complexity for example, are not only faster in order, but also consume less memory and thus usually do no need out-of-core computing.
+Calculation of ${x_j^Ty}_{j=1}^p$ is needed only once for the whole solution path, so it would be neglected too.
 We will assume that strong rule screening is always powerful in the sense that $|\mathcal{R}_b|=o(p)\approx0$, but safe rule screening may not.
@@
 
-Under these assumptions, there are two dominating parts in the algorithm for each batch.
-First, the computation of $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ at the beginning of the batch, which requires $np$ multiplications.
-Then, for each $\lambda$-value $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_b\setminus\mathcal{R}_b|\approx|\mathcal{S}_b|$ KKT condition checks and each KKT condition check requires $n$ multiplications.
-These sum up to $n\sum_{b=1}^B|\mathcal{S}_b|$ multiplications.
-Combining these two parts, we will have the average cost per $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$ to be
+Under these assumptions, there are two dominating parts in the algorithm within each update.
+First, the computation of $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ at the time of updating the reference, which requires $np$ multiplications.
+Then, for each $\lambda$-value $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_{k+b}\setminus\mathcal{R}_{k+b}|\approx|\mathcal{S}_{k+b}|$ KKT condition checks and each KKT condition check requires $n$ multiplications.
+These sum up to $n\sum_{i=k}^{k+B}|\mathcal{S}_k|$ multiplications, where $k+B$ is the start of the next update.
+Combining these two parts, we will have the average cost per $\lambda$-value in the update $\lambda_{k+1},...,\lambda_{k+B}$ to be
 
 \begin{equation}
-    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_b|}{B}.
+    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_{k+b}|}{B}.
 \end{equation}
@@
 The first term is the average cost for safe screening.
-Increasing batch size $B$ means reusing calculation at the batch head more times for the safe screening and thus reducing the average cost.
+Delaying next update (increasing $B$) means reusing calculation at the previous update more times for the safe screening and thus reducing the average cost.
 The second term is the average cost for KKT condition checking.
-As the batch size $B$ increases, safe rule screening becomes less powerful and the number of KKT condition checks required ($|\mathcal{S}_b|$) increases.
-The following plot illustrates the effect of $B$ on $|\mathcal{S}_b|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
-The y axis is the proportion of discarded features, calculated as $1-|\mathcal{S}_b|/p$.
+If the old reference is reused too many times, safe rule screening becomes less powerful and the number of KKT condition checks required ($|\mathcal{S}_{k+b}|$) increases.
+
+To better illustrate this two effects, we considered the most naive and simple updating scheme: update the reference periodically after every other $B$ $\lambda$ values.
+The following plot illustrates the effect of update delay $B$ on $|\mathcal{S}_{k+b}|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
+The y axis is the proportion of discarded features, calculated as $1-|\mathcal{S}_{k+b}|/p$.
 
@@
     \centering
-    \includegraphics[scale = 0.5]{plots/batchsizes.png}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different batch sizes.}
+    \includegraphics[scale = 0.5]{plots/batchsizes.png}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
     \label{fig:3.4.1}
@@
 
-BEDPP (Basic EDPP) rule is the special case of batched EDPP with only one batch of the largest possible size $B=K=100$.
-When the batch is large, the safe rule screening will eventually fail to discard any features and make the KKT condition checking cost increase to its maximum $np$.
-SEDPP rule is the special case where all batches have the smallest possible batch size $B=1$.
-It remains very powerful along the path, making the KKT condition checking cost almost 0, but the safe screening itself is costly and takes $np$ time per $\lambda$-value.
-Batched EDPP can strike a balance between BEDPP and SEDPP.
-In this example, using batches with fixed sizes $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
+BEDPP (Basic EDPP) rule is the special case of adaptive EDPP that never updates ($B=K$).
+When the reference does not get updated for a long time, the safe rule screening will eventually fail to discard any features and make the KKT condition checking cost increase to its maximum $np$.
+SEDPP rule is the special case that updates at every $\lambda$ value ($B=1$).
+It remains very powerful along the path, making the KKT condition checking cost small, but the safe screening itself is costly and takes $np$ time per $\lambda$-value.
+Adaptive EDPP can strike a balance between BEDPP and SEDPP.
+In this example, simply using fixed update period $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
 
-This example also shows the performance of batch EDPP rule changes along the path of $\lambda$-values.
-Take the batched EDPP with $B=10$ as an example.
-For the first batch of 10 $\lambda$-values, the batched EDPP stays powerful even at the end, which means this batch is still exploitable.
-We may want to extend this batch to reduce average safe screening cost without harming the KKT condition checking cost much.
-For the last batch however, the screening power is close to 0 for the last few $\lambda$-values, which means this batch becomes useless at this point.
-Starting a new batch earlier can greatly reduce the KKT condition checking cost with relatively small increase in safe screening cost.
-Also, the performance of batch EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
-These suggest that starting a new batch after every fixed number of $\lambda$-values cannot not be consistently efficient and we want a method that can automatically determine whether to start a new batch given current performance.
+This example also shows the timing of updates should be decided carefully and adaptively.
+For the first 10 $\lambda$-values, the safe rule stays powerful, which means the old reference is still exploitable.
+We may want delay the update to reduce average safe screening cost without harming the KKT condition checking cost much.
+For the last 20 $\lambda$-values however, the screening power drops to 0 quickly, which means the reference becomes useless quickly.
+Updating more frequently can greatly reduce the KKT condition checking cost with relatively small increase in safe screening cost.
+Also, the performance of adaptive EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
+These suggest that simple updating rules like periodic updating cannot not be consistently efficient and we want a method that can automatically determine whether to update given current performance.
 
-\subsubsection{Adaptive batch starting algorithm}
+\subsubsection{Efficient updating algorithm}
 
-From previous example, we assume the average cost is a convex function of batch size $B$ which decreases first and then after some optimal value increases again.
-If we want to minimize the average cost per $\lambda$-value, we need to end the current batch when extending the current batch by 1 $\lambda$-value will increase the average cost.
-That is, end the current batch at $\lambda_{B-1}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$.
-From (13), this condition will be:
+From previous example, we assume the average cost is a convex function of distance from last update $B$, which decreases first and then after some optimal value increases again.
+If we want to minimize the average cost per $\lambda$-value, we need to update when using the old reference for one more $\lambda$-value will increase the average cost.
+That is, we should update the reference to $\lambda_{k+B}$ when $\bar{T}_k(B+1)>\bar{T}_k(B)$.
+For practice, we will update the reference to $\lambda_{k+B}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$ instead, because $\bar{T}_k(B+1)$ cannot be calculated without doing screening at $\lambda_{k+B+1}$.
+These two conditions should be close and thus this substitution should also be close to optimal.
+From (13), the latter condition will be:
 
 \begin{equation}
-    (B-1)|\mathcal{S}_B|-\sum_{b=1}^{B-1}|\mathcal{S}_b|>p.
+    (B-1)|\mathcal{S}_{k+B}|-\sum_{b=1}^{B-1}|\mathcal{S}_{k+b}|>p.
 \end{equation}
-In practice, we will end the batch at $\lambda_B$ and start at $\lambda_{B+1}$ instead, because evaluating $\mathcal{S}_B$ needs screening at $\lambda_B$ and if we have already done the screening, it would be a waste not to use the screening result.
 
-This batch restarting condition is a greedy condition that only considers the current batch cost.
-In practice, we cannot know about future batches so this is the most reasonable condition.
-In fact, it can handle the three most common scenarios well.
-First, if the screening power stays high, meaning $\mathcal{S}_b$ is small for all $b$, then the left-hand-side of (14) will be small and thus at this point we will extend the current batch to further exploit it.
-Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_B$ is large but $\mathcal{S}_b$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (14) will be large and we will end the useless current batch and start a new batch.
-Last, if the screening power drops dramatically right after the beginning of the current batch, meaning $\mathcal{S}_b$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (14) will be approximately $p-|\mathcal{S}_1|<p$.
-We will not end the current batch although it becomes useless, because if we did, the next batch would be useless as well.
+This updating condition is a greedy condition that only considers the cost up to the current $\lambda$ value.
+In practice, we cannot know about future $\lambda$ values so this is the most reasonable condition.
+In fact, it provides a robust strategy towards three most common scenarios.
+First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of (14) will be small and thus at this point we will not update to further exploit the last update.
+Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (14) will be large and we will update the useless old reference to a new helpful one.
+Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (14) will be approximately $p-|\mathcal{S}_1|<p$.
+We will not update although old reference is useless, because if we did, the new update would become useless quickly as well.
 
-Combined with Algorithm 2, we will propose the pathwise coordinate descent with adaptive batched safe strong rule screening.
-After ending a batch, if there are still unsolved $\lambda$-values in the path $\lambda_0,\lambda_1,...,\lambda_K$, we can just start a new batch with the rest unsolved $\lambda$-values and apply the same algorithm.
-
-\begin{algorithm}[H]
-    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Pre}{Pre-compute}\SetKwInOut{Initialize}{Initialize}
-    \SetAlgoLined
-    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p, \hat{\beta}(\lambda_k), r(\lambda_k), \lambda_{k+1},...,\lambda_{K}$}
-    \Pre{ $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$}
-    \BlankLine
-    $B\xleftarrow{}1$
-
-    \Repeat{$(B-1)|\mathcal{S}_B|-\sum_{b=1}^{B-1}|\mathcal{S}_{b}|>p$ or $B>K$}{
-        Safe Screening: $\mathcal{S}_{k+B}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
-
-        Strong Screening: $\mathcal{R}_{k+B}\xleftarrow{}\{j\in \mathcal{S}_{k+B}:x_j$ not discarded by batched SSR$\}$.
-
-        \Initialize{$\hat{\beta}(\lambda_{k+B})=\hat{\beta}(\lambda_{k+B-1}), r(\lambda_{k+B})=r(\lambda_{k+B-1})$}
-
-        \Repeat{Post-convergence check passes}{
-            Pathwise coordinate descent in Algorithm 1 with only features in $\mathcal{R}_{k+B}$ and with warm start $\hat{\beta}(\lambda_{k+B}), r(\lambda_{k+B})$, until converge.
-Save the outputs in $\hat{\beta}(\lambda_{k+B}), r(\lambda_{k+B})$.
-
-            Post-convergence check for all $j\in \mathcal{S}_{k+B}\setminus\mathcal{R}_{k+B}$,
-
-            \uIf{Post-convergence check does not pass}{
-                Add violating features to $\mathcal{R}_{k+B}$\;
-            }
-        }
-        $B\xleftarrow{}B+1$
-    }
-    \Output{$\{\hat{\beta}(\lambda_{k+b})\}_{b=1}^B, r(\lambda_{k+B}),\lambda_{k+B+1},...,\lambda_K$}
-    \caption{Pathwise coordinate descent with adaptive batched safe strong rule screening}
-\end{algorithm}
+This adaptive updating condition fills in the condition on line 11 in Algorithm 2 and forms a complete pathwise lasso algorithm with adaptive safe strong screening.
 
@@
 
-The structure of the batched safe strong rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
-After a batched safe strong rule is built, we can automatically apply the adaptive batch starting algorithm to make it an adaptive batched safe strong rule.
+The structure of the adaptive safe strong rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
+After an adaptive safe strong rule is built, we can automatically apply the adaptive update algorithm to form a pathwise algorithm with adaptive safe strong screening.
 We are going to derive the extensions to two lasso type problems and show these extensions improve computation efficiency.
 
-\subsection{Batched safe strong rule for sparse logistic regression}
+\subsection{Adaptive safe strong rule for sparse logistic regression}
 
@@
 For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\citep{wang2014safe} is used.
-It was proposed as a one-step rule but we will extend it to a batched rule.
+It was proposed as a one-step rule but it can be extended as a sequential rule with some minimal change and thus can be extended as adaptive rule.
 Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
 
-\begin{theorem}[Batched Slores]
+\begin{theorem}[Adaptive Slores]
 For the sparse logistic regression model (15), let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$.
 Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-$\forall\theta\in(0,1)^n$, let $x_*=argmax_{x_j}|x_j^Ty/n|$ and
+$\forall\theta\in(0,1)^n$, let
 
@@
 
-Under condition (2) except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
-For some $B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, let
+Under condition (2) except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
+For any $k+b>k$, let
 
@@
 
-When computing the batched Slores, $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ need to be computed only once, stored and reused for the whole solution path $\lambda_0>\lambda_1>...>\lambda_K$.
-Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed once for each batch.
-Thus algorithm 3 for adaptive batched safe strong rule can be done with Slores rule instead of EDPP rule to do screening for sparse logistic regression model.
+When computing the adaptive Slores, $\{x_j^Ty\}_{j=1}^p$ needs to be computed only once, stored and reused for the whole solution path.
+$\{x_j^Tx_*\}_{j=1}^p$ can be reused unless $x_*$ changes.
+Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed at the time of each update.
+Thus algorithm 2 for adaptive safe strong rule can be done with Slores rule instead of EDPP rule to form Ada-SSR-Slores that does screening for sparse logistic regression model.
 
-\subsection{Batched safe strong rule for group lasso}
+\subsection{Adaptive safe strong rule for group lasso}
 
@@
 
-For safe rule screening, we have SEDPP for group lasso\citep{wang2013lasso} and we can extend it the batched EDPP rule for group lasso.
+For safe rule screening, we have SEDPP for group lasso\citep{wang2013lasso} and we can extend it the adaptive EDPP rule for group lasso.
 
-\begin{theorem}[Batched EDPP for group lasso]
+\begin{theorem}[Adaptive EDPP for group lasso]
 For the group lasso problem (22), let $\lambda_0:=\max_j\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$.
@@
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for some $B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for any  $k+b>k$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
         \begin{equation}
@@
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for some $B$ and any $b$ s.t.
-$0<b\leq B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for any $b>0$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
         \begin{equation}
@@
 
-Similar to Batched EDPP rule, three expensive computations are $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$ and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
+Similar to Adaptive EDPP rule, three expensive computations are $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$ and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
 The first and second only need to be computed once for the whole solution path.
-The last only needs to be computed once per batch with cost $O(np)$.
+The last only needs to be computed at the time of each update with cost $O(np)$.
+The adaptive EDPP for group lasso, combined with the previous SSR, forms the Ada-SSR-EDPP for group lasso.
 
@@
 
-In this section conduct experiments solving lasso model on both simulated data sets and real data sets, to show our proposed adaptive batched safe strong rule screening method outperforms previous screening method such as SSR, SEDPP, HSSR and Slores.
-Active-set cycling in \ref{sec:active} is always used with all screening methods because it can be easily combined with any screening methods with on extra cost.
+In this section conduct experiments solving lasso model on both simulated data sets and real data sets, to show our proposed adaptive safe strong rule screening method outperforms previous screening method such as SSR, SEDPP, HSSR and Slores.
+Active-set cycling in \ref{sec:active} is always used with all screening methods because it can be easily combined with any screening methods with no extra cost.
 
-The adaptive batched safe strong rule screening is implemented in the \textbf{R} package \textbf{biglasso} and we will use this package for our experiment.
+The adaptive safe strong rule screening is implemented in the \textbf{R} package \textbf{biglasso} and we will use this package for our experiment.
 Compared to traditional packages that solve lasso problem, such as \textbf{glmnet}, \textbf{biglasso} focuses on efficiently solving lasso problem with high-dimensional data sets that have a large number of features.
@@
 
-For all the following experiments, we will solve the lasso model along a path of $100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_K=0.05\lambda_0$ and the rest $\lambda$-values equally spaced between them on log scale.
+For all the following experiments, we will solve the lasso model along a path of $100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_K=0.05\lambda_0$ and the rest $\lambda$-values equally spaced between on log scale.
 
@@
 
-In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive batched safe strong rule (ABSSR).
-The safe rule used in ABSSR will be batched EDPP rule.
+In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive safe strong rule (ASSR).
+The safe rule used in ASSR will be adaptive EDPP rule.
 Note that AC is always incorporated with all other screening rules, so using AC alone can be considered as a baseline for this comparison.
@@
 Figure 2 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
-The ABSSR is uniformly the fastest under all settings.
+The ASSR is uniformly the fastest under all settings.
 Most of the time it is 2-4 times faster than any other screening methods.
@@
 
-There are several atypical cases when ABSSR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
-This corresponds a small data set and computation will not be challenging.
+There are several atypical cases when ASSR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
+This corresponds a small data set and computation will be less challenging.
 (2) $\beta_{max}$ is close to zero.
@@
 We also tried varying other factors, for example, varying the correlation among features in $X$ or varying the sparsity with fixed signal strength.
-The ABSSR also shows uniform advantage over other method when those factors vary in reasonable ranges.
+The ASSR also shows uniform advantage over other method when those factors vary in reasonable ranges.
 
@@
 
-In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and ABSSR with Slores as the safe rule (ABSlores).
+In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and ASSR with Slores as the safe rule (ASlores).
 SSR is implemented in all of the three screening methods so it will be considered as the baseline.
@@
 Figure 3 shows the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
-ABSlores is also uniformly faster than other methods and this improvement is significant except for some atypical cases.
+ASlores is also uniformly faster than other methods and this improvement is significant except for some atypical cases motioned before.
 
@@
 HSSR & 1.21 (0.01) & 3.44 (0.07) & 23.85 (0.06) & 31.05 (0.80) \\
-ABSSR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\\hline
+ASSR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\\hline
 \end{tabular}
@@
 
-ABSSR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\%.
+ASSR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\%.
 Also note that the performance of SEDPP varies a lot in MNIST and NYT data sets, where the response is randomly selected in each replication, suggesting that the speed of SEDPP is sensitive to the data.
-ABSSR is built with SEDPP as the safe rule but does not have the problem of instability, because it can adaptively adjust itself according the performance of the safe rule.
+ASSR is built with SEDPP as the safe rule but does not have the problem of instability, because it can adaptively adjust itself according the performance of the safe rule.
 
@@
 
+In this paper, we proposed the novel adaptive safe strong screening framework for efficient lasso type problem optimization over the solution path.
+The key idea is cleverly reusing the reference for screening along the path until updating to a new reference is beneficial for computation cost.
+We developed three instances in this framework: Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR EDPP for group lasso, for 3 different types of lasso problems.
+We tested the first two in extensive numeric experiments on both simulated data and real data, including a ultra big data that does not fit into the memory.
+Our proposed rules outperformed other state-of-the-art screening methods uniformly, especially in the most challenging scenarios.
+
+Ada-SSR-EDPP and Ada-SSR-Slores have been implemented in  publicly accessible \textbf{R} packages \textbf{biglasso}\citep{zeng2017biglasso}, which was used to carry out the numeric experiments.
+
+Our adaptive safe strong screening framework also has great flexibility for extensions.
+It can substitute coordinate descent with any other faster lasso problem optimizer, SSR with any other stronger strong rules and the adaptive updating algorithm with any other cleverer algorithm.
+Most importantly, most sequential safe rules can be modified as adaptive safe rules and fit into our framework.
+This lead to several future extensions.
+First, if a stronger safe rule is developed, our framework can better exploit its power and lead to an even faster algorithm.
+Second, there are still many lasso type problems that do not have corresponding sequential safe rules, such as sparse Cox regression, sparse Poisson regression and sparse SVM.
+Once they are developed, they can be fit into our framework to produce efficient algorithm for other types of lasso problem.
+
 \bibliography{ref}

### 2020-09-18 batch-hssr.tex
Splitting into header and content files

--- 2020-02-17 main.tex
@@
 \usepackage{graphicx}
+\usepackage{float}
 \newtheorem{theorem}{Theorem}[section]
-
+\bibliographystyle{ims}
 % Custom commands / shortcuts
@@
 
-\title{Efficient Feature Screening for Lasso-Type
-Problems via Batched Safe-Strong Rules}
+\title{Adaptive Hybrid Screening for Efficient Lasso Optimization}
 \author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
@@
 
-\section{Introduction}
+\input{main}
 
-The lasso (least absolute shrinkage and selection operator) model\citep{tibshirani1996regression}, is a popular model in statistics and machine learning, especially in high-dimensional problems.
-The model can be defined as the following modification of the least squares optimization problem:
-\begin{equation}
-    \hat{\beta}(\lambda)=\underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}||y-X\beta||_2^2+\lambda||\beta||_1,
-\end{equation}
-where $y$ is the $n\times 1$ response vector correspond to $n$ observations, $X=(x_1,x_2,...,x_p)$ is the $n\times p$ feature matrix correspond to $p$ features, $\beta\in \mathbb{R}^p$ is the $p\times 1$ coefficient vector and $\lambda$ is the regularization tuning parameter.
-$||\cdot||_2$ denotes the $l_2$ (Euclidean) norm and $||\cdot||_1$ denotes the $l_1$ norm.
-
-The lasso model has several attractive properties compared to least squares regression, including increased stability of estimation, increased prediction accuracy, and automatic variable selection arising from the fact that it yields sparse estimates of $\beta$.
-As a result, it is widely applied in different fields, such as gene expression data analysis, image recognition and text mining, and has been extended in several ways, such as group lasso\cite{yuan2006model}, elastic net\cite{zou2005regularization} and sparse generalized linear models.
-Because of its wide popularity, solving the lasso model efficiently is an important topic in statistics and machine learning.
-
-Because the optimal value of $\lambda$ is not known in advance, typical practice is to solve for $\beta$ along a sequence of values of the tuning parameter $\lambda$, known as the solution path.
-Pathwise algorithms can be efficiently implemented by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.
-In particular, the pathwise coordinate descent algorithm\cite{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS (least angle regression)\cite{efron2004least}, especially in high dimensional settings where $p$ is large.
-In sparse settings, it scales up very well with a computational cost of approximately $O(np)$.
-As a result, it is widely used to fit the lasso and other penalized regression models.
-
-However, modern data collection and storage techniques allow researchers to measure an increasingly large number of features, which introduce additional computational challenges.
-In particular, it may not be possible to store the feature matrix, which can require many GBs of memory to store, in memory.
-One can resolve this problem by using a memory mapping package such as \textbf{bigmemory}, which allows us to store the feature matrix on disk and read it portions of it as needed; however, this results in frequent reading from disk, which is extremely slow compared to other parts of the algorithm and becomes a bottleneck with respect to the computational burden of fitting lasso models on very large data sets.
-
-One promising technique to address this challenge is feature screening.
-The lasso model solution is sparse in the sense that most coefficients will be exactly zero; for these ``inactive'' coefficients we do not need their associated features.
-In theory, if we knew which coefficients were nonzero at each value of $\lambda$, we could read into memory only those features and leave the remaining features on disk.
-In reality, we cannot know this prior to fitting the model -- however, through the clever use of feature screening rules, we can greatly reduce the number of times inactive features are read into memory, thereby minimizing the computational burden.
-In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision and a decision is made for each $\lambda$ values: for example, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
-
-There are two important categories of features screening rules: ``strong'' rules\cite{tibshirani2011regression}\cite{qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules\cite{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
-As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
-This check is not necessary with safe rules.
-However, safe rules are considerably less powerful at discarding features than strong rules.
-More recently, hybrid approaches \cite{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.
-
-Previous screening rules can also be divided into two categories, sequential rules and one-step rules, by how the screening is carried out along the path of $\lambda$ values.
-Sequential rules do heavy computation for each $\lambda$ values, so they are slower but relatively powerful at each $\lambda$ values.
-One-step rules only require heavy computation at the beginning and thus are faster but they cannot remain powerful along the path for long.
-
-In this paper, we proposed an adaptive batched screening scheme that changes how screening is done along the path of $\lambda$ values and implement it into hybrid approaches to form adaptive batched safe-strong rules.
-We divided the set of $\lambda$ values into batches and screening within each batch is based on the same solution at one $\lambda$ value at the beginning of the batch.
-This screening scheme helps avoid disadvantages of both sequential rules and one-step rules.
-On one hand, basing on the same solution avoids many costly computation within a batch and on the other hand, referring to solution at a close $\lambda$ value provides more screening power.
-An adaptive choice of batches sizes are applied using the screening performance from previous $\lambda$ values to better balance these two effects.
-It will be shown that our adaptive rule can greatly reduce the computation time and outperform other methods under all scenarios.
-Similar to hybrid approaches, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
-For example we extended the method to work with logistic regression with lasso penalty.
-
-This manuscript provides a brief review of existing feature screening rules in Section\ref{sec:existing} as well as the following novel contributions:
-
-\begin{itemize}
-    \item A new feature screening framework (Section ?3.2??), which does screening in batches of $\lambda$ values with any safe screening rules, which can generate a family of more efficient and scalable screening rule, compared to previous screening rules that are either sequential or one-step.
-    \item Two specific applications of this framework, Batch-SSR-SEDPP and Batch-SSR-Slores, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section ?3.3??).
-    \item An algorithm to adaptively determine efficient batch sizes (Section \ref{sec:batch-size}).
-    \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
-    \item The Batch-SSR-SEDPP and Batch-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\cite{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
-\end{itemize}
-
-\section{Existing feature screening rules}
-\label{sec:existing}
-
-Throughout this paper, it will be assumed that $y$ is centeredand $\{x_j\}_{j=1}^p$ are centered and standardized:
-\begin{equation}
-    \sum_{i=1}^ny_i=0, \qquad \sum_{i=1}^n x_{ij}=0, \qquad \sum_{i=1}^n x_{ij}^2=n,\qquad j=1,2,...,p.
-\end{equation}
-This standardization make it reasonable to apply the same penalty to all features, even if originally measured in different units.
-It also improves the efficiency and stability of the optimization, and helps to simplify optimization.
-For example, under this standardization, the intercept is exactly 0 and thus may be ignored.
-Standardization also simplifies the formulas for screening rules and thus allows for more efficient implementation.
-
-Typical practice when fitting lasso models is to solve for $\hat{\beta}(\lambda)$ along a decreasing sequence of $K+1$ values of $\lambda$: $\lambda_0 > \lambda_1 > \cdots > \lambda_K$.
-As we will discuss shortly, we set $\lambda_0=\max_j|x_j^Ty/n|$ throughout; this ensures that $\hat{\beta}(\lambda_0)=0$, making it a natural point from which to start.
-
-Pathwise coordinate descent is a popular algorithm fitting a solution path for lasso problem.
-For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using Algorithm~\ref{Alg:pathwise-coordinate-descent}.
-Note that the algorithm uses the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in obtaining the next solution along the path, a strategy known as a ``warm start''.
-
-\begin{algorithm}[H]\label{Alg:pathwise-coordinate-descent}
-    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Initialize}{Initialize}
-    \SetAlgoLined
-    \Input{$\hat{\beta}(\lambda_k), \{x_j\}_{j=1}^p, r(\lambda_k)$}
-    \Initialize{ $r = r(\lambda_k),\hat{\beta} = \hat{\beta}(\lambda_k)$}
-    \BlankLine
-    \While{not converged}{
-        \For{$j \xleftarrow{}$ 1 \KwTo p}{
-            $z_j\xleftarrow{}\hat{\beta} + x_j^Tr/n$\;
-            \uIf{$z_j > \lambda$}{
-                $\beta_j^{new}\xleftarrow{} z_j-\lambda$\;
-            }\uElseIf{$z_j < -\lambda$}{
-                $\beta_j^{new}\xleftarrow{} z_j+\lambda$\;
-            }\Else{
-                $\beta_j^{new}\xleftarrow{} 0$\;
-            }
-            $r\xleftarrow{}r-(\beta_j^{new}-\hat{\beta}_j)x_j$\;
-            $\hat{\beta}_j\xleftarrow{}\beta_j^{new}$\;
-        }
-    }
-    \Output{$\hat{\beta}(\lambda_{k+1})\xleftarrow{}\hat{\beta},r(\lambda_{k+1})\xleftarrow{}r$}
-    \caption{Pathwise coordinate descent with warm start $\hat{\beta}(\lambda_k),r(\lambda_k)$}
-\end{algorithm}
-
-In convex optimization, the Karush-Kuhn-Tucker (KKT) conditions are both necessary and sufficient for any optimal solution.
-Screening rules take advantage of these KKT conditions in order to discard inactive coefficients.
-For the lasso, the KKT conditions governing the optimal solution $\hat{\beta}(\lambda)$ are given by
-\begin{equation}
-  \begin{aligned}
-    &x_j^Tr(\lambda)/n& &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if} \quad \hat{\beta}(\lambda)_j\neq 0,\\
-    |&x_j^Tr(\lambda)/n|& &\leq \lambda & & \textrm{if} \quad \hat{\beta}(\lambda)_j= 0.
-  \end{aligned}
-\end{equation}
-If the residuals were known, we could safely conclude that $\hat{\beta}(\lambda)_j=0$ by checking the second condition holds as a strict inequality.
-The complication, of course, is that the residuals are not known until after we have solved for all the coefficients.
-However, when fitting a solution path, residuals at previous $\lambda$-values provide information about residuals at the next $\lambda$-value and thus be used for screening.
-Note that in Algorithm~\ref{Alg:pathwise-coordinate-descent}, the residuals $r$ are computed at each $\lambda$-value and can thus be conveniently reused for the purpose of feature screening.
-
-\subsection{Active-set Cycling}
-
-Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \cite{lee2007efficient}.
-When solving the coefficients for at $\lambda_{k+1}$, first only consider features whose coefficients were non-zero at $\lambda_k$ and discard other features with zero coefficients at $\lambda_k$.
-We compute the solution for the smaller model with these reduced number of coefficients.
-
-After computing the solution, a post-convergence KKT conditions check is performed.
-Because the KKT conditions are sufficient for the solution to be optimal, if there is no violation, the solution to the smaller model will be exactly the same as if we solve the model with all features.
-If there are violations, corresponding features will be added to the model and this procedure will repeat.
-Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm provides substantial speed up.
-
-\subsection{Strong rules}
-
-Sequential strong rule (SSR) \cite{tibshirani2011regression} is a fast and powerful feature screening rule.
-Given the solution $\hat{\beta}(\lambda_k)$ at $\lambda_k$, we can compute the residual vector as $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$.
-The SSR discards the $j$-th feature at $\lambda_{k+1}$ if:
-
-\begin{equation}
-    |x_j^Tr(\lambda_k)/n|<2\lambda_{k+1}-\lambda_k.
-\end{equation}
-
-The SSR is derived from the KKT condition and the "unit-slope" assumption.
-In (2), if we denote the left-hand-side as $c_j(\lambda)=x_j^Tr(\lambda)/n$, then the "unit-slope" assumption assumes a unit bound on the slope of $c_j(\lambda)$ over $\lambda$.
-That is:
-
-\begin{equation}
-    |c_j(\lambda)-c_j(\lambda')|\leq |\lambda-\lambda'|,\qquad \forall \lambda,\lambda'\in(0,\lambda_0].
-\end{equation}
-
-Under this condition and (4), using triangle inequality, $c_j(\lambda_k)$ can be bounded as the following:
-
-\begin{equation}
-    \begin{split}
-        |c_j(\lambda_{k+1})| &\leq |c_j(\lambda_{k+1})-c_j(\lambda_k)| + |c_j(\lambda_k)|\\
-    &< \lambda_k - \lambda_{k+1} + (2\lambda_{k+1}-\lambda_k)\\
-    &=\lambda_{k+1},
-    \end{split}
-\end{equation}
-and then KKT conditions (2) guarantees $\hat{\beta}_j(\lambda_{k+1})=0$.
-
-The biggest problem of SSR is that the "unit-slope" condition (5) may not hold and thus discarded features are not guaranteed to have zero coefficients.
-A post-convergence KKT check is needed for the discarded features to make sure their coefficients are truly zero.
-If violations occur, we need to refit the model adding the violating features and repeat the post-convergence check.
-The cost for each post-convergence check is O(np) and especially costly when violations occur.
-However, previous studies have shown that violations are rare and thus additional cost is acceptable.
-
-A nice property about SSR with post-convergence check is that some quantities can be reused.
-When doing post-convergence check at $\lambda_k$, $x_j^Tr(\lambda_k)/n$ is calculated in (2).
-Then in SSR screening at $\lambda_{k+1}$ (4), this quantity is used again.
-In fact, when the quantity $x_j^Tr(\lambda_k)/n$ is already computed, other parts of the computation of (4) have almost zero cost.
-In conclusion, the computation cost of SSR is generally only the cost of the post-convergence check, which is O(npK).
-
-\subsection{Safe rules}
-
-Compared to strong rules, safe rules can discard features safely.
-Those discarded features are guaranteed to have zero coefficients and we do not need an addition check to validate them.
-We will mainly focus on enhanced dual polytope projections (EDPP) rules\cite{wang2013lasso}, because they outperform other current safe rules and are easy to incorporate in our method.
-
-The EDPP rules are derived from the dual formulation of the lasso problem (1):
-
-\begin{equation}
-    \begin{split}
-        \hat{\theta}(\lambda) = \underset{\theta\in \mathbb{R}^n}{\mathrm{argmax}}\frac{1}{2n}||y||_2^2-\frac{n\lambda}{2}||\theta-\frac{y}{n\lambda}||_2^2\\
-        \textrm{subject to } |x_j^T\theta|\leq 1,\quad \forall j=1,2,...,p.
-    \end{split}
-\end{equation}
-This is minimizing the distance between $\theta$ and the rescaled response $\frac{y}{n\lambda}$ subject to the conditions $|x_j^T\theta|\leq 1$.
-Geometrically $\hat{\theta}(\lambda)$ can be viewed as the projection of the rescaled response $\frac{y}{n\lambda}$ onto the polytope defined by $|x_j^T\theta|\leq 1$.
-As $\lambda$ decreases alone the solution path, the rescaled response $\frac{y}{n\lambda}$ moves further away from 0 and the projection $\hat{\theta}(\lambda)$ moves with it.
-Because $\hat{\theta}(\lambda)$ is a projection onto a non-empty closed convex set, the movement of the projection can be bounded and thus $\hat{\theta}(\lambda)$ can be bounded given some previous solution $\hat{\theta}(\lambda')$ at some $\lambda'>\lambda$.
-
-In fact, the solution of the primal problem (1) and the solution of the dual problem (7) can be linked by:
-\begin{equation}
-    \hat{\theta}(\lambda)=\frac{y-X\hat{\beta}(\lambda)}{n\lambda}=\frac{r(\lambda)}{n\lambda},
-\end{equation}
-so bounding $\hat{\theta}(\lambda)$ is essentially bounding the residual vector $r(\lambda)$.
-Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\cite{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\cite{zeng2017efficient}:
-
-\begin{theorem}[BEDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$. Under (2) and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
-    \begin{equation}
-        |(\lambda_0+\lambda)x_j^Ty-(\lambda_0-\lambda)sign(x_*^Ty)\lambda_0x_j^Tx_*|<2n\lambda_0\lambda-(\lambda_0-\lambda)\sqrt{n||y||_2^2-n^2\lambda_0^2}.
-    \end{equation}
-\end{theorem}
-
-\begin{theorem}[SEDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
-    \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then $\hat{\beta}_j(\lambda_{k+1})=0$ if
-        \begin{equation}
-            \begin{split}
-                &\left|2\lambda_{k+1}x_j^Tr(\lambda_k)+(\lambda_k-\lambda_{k+1})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_k)x_j^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\\&<2n\lambda_k\lambda_{k+1}-(\lambda_k-\lambda_{k+1})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
-            \end{split}
-        \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, SEDPP rule reduces to BEDPP rule. $\hat{\beta}_j(\lambda_1)=0$ if (9) holds with $\lambda=\lambda_1$.
-    \end{enumerate}
-\end{theorem}
-
-In BEDPP rule (9), the most costly parts of computation that take O(np) time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
-These quantities does not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
-After this step is finished, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with O(np) cost.
-
-In SEDPP rule (10), it requires computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ ($x_j^T\hat{y}(\lambda_k)$ can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$).
-For screening at every $\lambda_{k+1}$, $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ need to be recalculated and this step takes O(np) time.
-Thus SEDPP is a sequential rule and computation of the sequence takes O(npK) time.
-
-BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ by comparing it to $r(\lambda_0)=y$.
-As $\lambda_k$ gets further away from $\lambda_0$, this bound becomes less precise and the screening rule becomes less powerful.
-SEDPP is slower, but at each $\lambda_{k+1}$, it is comparing $r(\lambda_{k+1})$ to $r(\lambda_k)$.
-Because $\lambda_{k+1}$ and $\lambda_k$ are close, the bound will be tight and screening will keep being powerful.
-
-\subsection{Hybrid safe-strong rules}
-
-The hybrid safe-strong rules (HSSR) \cite{zeng2017efficient} was proposed to combine SSR with any member of safe rules to take advantage of both.
-More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments.
-This algorithm discards features that are discarded by either SSR or BEDPP rule.
-Then, when doing post-convergence check, it only checks features that are discarded by SSR but not discarded by BEDPP rule, instead of all features that are discarded by SSR.
-
-BEDPP rule is fast because heavy computation only occurs at the first step.
-SSR only requires heavy computation at the post-convergence check step.
-Now the set of features that need a post-convergence check is narrowed down by BEDPP rule and thus the cost of the post convergence check is reduced directly.
-Combining this two rules lead to a hybrid rule that outperforms using any screening rules alone in experiments.
-
-\subsection{Batch screening iterative lasso}
-
-Batch screening iterative lasso (BASIL) \cite{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches.
-Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at.
-First we do the screening for each $\lambda_{k+b}$ value in the batch based on solution at $\lambda_k$ by discarding the $j$-th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
-Then at each $\lambda_{k+b}$ value we solve the lasso problem with only the features that are not discarded.
-Last at post-convergence check, we search for largest $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that KKT conditions hold for solution at $\lambda_{k+b}$ and accept only the solution from $\lambda_{k+1}$ to $\lambda_{k+b}$.
-Next, we move to a new batch by replacing the batch head $k$ with $k+b$ and repeat the same procedure again.
-
-The BASIL is most beneficial when the whole $X$ matrix is to large to be fit into the RAM, thus we need to read in a small number of columns $x_j$ from the hard disk at a time.
-In the post-convergence check for every batch, for each $j$, $x_j$ only needs to be read in once and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$.
-Moreover, similar to SSR with ordinary post-convergence check, $x_j^Tr(\lambda_{x+b})$ computed at BASIL's post-convergence check step can be reused for screening at next batch.
-
-\section{Batched safe-strong rule}
-\label{sec:method}
-
-In this section, we will introduce the batched safe-strong rules, combine them with pathwise coordinate descent algorithm and propose a strategy to adaptively start new batches.
-
-\subsection{Batched EDPP rule}
-
-From the SEDPP rule (10) in Theorem 2.2, we can do screening at $\lambda_{k+1}$ given the solution at $\lambda_k$.
-Now consider we are solving the lasso problem along the path $\lambda_0,...,\lambda_k,\lambda_{k+2},...,\lambda_K$ instead.
-Using the SEDPP rule, we can do screening at $\lambda_{k+2}$ as well, given the solution at $\lambda_k$, which is considered the previous solution now.
-Similarly, given the solution at $\lambda_k$, we can do screening for a batch of $B$ $\lambda$-values: $\lambda_{k+1},...,\lambda_{k+B}$ and then all the discarded features are guaranteed to be zero.
-Batched EDPP is still a safe rule, but it is neither sequential nor one-step.
-
-Similar to SEDPP, the batched EDPP rule can be stated in the following theorem:
-
-\begin{theorem}[Batched EDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
-    \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some $B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
-        \begin{equation}
-            \begin{split}
-                &\left|2\lambda_{k+b}x_j^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_k)x_j^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\\&<2n\lambda_k\lambda_{k+b}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
-            \end{split}
-        \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some $B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
-        \begin{equation}
-        |(\lambda_0+\lambda_b)x_j^Ty-(\lambda_0-\lambda_b)sign(x_*^Ty)\lambda_0x_j^Tx_*|<2n\lambda_0\lambda_b-(\lambda_0-\lambda_b)\sqrt{n||y||_2^2-n^2\lambda_0^2}.
-    \end{equation}
-    \end{enumerate}
-\end{theorem}
-
-For each $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (11) or (12) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
-The most expensive computations are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, for $j=1,2,...,p$.
-$x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the batch and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that batch.
-These two computations take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
-
-Compared to sequential methods like SEDPP, the batched method only requires one $O(np)$ computation in one batch, while SEDPP requires one $O(np)$ computation for each $\lambda$-value.
-Compared to one-step methods like BEDPP, if the batch size is not too large, the solution at the batch head $\lambda_k$ and the solution at some $\lambda_{k+b}$ in the batch are usually relatively close, so screening at $\lambda_{k+b}$ using solution at $\lambda_k$ will remain powerful.
-For one-step method, as $\lambda_k$ gets further away from $\lambda_0$, the screening power can drop drastically and
-may not be any beneficial after that.
-
-\subsection{Batched strong rule after batched EDPP rule}
-
-Because HSSR \cite{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the batched EDPP rule screening.
-The batched SSR and batched EDPP rule combined will form our batched safe strong rule.
-
-For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (2).
-However, combined with safe rules, previous post-convergence check only needs to check features that are not discarded at the previous $\lambda$-value.
-Thus, for features that are discarded at the previous $\lambda$-value but not at the current $\lambda$-value, their corresponding $x_j^Tr(\lambda_k)$ have not been computed yet and thus cannot be used without additional cost.
-Similar to the idea of BASIL \cite{qian2019fast}, we can also do the strong rule screening in batches to reduce the number of required computations.
-
-We are going to combine batched EDPP rule and batched SSR to form the batch safe strong rule as following.
-First, we determine a batch $\lambda_{k+1},...,\lambda_{k+B}$, and both batched EDPP rule and batched SSR will be conducted in this batch.
-Second $x_j^Tr(\lambda_k)$ will be computed and stored.
-Then for each $\lambda_{k+b}$ in the batch, after doing batched EDPP rule screening, a batched SSR screening is carried out on the features that have not been discarded by batched EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
-Last, a post-convergence check is conducted on the features that were discarded by batched SSR but not discarded by batched EDPP rule.
-
-By choosing the same batch for batched EDPP rule and batched SSR, the quantity $x_j^Tr(\lambda_k)$ only needs to be computed once and can be used by both rules.
-Also, because batched EDPP rule can stay powerful, it keeps the set of features that require post-convergence check small, while because basic EDPP loses power for $\lambda$-values that are far away from $\lambda_0$, post-convergence check for HSSR will be more expensive.
-
-\subsection{Coordinate descent with batched safe strong rule}
-
-In this section, we will show the algorithm to do pathwise coordinate descent with our batched safe strong rule screening.
-We will only show the algorithm for solving one batch $\lambda_{k+1},...,\lambda_{k+B}$.
-After finishing this batch, we just need to start a new batch and apply the same algorithm using the output from last batch as input.
-Note here for the first batch with batch head $\lambda_0$, the residuals vector $r(\lambda_0)$ is just the response $y$, because all the $\hat{\beta}(\lambda_0)$ are zero.
-$\{x_j^Ty\}_{j=1}^p$ need to be computed at the beginning and stored for the whole path.
-
-\begin{algorithm}[H]
-    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Pre}{Pre-compute}\SetKwInOut{Initialize}{Initialize}
-    \SetAlgoLined
-    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p, \hat{\beta}(\lambda_k), r(\lambda_k), \lambda_{k+1},...,\lambda_{k+B}$}
-    \Pre{ $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$}
-    \BlankLine
-    \For{$b\xleftarrow{}$ 1 \KwTo B}{
-        Safe Screening: $\mathcal{S}_{k+b}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
-
-        Strong Screening: $\mathcal{R}_{k+b}\xleftarrow{}\{j\in \mathcal{S}_{k+b}:x_j$ not discarded by batched SSR$\}$.
-
-        \Initialize{$\hat{\beta}(\lambda_{k+b})=\hat{\beta}(\lambda_{k+b-1}), r(\lambda_{k+b})=r(\lambda_{k+b-1})$}
-
-        \Repeat{Post-convergence check passes}{
-            Pathwise coordinate descent in Algorithm 1 with only features in $\mathcal{R}_{k+b}$ and with warm start $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$, until converge.
-Save the outputs in $\hat{\beta}(\lambda_{k+b}), r(\lambda_{k+b})$.
-
-            Post-convergence check for all $j\in \mathcal{S}_{k+b}\setminus\mathcal{R}_{k+b}$,
-
-            \uIf{Post-convergence check does not pass}{
-                Add violating features to $\mathcal{R}_{k+b}$\;
-            }
-        }
-    }
-    \Output{$\{\hat{\beta}(\lambda_{k+b})\}_{b=1}^B, r(\lambda_{k+B})$}
-    \caption{Pathwise coordinate descent with batched safe strong rule screening}
-\end{algorithm}
-
-\subsection{Adaptive batched safe strong rule}
-
-In this section we will develop an algorithm to adaptively determining when to end the current batch and start a new batch, by evaluating screening power at previous $\lambda$-values in current batch.
-Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 2.
-Then we will propose an adaptive algorithm that can minimize the entire computation cost.
-
-\subsubsection{Complexity analysis}
-
-This complexity analysis will only consider calculations with $O(np)$ complexity.
-The rest calculations, those with $O(p)$ complexity for example, are not only faster in order, but also require no out-of-core computing.
-Calculation of ${x_j^Ty}_{j=1}^p$ is needed for pathwise coordinate descent in algorithm 1 and is not additional cost for screening, so it would not be considered either.
-We will assume that strong rule screening is always powerful in the sense that $|\mathcal{R}_b|=o(p)\approx0$, but safe rule screening may not.
-We also assume that post-convergence check will mostly pass in the first iteration and thus is only needed approximately once per $\lambda$-value.
-
-Under these assumptions, there are two dominating parts in the algorithm for each batch.
-First, the computation of $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ at the beginning of the batch, which requires $np$ multiplications.
-Then, for each $\lambda$-value $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_b\setminus\mathcal{R}_b|\approx|\mathcal{S}_b|$ KKT condition checks and each KKT condition check requires $n$ multiplications.
-These sum up to $n\sum_{b=1}^B|\mathcal{S}_b|$ multiplications.
-Combining these two parts, we will have the average cost per $\lambda$-value in the batch $\lambda_{k+1},...,\lambda_{k+B}$ to be
-
-\begin{equation}
-    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_b|}{B}.
-\end{equation}
-
-The first term is the average cost for safe screening.
-Increasing batch size $B$ means reusing calculation at the batch head more times for the safe screening and thus reducing the average cost.
-The second term is the average cost for KKT condition checking.
-As the batch size $B$ increases, safe rule screening becomes less powerful and the number of KKT condition checks required ($|\mathcal{S}_b|$) increases.
-The following plot illustrates the effect of $B$ on $|\mathcal{S}_b|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
-The y axis is the proportion of discarded features, calculated as $1-|\mathcal{S}_b|/p$.
-
-\begin{center}
-    \includegraphics[scale = 0.5]{plots/batchsizes.png}
-\end{center}
-
-BEDPP (Basic EDPP) rule is the special case of batched EDPP with only one batch of the largest possible size $B=K=100$.
-When the batch is large, the safe rule screening will eventually fail to discard any features and make the KKT condition checking cost increase to its maximum $np$.
-SEDPP rule is the special case where all batches have the smallest possible batch size $B=1$.
-It remains very powerful along the path, making the KKT condition checking cost almost 0, but the safe screening itself is costly and takes $np$ time per $\lambda$-value.
-Batched EDPP can strike a balance between BEDPP and SEDPP.
-In this example, using batches with fixed sizes $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
-
-This example also shows the performance of batch EDPP rule changes along the path of $\lambda$-values.
-Take the batched EDPP with $B=10$ as an example.
-For the first batch of 10 $\lambda$-values, the batched EDPP stays powerful even at the end, which means this batch is still exploitable.
-We may want to extend this batch to reduce average safe screening cost without harming the KKT condition checking cost much.
-For the last batch however, the screening power is close to 0 for the last few $\lambda$-values, which means this batch becomes useless at this point.
-Starting a new batch earlier can greatly reduce the KKT condition checking cost with relatively small increase in safe screening cost.
-Also, the performance of batch EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
-These suggest that starting a new batch after every fixed number of $\lambda$-values cannot not be consistently efficient and we want a method that can automatically determine whether to start a new batch given current performance.
-
-\subsubsection{Adaptive batch starting algorithm}
-
-From previous example, we assume the average cost is a convex function of batch size $B$ which decreases first and then after some optimal value increases again.
-If we want to minimize the average cost per $\lambda$-value, we need to end the current batch when extending the current batch by 1 $\lambda$-value will increase the average cost.
-That is, end the current batch at $\lambda_{B-1}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$.
-From (13), this condition will be:
-
-\begin{equation}
-    (B-1)|\mathcal{S}_B|-\sum_{b=1}^{B-1}|\mathcal{S}_b|>p.
-\end{equation}
-In practice, we will end the batch at $\lambda_B$ and start at $\lambda_{B+1}$ instead, because evaluating $\mathcal{S}_B$ needs screening at $\lambda_B$ and if we have already done the screening, it would be a waste not to use the screening result.
-
-This batch restarting condition is a greedy condition that only considers the current batch cost.
-In practice, we cannot know about future batches so this is the most reasonable condition.
-In fact, it can handle the three most common scenarios well.
-First, if the screening power stays high, meaning $\mathcal{S}_b$ is small for all $b$, then the left-hand-side of (14) will be small and thus at this point we will extend the current batch to further exploit it.
-Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_B$ is large but $\mathcal{S}_b$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (14) will be large and we will end the useless current batch and start a new batch.
-Last, if the screening power drops dramatically right after the beginning of the current batch, meaning $\mathcal{S}_b$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (14) will be approximately $p-|\mathcal{S}_1|<p$.
-We will not end the current batch although it becomes useless, because if we did, the next batch would be useless as well.
-
-Combined with Algorithm 2, we will propose the pathwise coordinate descent with adaptive batched safe strong rule screening.
-After ending a batch, if there are still unsolved $\lambda$-values in the path $\lambda_0,\lambda_1,...,\lambda_K$, we can just start a new batch with the rest unsolved $\lambda$-values and apply the same algorithm.
-
-\begin{algorithm}[H]
-    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Pre}{Pre-compute}\SetKwInOut{Initialize}{Initialize}
-    \SetAlgoLined
-    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p, \hat{\beta}(\lambda_k), r(\lambda_k), \lambda_{k+1},...,\lambda_{K}$}
-    \Pre{ $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$}
-    \BlankLine
-    $B\xleftarrow{}1$
-
-    \Repeat{$(B-1)|\mathcal{S}_B|-\sum_{b=1}^{B-1}|\mathcal{S}_{b}|>p$ or $B>K$}{
-        Safe Screening: $\mathcal{S}_{k+B}\xleftarrow{}\{j:x_j$ not discarded by batched EDPP rule$\}$.
-
-        Strong Screening: $\mathcal{R}_{k+B}\xleftarrow{}\{j\in \mathcal{S}_{k+B}:x_j$ not discarded by batched SSR$\}$.
-
-        \Initialize{$\hat{\beta}(\lambda_{k+B})=\hat{\beta}(\lambda_{k+B-1}), r(\lambda_{k+B})=r(\lambda_{k+B-1})$}
-
-        \Repeat{Post-convergence check passes}{
-            Pathwise coordinate descent in Algorithm 1 with only features in $\mathcal{R}_{k+B}$ and with warm start $\hat{\beta}(\lambda_{k+B}), r(\lambda_{k+B})$, until converge.
-Save the outputs in $\hat{\beta}(\lambda_{k+B}), r(\lambda_{k+B})$.
-
-            Post-convergence check for all $j\in \mathcal{S}_{k+B}\setminus\mathcal{R}_{k+B}$,
-
-            \uIf{Post-convergence check does not pass}{
-                Add violating features to $\mathcal{R}_{k+B}$\;
-            }
-        }
-        $B\xleftarrow{}B+1$
-    }
-    \Output{$\{\hat{\beta}(\lambda_{k+b})\}_{b=1}^B, r(\lambda_{k+B}),\lambda_{k+B+1},...,\lambda_K$}
-    \caption{Pathwise coordinate descent with adaptive batched safe strong rule screening}
-\end{algorithm}
-
-\section{Extension to other lasso type problems}
-\label{sec:4}
-
-The structure of the batched safe strong rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
-We are going to derive the extensions to two lasso type problems and show these extensions improve computation efficiency.
-
-\subsection{Batched safe strong rule for sparse logistic regression}
-
-The sparse logistic regression model can be defined as:
-
-\begin{equation}
-    \hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}-\frac{1}{n}\sum_{i=1}^n\{y_i\log\pi_i(\beta)+(1-y_i)\log(1-\pi_i(\beta))\}+\lambda||\beta||_1,
-\end{equation}
-where $\pi(\beta)=\{\pi_i(\beta)\}_{i=1}^n=\{p(y_i=1|x_{i1},x_{i2},...,x_{ip})\}_{i=1}^n=\{e^{\eta_i(\beta)}/(1+e^{\eta_i(\beta)})\}_{i=1}^n$ is the predicted value vector and $\eta(\beta)=X\beta$ is the linear function.
-$X$ are still the $n\times p$ standardized feature matrix but in this model the $y\in\{0,1\}^n$ is an unstandardized binary response vector.
-$\beta$ is still the $p\times1$ coefficient vector but we also need a $\beta_0$ as the intercept.
-
-We can use SSR to do the strong rule screening with a small change according to the KKT condition.
-The residual vector now is $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
-Then the SSR discards the $j$-th feature at $\lambda_{k+1}$ if (4) holds.
-
-For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\cite{wang2014safe} is used.
-It was proposed as a one-step rule but we will extend it to a batched rule.
-Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
-
-\begin{theorem}[Batched Slores]
-For the sparse logistic regression model (15), let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$.
-Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-$\forall\theta\in(0,1)^n$, let $x_*=argmax_{x_j}|x_j^Ty/n|$ and
-
-\begin{equation}
-    \begin{split}
-        g(\theta)&=\frac{1}{n}\sum_{i=1}^n\{\theta_i\log \theta_i+(1-\theta_i)\log(1-\theta_i)\},\\
-    \nabla g_i(\theta) &= \frac{1}{n}\log\frac{\theta_i}{1-\theta_i}.
-    \end{split}
-\end{equation}
-
-Under condition (2) except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
-For some $B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, let
-
-\begin{equation}
-    R(\lambda_{k+b})=\sqrt{\frac{n}{2}\bigg[g\bigg(\frac{\lambda_{k+b}}{\lambda_k}\theta(\lambda_k)\bigg)-g\bigg(\theta(\lambda_k)\bigg)+\bigg(1-\frac{\lambda_{k+b}}{\lambda_k}\bigg)\bigg(\nabla g\big(\theta(\lambda_k)\big)\bigg)^T\theta(\lambda_k)\bigg]},
-\end{equation}
-
-$d(\lambda_{k+b})=\sqrt{n}(\lambda_k-\lambda_{k+b})/R(\lambda_{k+b})$. For $\xi = -1,1$ and $j=1,2,...,p$,
-
-\begin{enumerate}
-    \item If $-\xi sign(x_*^Ty)x_j^Tx_*\geq nd(\lambda_{k+b})$, then
-
-    \begin{equation}
-        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=\sqrt{n}R(\lambda_{k+b})-\xi x_j^Tr(\lambda_k);
-    \end{equation}
-
-    \item If $-\xi sign(x_*^Ty)x_j^Tx_*< nd(\lambda_{k+b})$, then
-
-    \begin{equation}
-        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=R(\lambda_{k+b})\sqrt{n+nu_\xi^2-2\xi u_\xi sign(x_*^Ty)x_j^Tx_*}-nu_\xi(\lambda_k-\lambda_{k+b})-\xi x_j^Tr(\lambda_k),
-    \end{equation}
-    where
-    \begin{align}
-        u_\xi&=\frac{-\xi a_1+\sqrt{\Delta}}{2a_2},\\
-        a_0&=(x_j^Tx_*)^2-n^2d^2(\lambda_{k+b}),\nonumber\\
-        a_1&=-2n\,sign(x_*^Ty)x_j^Tx_*\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
-        a_2&=n^2\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
-        \Delta&=a_1^2-4a_0a_1.\nonumber
-    \end{align}
-\end{enumerate}
-
-Then $\hat{\beta}_j(\lambda_{k+b})=0$ if
-        \begin{equation}
-            \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))
-        \end{equation}
-\end{theorem}
-
-When computing the batched Slores, $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ need to be computed only once, stored and reused for the whole solution path $\lambda_0>\lambda_1>...>\lambda_K$.
-Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed once for each batch.
-Thus algorithm 3 for adaptive batched safe strong rule can be done with Slores rule instead of EDPP rule to do screening for sparse logistic regression model.
-
-\subsection{Batched safe strong rule for group lasso}
-
-The group lasso problem \cite{yuan2006model} can be defined as:
-
-\begin{equation}
-    \hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}\bigg|\bigg|y-\sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2+\lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_1,
-\end{equation}
-where $\beta=(\beta_1^T,...,\beta_G^T)^T$, $X_g$ is a $n\times p_g$ sub-matrix consisting of columns of $X$ corresponding to features in group $g$, $g=1,2,...,G$.
-Besides standardization in (2), we apply an addition level of standardization at the group level\cite{breheny2015group}:
-
-\begin{equation}
-    X_g^TX_g=nI_{p_g\times p_g},\qquad g=1,2,...,G.
-\end{equation}
-
-According to the KKT condition, we can use SSR to do strong rule screening.
-Given $r(\lambda_k)=y-\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, we discard features in the $g$-th group at $\lambda_{k+1}$ if:
-
-\begin{equation}
-    \bigg|\bigg|\frac{1}{n}X_g^Tr(\lambda_k)\bigg|\bigg|_2<\sqrt{p_g}(2\lambda_{k+1}-\lambda_k).
-\end{equation}
-
-For safe rule screening, we have SEDPP for group lasso\cite{wang2013lasso} and we can extend it the batched EDPP rule for group lasso.
-
-\begin{theorem}[Batched EDPP for group lasso]
-For the group lasso problem (22), let $\lambda_0:=\max_j\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$.
-Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-Under condition (2) and (23)
-    \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for some $B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
-        \begin{equation}
-            \begin{split}
-                &\left|\left|2\lambda_{k+b}X_g^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( X_g^Ty-\frac{y^T\hat{y}(\lambda_k)X_g^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\right|_2\\
-                &<2n\lambda_k\lambda_{k+b}\sqrt{p_g}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
-            \end{split}
-        \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for some $B$ and any $b$ s.t.
-$0<b\leq B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
-        \begin{equation}
-        \left|\left|(\lambda_0+\lambda_b)X_g^Ty-(\lambda_0-\lambda_b)X_g^TX_*X_*^Ty\right|\right|_2<2n\lambda_0\lambda_b\sqrt{p_g}-(\lambda_0-\lambda_b)\sqrt{n||y||_2^2-n^2\lambda_0^2p_*}.
-    \end{equation}
-    \end{enumerate}
-\end{theorem}
-
-Similar to Batched EDPP rule, three expensive computations are $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$ and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
-The first and second only need to be computed once for the whole solution path.
-The last only needs to be computed once per batch with cost $O(np)$.
-
-\section{Experiments}
-\label{sec:5}
-
-\subsection{Simulations}
-\label{sec:sim}
-\begin{itemize}
-    \item Introduction to biglasso package
-\end{itemize}
-\begin{itemize}
-    \item Comparing active set cycling, strong rules, SEDPP, Hybrid SSR, and proposed Batched SSR
-    \item Varying n, p. Computation time for all methods grow linearly and ratios among them are constant.
-    \item Varying signal-noise ratio. As the signal increases, the proposed method has larger advantage over other method.
-    \item Varying $||\beta||_0$, number of non-zero coefficients, or sparsity. When the model is sparser, the proposed method has larger advantage over other methods.
-\end{itemize}
-
-\subsection{Real data analysis}
-\label{sec:real-data}
-
-\subsection{Big data performance}
-
-\begin{itemize}
-    \item Analyse and profile different methods. Compare them in big data case ?
-\end{itemize}
-
-\section{Conclusion}
-\label{sec:6}
-
-\bibliographystyle{unsrt}
 \bibliography{ref}

### 2020-09-18 main.tex
Splitting into header and content files
Updates from Overleaf

@@
 \begin{itemize}
-    \item A new feature screening framework (Section ?3.2??), which updates the reference for screening alone the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
-    \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section ?3.4,4.1??).
+    \item A new feature screening framework (Section 3.1,3.2), which updates the reference for screening alone the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
+    \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section 3.4,4.1,4.2).
     \item An algorithm to determine when to update to a new reference $\lambda$ value for best efficiency (Section \ref{sec:adaptive}).
@@
 
-Pathwise coordinate descent is a popular algorithm fitting a solution path for lasso problem.
-For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using Algorithm~\ref{Alg:pathwise-coordinate-descent}.
-Note that the algorithm uses the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in obtaining the next solution along the path, a strategy known as a ``warm start''.
-
-\begin{algorithm}[H]\label{Alg:pathwise-coordinate-descent}
-    \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Initialize}{Initialize}
-    \SetAlgoLined
-    \Input{$\hat{\beta}(\lambda_k), \{x_j\}_{j=1}^p, r(\lambda_k)$}
-    \Initialize{ $r = r(\lambda_k),\hat{\beta} = \hat{\beta}(\lambda_k)$}
-    \BlankLine
-    \While{not converged}{
-        \For{$j \xleftarrow{}$ 1 \KwTo p}{
-            $z_j\xleftarrow{}\hat{\beta} + x_j^Tr/n$\;
-            \uIf{$z_j > \lambda$}{
-                $\beta_j^{new}\xleftarrow{} z_j-\lambda$\;
-            }\uElseIf{$z_j < -\lambda$}{
-                $\beta_j^{new}\xleftarrow{} z_j+\lambda$\;
-            }\Else{
-                $\beta_j^{new}\xleftarrow{} 0$\;
-            }
-            $r\xleftarrow{}r-(\beta_j^{new}-\hat{\beta}_j)x_j$\;
-            $\hat{\beta}_j\xleftarrow{}\beta_j^{new}$\;
-        }
-    }
-    \Output{$\hat{\beta}(\lambda_{k+1})\xleftarrow{}\hat{\beta},r(\lambda_{k+1})\xleftarrow{}r$}
-    \caption{Pathwise coordinate descent with warm start $\hat{\beta}(\lambda_k),r(\lambda_k)$}
-\end{algorithm}
+ Pathwise algorithms are developed to address the challenge of the sequence with a strategy known as the ``warm start''.
+For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in the algorithm.
+Pathwise coordinate descent is a popular pathwise algorithm fitting a solution path for lasso problem and will be used as the lasso algorithm for the rest of the paper.
 
@@
 
-The SSR is derived from the KKT condition and the "unit-slope" assumption.
-In (2), if we denote the left-hand-side as $c_j(\lambda)=x_j^Tr(\lambda)/n$, then the "unit-slope" assumption assumes a unit bound on the slope of $c_j(\lambda)$ over $\lambda$.
-That is:
+The SSR is derived from the KKT condition and the "unit-slope" assumption that the size of the slope of $x_j^Tr(\lambda)/n$ over $\lambda$ is bounded by 1.
 
-\begin{equation}
-    |c_j(\lambda)-c_j(\lambda')|\leq |\lambda-\lambda'|,\qquad \forall \lambda,\lambda'\in(0,\lambda_0].
-\end{equation}
-
-Under this condition and (4), using triangle inequality, $c_j(\lambda_k)$ can be bounded as the following:
-
-\begin{equation}
-    \begin{split}
-        |c_j(\lambda_{k+1})| &\leq |c_j(\lambda_{k+1})-c_j(\lambda_k)| + |c_j(\lambda_k)|\\
-    &< \lambda_k - \lambda_{k+1} + (2\lambda_{k+1}-\lambda_k)\\
-    &=\lambda_{k+1},
-    \end{split}
-\end{equation}
-and then KKT conditions (2) guarantees $\hat{\beta}_j(\lambda_{k+1})=0$.
-
-The biggest problem of SSR is that the "unit-slope" condition (5) may not hold and thus discarded features are not guaranteed to have zero coefficients.
+The biggest problem of SSR is that the "unit-slope" assumption may not hold and thus discarded features are not guaranteed to have zero coefficients.
 A post-convergence KKT check is needed for the discarded features to make sure their coefficients are truly zero.
@@
 
-A nice property about SSR with post-convergence check is that some quantities can be reused.
-When doing post-convergence check at $\lambda_k$, $x_j^Tr(\lambda_k)/n$ is calculated in (2).
-Then in SSR screening at $\lambda_{k+1}$ (4), this quantity is used again.
-In fact, when the quantity $x_j^Tr(\lambda_k)/n$ is already computed, other parts of the computation of (4) have almost zero cost.
+A nice property about SSR with post-convergence check is the quantity $x_j^Tr(\lambda_k)/n$ is calculated at $\lambda_k$ in (2) during post-convergence check.
+Then in SSR screening at $\lambda_{k+1}$ (4), this quantity is reused.
+Besides the quantity $x_j^Tr(\lambda_k)/n$, other parts of the computation of (4) have almost zero cost.
 In conclusion, the computation cost of SSR is generally only the cost of the post-convergence check, which is O(npK).
@@
 
-The EDPP rules are derived from the dual formulation of the lasso problem (1):
-
-\begin{equation}
-    \begin{split}
-        \hat{\theta}(\lambda) = \underset{\theta\in \mathbb{R}^n}{\mathrm{argmax}}\frac{1}{2n}||y||_2^2-\frac{n\lambda}{2}||\theta-\frac{y}{n\lambda}||_2^2\\
-        \textrm{subject to } |x_j^T\theta|\leq 1,\quad \forall j=1,2,...,p.
-    \end{split}
-\end{equation}
-This is minimizing the distance between $\theta$ and the rescaled response $\frac{y}{n\lambda}$ subject to the conditions $|x_j^T\theta|\leq 1$.
-Geometrically $\hat{\theta}(\lambda)$ can be viewed as the projection of the rescaled response $\frac{y}{n\lambda}$ onto the polytope defined by $|x_j^T\theta|\leq 1$.
-As $\lambda$ decreases alone the solution path, the rescaled response $\frac{y}{n\lambda}$ moves further away from 0 and the projection $\hat{\theta}(\lambda)$ moves with it.
-Because $\hat{\theta}(\lambda)$ is a projection onto a non-empty closed convex set, the movement of the projection can be bounded and thus $\hat{\theta}(\lambda)$ can be bounded given some previous solution $\hat{\theta}(\lambda')$ at some $\lambda'>\lambda$.
-
-In fact, the solution of the primal problem (1) and the solution of the dual problem (7) can be linked by:
-\begin{equation}
-    \hat{\theta}(\lambda)=\frac{y-X\hat{\beta}(\lambda)}{n\lambda}=\frac{r(\lambda)}{n\lambda},
-\end{equation}
-so bounding $\hat{\theta}(\lambda)$ is essentially bounding the residual vector $r(\lambda)$.
+The EDPP rules are derived from the dual formulation of the lasso problem and provide a bound for the residual vector $r(\lambda)$.
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
@@
 
-In BEDPP rule (9), the most costly parts of computation that take O(np) time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
+In BEDPP rule (4), the most costly parts of computation that take O(np) time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
 These quantities does not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
-After this step is finished, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with O(np) cost.
+After this step, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with O(np) cost.
 
-In SEDPP rule (10), it requires computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ ($x_j^T\hat{y}(\lambda_k)$ can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$).
+In SEDPP rule (5), it requires computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ ($x_j^T\hat{y}(\lambda_k)$ can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$).
 For screening at every $\lambda_{k+1}$, $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ need to be recalculated and this step takes O(np) time.
@@
 
-\subsection{Adaptive EDPP safe rule}
+\subsection{Adaptive safe rule}
 
-From the SEDPP rule (10) in Theorem 2.2, we can do screening at $\lambda_{k+1}$ given the solution at $\lambda_k$.
+From the SEDPP rule (6) in Theorem 2.2, we can do screening at $\lambda_{k+1}$ given the solution at $\lambda_k$.
 Now consider we are solving the lasso problem along the path $\lambda_0,...,\lambda_k,\lambda_{k+2},...,\lambda_K$ instead.
@@
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some $B$ and any $b$ s.t.
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some update point $k+B$ and any $b$ s.t.
 $k<k+b\leq k+B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
@@
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some $B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some update point $k+B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
         \begin{equation}
@@
 
-For each $\lambda$-value in one update $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (11) or (12) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
+For each $\lambda$-value in one update $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (7) or (8) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
 The most expensive computations are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, for $j=1,2,...,p$.
 $x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the update and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that update.
-These two computations take $O(np)$ time and the rest computation in (11) and (12) take at most a lower order of $O(p)$ time.
+These two computations take $O(np)$ time and the rest computation in (7) and (8) take at most a lower order of $O(p)$ time.
 
@@
 
-\subsection{Adaptive safe strong rule on top of adaptive EDPP rule}
+\subsection{Adaptive safe strong rule on top of adaptive safe rule}
 
@@
 
-In this section we will fill in line 11 in Algorithm 2.
+In this section we will fill in line 11 in Algorithm 1.
 We will develop an algorithm to adaptively determining when update the reference for screening, by evaluating screening power at previous $\lambda$-values since the last update.
-Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 2.
+Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 1.
 Then we will propose an adaptive algorithm that can minimize the entire computation cost.
@@
 
-To better illustrate this two effects, we considered the most naive and simple updating scheme: update the reference periodically after every other $B$ $\lambda$ values.
+To better illustrate these two effects, we considered the most naive and simple updating scheme: update the reference periodically after every other $B$ $\lambda$ values.
 The following plot illustrates the effect of update delay $B$ on $|\mathcal{S}_{k+b}|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
@@
 These two conditions should be close and thus this substitution should also be close to optimal.
-From (13), the latter condition will be:
+Combined with (9), the latter condition will be:
 
@@
 In fact, it provides a robust strategy towards three most common scenarios.
-First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of (14) will be small and thus at this point we will not update to further exploit the last update.
-Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (14) will be large and we will update the useless old reference to a new helpful one.
-Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (14) will be approximately $p-|\mathcal{S}_1|<p$.
+First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of (10) will be small and thus at this point we will not update to further exploit the last update.
+Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (10) will be large and we will update the useless old reference to a new helpful one.
+Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (10) will be approximately $p-|\mathcal{S}_1|<p$.
 We will not update although old reference is useless, because if we did, the new update would become useless quickly as well.
 
-This adaptive updating condition fills in the condition on line 11 in Algorithm 2 and forms a complete pathwise lasso algorithm with adaptive safe strong screening.
+This adaptive updating condition fills in the condition on line 11 in Algorithm 1 and forms a complete pathwise lasso algorithm with adaptive safe strong screening.
 
@@
 Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed at the time of each update.
-Thus algorithm 2 for adaptive safe strong rule can be done with Slores rule instead of EDPP rule to form Ada-SSR-Slores that does screening for sparse logistic regression model.
+Thus algorithm 1 for adaptive safe strong rule can be done with Slores rule instead of EDPP rule to form Ada-SSR-Slores that does screening for sparse logistic regression model.
 

### 2020-09-19 main.tex
Update plots

@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-\usepackage{geometry}
-\geometry{margin=1in}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage[ruled,vlined, linesnumbered]{algorithm2e}
-\usepackage[english]{babel}
-\usepackage[nottoc]{tocbibind}
-\usepackage{color}
-\usepackage{natbib}
-\usepackage{graphicx}
-\usepackage{float}
-\newtheorem{theorem}{Theorem}[section]
-\bibliographystyle{abbrvnat}
-% Custom commands / shortcuts
-\providecommand{\sign}{\textrm{sign}}
-\providecommand{\note}[1]{\textcolor{red}{#1}}
-\providecommand{\lam}{\lambda}
-
-\title{Adaptive Safe Strong Screening for Efficient Lasso-Type
-Problems Optimization over the Solution Path}
-\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
-  \and
-  Patrick Breheny\\Department of Biostatistics\\University of Iowa}
-\date{}
-
-\begin{document}
-
-\maketitle
-
 \section{Introduction}
@@
     \centering
-    \includegraphics[scale = 0.5]{plots/batchsizes.png}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
+    \includegraphics[scale = 0.6]{plots/batchsizes.pdf}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
     \label{fig:3.4.1}

### 2020-09-25 main.tex
Rename to adaptive hybrid rule

@@
 Because the optimal value of $\lambda$ is not known in advance, typical practice is to solve for $\beta$ along a sequence of values of the tuning parameter $\lambda$, known as the solution path.
-Pathwise algorithms can be efficiently implemented by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.
+Pathwise algorithms can be efficiently implemented to address this challenge, by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.
 In particular, the pathwise coordinate descent algorithm\citep{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS (least angle regression)\citep{efron2004least}, especially in high dimensional settings where $p$ is large.
@@
 In reality, we cannot know this prior to fitting the model -- however, through the clever use of feature screening rules, we can greatly reduce the number of times inactive features are read into memory, thereby minimizing the computational burden.
+There are many screening techniques where the solution obtained after screening will still be the global optimum given it exists, and in this paper we will only focus on this type of screening.
 In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision and a decision is made for each $\lambda$ values: for example, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
@@
 Previous safe screening rules can also be divided into two categories, sequential rules and one-step rules, by how the screening is carried out along the path of $\lambda$ values.
-Sequential rules do heavy computation for each $\lambda$ values using solution from its previous $\lambda$ value, so they are slower but relatively powerful at each $\lambda$ values.
-One-step rules only require heavy computation at the beginning and thus are faster but they cannot remain powerful along the path for long.
+Sequential rules address the challenge of the solution path and do screening for each $\lambda$ values using solution from its previous $\lambda$ value, so they require heavy computation but are relatively powerful, at each $\lambda$ values.
+One-step rules only require heavy computation at the beginning and thus are faster but they cannot remain powerful along the path for long because they don't utilize previous solution.
 
@@
 It will be shown that our adaptive rule can greatly reduce the computation time and outperform other methods under all scenarios.
-Following the hybrid approaches, we also combined our approach with strong rules to form adaptive safe strong rules.
-Similar to hybrid approaches, our method can also utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
+Following the hybrid approaches, we also combined our approach with strong rules to form adaptive hybrid rules.
+Our method can utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
 For example we extended the method to work with logistic regression with lasso penalty and group lasso.
@@
 
-Throughout this paper, it will be assumed that $y$ is centeredand $\{x_j\}_{j=1}^p$ are centered and standardized:
+Throughout this paper, it will be assumed that $y$ is centered and $\{x_j\}_{j=1}^p$ are centered and standardized:
 \begin{equation}
@@
 
- Pathwise algorithms are developed to address the challenge of the sequence with a strategy known as the ``warm start''.
+ Pathwise algorithms are developed to address the challenge of the solution path with a strategy known as the ``warm start''.
 For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in the algorithm.
@@
 However, when fitting a solution path, residuals at previous $\lambda$-values provide information about residuals at the next $\lambda$-value and thus be used for screening.
-Note that in Algorithm~\ref{Alg:pathwise-coordinate-descent}, the residuals $r$ are computed at each $\lambda$-value and can thus be conveniently reused for the purpose of feature screening.
+Note that if we have $\lambda_0=\max_j|x_j^Ty/n|$ and $\hat{\beta}(\lambda_0)=0$, then $r(\lambda_0)=y$ satisfies the KKT conditions and thus $\hat{\beta}(\lambda_0)=0$ is the optimal solution.
 
@@
 
-\section{Adaptive safe-strong rule}
+\section{Adaptive hybrid rule}
 \label{sec:method}
 
-In this section, we will introduce the framework of adaptive safe-strong rules, implement them with EDPP as the safe rule to form Ada-SSR-EDPP and propose a strategy to adaptively updating the reference.
+In this section, we will introduce the framework of adaptive hybrid rules, implement them with EDPP as the safe rule to form Ada-SSR-EDPP and propose a strategy to adaptively updating the reference.
 
@@
 
-\subsection{Adaptive safe strong rule on top of adaptive safe rule}
+\subsection{Adaptive hybrid rule on top of adaptive safe rule}
 
 Because HSSR \citep{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
-The SSR and adpative EDPP rule combined will form our adaptive safe strong rule: Ada-SSR-EDPP.
+The SSR and adpative EDPP rule combined will form our adaptive hybrid rule: Ada-SSR-EDPP.
 
@@
 
-\subsection{Pathwise lasso algorithm with adaptive safe strong rule}
+\subsection{Pathwise lasso algorithm with adaptive hybrid rule}
 
-In this section, we will show the algorithm to solve the lasso problem over the solution path with pathwise coordinate descent algorithm and our adaptive safe strong screening rule.
+In this section, we will show the algorithm to solve the lasso problem over the solution path with pathwise coordinate descent algorithm and our adaptive hybrid screening rule.
 The pathwise coordinate descent algorithm can be substituted by any other pathwise lasso algorithms and the adaptive EDPP can also be substituted by any other adaptive safe rules in our framework.
@@
     \Output{$\{\hat{\beta}(\lambda_{k})\}_{k=1}^K, r(\lambda_{k+B})$}
-    \caption{Pathwise lasso algorithm with adaptive safe strong rule screening}
+    \caption{Pathwise lasso algorithm with adaptive hybrid rule screening}
 \end{algorithm}
@@
 These two conditions should be close and thus this substitution should also be close to optimal.
-Combined with (9), the latter condition will be:
+Combined with (9), the latter condition will approximately be:
 
@@
 
-This adaptive updating condition fills in the condition on line 11 in Algorithm 1 and forms a complete pathwise lasso algorithm with adaptive safe strong screening.
+This adaptive updating condition fills in the condition on line 11 in Algorithm 1 and forms a complete pathwise lasso algorithm with adaptive hybrid screening.
 
@@
 
-The structure of the adaptive safe strong rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
-After an adaptive safe strong rule is built, we can automatically apply the adaptive update algorithm to form a pathwise algorithm with adaptive safe strong screening.
+The structure of the adaptive hybrid rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
+After an adaptive safe rule is built, we can automatically apply the adaptive strong rule and the adaptive update algorithm to form a pathwise algorithm with adaptive hybrid screening.
 We are going to derive the extensions to two lasso type problems and show these extensions improve computation efficiency.
 
-\subsection{Adaptive safe strong rule for sparse logistic regression}
+\subsection{Adaptive safe rule for sparse logistic regression}
 
@@
 Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed at the time of each update.
-Thus algorithm 1 for adaptive safe strong rule can be done with Slores rule instead of EDPP rule to form Ada-SSR-Slores that does screening for sparse logistic regression model.
+Thus algorithm 1 for adaptive hybrid rule can be done with Slores rule instead of EDPP rule to form Ada-SSR-Slores that does screening for sparse logistic regression model.
 
-\subsection{Adaptive safe strong rule for group lasso}
+\subsection{Adaptive safe rule for group lasso}
 
@@
 
-In this section conduct experiments solving lasso model on both simulated data sets and real data sets, to show our proposed adaptive safe strong rule screening method outperforms previous screening method such as SSR, SEDPP, HSSR and Slores.
+In this section conduct experiments solving lasso model on both simulated data sets and real data sets, to show our proposed adaptive hybrid rule screening method outperforms previous screening method such as SSR, SEDPP, HSSR and Slores.
 Active-set cycling in \ref{sec:active} is always used with all screening methods because it can be easily combined with any screening methods with no extra cost.
 
-The adaptive safe strong rule screening is implemented in the \textbf{R} package \textbf{biglasso} and we will use this package for our experiment.
+The adaptive hybrid rule screening is implemented in the \textbf{R} package \textbf{biglasso} and we will use this package for our experiment.
 Compared to traditional packages that solve lasso problem, such as \textbf{glmnet}, \textbf{biglasso} focuses on efficiently solving lasso problem with high-dimensional data sets that have a large number of features.
@@
 
-In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive safe strong rule (ASSR).
-The safe rule used in ASSR will be adaptive EDPP rule.
+In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive hybrid rule (AHR).
+The safe rule used in AHR will be adaptive EDPP rule.
 Note that AC is always incorporated with all other screening rules, so using AC alone can be considered as a baseline for this comparison.
@@
 Figure 2 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
-The ASSR is uniformly the fastest under all settings.
+The AHR is uniformly the fastest under all settings.
 Most of the time it is 2-4 times faster than any other screening methods.
@@
 
-There are several atypical cases when ASSR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
+There are several atypical cases when AHR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
 This corresponds a small data set and computation will be less challenging.
@@
 We also tried varying other factors, for example, varying the correlation among features in $X$ or varying the sparsity with fixed signal strength.
-The ASSR also shows uniform advantage over other method when those factors vary in reasonable ranges.
+The AHR also shows uniform advantage over other method when those factors vary in reasonable ranges.
 
@@
 
-In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and ASSR with Slores as the safe rule (ASlores).
+In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and AHR with Slores as the safe rule (ASlores).
 SSR is implemented in all of the three screening methods so it will be considered as the baseline.
@@
 In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test these screening methods on some real data sets to make sure our comparison conclusion is representative in real world.
-Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2017efficient}, we will test on the following data sets:
+Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2017efficient}, we will test the lasso screening methods on the following data sets:
 
@@
 HSSR & 1.21 (0.01) & 3.44 (0.07) & 23.85 (0.06) & 31.05 (0.80) \\
-ASSR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\\hline
+AHR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\\hline
 \end{tabular}
@@
 
-ASSR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\%.
+AHR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\%.
 Also note that the performance of SEDPP varies a lot in MNIST and NYT data sets, where the response is randomly selected in each replication, suggesting that the speed of SEDPP is sensitive to the data.
-ASSR is built with SEDPP as the safe rule but does not have the problem of instability, because it can adaptively adjust itself according the performance of the safe rule.
+AHR is built with SEDPP as the safe rule but does not have the problem of instability, because it can adaptively adjust itself according the performance of the safe rule.
 
@@
 
-In this paper, we proposed the novel adaptive safe strong screening framework for efficient lasso type problem optimization over the solution path.
+In this paper, we proposed the novel adaptive hybrid screening framework for efficient lasso type problem optimization over the solution path.
 The key idea is cleverly reusing the reference for screening along the path until updating to a new reference is beneficial for computation cost.
@@
 
-Our adaptive safe strong screening framework also has great flexibility for extensions.
+Our adaptive hybrid screening framework also has great flexibility for extensions.
 It can substitute coordinate descent with any other faster lasso problem optimizer, SSR with any other stronger strong rules and the adaptive updating algorithm with any other cleverer algorithm.
@@
 Once they are developed, they can be fit into our framework to produce efficient algorithm for other types of lasso problem.
-
-\bibliography{ref}
-
-\end{document}

### 2020-10-09 main.tex
Edits to Section 1

@@
+\pb{Needs an abstract}
+
 \section{Introduction}
 
-The lasso (least absolute shrinkage and selection operator) model\citep{tibshirani1996regression}, is a popular model in statistics and machine learning, especially in high-dimensional problems.
+The least absolute shrinkage and selection operator, or lasso \citep{tibshirani1996regression}, is a popular model in statistics and machine learning, especially in high-dimensional problems.
 The model can be defined as the following modification of the least squares optimization problem:
@@
 \end{equation}
-where $y$ is the $n\times 1$ response vector correspond to $n$ observations, $X=(x_1,x_2,...,x_p)$ is the $n\times p$ feature matrix correspond to $p$ features, $\beta\in \mathbb{R}^p$ is the $p\times 1$ coefficient vector and $\lambda$ is the regularization tuning parameter.
-$||\cdot||_2$ denotes the $l_2$ (Euclidean) norm and $||\cdot||_1$ denotes the $l_1$ norm.
+where $y$ is an $n\times 1$ vector of responses, $X=(x_1,x_2,...,x_p)$ is an $n\times p$ matrix of features, $\beta\in \mathbb{R}^p$ is the $p\times 1$ coefficient vector and $\lambda$ is the regularization tuning parameter.
+Throughout, we use $||\cdot||_2$ denotes the $l_2$ (Euclidean) norm and $||\cdot||_1$ denotes the $l_1$ norm.
 
 The lasso model has several attractive properties compared to least squares regression, including increased stability of estimation, increased prediction accuracy, and automatic variable selection arising from the fact that it yields sparse estimates of $\beta$.
-As a result, it is widely applied in different fields, such as gene expression data analysis, image recognition and text mining, and has been extended in several ways, such as group lasso\citep{yuan2006model}, elastic net\citep{zou2005regularization} and sparse generalized linear models.
-Because of its wide popularity, solving the lasso model efficiently is an important topic in statistics and machine learning.
+As a result, it is widely applied in different fields, such as gene expression data analysis, image recognition and text mining, and has been extended in several ways, such as group lasso \citep{yuan2006model}, elastic net \citep{zou2005regularization} and sparse generalized linear models.
+Because of its wide popularity, solving the lasso efficiently is an important topic in statistics and machine learning.
 
+\pb{I think we need to introduce the point of the paper here; do we need this paragraph?
 Because the optimal value of $\lambda$ is not known in advance, typical practice is to solve for $\beta$ along a sequence of values of the tuning parameter $\lambda$, known as the solution path.
 Pathwise algorithms can be efficiently implemented to address this challenge, by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.
-In particular, the pathwise coordinate descent algorithm\citep{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS (least angle regression)\citep{efron2004least}, especially in high dimensional settings where $p$ is large.
+In particular, the pathwise coordinate descent algorithm \citep{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS \citep[least angle regression, ][]{efron2004least}, especially in high dimensional settings where $p$ is large.
 In sparse settings, it scales up very well with a computational cost of approximately $O(np)$.
+}
 
-However, modern data collection and storage techniques allow researchers to measure an increasingly large number of features, which introduce additional computational challenges.
+\pb{How about just: While efficiently algorithms have been developed \citep{friedman2007pathwise}, modern data collection \ldots}
+
+Modern data collection and storage techniques allow researchers to measure an increasingly large number of features, which introduce additional computational challenges.
 In particular, it may not be possible to store the feature matrix, which can require many GBs of memory to store, in memory.
@@
 There are many screening techniques where the solution obtained after screening will still be the global optimum given it exists, and in this paper we will only focus on this type of screening.
-In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision and a decision is made for each $\lambda$ values: for example, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
+In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision.
+In particular, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
 
-There are two important categories of features screening rules: ``strong'' rules\citep{tibshirani2011regression}\citep{qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules\citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
+There are two important categories of feature screening rules: ``strong'' rules \citep{tibshirani2011regression, qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules \citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
 As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
@@
 However, safe rules are considerably less powerful at discarding features than strong rules.
-More recently, hybrid approaches \citep{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.
+More recently, hybrid approaches \pb{update this citation} \citep{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.
 
-Previous safe screening rules can also be divided into two categories, sequential rules and one-step rules, by how the screening is carried out along the path of $\lambda$ values.
-Sequential rules address the challenge of the solution path and do screening for each $\lambda$ values using solution from its previous $\lambda$ value, so they require heavy computation but are relatively powerful, at each $\lambda$ values.
-One-step rules only require heavy computation at the beginning and thus are faster but they cannot remain powerful along the path for long because they don't utilize previous solution.
+Safe screening rules can be implemented in one of two ways.
+Sequential rules are recalculated at each $\lambda$ value along the path using the previous solution, so they require heavy computation but are relatively powerful.
+One-step rules are only calculated once, at the beginning of the path.
+As a result, they require far less computational burden but they lose efficacy as the thus are faster but they cannot remain powerful along the path for long because they don't utilize previous solution.
 
-In this paper, we proposed an adaptive safe screening scheme that changes how screening is done along the path of $\lambda$ values.
-We do safe screening on $\lambda$ values alone the path referencing to the same solution at the $\lambda$ value in the beginning, as in one-step rules, until it is beneficial to update to a new $\lambda$ value as the reference.
-This screening scheme helps avoid disadvantages of both sequential rules and one-step rules.
-On one hand, reusing the same solution as reference avoids many costly computation before updating and on the other hand, referring to solution at a closer $\lambda$ value provides more screening power.
-An adaptive scheme determines when to update the reference based on the previous screening performance, to better balance these two effects.
-It will be shown that our adaptive rule can greatly reduce the computation time and outperform other methods under all scenarios.
+In this paper, we propose an adaptive safe screening scheme.
+We begin by calculating a safe rule and applying it to multiple solution steps along the path.
+However, unlike the one-step implementation, we monitor the power of this rule and once it is no longer effective, construct a new safe rule.
+This process is repeated along the path, waiting until it is beneficial before investing in a new safe rule calculation.
+This scheme avoids disadvantages of both sequential rules and one-step rules.
+Reusing the same solution when the safe rule is still effective avoids unnecessary computations, while periodically updating the rules ensures that they maintain power across the entire path.
+We show that this adaptive approach can greatly reduce the computation time and outperforms other methods in all scenarios.
 Following the hybrid approaches, we also combined our approach with strong rules to form adaptive hybrid rules.
-Our method can utilize any member of safe rules, giving it the potential for further speed up given new safe rules and the flexibility to extend to other lasso type models.
-For example we extended the method to work with logistic regression with lasso penalty and group lasso.
+Our method is general, and capable of utilizing any sequential safe rule, and thus readily extended to other lasso type models for which safe rules exist.
+Here, we illustrate its extensions to the logistic regression loss function and to the group lasso penalty.
 
@@
 \begin{itemize}
-    \item A new feature screening framework (Section 3.1,3.2), which updates the reference for screening alone the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
+    \item A new feature screening framework (Section 3.1,3.2), which updates the reference for screening along the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
     \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section 3.4,4.1,4.2).
@@
     \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
-    \item The Ada-SSR-SEDPP and Ada-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso}\citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
+    \item The Ada-SSR-SEDPP and Ada-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso} \citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
 \end{itemize}

### 2020-10-15 main.tex
Updates from Overleaf

--- 2020-09-25 main.tex
@@
 \begin{theorem}[Adaptive EDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
+    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$.
+Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$ and the last updated reference point is $\lambda_k$.
+Under condition (2)
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some update point $k+B$ and any $b$ s.t.
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some next update point $k+B$ and any $b$ s.t.
 $k<k+b\leq k+B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
@@
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some update point $k+B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some next update point $k+B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
         \begin{equation}
@@
 
-We also tried varying other factors, for example, varying the correlation among features in $X$ or varying the sparsity with fixed signal strength.
+We also tried varying other factors, for example, varying the correlation among features in $X$, varying the sparsity with fixed signal strength or varying the minimum $\lambda$-value $\lambda_K$.
 The AHR also shows uniform advantage over other method when those factors vary in reasonable ranges.
@@
 In previous sections, we used simulation to compare the screening methods under different scenario.
-In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test these screening methods on some real data sets to make sure our comparison conclusion is representative in real world.
+In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test the screening methods for lasso model on some real data sets to make sure our comparison conclusion is representative in real world.
 Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2017efficient}, we will test the lasso screening methods on the following data sets:
@@
 For 2 and 4, since in each experiment the response is randomly selected, we replicate the experiment 50 times to get an accurate estimate.
-The following table compares the average computation time for different screening methods in these data sets.
+Table 1 compares the average computation time for different screening methods in these data sets.
 
@@
 
+Ultra high dimensional big data that is too large to be fit into the memory is the real challenge and is the place where the help of a good screening method is wanted most.
+We test the screening methods on a data from a genome-wide association study on 1,080 subjects with heart conditions.
+We want to identify genetic factors that are associated with some heart condition severity measurements.
+After imputing and filtering, there are $p=11,830,470$ SNP measurements used as the features.
+The size of the file storing the feature matrix is 96G and we conduct the test on a machine with 32G RAM.
+
+For the lasso model, we choose the Left ventricular ejection fraction (LVEF) as the response.
+It measures the proportion of blood being pumped out of the left ventricle of the heart (the main pumping chamber) with each contraction.
+Lower value means severer heart failure.
+$n=973$ out of 1,080 subjects have this measurement and they will be considered as the sample for this analysis.
+The experiment is replicated 5 times to take the average, shown in the Table 2.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{l|l|l|l|l|l}
+\hline
+
+Screening method & AC\,\,\,\,\,\,\,\,\,    & SSR\,\,\,\,\,\,   & SEDPP & HSSR\,\,\,  & AHR\,\,\,\,\,\,  \\
+\hline
+Time & 256.4 & 79.2 & 79.3 & 84.1 & 54.0\\
+Standard error & 0.59 & 0.10 & 0.03 & 0.03 & 0.22
+ \\\hline
+\end{tabular}
+\caption{Average computing time in minute and standard error for solving the lasso model on big data}
+\end{table}
+
 \begin{itemize}

### 2020-10-16 main.tex
Add logistic big data result.

@@
 The size of the file storing the feature matrix is 96G and we conduct the test on a machine with 32G RAM.
+We choose a larger $\lambda_{\min} =0.5\lambda_{\max}$ to avoid having more features selected than the number of observations, where the solution becomes not unique.
 
@@
 \hline
-Time & 256.4 & 79.2 & 79.3 & 84.1 & 54.0\\
-Standard error & 0.59 & 0.10 & 0.03 & 0.03 & 0.22
+Time & 183.6 & 78.6 & 78.6 & 84.9 & 13.6\\
+Standard error & 0.43 & 0.65 & 0.20 & 0.48 & 0.15
  \\\hline
@@
 
-\begin{itemize}
-    \item Analyse and profile different methods. Compare them in big data case ?
-\end{itemize}
+For the sparse logistic model, we choose the New York Heart Association (NYHA) Functional Classification as the response.
+It classifies patients by how much they are limited during physical activity.
+The classes range from 1 to 4 so we combine class 1 and 2 as the negative class with no or slight limitation of physical activity and class 3 and 4 as the positive class with substantial limitation.
+$n=1008$ out of 1,080 subjects have this measurement and they will be considered as the sample for this analysis.
+The experiment is replicated 5 times to take the average, shown in the Table 3.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{l|l|l|l}
+\hline
+
+Screening method & SSR\,\,\,\,\,\,\,\,\,    & HSlores\,\,\,\,\,\,   & ASlores   \\
+\hline
+Time & 82.7 & 107.5 & 51.7 \\
+Standard error & 0.10 & 0.67 & 0.17 
+ \\\hline
+\end{tabular}
+\caption{Average computing time in minute and standard error for solving the sparse logistic model on big data}
+\end{table}
+
+For both the lasso model and the sparse logistic model, the purposed adaptive hybrid methods outperforms other methods with great reduction in computation time.
+On the lasso model, the adaptive hybrid method achieves 6 times speedup.
 

### 2020-12-04 main.tex
Updates from Overleaf

@@
-\pb{Needs an abstract}
+\begin{abstract}
+    Lasso type models are popular in statistics and machine learning, especially for variable selection in high-dimensional data.
+Typical practice is to tune the size of lasso penalty along a path of values.
+Due to modern data collection techniques, researchers need to analyse ultra high-dimension data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
+Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.
+In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
+It reuses previous solutions in the path and avoids unhelpful heavy computations.
+It is a flexible framework that can be easily extended to different types of lasso models.
+The Ada-SSR-EDPP for the standard lasso model and the Ada-SSR-Slores for the sparse logistic model are shown as examples.
+We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
+\end{abstract}
 
@@
 
-\pb{I think we need to introduce the point of the paper here; do we need this paragraph?
 Because the optimal value of $\lambda$ is not known in advance, typical practice is to solve for $\beta$ along a sequence of values of the tuning parameter $\lambda$, known as the solution path.
-Pathwise algorithms can be efficiently implemented to address this challenge, by using the solution at a previous $\lambda$ value as a ``warm start'' for the next value of $\lambda$.
-In particular, the pathwise coordinate descent algorithm \citep{friedman2007pathwise}, which optimizes $\beta(\lambda)$ one element at a time with the remaining coordinates held fixed, has been shown to outperform other lasso algorithms such as LARS \citep[least angle regression, ][]{efron2004least}, especially in high dimensional settings where $p$ is large.
-In sparse settings, it scales up very well with a computational cost of approximately $O(np)$.
-}
-
-\pb{How about just: While efficiently algorithms have been developed \citep{friedman2007pathwise}, modern data collection \ldots}
-
-Modern data collection and storage techniques allow researchers to measure an increasingly large number of features, which introduce additional computational challenges.
+While efficiently algorithms have been developed \citep{friedman2007pathwise} for the solution path, modern data collection and storage techniques allow researchers to measure an increasingly large number of features, which introduce additional computational challenges.
 In particular, it may not be possible to store the feature matrix, which can require many GBs of memory to store, in memory.
@@
 However, safe rules are considerably less powerful at discarding features than strong rules.
-More recently, hybrid approaches \pb{update this citation} \citep{zeng2017efficient} combining the two types of rules have been shown to be more efficient than either type of rule alone.
+More recently, hybrid approaches \citep{zeng2021hybrid} combining the two types of rules have been shown to be more efficient than either type of rule alone.
 
@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\citep{zeng2017efficient}:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\citep{zeng2021hybrid}:
 
@@
 
-The hybrid safe-strong rules (HSSR) \citep{zeng2017efficient} was proposed to combine SSR with any member of safe rules to take advantage of both.
+The hybrid safe-strong rules (HSSR) \citep{zeng2021hybrid} was proposed to combine SSR with any member of safe rules to take advantage of both.
 More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments.
@@
 
-Because HSSR \citep{zeng2017efficient} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
+Because HSSR \citep{zeng2021hybrid} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
 The SSR and adpative EDPP rule combined will form our adaptive hybrid rule: Ada-SSR-EDPP.
@@
 \end{equation}
-where $\pi(\beta)=\{\pi_i(\beta)\}_{i=1}^n=\{p(y_i=1|x_{i1},x_{i2},...,x_{ip})\}_{i=1}^n=\{e^{\eta_i(\beta)}/(1+e^{\eta_i(\beta)})\}_{i=1}^n$ is the predicted value vector and $\eta(\beta)=X\beta$ is the linear function.
+where $\pi(\beta)=\{\pi_i(\beta)\}_{i=1}^n=\{p(y_i=1|x_{i1},x_{i2},...,x_{ip})\}_{i=1}^n=\{e^{\eta_i(\beta)}/(1+e^{\eta_i(\beta)})\}_{i=1}^n$ is the predicted value vector and $\eta(\beta)=X\beta+\beta_0\mathbf{1}$ is the linear function.
 $X$ are still the $n\times p$ standardized feature matrix but in this model the $y\in\{0,1\}^n$ is an unstandardized binary response vector.
@@
 \begin{equation}
-    \hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}\bigg|\bigg|y-\sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2+\lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_1,
+    \hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}\bigg|\bigg|y-\sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2+\lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_2,
 \end{equation}
@@
 In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive hybrid rule (AHR).
-The safe rule used in AHR will be adaptive EDPP rule.
+The AHR is Ada-SSR-EDPP which uses EDPP as the safe rule.
 Note that AC is always incorporated with all other screening rules, so using AC alone can be considered as a baseline for this comparison.
@@
 $\beta$ will have $s$ randomly selected elements equally spaced between $[-\beta_{max},\beta_{max}]$ and the rest $p-s$ elements are zeros.
+The lasso model is solved along a grid of $L$ $\lambda$-values equally spaced on the log scale between $[\lambda_{\max},\lambda_{\min}]$.
 Each setting is replicated $10$ times to calculate the average time cost.
-We consider the following cases:
+By default we set $p=10,000$, $n=1,000$, $s=20$, $\beta_{max}=1$, $L=100$, $\lambda_{\min}/\lambda_{\max}=0.05$.
+We consider the following cases where one of the variables above is varying at a time:
 
 \begin{enumerate}
-    \item \textbf{Varying number of features $\mathbf{p}$:} we fix $n=1,000$, $s=20$, $\beta_{max}=1$ and vary $p$ from $1,000$ to $100,000$.
-    \item \textbf{Varying sample size $\mathbf{n}$:} we fix $p=10,000$, $s=20$, $\beta_{max}=1$ and vary $n$ from $200$ to $10,000$.
-    \item \textbf{Varying signal strength $\mathbf{\beta_{max}}$:} we fix $p=10,000$, $n=1,000$, $s=20$ and vary $\beta_{max}$ from $0.05$ to $1$.
-    \item \textbf{Varying sparsity $\mathbf{s}$:} we fix $p=10,000$, $n=1,000$, total signal size $\beta_{max}\times s=20$ and vary $s$ from $10$ to $300$.
+    \item \textbf{Varying number of features:} $p$ from $1,000$ to $100,000$.
+    \item \textbf{Varying sample size:} $n$ from $200$ to $10,000$.
+    \item \textbf{Varying signal strength:} $\beta_{max}$ from $0.05$ to $1$.
+    \item \textbf{Varying sparsity:} $s$ from $10$ to $300$ while controlling total signal size $\beta_{max}\times s=20$.
+    \item \textbf{Varying number of grid points:}  $L$ from $20$ to $1000$.
+    \item \textbf{Varying range of grid:}  $\lambda_{\min}/\lambda_{\max}$ from $0.5$ to $0.002$.
+    \item \textbf{Varying number of grid points $L$ with fixed spacing:} $L$ from $20$ to $1000$ while controlling $\lambda_{\min}/\lambda_{\max}$ so that the spacing of the $\lambda$-values on the log scale is the same.
 \end{enumerate}
@@
     \centering
-    \includegraphics[scale = 0.59]{plots/gaus1.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[scale = 0.59]{plots/511.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
 Fourth column: varying sparsity $s$.}
-    \label{fig:5.1.1}
+    \label{fig:5.1.1a}
 \end{figure}
 
-Figure 2 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 0.59]{plots/511b.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+Top row: computation time in second.
+Bottom row: relative computation time compared to AC.
+First column: Varying number of grid points $L$.
+Second column: Varying range of grid $\lambda_{\min}/\lambda_{\max}$.
+Third column: Varying number of grid points $L$ with fixed spacing.}
+    \label{fig:5.1.1b}
+\end{figure}
+
+Figure 2 and Figure 3 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
 The AHR is uniformly the fastest under all settings.
-Most of the time it is 2-4 times faster than any other screening methods.
-It outperforms other methods especially when the data set is large (large $n$ or large $p$) or the active features are sparse among all features (small $s$).
+Most of the time it is 2-8 times faster than any other screening methods.
+It outperforms other methods especially when the data set is large (large $n$ or large $p$), the active features are sparse among all features (small $s$) or the grid of $\lambda$-value is fine (large $L$ or $\lambda_{\min}/\lambda_{\max}$).
 
@@
 Lasso model would not be the optimal model to analyse such an data set.
+(4) $L$ is small.
+In this case, only a coarse grid of $\lambda$-values are considered.
+The $\lambda$-value selected in this case may be far from optimal.
 
@@
 
-In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and AHR with Slores as the safe rule (ASlores).
+In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and the adaptive method Ada-SSR-Slores with Slores as the safe rule (ASlores).
 SSR is implemented in all of the three screening methods so it will be considered as the baseline.
@@
 Each setting is replicated $10$ times to calculate the average time cost.
-We consider the same 4 cases we have considered in the previous experiment.
+We consider the same 7 cases we have considered in the previous experiment.
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
 Fourth column: varying sparsity $s$.}
-    \label{fig:5.1.2}
+    \label{fig:5.1.2a}
 \end{figure}
 
-Figure 3 shows the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
+\begin{figure}[h]
+    \centering
+    \includegraphics[scale = 0.59]{plots/512b.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+Top row: computation time in second.
+Bottom row: relative computation time compared to SSR.
+First column: Varying number of grid points $L$.
+Second column: Varying range of grid $\lambda_{\min}/\lambda_{\max}$.
+Third column: Varying number of grid points $L$ with fixed spacing.}
+    \label{fig:5.1.2b}
+\end{figure}
+
+Figure 4 and 5 show the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
 ASlores is also uniformly faster than other methods and this improvement is significant except for some atypical cases motioned before.
@@
 In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test the screening methods for lasso model on some real data sets to make sure our comparison conclusion is representative in real world.
-Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2017efficient}, we will test the lasso screening methods on the following data sets:
+Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2021hybrid}, we will test the lasso screening methods on the following data sets:
 

### 2020-12-04 batch-hssr.tex
Edits to Section 1
Some edits to Section 2

@@
 \providecommand{\sign}{\textrm{sign}}
-\providecommand{\note}[1]{\textcolor{red}{#1}}
+\providecommand{\pb}[1]{\textcolor{red}{#1}}
 \providecommand{\lam}{\lambda}
@@
 
+\begin{abstract}
+Lasso type models are popular in statistics and machine learning, especially for variable selection in high-dimensional data.
+Typical practice is to tune the size of lasso penalty along a path of values.
+Due to modern data collection techniques, researchers need to analyse ultra high-dimension data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
+Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.
+In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
+It reuses previous solutions in the path and avoids unhelpful heavy computations.
+It is a flexible framework that can be easily extended to different types of lasso models.
+The Ada-SSR-EDPP for the standard lasso model and the Ada-SSR-Slores for the sparse logistic model are shown as examples.
+We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
+\end{abstract}
+
 \input{main}

### 2020-12-04 main.tex
Some edits to Section 2

@@
-\begin{abstract}
-    Lasso type models are popular in statistics and machine learning, especially for variable selection in high-dimensional data.
-Typical practice is to tune the size of lasso penalty along a path of values.
-Due to modern data collection techniques, researchers need to analyse ultra high-dimension data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
-Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.
-In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
-It reuses previous solutions in the path and avoids unhelpful heavy computations.
-It is a flexible framework that can be easily extended to different types of lasso models.
-The Ada-SSR-EDPP for the standard lasso model and the Ada-SSR-Slores for the sparse logistic model are shown as examples.
-We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
-\end{abstract}
-
 \section{Introduction}
@@
 However, safe rules are considerably less powerful at discarding features than strong rules.
-More recently, hybrid approaches \citep{zeng2021hybrid} combining the two types of rules have been shown to be more efficient than either type of rule alone.
+More recently, hybrid approaches \citep{Zeng2021} combining the two types of rules have been shown to be more efficient than either type of rule alone.
 
@@
 \end{equation}
-This standardization make it reasonable to apply the same penalty to all features, even if originally measured in different units.
+Standardization ensures that the penalty is applied equally to all features, even if originally measured in different units.
 It also improves the efficiency and stability of the optimization, and helps to simplify optimization.
@@
 Standardization also simplifies the formulas for screening rules and thus allows for more efficient implementation.
+Furthermore, this can be done without loss of generality as one can always obtain the solution on the original scale through a simple linear transformation of the standardized solution.
 
@@
 
- Pathwise algorithms are developed to address the challenge of the solution path with a strategy known as the ``warm start''.
+The goal of pathwise algorithms is to solve for this entire solution path.
+This can be done efficiently by using ``warm starts'': using previous points on the path as initial values, as these are likely to be relatively close to the solution.
 For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in the algorithm.
-Pathwise coordinate descent is a popular pathwise algorithm fitting a solution path for lasso problem and will be used as the lasso algorithm for the rest of the paper.
+Pathwise coordinate descent is a algorithm that takes advantage of this idea and will be used as the lasso algorithm for the rest of the paper.
 
@@
   \begin{aligned}
-    &x_j^Tr(\lambda)/n& &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if} \quad \hat{\beta}(\lambda)_j\neq 0,\\
-    |&x_j^Tr(\lambda)/n|& &\leq \lambda & & \textrm{if} \quad \hat{\beta}(\lambda)_j= 0.
+    x_j^Tr(\lambda)/n &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if } \hat{\beta}(\lambda)_j\neq 0,\\
+    |x_j^Tr(\lambda)/n| &\leq \lambda & & \textrm{if } \hat{\beta}(\lambda)_j= 0.
   \end{aligned}
 \end{equation}
-If the residuals were known, we could safely conclude that $\hat{\beta}(\lambda)_j=0$ by checking the second condition holds as a strict inequality.
+If the residuals were known, we could safely conclude that $\hat{\beta}(\lambda)_j=0$ by verifying that the second condition holds as a strict inequality.
 The complication, of course, is that the residuals are not known until after we have solved for all the coefficients.
-However, when fitting a solution path, residuals at previous $\lambda$-values provide information about residuals at the next $\lambda$-value and thus be used for screening.
+However, when fitting a solution path, residuals at previous $\lambda$ values provide information about residuals at the next $\lambda$ value and thus may be used for screening.
 Note that if we have $\lambda_0=\max_j|x_j^Ty/n|$ and $\hat{\beta}(\lambda_0)=0$, then $r(\lambda_0)=y$ satisfies the KKT conditions and thus $\hat{\beta}(\lambda_0)=0$ is the optimal solution.
@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\citep{zeng2021hybrid}:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\citep{Zeng2021}:
 
@@
 
-The hybrid safe-strong rules (HSSR) \citep{zeng2021hybrid} was proposed to combine SSR with any member of safe rules to take advantage of both.
+The hybrid safe-strong rules (HSSR) \citep{Zeng2021} was proposed to combine SSR with any member of safe rules to take advantage of both.
 More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments.
@@
 
-Because HSSR \citep{zeng2021hybrid} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
+Because HSSR \citep{Zeng2021} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
 The SSR and adpative EDPP rule combined will form our adaptive hybrid rule: Ada-SSR-EDPP.
@@
 In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test the screening methods for lasso model on some real data sets to make sure our comparison conclusion is representative in real world.
-Following the studies of \citep{wang2013lasso, xiang2016screening, zeng2021hybrid}, we will test the lasso screening methods on the following data sets:
+Following the studies of \citep{wang2013lasso, xiang2016screening, Zeng2021}, we will test the lasso screening methods on the following data sets:
 

### 2020-12-04 main.tex
Edits to 2.1

@@
 
-Before introducing current screening rules, there is also a similar idea to reduce the number of features for part of computation, called active-set cycling (AC) \citep{lee2007efficient}.
+The simplest of all screening rules is to simply assume that features currently in the model will stay in the model and features currently excluded will remain excluded.
+This is known as active-set cycling (AC) \citep{lee2007efficient}.
 It can be implemented on top of any lasso algorithm with no additional cost.
-When solving the coefficients for at $\lambda_{k+1}$, first only consider features whose coefficients were non-zero at $\lambda_k$ and discard other features with zero coefficients at $\lambda_k$.
-We compute the solution for the smaller model with these reduced number of coefficients.
+When solving the coefficients for at $\lambda_{k+1}$, AC considers only features whose coefficients were non-zero at $\lambda_k$ and discards the other features.
+The lasso problem is then solved over this reduced number of coefficients.
 
@@
 Because the KKT conditions are sufficient for the solution to be optimal, if there is no violation, the solution to the smaller model will be exactly the same as if we solve the model with all features.
-If there are violations, corresponding features will be added to the model and this procedure will repeat.
-Because features don't enter the model very frequently, usually small number of repetitions will be needed and thus the algorithm provides substantial speed up.
+If there are violations, corresponding features will be added to the model and this procedure is repeated.
+Because features enter the model relatively infrequently, typically only a small number of repetitions are needed, thereby providing a substantial speed up compared to solving the full lasso problem every time.
 

### 2020-12-04 main.tex
Edits to 2.2

@@
 
-Sequential strong rule (SSR) \citep{tibshirani2011regression} is a fast and powerful feature screening rule.
-Given the solution $\hat{\beta}(\lambda_k)$ at $\lambda_k$, we can compute the residual vector as $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$.
-The SSR discards the $j$-th feature at $\lambda_{k+1}$ if:
+Each post-convergence check requires $O(np)$ operations and is therefore costly to repeat when violations occur.
+These violations are inevitable in active-set cycling, as they occur every time a feature is added to the model.
+Sequential strong rules (SSR) \citep{tibshirani2011regression} attempt to retain the basic idea of active-set cycling, but reduce violations by retaining features that are ``close'' to entering the model.
 
+Given the solution $\hat{\beta}(\lambda_k)$ and residual vector $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$ at $\lambda_k$, the SSR discards the $j$-th feature at $\lambda_{k+1}$ if:
 \begin{equation}
@@
 \end{equation}
+The SSR is derived from the KKT condition and the ``unit-slope'' assumption that the size of the slope of $x_j^Tr(\lambda)/n$ over $\lambda$ is bounded by 1.
 
-The SSR is derived from the KKT condition and the "unit-slope" assumption that the size of the slope of $x_j^Tr(\lambda)/n$ over $\lambda$ is bounded by 1.
-
-The biggest problem of SSR is that the "unit-slope" assumption may not hold and thus discarded features are not guaranteed to have zero coefficients.
-A post-convergence KKT check is needed for the discarded features to make sure their coefficients are truly zero.
-If violations occur, we need to refit the model adding the violating features and repeat the post-convergence check.
-The cost for each post-convergence check is O(np) and especially costly when violations occur.
-However, previous studies have shown that violations are rare and thus additional cost is acceptable.
+The biggest problem of SSR is that the ``unit-slope'' assumption may not hold and thus discarded features are not guaranteed to have zero coefficients.
+As with AC, a post-convergence KKT check is therefore needed for the discarded features to make sure their coefficients are truly zero.
+If violations occur, we again need to refit the model, adding the violating features and repeating the post-convergence check.
+However, previous studies have shown that violations are rare, so the additional $O(np)$ cost for repeating a KKT check hardly ever arises.
 

### 2020-12-04 main.tex
Edits to 2.3

@@
 \begin{equation}
+  \label{eq:lasso}
   \hat{\beta}(\lambda)=\underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}||y-X\beta||_2^2+\lambda||\beta||_1,
@@
 \begin{equation}
+  \label{eq:std}
   \sum_{i=1}^ny_i=0, \qquad \sum_{i=1}^n x_{ij}=0, \qquad \sum_{i=1}^n x_{ij}^2=n,\qquad j=1,2,...,p.
@@
 \begin{equation}
+  \label{eq:kkt}
   \begin{aligned}
@@
 \begin{equation}
+  \label{eq:ssr}
   |x_j^Tr(\lambda_k)/n|<2\lambda_{k+1}-\lambda_k.
@@
 
-A nice property about SSR with post-convergence check is the quantity $x_j^Tr(\lambda_k)/n$ is calculated at $\lambda_k$ in (2) during post-convergence check.
-Then in SSR screening at $\lambda_{k+1}$ (4), this quantity is reused.
-Besides the quantity $x_j^Tr(\lambda_k)/n$, other parts of the computation of (4) have almost zero cost.
-In conclusion, the computation cost of SSR is generally only the cost of the post-convergence check, which is O(npK).
+SSR possesses the nice property that the quantity $x_j^Tr(\lambda_k)/n$ needed for SSR screening \eqref{eq:ssr} at $\lambda_{k+1}$ has already been calculated during post-convergence checking at $\lambda_k$ in \eqref{eq:kkt}.
+As this is the only computationally intensive aspect of SSR screening, and SSR violations are rare, its computational cost is roughly $O(npK)$.
 
@@
 
-Compared to strong rules, safe rules can discard features safely.
-Those discarded features are guaranteed to have zero coefficients and we do not need an addition check to validate them.
-We will mainly focus on enhanced dual polytope projections (EDPP) rules\citep{wang2013lasso}, because they outperform other current safe rules and are easy to incorporate in our method.
+Compared to strong rules, safe rules are never violated.
+Features can be discarded safely, with no need for post-covergence checking, as the coefficients are guaranteed to be zero by the rule.
+We will mainly focus on enhanced dual polytope projections (EDPP) rules\citep{wang2013lasso} because they outperform other known safe rules and are easy to incorporate into our method.
 
@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization (2) can be simplified in the following theorems\citep{Zeng2021}:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization \eqref{eq:std} can be simplified in the following theorems \citep{Zeng2021}:
 
 \begin{theorem}[BEDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$. Under (2) and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
+    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$.
+Under \eqref{eq:std} and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
     \begin{equation}
@@
 \begin{theorem}[SEDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition (2)
+    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition \eqref{eq:std}
     \begin{enumerate}
@@
 
-In BEDPP rule (4), the most costly parts of computation that take O(np) time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
-These quantities does not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
-After this step, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with O(np) cost.
+In BEDPP rule (4), the most costly parts of computation that take $O(np)$ time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
+These quantities do not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
+After this step, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with $O(np)$ cost.
 
-In SEDPP rule (5), it requires computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ ($x_j^T\hat{y}(\lambda_k)$ can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$).
-For screening at every $\lambda_{k+1}$, $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ need to be recalculated and this step takes O(np) time.
-Thus SEDPP is a sequential rule and computation of the sequence takes O(npK) time.
+In contrast, the SEDPP rule (5) requires $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which must be recomputed at every $\lam$.
+This is the primary source of computational burden, as the other terms in the rule are $\{x_j^Ty\}_{j=1}^p$, which only needs to be calculated once, and $x_j^T\hat{y}(\lambda_k)$, which can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$.
+Thus, the sequential safe rule SEDPP requires $O(npK)$ operations.
 
-BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ using $r(\lambda_0)=y$ as a reference.
+Comparing the two, BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ using $r(\lambda_0)=y$ as a reference.
 As $\lambda_k$ gets further away from $\lambda_0$, this bound becomes less precise and the screening rule becomes less powerful.
 SEDPP is slower, but at each $\lambda_{k+1}$, it uses $r(\lambda_{k})$ as the reference.
-Because $\lambda_{k+1}$ and $\lambda_k$ are close, the bound will be tight and screening will keep being powerful.
+Because $\lambda_{k+1}$ and $\lambda_k$ are close, the bound remains tight and screening continues to be powerful over the entire path.
 
@@
 \begin{theorem}[Adaptive EDPP]
-    For the lasso problem (1), let $\lambda_0:=\max_j|x_j^Ty/n|$.
+    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$.
 Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$ and the last updated reference point is $\lambda_k$.
-Under condition (2)
+Under condition \eqref{eq:std}
     \begin{enumerate}
@@
 This combination is not trivial.
-For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (2).
+For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (3).
 However, combined with safe rules, previous post-convergence check only needs to check features that are not discarded at the previous $\lambda$-value.
@@
 
-Under condition (2) except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
+Under condition \eqref{eq:std} except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
 For any $k+b>k$, let
@@
 where $\beta=(\beta_1^T,...,\beta_G^T)^T$, $X_g$ is a $n\times p_g$ sub-matrix consisting of columns of $X$ corresponding to features in group $g$, $g=1,2,...,G$.
-Besides standardization in (2), we apply an addition level of standardization at the group level\citep{breheny2015group}:
+Besides standardization in \eqref{eq:std}, we apply an addition level of standardization at the group level\citep{breheny2015group}:
 
@@
 Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-Under condition (2) and (23)
+Under condition \eqref{eq:std} and (23)
     \begin{enumerate}
@@
 
-In this part, we will solve the standard lasso problem (1) with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive hybrid rule (AHR).
+In this part, we will solve the standard lasso problem \eqref{eq:lasso} with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive hybrid rule (AHR).
 The AHR is Ada-SSR-EDPP which uses EDPP as the safe rule.
@@
 
-There are several atypical cases when AHR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
+There are several atypical cases when AHR's advantage over other methods is not as significant: \eqref{eq:lasso} $p$ or $n$ is small.
 This corresponds a small data set and computation will be less challenging.

### 2021-01-08 main.tex
Updates from Overleaf

@@
 Safe screening rules can be implemented in one of two ways.
-Sequential rules are recalculated at each $\lambda$ value along the path using the previous solution, so they require heavy computation but are relatively powerful.
-One-step rules are only calculated once, at the beginning of the path.
+Sequential rules do screening at each $\lambda$ value along the path using the previous solution as the reference, so they require heavy computation but are relatively powerful.
+One-step only use the solution at the beginning of the path as the reference.
 As a result, they require far less computational burden but they lose efficacy as the thus are faster but they cannot remain powerful along the path for long because they don't utilize previous solution.
@@
 In this paper, we propose an adaptive safe screening scheme.
-We begin by calculating a safe rule and applying it to multiple solution steps along the path.
-However, unlike the one-step implementation, we monitor the power of this rule and once it is no longer effective, construct a new safe rule.
-This process is repeated along the path, waiting until it is beneficial before investing in a new safe rule calculation.
+We begin choosing a solution as the reference for the safe rule and applying it to multiple solution steps along the path.
+However, unlike the one-step implementation, we monitor the power of the rule with this reference and once it is no longer effective, update the reference of the safe rule to the latest solution.
+This process is repeated along the path, waiting until it is beneficial before investing in a new safe rule reference.
 This scheme avoids disadvantages of both sequential rules and one-step rules.
-Reusing the same solution when the safe rule is still effective avoids unnecessary computations, while periodically updating the rules ensures that they maintain power across the entire path.
+Reusing the same solution as reference when the safe rule is still effective avoids unnecessary computations, while periodically updating the reference ensures that they maintain power across the entire path.
 We show that this adaptive approach can greatly reduce the computation time and outperforms other methods in all scenarios.
@@
   \begin{aligned}
-    x_j^Tr(\lambda)/n &= \lambda \, \sign \, \hat{\beta}(\lambda)_j & & \textrm{if } \hat{\beta}(\lambda)_j\neq 0,\\
-    |x_j^Tr(\lambda)/n| &\leq \lambda & & \textrm{if } \hat{\beta}(\lambda)_j= 0.
+    x_j^Tr(\lambda)/n &= \lambda \, \sign \, \hat{\beta}_j(\lambda) & & \textrm{if } \hat{\beta}_j(\lambda)\neq 0,\\
+    |x_j^Tr(\lambda)/n| &\leq \lambda & & \textrm{if } \hat{\beta}_j(\lambda)= 0.
   \end{aligned}
 \end{equation}
-If the residuals were known, we could safely conclude that $\hat{\beta}(\lambda)_j=0$ by verifying that the second condition holds as a strict inequality.
+If the residuals were known, we could safely conclude that $\hat{\beta}_j(\lambda)=0$ by verifying that the second condition holds as a strict inequality.
 The complication, of course, is that the residuals are not known until after we have solved for all the coefficients.
@@
 If there are violations, corresponding features will be added to the model and this procedure is repeated.
+There are a finite number of features that can be added, so the procedure will end after finite repetitions.
 Because features enter the model relatively infrequently, typically only a small number of repetitions are needed, thereby providing a substantial speed up compared to solving the full lasso problem every time.
@@
 If violations occur, we again need to refit the model, adding the violating features and repeating the post-convergence check.
-However, previous studies have shown that violations are rare, so the additional $O(np)$ cost for repeating a KKT check hardly ever arises.
+Similar to the procedure in AC, there are a finite number of features that can be added, so the procedure will end after finite repetitions.
+Moreover, previous studies have shown that violations are rare, so the additional $O(np)$ cost for repeating a KKT check hardly ever arises.
 
@@
     \begin{equation}
+        \label{eq:bedpp}
         |(\lambda_0+\lambda)x_j^Ty-(\lambda_0-\lambda)sign(x_*^Ty)\lambda_0x_j^Tx_*|<2n\lambda_0\lambda-(\lambda_0-\lambda)\sqrt{n||y||_2^2-n^2\lambda_0^2}.
@@
         \begin{equation}
+            \label{eq:sedpp}
             \begin{split}
@@
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, SEDPP rule reduces to BEDPP rule. $\hat{\beta}_j(\lambda_1)=0$ if (9) holds with $\lambda=\lambda_1$.
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, SEDPP rule reduces to BEDPP rule. $\hat{\beta}_j(\lambda_1)=0$ if \eqref{eq:bedpp} holds with $\lambda=\lambda_1$.
     \end{enumerate}
@@
 
-In BEDPP rule (4), the most costly parts of computation that take $O(np)$ time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
+In BEDPP rule \eqref{eq:bedpp}, the most costly parts of computation that take $O(np)$ time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
 These quantities do not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
@@
 
-In contrast, the SEDPP rule (5) requires $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which must be recomputed at every $\lam$.
+In contrast, the SEDPP rule \eqref{eq:sedpp} requires $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which must be recomputed at every $\lam$.
 This is the primary source of computational burden, as the other terms in the rule are $\{x_j^Ty\}_{j=1}^p$, which only needs to be calculated once, and $x_j^T\hat{y}(\lambda_k)$, which can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$.
@@
 
-From the SEDPP rule (6) in Theorem 2.2, we can do screening at $\lambda_{k+1}$ given the solution at $\lambda_k$.
+From the SEDPP rule \eqref{eq:sedpp} in Theorem 2.2, we can do screening at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference.
 Now consider we are solving the lasso problem along the path $\lambda_0,...,\lambda_k,\lambda_{k+2},...,\lambda_K$ instead.
-Using the SEDPP rule, we can do screening at $\lambda_{k+2}$ as well, given the solution at $\lambda_k$, which is considered the previous solution now.
-Similarly, with solution at $\lambda_k$ as the reference, we can keep screening for a number of $\lambda$-values: $\lambda_{k+1},\lambda_{k+2},...$ until it is beneficial to update the solution at some $\lambda_{K+B}$ as the new reference and in this way all the discarded features are guaranteed to be zero.
+Using the SEDPP rule, we can do screening at $\lambda_{k+2}$ using the solution at $\lambda_k$ as a reference as well, which is considered the previous solution now.
+Similarly, with solution at $\lambda_k$ as the reference, we can keep screening for a number of $\lambda$-values: $\lambda_{k+1},\lambda_{k+2},...$ until it is beneficial to update the reference to the newer solution at some $\lambda_{K+B}$ and in this way all the discarded features are guaranteed to be zero.
 Adaptive EDPP is still a safe rule, but it is neither sequential nor one-step.
@@
         \begin{equation}
+            \label{eq:aedpp1}
             \begin{split}
@@
         \begin{equation}
+            \label{eq:aedpp2}
             |(\lambda_0+\lambda_b)x_j^Ty-(\lambda_0-\lambda_b)sign(x_*^Ty)\lambda_0x_j^Tx_*|<2n\lambda_0\lambda_b-(\lambda_0-\lambda_b)\sqrt{n||y||_2^2-n^2\lambda_0^2}.
@@
 
-For each $\lambda$-value in one update $\lambda_{k+1},...,\lambda_{k+B}$, the computation in (7) or (8) is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
+For each $\lambda$-value in one update $\lambda_{k+1},...,\lambda_{k+B}$, the computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
 The most expensive computations are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, for $j=1,2,...,p$.
 $x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the update and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that update.
-These two computations take $O(np)$ time and the rest computation in (7) and (8) take at most a lower order of $O(p)$ time.
+These two computations take $O(np)$ time and the rest computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} take at most a lower order of $O(p)$ time.
 
 Compared to one-step methods like BEDPP, after updating, the solution as the reference at $\lambda_k$ and the solution at some $\lambda_{k+b}$ in that update are usually relatively close, so screening at $\lambda_{k+b}$ using solution at $\lambda_k$ will remain powerful.
-For one-step method, as $\lambda_k$ gets further away from $\lambda_0$, the screening power can drop drastically and
-may not be any beneficial after that.
+For one-step method, as $\lambda_k$ gets further away from $\lambda_0$, the screening power can drop drastically and may not be any beneficial after that.
 Compared to sequential methods like SEDPP, the adaptive method only requires one $O(np)$ computation in one update, while SEDPP requires one $O(np)$ computation for each $\lambda$-value.
@@
 This combination is not trivial.
-For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in (4) is already computed in the previous post-convergence check in (3).
+For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in \eqref{eq:ssr} is already computed in the previous post-convergence check in \eqref{eq:kkt}.
 However, combined with safe rules, previous post-convergence check only needs to check features that are not discarded at the previous $\lambda$-value.
@@
 The rest calculations, those with $O(p)$ complexity for example, are not only faster in order, but also consume less memory and thus usually do no need out-of-core computing.
-Calculation of ${x_j^Ty}_{j=1}^p$ is needed only once for the whole solution path, so it would be neglected too.
+Calculation of $\{x_j^Ty\}_{j=1}^p$ is needed only once for the whole solution path, so it would be neglected too.
 We will assume that strong rule screening is always powerful in the sense that $|\mathcal{R}_b|=o(p)\approx0$, but safe rule screening may not.
@@
 \begin{equation}
+    \label{eq:cost}
     \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_{k+b}|}{B}.
@@
 Updating more frequently can greatly reduce the KKT condition checking cost with relatively small increase in safe screening cost.
-Also, the performance of adaptive EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
+Moreover, the performance of adaptive EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
 These suggest that simple updating rules like periodic updating cannot not be consistently efficient and we want a method that can automatically determine whether to update given current performance.
@@
 These two conditions should be close and thus this substitution should also be close to optimal.
-Combined with (9), the latter condition will approximately be:
+Combined with \eqref{eq:cost}, the latter condition will approximately be:
 
 \begin{equation}
+    \label{eq:crit}
     (B-1)|\mathcal{S}_{k+B}|-\sum_{b=1}^{B-1}|\mathcal{S}_{k+b}|>p.
@@
 In fact, it provides a robust strategy towards three most common scenarios.
-First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of (10) will be small and thus at this point we will not update to further exploit the last update.
-Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of (10) will be large and we will update the useless old reference to a new helpful one.
-Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of (10) will be approximately $p-|\mathcal{S}_1|<p$.
+First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of \eqref{eq:crit} will be small and thus at this point we will not update to further exploit the last update.
+Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of \eqref{eq:crit} will be large and we will update the useless old reference to a new helpful one.
+Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of \eqref{eq:crit} will be approximately $p-|\mathcal{S}_1|<p$.
 We will not update although old reference is useless, because if we did, the new update would become useless quickly as well.
@@
 \begin{equation}
+    \label{eq:logis}
     \hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}-\frac{1}{n}\sum_{i=1}^n\{y_i\log\pi_i(\beta)+(1-y_i)\log(1-\pi_i(\beta))\}+\lambda||\beta||_1,
@@
 The residual vector now is $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
-Then the SSR discards the $j$-th feature at $\lambda_{k+1}$ if (4) holds.
+Then the SSR discards the $j$-th feature at $\lambda_{k+1}$ if \eqref{eq:ssr} holds.
 
@@
 \begin{theorem}[Adaptive Slores]
-For the sparse logistic regression model (15), let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$.
+For the sparse logistic regression model \eqref{eq:logis}, let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$.
 Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
@@
 \begin{equation}
+    \label{eq:glasso}
     \hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}\bigg|\bigg|y-\sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2+\lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_2,
@@
 \begin{equation}
+    \label{eq:stdg}
     X_g^TX_g=nI_{p_g\times p_g},\qquad g=1,2,...,G.
@@
 \begin{theorem}[Adaptive EDPP for group lasso]
-For the group lasso problem (22), let $\lambda_0:=\max_j\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$.
+For the group lasso problem \eqref{eq:glasso}, let $\lambda_0:=\max_j\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$.
 Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-Under condition \eqref{eq:std} and (23)
+Under condition \eqref{eq:std} and \eqref{eq:stdg}
     \begin{enumerate}
@@
 
-There are several atypical cases when AHR's advantage over other methods is not as significant: \eqref{eq:lasso} $p$ or $n$ is small.
+There are several atypical cases when AHR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
 This corresponds a small data set and computation will be less challenging.

### 2021-01-08 main.tex
Edits to 2.4

@@
 
-\subsection{Hybrid safe-strong rules}
+\subsection{Other approaches to screening}
 
-The hybrid safe-strong rules (HSSR) \citep{Zeng2021} was proposed to combine SSR with any member of safe rules to take advantage of both.
-More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments.
+Hybrid safe-strong rules (HSSR) \citep{Zeng2021} were proposed to combine SSR with any safe rule, thereby taking advantage of both.
+Specifically, they recommended combining SSR with BEDPP rule, which showed the greatest efficiency in experiments.
 This algorithm discards features that are discarded by either SSR or BEDPP rule.
-Then, when doing post-convergence check, it only checks features that are discarded by SSR but not discarded by BEDPP rule, instead of all features that are discarded by SSR.
+Then, during the post-convergence check, it checks only those features discarded by SSR but not by BEDPP, as the latter can be safely discarded and do not need post-convergence checking.
+By doing so, the hybrid approach greatly reduces the computational burden of post-convergence KKT checking.
+As shown in that paper, hybrid rules combine the advantages of each type of rule, and result in an algorithm that is faster than either strong or safe rules alone.
 
-BEDPP rule is fast because heavy computation only occurs at the first step.
-SSR only requires heavy computation at the post-convergence check step.
-Now the set of features that need a post-convergence check is narrowed down by BEDPP rule and thus the cost of the post convergence check is reduced directly.
-Combining this two rules lead to a hybrid rule that outperforms using any screening rules alone in experiments.
-
-\subsection{Batch screening iterative lasso}
-
-Batch screening iterative lasso (BASIL) \citep{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches.
+Batch screening iterative lasso (BASIL) \citep{qian2019fast} was proposed to carry out SSR screening and post-convergence checking in batches.
 Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at.
-First we do the screening for each $\lambda_{k+b}$ value in the batch based on solution at $\lambda_k$ by discarding the $j$-th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
-Then at each $\lambda_{k+b}$ value we solve the lasso problem with only the features that are not discarded.
-Last at post-convergence check, we search for largest $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that KKT conditions hold for solution at $\lambda_{k+b}$ and accept only the solution from $\lambda_{k+1}$ to $\lambda_{k+b}$.
+First, screening is carried out for each $\lambda_{k+b}$ in the batch based $r(\lambda_k$ by discarding the $j$th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+The lasso problem is then solved for $\lam$ values in the batch using only features that are not discarded.
+Finally, during post-convergence checking, we search for last $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that the KKT conditions hold at $\lambda_{k+b}$ and accept only the solutions from $\lambda_{k+1}$ to $\lambda_{k+b}$.
 Next, we move to a new batch by replacing the batch head $k$ with $k+b$ and repeat the same procedure again.
 
-The BASIL is most beneficial when the whole $X$ matrix is to large to be fit into the RAM, thus we need to read in a small number of columns $x_j$ from the hard disk at a time.
-In the post-convergence check for every batch, for each $j$, $x_j$ only needs to be read in once and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$.
-Moreover, similar to SSR with ordinary post-convergence check, $x_j^Tr(\lambda_{x+b})$ computed at BASIL's post-convergence check step can be reused for screening at next batch.
+BASIL is most beneficial when $X$ is to large to be fit into the RAM, as it minimizes the amount of time spent reading from disk.
+During post-convergence checking, each $x_j$ only needs to be read in once for the entire batch and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$.
+Moreover, similar to SSR, the $x_j^Tr(\lambda_{x+b})$ values computed at BASIL's post-convergence check can be reused for screening at next batch.
+
+\pb{Mention Sure Iterative Screening and why we do not focus on it here; maybe in general, just introduce the idea of stochastic screening}
 

### 2021-01-08 main.tex
Updates from Overleaf

--- 2021-01-08 main.tex
@@
     \centering
-    \includegraphics[scale = 0.59]{plots/bin1.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[scale = 0.59]{plots/512.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.

### 2021-01-12 main.tex
Edits to 3.1

@@
 \subsection{Safe rules}
+\label{sec:safe}
 
@@
 
-\pb{Mention Sure Iterative Screening and why we do not focus on it here; maybe in general, just introduce the idea of stochastic screening}
+\pb{Mention Sure Independence Screening \citep{Fan2008} and why we do not focus on it here; maybe in general, just introduce the idea of stochastic screening}
 
-\section{Adaptive hybrid rule}
+\section{Adaptive screening}
 \label{sec:method}
 
-In this section, we will introduce the framework of adaptive hybrid rules, implement them with EDPP as the safe rule to form Ada-SSR-EDPP and propose a strategy to adaptively updating the reference.
+% In this section, we will introduce the framework of adaptive hybrid rules, implement them with EDPP as the safe rule to form Ada-SSR-EDPP and propose a strategy to adaptively updating the reference.
 
-\subsection{Adaptive safe rule}
+\subsection{Adaptive safe rules}
 
-From the SEDPP rule \eqref{eq:sedpp} in Theorem 2.2, we can do screening at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference.
-Now consider we are solving the lasso problem along the path $\lambda_0,...,\lambda_k,\lambda_{k+2},...,\lambda_K$ instead.
-Using the SEDPP rule, we can do screening at $\lambda_{k+2}$ using the solution at $\lambda_k$ as a reference as well, which is considered the previous solution now.
-Similarly, with solution at $\lambda_k$ as the reference, we can keep screening for a number of $\lambda$-values: $\lambda_{k+1},\lambda_{k+2},...$ until it is beneficial to update the reference to the newer solution at some $\lambda_{K+B}$ and in this way all the discarded features are guaranteed to be zero.
+The SEDPP rule \eqref{eq:sedpp} from Theorem 2.2 allows us to screen features at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference.
+However, since the grid of $\lam$ values is arbitrary, the rule can be just as easily applied to screen solutions at $\lam_{k+2}, \lam_{k+3}, \ldots$.
+The difference is that in typical SEDPP usage, we would update the reference solution at every step of path; here, we are proposing to re-use solutions for several values of $\lam$, only updating the reference when it is computationally beneficial to do so.
+We refer to this modification as \emph{adaptive EDPP}.
 Adaptive EDPP is still a safe rule, but it is neither sequential nor one-step.
+A similar idea would be to use the reference solution in batches, each one being used for a fixed number of $\lam$ steps.
+However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better.
+\pb{Do we have evidence for this?}
 
-Similar to SEDPP, the Adaptive EDPP rule can be stated in the following theorem:
+The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+2}, \ldots, \lam_{k+B}$.
 
@@
 
-For each $\lambda$-value in one update $\lambda_{k+1},...,\lambda_{k+B}$, the computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} is the same, except for one quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
-The most expensive computations are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, for $j=1,2,...,p$.
-$x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$-values, $x_j^Tr(\lambda_k)$ are the same for all $\lambda$-values within the update and $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so once they are computed, they can be stored and reused to avoid more computation in that update.
-These two computations take $O(np)$ time and the rest computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} take at most a lower order of $O(p)$ time.
+For each $\lambda$ value in $\lambda_{k+1},...,\lambda_{k+B}$, the computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} is the same, except for the quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
+The expensive computations in calculating these rules are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, all of which must be calculated for $j=1,2,...,p$ and thus require $O(np)$ operations; all other computations require at most $O(p)$ operations.
+However, since $x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$ values and $x_j^Tr(\lambda_k)$ is the same for all $\lambda$ values within the block, once they have been calculated once, they can be stored and reused to avoid additional computation for all remaining steps in the block.
+Note that $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so this term also can be calculated efficiently.
 
-Compared to one-step methods like BEDPP, after updating, the solution as the reference at $\lambda_k$ and the solution at some $\lambda_{k+b}$ in that update are usually relatively close, so screening at $\lambda_{k+b}$ using solution at $\lambda_k$ will remain powerful.
-For one-step method, as $\lambda_k$ gets further away from $\lambda_0$, the screening power can drop drastically and may not be any beneficial after that.
-Compared to sequential methods like SEDPP, the adaptive method only requires one $O(np)$ computation in one update, while SEDPP requires one $O(np)$ computation for each $\lambda$-value.
-The framework of adaptive safe screening can also be easily applied to other sequential safe rules, to form a family of adaptive safe rules to achieve the same improvement.
+Compared to one-step methods like BEDPP, the reference solutions are continually updated.
+As a result, the reference is always relatively close to the solution, and screening remains powerful over the entire path, unlike one-step methods where screening power drops drastically as $\lambda_k$ gets further away from $\lambda_0$.
+Compared to sequential methods like SEDPP, the adaptive method only requires $O(np)$ computations per update, while SEDPP requires $O(np)$ computations for each $\lambda$ value.
+The framework of adaptive safe screening can also be easily applied to other sequential safe rules, to form a family of adaptive safe rules.
 
-\subsection{Adaptive hybrid rule on top of adaptive safe rule}
+\subsection{Adaptive hybrid rules}
 

### 2021-01-14 main.tex
Updates from Overleaf

--- 2021-01-08 main.tex
@@
 These violations are inevitable in active-set cycling, as they occur every time a feature is added to the model.
-Sequential strong rules (SSR) \citep{tibshirani2011regression} attempt to retain the basic idea of active-set cycling, but reduce violations by retaining features that are ``close'' to entering the model.
+Sequential strong rules (SSR) \citep{tibshirani2011regression} have the basic idea of active-set cycling, but reduce violations by retaining features that are ``close'' to entering the model.
 

### 2021-01-15 main.tex
Edits to 3.2, 3.3

@@
 
-Because HSSR \citep{Zeng2021} have been shown to provide significant speedup compared to safe rules alone, we should also consider adding a strong rule screening after the adaptive EDPP rule screening.
-The SSR and adpative EDPP rule combined will form our adaptive hybrid rule: Ada-SSR-EDPP.
+Since HSSR \citep{Zeng2021} have been shown to provide significant speedup compared to safe rules alone, we also consider incorporating strong rules into adaptive EDPP screening.
+We refer to the adaptive hybrid rule formed by combining SSR and adaptive EDPP as Ada-SSR-EDPP.
 
 This combination is not trivial.
-For ordinary SSR, the quantities $x_j^Tr(\lambda_k)$ used in \eqref{eq:ssr} is already computed in the previous post-convergence check in \eqref{eq:kkt}.
-However, combined with safe rules, previous post-convergence check only needs to check features that are not discarded at the previous $\lambda$-value.
-Thus, for features that are discarded at the previous $\lambda$-value but not at the current $\lambda$-value, their corresponding $x_j^Tr(\lambda_k)$ have not been computed yet and thus cannot be used without additional cost.
+For ordinary SSR, the quantity $x_j^Tr(\lambda_k)$ used in \eqref{eq:ssr} is already computed in the previous post-convergence check in \eqref{eq:kkt}.
+However, when combined with safe rules, the post-convergence check is not applied to all features.
+For any feature that was safely discarded at the previous $\lambda$, but not the current $\lambda$, the quantity $x_j^Tr(\lambda_k)$ has not been computed yet and thus cannot be used without additional cost.
 Similar to the idea of BASIL \citep{qian2019fast}, we can also do the strong rule screening adaptively by using the latest $x_j^Tr(\lambda_k)$ available, which is computed by adaptive EDPP rule at the latest update, to reduce the number of required computations.
 
-We are going to combine adaptive EDPP rule and SSR to form the Ada-SSR-EDPP as following.
-Suppose we have a latest updated reference $\lambda_k$ with $x_j^Tr(\lambda_k)$ computed and want the solution at some following $\lambda_{k+b}$.
-First, we do adaptive EDPP rule screening.
-Second, an adaptive SSR screening is carried out on the features that have not been discarded by adaptive EDPP rule and discard features that satisfies: $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
-Third, a post-convergence check is conducted on the features that were discarded by adaptive SSR but not discarded by adaptive EDPP rule.
-Then we move on to the next $\lambda_{k+b+1}$ and repeat the same procedure, unless we determine an update is needed.
+We combine adaptive EDPP and SSR to form Ada-SSR-EDPP as follows. Let $\lambda_k$ denote the point in the path at which the EDPP reference has been most recently updated, and
+%$x_j^Tr(\lambda_k)$ computed and
+we want the solution at $\lambda_{k+b}$.
+First, carry out adaptive EDPP screening.
+Second, apply adaptive SSR screening to the features that have not been discarded by adaptive EDPP and discard any feature that satisfies $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Third, conduct a post-convergence check on the features that were discarded by adaptive SSR but not discarded by adaptive EDPP.
+This procedure is then repeated for $\lambda_{k+b+1}$ (unless an EDPP update is applied).
 
 By choosing the same reference for adaptive EDPP rule and adaptive SSR, the quantity $x_j^Tr(\lambda_k)$ only needs to be computed once and can be used by both rules.
-Also, because adaptive EDPP rule can stay powerful, it keeps the set of features that require post-convergence check small, while because basic EDPP loses power for $\lambda$-values that are far away from $\lambda_0$, post-convergence check for HSSR will be more expensive.
+Also, because the adaptive EDPP rule remains powerful, the set of features that require post-convergence checking remains small.
+This is unlike the original hybrid rules using basic EDPP, where the loss of power in EDPP screening for $\lambda \ll \lambda_0$ leads to expensive post-convergence checking.
 
@@
 
-In this section, we will show the algorithm to solve the lasso problem over the solution path with pathwise coordinate descent algorithm and our adaptive hybrid screening rule.
-The pathwise coordinate descent algorithm can be substituted by any other pathwise lasso algorithms and the adaptive EDPP can also be substituted by any other adaptive safe rules in our framework.
+Below, we provide the explicit algorithm used to solve for the lasso solution path using our proposed adaptive hybrid screening rule.
+For the numeric experiments in Section~\ref{sec:experiments}, this algorithm was implemented using pathwise coordinate descent, but the algorithm can use any algorithm for solving the lasso problem.
+Likewise, any adaptive safe rule could be substituted in place of EDPP screening.
 Note here the first reference chosen will be $\lambda_0$, where the residuals vector $r(\lambda_0)$ is just the response $y$, because all the $\hat{\beta}(\lambda_0)$ are zero.
-$\{x_j^Ty\}_{j=1}^p$ need to be computed at the beginning and stored for the whole path.
+The quantity $\{x_j^Ty\}_{j=1}^p$ is therefore computed at the beginning and stored for the whole path.
 
@@
         \Repeat{Post-convergence check passes}{
-            Pathwise lasso algorithm with only features in $\mathcal{R}_{k}$ and with warm start $\hat{\beta}(\lambda_{k}), r(\lambda_{k})$, until converge.
+            Solve lasso problem using only features in $\mathcal{R}_{k}$, with warm start $\hat{\beta}(\lambda_{k}), r(\lambda_{k})$.
 
@@
 \section{Experiments}
-\label{sec:5}
+\label{sec:experiments}
 

### 2021-01-15 main.tex
Updates from Overleaf

--- 2021-01-14 main.tex
@@
 
-\pb{Mention Sure Independence Screening \citep{Fan2008} and why we do not focus on it here; maybe in general, just introduce the idea of stochastic screening}
+In this paper, we will only focus on screening methods that never falsely discard an active feature.
+There are also almost sure screening methods where probability of false discards is positive but tends to 0 under certain conditions, such as Sure Independence Screening \citep{Fan2008}.
 
@@
 The SEDPP rule \eqref{eq:sedpp} from Theorem 2.2 allows us to screen features at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference.
-However, since the grid of $\lam$ values is arbitrary, the rule can be just as easily applied to screen solutions at $\lam_{k+2}, \lam_{k+3}, \ldots$.
+However, since the grid of $\lam$ values is arbitrary, the rule with the same reference can be just as easily applied to screen solutions at $\lam_{k+2}, \lam_{k+3}, \ldots$, until some $\lam_{k+B}$, where we update the reference to the current solution at $\lam_{k+B}$ and screen the following $\lam$ values.
 The difference is that in typical SEDPP usage, we would update the reference solution at every step of path; here, we are proposing to re-use solutions for several values of $\lam$, only updating the reference when it is computationally beneficial to do so.
@@
 
-The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+2}, \ldots, \lam_{k+B}$.
+The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+1}, \ldots, \lam_{k+B}$.
 
@@
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some next update point $k+B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some next update point $B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
         \begin{equation}
@@
     }
-    \Output{$\{\hat{\beta}(\lambda_{k})\}_{k=1}^K, r(\lambda_{k+B})$}
+    \Output{$\{\hat{\beta}(\lambda_{k})\}_{k=1}^K$}
     \caption{Pathwise lasso algorithm with adaptive hybrid rule screening}
@@
 In this section we will fill in line 11 in Algorithm 1.
-We will develop an algorithm to adaptively determining when update the reference for screening, by evaluating screening power at previous $\lambda$-values since the last update.
+We will develop an algorithm to adaptively determining when to update the reference for screening, by evaluating screening power at previous $\lambda$-values since the last update.
 Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 1.
@@
 
-To better illustrate these two effects, we considered the most naive and simple updating scheme: update the reference periodically after every other $B$ $\lambda$ values.
+To better illustrate these two effects, we considered the most naive and simple updating scheme: update the reference after every batch of $B$ $\lambda$ values.
 The following plot illustrates the effect of update delay $B$ on $|\mathcal{S}_{k+b}|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
@@
 
-BEDPP (Basic EDPP) rule is the special case of adaptive EDPP that never updates ($B=K$).
+BEDPP rule is the special case of adaptive EDPP that never updates ($B=K$).
 When the reference does not get updated for a long time, the safe rule screening will eventually fail to discard any features and make the KKT condition checking cost increase to its maximum $np$.
@@
 Adaptive EDPP can strike a balance between BEDPP and SEDPP.
-In this example, simply using fixed update period $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
+In this example, simply using fixed update delay $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
 
@@
 For the first 10 $\lambda$-values, the safe rule stays powerful, which means the old reference is still exploitable.
-We may want delay the update to reduce average safe screening cost without harming the KKT condition checking cost much.
+We may want delay the update to reduce average safe screening cost with little harm to the KKT condition checking cost.
 For the last 20 $\lambda$-values however, the screening power drops to 0 quickly, which means the reference becomes useless quickly.
-Updating more frequently can greatly reduce the KKT condition checking cost with relatively small increase in safe screening cost.
+Updating more frequently can greatly reduce the KKT condition checking cost with a relatively small additional safe screening cost.
 Moreover, the performance of adaptive EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
-These suggest that simple updating rules like periodic updating cannot not be consistently efficient and we want a method that can automatically determine whether to update given current performance.
+These suggest that simple updating rules like fixed batch updating cannot not be consistently efficient and we want a method that can automatically determine whether to update given current performance.
 
@@
 
-From previous example, we assume the average cost is a convex function of distance from last update $B$, which decreases first and then after some optimal value increases again.
+From previous example, we assume the average cost is a convex function of update delay $B$, which decreases first and then after some optimal value increases again.
 If we want to minimize the average cost per $\lambda$-value, we need to update when using the old reference for one more $\lambda$-value will increase the average cost.
@@
 In fact, it provides a robust strategy towards three most common scenarios.
-First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of \eqref{eq:crit} will be small and thus at this point we will not update to further exploit the last update.
-Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of \eqref{eq:crit} will be large and we will update the useless old reference to a new helpful one.
+First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of \eqref{eq:crit} will be small and thus at this point we will not update to further exploit the old reference.
+Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of \eqref{eq:crit} will be large and we will update the useless old reference to a helpful new one.
 Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of \eqref{eq:crit} will be approximately $p-|\mathcal{S}_1|<p$.
-We will not update although old reference is useless, because if we did, the new update would become useless quickly as well.
+We will not update although old reference is useless, because if we did, the new reference would become useless quickly as well.
 
-This adaptive updating condition fills in the condition on line 11 in Algorithm 1 and forms a complete pathwise lasso algorithm with adaptive hybrid screening.
+This updating condition fills in the condition on line 11 in Algorithm 1 and forms a complete pathwise lasso algorithm with adaptive hybrid screening.
 
@@
 Under condition \eqref{eq:std} except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
-For any $k+b>k$, let
+For some next update point $k+B$ and any $b$ s.t.
+$k<k+b\leq k+B\leq K$, let
 
@@
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for any  $k+b>k$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for some next update point $k+B$ and any $b$ s.t.
+$k<k+b\leq k+B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
         \begin{equation}
@@
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for any $b>0$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for some next update point $B$ and any $b$ s.t.
+$0<b\leq B\leq K$, $\hat{\beta}_g(\lambda_{b})=0$ if
         \begin{equation}

### 2021-01-16 main.tex
Edits to 3.4

@@
 In reality, we cannot know this prior to fitting the model -- however, through the clever use of feature screening rules, we can greatly reduce the number of times inactive features are read into memory, thereby minimizing the computational burden.
-There are many screening techniques where the solution obtained after screening will still be the global optimum given it exists, and in this paper we will only focus on this type of screening.
+There are many screening techniques where the solution obtained after screening is guaranteed to be the global optimum if one exists, and in this paper we focus only on this type of screening.
 In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision.
@@
 Typical practice when fitting lasso models is to solve for $\hat{\beta}(\lambda)$ along a decreasing sequence of $K+1$ values of $\lambda$: $\lambda_0 > \lambda_1 > \cdots > \lambda_K$.
-As we will discuss shortly, we set $\lambda_0=\max_j|x_j^Ty/n|$ throughout; this ensures that $\hat{\beta}(\lambda_0)=0$, making it a natural point from which to start.
+As we discuss shortly, we set $\lambda_0=\max_j|x_j^Ty/n|$ throughout; this ensures that $\hat{\beta}(\lambda_0)=0$, making it a natural point from which to start.
 
@@
 Features can be discarded safely, with no need for post-covergence checking, as the coefficients are guaranteed to be zero by the rule.
-We will mainly focus on enhanced dual polytope projections (EDPP) rules\citep{wang2013lasso} because they outperform other known safe rules and are easy to incorporate into our method.
+We mainly focus on enhanced dual polytope projections (EDPP) rules\citep{wang2013lasso} because they outperform other known safe rules and are easy to incorporate into our method.
 
@@
 
-In this paper, we will only focus on screening methods that never falsely discard an active feature.
-There are also almost sure screening methods where probability of false discards is positive but tends to 0 under certain conditions, such as Sure Independence Screening \citep{Fan2008}.
+In addition to the deterministic screening methods we have described, there are also probabilistic screening rules such as Sure Independence Screening \citep{Fan2008}.
+In this paper, we consider only screening methods that never falsely discard an active feature and that are thus guaranteed to converge to the global solution.
+This is not the case for probabilistic screening approaches, which construct screening rules such that the probability of incorrectly discarding active features tends to 0 asymptotically under certain conditions, but for any finite sample size, have a positive probability of converging to an inferior solution.
 
@@
 A similar idea would be to use the reference solution in batches, each one being used for a fixed number of $\lam$ steps.
-However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better.
-\pb{Do we have evidence for this?}
+However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better (see Section~\ref{sec:adaptive}).
 
@@
 \begin{algorithm}[H]
+  \label{alg:path}
     \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}\SetKwInOut{Pre}{Pre-compute}\SetKwInOut{Initialize}{Initialize}
@@
 
-In this section we will fill in line 11 in Algorithm 1.
-We will develop an algorithm to adaptively determining when to update the reference for screening, by evaluating screening power at previous $\lambda$-values since the last update.
+In this section we will fill in line 11 in Algorithm~\ref{alg:path}.
+We develop an algorithm to determine when to update the reference for screening.
+This decision is guided by evaluating screening power at previous $\lambda$ values, and is therefore adaptive, updating the reference more or less frequently as we continue along the solution path.
 Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 1.
@@
 This complexity analysis will only consider calculations with $O(np)$ complexity.
-The rest calculations, those with $O(p)$ complexity for example, are not only faster in order, but also consume less memory and thus usually do no need out-of-core computing.
-Calculation of $\{x_j^Ty\}_{j=1}^p$ is needed only once for the whole solution path, so it would be neglected too.
-We will assume that strong rule screening is always powerful in the sense that $|\mathcal{R}_b|=o(p)\approx0$, but safe rule screening may not.
-We also assume that post-convergence check will mostly pass in the first iteration and thus is only needed approximately once per $\lambda$-value.
+The remaining calculations, those with $O(p)$ complexity for example, are not only of lower order, but also consume less memory and thus usually do no require out-of-core computing.
+Calculation of $\{x_j^Ty\}_{j=1}^p$ is needed only once for the whole solution path; we ignore this as well as its computational cost is the same across all approaches.
+We assume that strong rule screening is always powerful in the sense that its set of non-discarded features, $\mathcal{R}_{k+b}$, satisfies $|\mathcal{R}_{k+b}|=o(p) \approx 0$, but that safe rule screening, with corresponding set $\mathcal{S}_{k+b}$, may not be.
+We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
 
@@
 First, the computation of $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ at the time of updating the reference, which requires $np$ multiplications.
-Then, for each $\lambda$-value $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_{k+b}\setminus\mathcal{R}_{k+b}|\approx|\mathcal{S}_{k+b}|$ KKT condition checks and each KKT condition check requires $n$ multiplications.
-These sum up to $n\sum_{i=k}^{k+B}|\mathcal{S}_k|$ multiplications, where $k+B$ is the start of the next update.
-Combining these two parts, we will have the average cost per $\lambda$-value in the update $\lambda_{k+1},...,\lambda_{k+B}$ to be
-
+Then, for each $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_{k+b} \setminus \mathcal{R}_{k+b}| \approx |\mathcal{S}_{k+b}|$ KKT condition checks, each of which requires $n$ multiplications.
+These sum to $n\sum_{i=k}^{k+B}|\mathcal{S}_k|$ multiplications, where $k+B$ is the start of the next update.
+Combining these two parts, the average cost per $\lambda$ in the block $\lambda_{k+1},...,\lambda_{k+B}$ is
 \begin{equation}
     \label{eq:cost}
-    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_{k+b}|}{B}.
+    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_{k+b}|}{B},
 \end{equation}
+where the first term represents the cost of updating the safe screening rule and the second term the cost of KKT checking.
+Delaying the next update (increasing $B$) means reusing calculations additional times, thus reducing the cost of safe screening (first term).
+However, reusing an old reference reduces the power of the safe rule, thereby increasing the cost of KKT checking (second term).
 
-The first term is the average cost for safe screening.
-Delaying next update (increasing $B$) means reusing calculation at the previous update more times for the safe screening and thus reducing the average cost.
-The second term is the average cost for KKT condition checking.
-If the old reference is reused too many times, safe rule screening becomes less powerful and the number of KKT condition checks required ($|\mathcal{S}_{k+b}|$) increases.
+To better illustrate these two effects, we considered a simple updating scheme: update the reference after every batch of $B$ $\lambda$ values.
+Figure~\ref{fig:batchsizes} illustrates the effect of the batch size $B$ on $|\mathcal{S}_{k+b}|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
+The vertical axis is the proportion of discarded features, $1-|\mathcal{S}_{k+b}|/p$.
 
-To better illustrate these two effects, we considered the most naive and simple updating scheme: update the reference after every batch of $B$ $\lambda$ values.
-The following plot illustrates the effect of update delay $B$ on $|\mathcal{S}_{k+b}|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
-The y axis is the proportion of discarded features, calculated as $1-|\mathcal{S}_{k+b}|/p$.
-
-\begin{figure}[H]
+\begin{figure}[ht]
     \centering
     \includegraphics[scale = 0.6]{plots/batchsizes.pdf}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
-    \label{fig:3.4.1}
+    \label{fig:batchsizes}
 \end{figure}
 
-BEDPP rule is the special case of adaptive EDPP that never updates ($B=K$).
-When the reference does not get updated for a long time, the safe rule screening will eventually fail to discard any features and make the KKT condition checking cost increase to its maximum $np$.
-SEDPP rule is the special case that updates at every $\lambda$ value ($B=1$).
-It remains very powerful along the path, making the KKT condition checking cost small, but the safe screening itself is costly and takes $np$ time per $\lambda$-value.
+BEDPP is the special case of adaptive EDPP that never updates ($B=K$).
+When the reference is not updated, safe rule screening will eventually fail to discard any features and the KKT condition checking cost will increase to its maximum, $np$.
+SEDPP is the special case that updates at every $\lambda$ value ($B=1$).
+It remains very powerful along the path, making the KKT condition checking cost small, but safe screening updates themselves are costly and require $np$ operations at every $\lambda$-value.
 Adaptive EDPP can strike a balance between BEDPP and SEDPP.
-In this example, simply using fixed update delay $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP.
+In this example, simply using a fixed batch size $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP \pb{I find this confusing \ldots by 50\% to more than 90\%?
+What does that mean?}.
 
-This example also shows the timing of updates should be decided carefully and adaptively.
-For the first 10 $\lambda$-values, the safe rule stays powerful, which means the old reference is still exploitable.
-We may want delay the update to reduce average safe screening cost with little harm to the KKT condition checking cost.
-For the last 20 $\lambda$-values however, the screening power drops to 0 quickly, which means the reference becomes useless quickly.
-Updating more frequently can greatly reduce the KKT condition checking cost with a relatively small additional safe screening cost.
-Moreover, the performance of adaptive EDPP rule also depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
-These suggest that simple updating rules like fixed batch updating cannot not be consistently efficient and we want a method that can automatically determine whether to update given current performance.
+This example also illustrates the appeal of choosing updates in an adaptive manner.
+For the first 10 $\lambda$ values, the safe rule stays powerful, which means the old reference is still useful.
+In this portion of the solution path, we want to delay the update in order to reduce the cost of safe screening, with little harm to the cost of KKT condition checking.
+For the last 20 $\lambda$ values however, the reference quickly becomes useless.
+In this portion of the solution path, we want to update more frequently in order to reduce the KKT condition checking cost.
+Moreover, the performance of adaptive EDPP depends on many factors such as the data, the range of $\lambda$-values and spacing between $\lambda$-values.
+Thus, simply updating the EDPP reference after a fixed batch size will not be as efficient as a method that can adaptively determine whether or not to update.
 
@@
 
-From previous example, we assume the average cost is a convex function of update delay $B$, which decreases first and then after some optimal value increases again.
-If we want to minimize the average cost per $\lambda$-value, we need to update when using the old reference for one more $\lambda$-value will increase the average cost.
-That is, we should update the reference to $\lambda_{k+B}$ when $\bar{T}_k(B+1)>\bar{T}_k(B)$.
-For practice, we will update the reference to $\lambda_{k+B}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$ instead, because $\bar{T}_k(B+1)$ cannot be calculated without doing screening at $\lambda_{k+B+1}$.
-These two conditions should be close and thus this substitution should also be close to optimal.
-Combined with \eqref{eq:cost}, the latter condition will approximately be:
+As explained in the previous section, it is reasonable to assume that the average cost, as a function of the update delay $B$, decreases at first, then reaches an optimal value before it begins increasing again.
+A reasonable approach to minimizing the average cost, therefore, is to update the reference at the point where reusing it one additional time would increase the average cost.
+That is, we should update the reference at $\lambda_{k+B}$ if $\bar{T}_k(B+1)>\bar{T}_k(B)$.
+In practice, we will instead update the reference to $\lambda_{k+B}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$, because $\bar{T}_k(B+1)$ cannot be calculated without having already carried out screening at $\lambda_{k+B+1}$.
+The two conditions should be close and thus this substitution should be near optimal.
+Combined with \eqref{eq:cost}, the latter condition is approximately
 
@@
 This updating condition is a greedy condition that only considers the cost up to the current $\lambda$ value.
-In practice, we cannot know about future $\lambda$ values so this is the most reasonable condition.
-In fact, it provides a robust strategy towards three most common scenarios.
+This is unavoidable in practice, as we cannot know about future $\lambda$ values.
+The resulting adaptive rule, \eqref{eq:crit}, provides a robust strategy that addresses the three most common scenarios.
 First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of \eqref{eq:crit} will be small and thus at this point we will not update to further exploit the old reference.
 Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of \eqref{eq:crit} will be large and we will update the useless old reference to a helpful new one.
-Last, if the screening power drops dramatically right after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of \eqref{eq:crit} will be approximately $p-|\mathcal{S}_1|<p$.
-We will not update although old reference is useless, because if we did, the new reference would become useless quickly as well.
+Last, if the screening power drops dramatically immediately after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of \eqref{eq:crit} will be approximately $p-|\mathcal{S}_1|$.
+This is less than $p$, so we will again not update.
+Although the old reference is useless, there is little point in calculating a new reference because if we did, it would quickly become useless as well.
 
-This updating condition fills in the condition on line 11 in Algorithm 1 and forms a complete pathwise lasso algorithm with adaptive hybrid screening.
+We use this updating condition at line 11 in Algorithm~\ref{alg:path} to form a complete pathwise lasso algorithm with adaptive hybrid screening.
 

### 2021-01-18 main.tex
Edits to section 4

@@
 \begin{theorem}[BEDPP]
-    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=argmax_{x_j}|x_j^Ty/n|$.
+    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$ and $x_*=\arg \max_{x_j}|x_j^Ty/n|$.
 Under \eqref{eq:std} and for any $\lambda\in(0,\lambda_0]$, we have $\hat{\beta}_j(\lambda)=0$ if
@@
 
-The structure of the adaptive hybrid rule is easily extendable to any lasso problems that have corresponding sequential strong rule and sequential safe rule.
-After an adaptive safe rule is built, we can automatically apply the adaptive strong rule and the adaptive update algorithm to form a pathwise algorithm with adaptive hybrid screening.
-We are going to derive the extensions to two lasso type problems and show these extensions improve computation efficiency.
+The structure of the adaptive hybrid rule is easily extendable to any lasso problems that have corresponding sequential strong and safe rules.
+After an adaptive safe rule is built, we can automatically apply the adaptive strong rule and adaptive update algorithm to form a pathwise algorithm with adaptive hybrid screening.
+Here, we derive extensions to two lasso-type problems and show these extensions improve computation efficiency.
 
@@
 
-The sparse logistic regression model can be defined as:
-
+Consider the sparse logistic regression model where estimates of the coefficient vector $\beta$ and intercept $\beta_0$ are obtained by minimizing
 \begin{equation}
     \label{eq:logis}
-    \hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}-\frac{1}{n}\sum_{i=1}^n\{y_i\log\pi_i(\beta)+(1-y_i)\log(1-\pi_i(\beta))\}+\lambda||\beta||_1,
+    %\hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}-
+  \frac{1}{n} \sum_{i=1}^n \big\{y_i\log\pi_i(\beta) + (1-y_i)\log(1 -\pi_i(\beta))\big\} + \lambda||\beta||_1,
 \end{equation}
 where $\pi(\beta)=\{\pi_i(\beta)\}_{i=1}^n=\{p(y_i=1|x_{i1},x_{i2},...,x_{ip})\}_{i=1}^n=\{e^{\eta_i(\beta)}/(1+e^{\eta_i(\beta)})\}_{i=1}^n$ is the predicted value vector and $\eta(\beta)=X\beta+\beta_0\mathbf{1}$ is the linear function.
-$X$ are still the $n\times p$ standardized feature matrix but in this model the $y\in\{0,1\}^n$ is an unstandardized binary response vector.
-$\beta$ is still the $p\times1$ coefficient vector but we also need a $\beta_0$ as the intercept.
+The quantity $X$ is still the $n\times p$ standardized feature matrix but in this model $y\in\{0,1\}^n$ is an unstandardized binary response vector; unlike linear regression, the intercept cannot be eliminated through centering in logistic regression.
 
-We can use SSR to do the strong rule screening with a small change according to the KKT condition.
+Sequential strong rules require only a small change for logistic regression.
 The residual vector now is $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
@@
 
-For safe rule screening, instead of EDPP rules, Slores (sparse logistic regression screening rule)\citep{wang2014safe} is used.
-It was proposed as a one-step rule but it can be extended as a sequential rule with some minimal change and thus can be extended as adaptive rule.
-Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
+Safe rules require more significant modification, as EDPP no longer applies.
+In its place, we use Slores \citep[sparse logistic regression screening rule,][]{wang2014safe}.
+It was proposed as a one-step rule but can be extended to an adaptive rule with minimal changes.
+%Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
 
 \begin{theorem}[Adaptive Slores]
-For the sparse logistic regression model \eqref{eq:logis}, let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$.
-Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-$\forall\theta\in(0,1)^n$, let
+For the sparse logistic regression model \eqref{eq:logis}, let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$, and suppose $\lambda_0>\lambda_1>...>\lambda_K$.
+For all $\theta\in(0,1)^n$, let
 
@@
 
-Under condition \eqref{eq:std} except for standardization for $y$, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
+Under the conditions on $X$ given in \eqref{eq:std}, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
 For some next update point $k+B$ and any $b$ s.t.
 $k<k+b\leq k+B\leq K$, let
-
 \begin{equation}
-    R(\lambda_{k+b})=\sqrt{\frac{n}{2}\bigg[g\bigg(\frac{\lambda_{k+b}}{\lambda_k}\theta(\lambda_k)\bigg)-g\bigg(\theta(\lambda_k)\bigg)+\bigg(1-\frac{\lambda_{k+b}}{\lambda_k}\bigg)\bigg(\nabla g\big(\theta(\lambda_k)\big)\bigg)^T\theta(\lambda_k)\bigg]},
+  R(\lambda_{k+b}) = \sqrt{\frac{n}{2} \bigg[g\bigg(\frac{\lambda_{k+b}}{\lambda_k}\theta(\lambda_k)\bigg) - g\bigg(\theta(\lambda_k)\bigg) + \bigg(1 - \frac{\lambda_{k+b}}{\lambda_k}\bigg) \bigg(\nabla g\big(\theta(\lambda_k)\big)\bigg)^T\theta(\lambda_k)\bigg]},
 \end{equation}
-
-$d(\lambda_{k+b})=\sqrt{n}(\lambda_k-\lambda_{k+b})/R(\lambda_{k+b})$. For $\xi = -1,1$ and $j=1,2,...,p$,
+and $d(\lambda_{k+b})=\sqrt{n}(\lambda_k-\lambda_{k+b})/R(\lambda_{k+b})$. For $\xi = -1,1$ and $j=1,2,...,p$,
 
 \begin{enumerate}
-    \item If $-\xi sign(x_*^Ty)x_j^Tx_*\geq nd(\lambda_{k+b})$, then
+    \item If $-\xi \sign(x_*^Ty)x_j^Tx_*\geq nd(\lambda_{k+b})$, then
 
@@
 
-    \item If $-\xi sign(x_*^Ty)x_j^Tx_*< nd(\lambda_{k+b})$, then
+    \item If $-\xi \sign(x_*^Ty)x_j^Tx_*< nd(\lambda_{k+b})$, then
 
     \begin{equation}
-        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=R(\lambda_{k+b})\sqrt{n+nu_\xi^2-2\xi u_\xi sign(x_*^Ty)x_j^Tx_*}-nu_\xi(\lambda_k-\lambda_{k+b})-\xi x_j^Tr(\lambda_k),
+        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=R(\lambda_{k+b})\sqrt{n+nu_\xi^2-2\xi u_\xi \sign(x_*^Ty)x_j^Tx_*}-nu_\xi(\lambda_k-\lambda_{k+b})-\xi x_j^Tr(\lambda_k),
     \end{equation}
@@
         a_0&=(x_j^Tx_*)^2-n^2d^2(\lambda_{k+b}),\nonumber\\
-        a_1&=-2n\,sign(x_*^Ty)x_j^Tx_*\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
+        a_1&=-2n\,\sign(x_*^Ty)x_j^Tx_*\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
         a_2&=n^2\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
@@
   \end{equation}
+  \pb{This appears to be missing something. This is not a true/false expression, it's just a number.}
 \end{theorem}
 
-When computing the adaptive Slores, $\{x_j^Ty\}_{j=1}^p$ needs to be computed only once, stored and reused for the whole solution path.
-$\{x_j^Tx_*\}_{j=1}^p$ can be reused unless $x_*$ changes.
-Other than those two terms, the only term that requires expensive $O(np)$ computation is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which only needs to be computed at the time of each update.
-Thus algorithm 1 for adaptive hybrid rule can be done with Slores rule instead of EDPP rule to form Ada-SSR-Slores that does screening for sparse logistic regression model.
+When computing the adaptive Slores, $\{x_j^Ty\}_{j=1}^p$ needs to be computed only once, after which it can be stored and reused for the whole solution path.
+The quantity $\{x_j^Tx_*\}_{j=1}^p$ can be similarly reused unless $x_*$ changes, which happens if the corresponding regression coefficient drops out of the model; this is relatively rare, but can happen.
+Other than those two terms, the only term that requires expensive $O(np)$ computations is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which needs to be computed only when we update the reference solution.
+Thus Algorithm~\ref{alg:path} can be applies to the sparse logistic model, with Slores replacing EDPP.
+We refer to the resulting algorithm as Ada-SSR-Slores.
 
@@
 
-The group lasso problem \citep{yuan2006model} can be defined as:
-
+The group lasso model \citep{yuan2006model} estimates $\beta$ by minimizing
 \begin{equation}
     \label{eq:glasso}
-    \hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}\frac{1}{2n}\bigg|\bigg|y-\sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2+\lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_2,
+    %\hat{\beta}(\lambda) = \underset{\beta\in \mathbb{R}^p}{\mathrm{argmin}}
+    \frac{1}{2n}\bigg|\bigg|y - \sum_{g=1}^GX_g\beta_g\bigg|\bigg|_2^2 + \lambda\sum_{g=1}^G\sqrt{p_g}||\beta_g||_2,
 \end{equation}
-where $\beta=(\beta_1^T,...,\beta_G^T)^T$, $X_g$ is a $n\times p_g$ sub-matrix consisting of columns of $X$ corresponding to features in group $g$, $g=1,2,...,G$.
-Besides standardization in \eqref{eq:std}, we apply an addition level of standardization at the group level\citep{breheny2015group}:
+where $\beta=(\beta_1^T,...,\beta_G^T)^T$, $X_g$ is a $n\times p_g$ sub-matrix consisting of columns of $X$ corresponding to the features in group $g$, $g=1,2,...,G$.
+In addition to the standardization conditions given in \eqref{eq:std}, we apply an additional standardization at the group level \citep{breheny2015group}:
 
@@
 
-According to the KKT condition, we can use SSR to do strong rule screening.
-Given $r(\lambda_k)=y-\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, we discard features in the $g$-th group at $\lambda_{k+1}$ if:
-
-\begin{equation}
-    \bigg|\bigg|\frac{1}{n}X_g^Tr(\lambda_k)\bigg|\bigg|_2<\sqrt{p_g}(2\lambda_{k+1}-\lambda_k).
+We can again use the KKT conditions to derive sequential strong rules. Given $r(\lambda_k)=y-\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, we discard features in the $g$-th group at $\lambda_{k+1}$ if
+\begin{equation} \bigg|\bigg|\frac{1}{n}X_g^Tr(\lambda_k)\bigg|\bigg|_2<\sqrt{p_g}(2\lambda_{k+1}-\lambda_k).
 \end{equation}
-
-For safe rule screening, we have SEDPP for group lasso\citep{wang2013lasso} and we can extend it the adaptive EDPP rule for group lasso.
+For safe rule screening, SEDPP rules for group lasso have been derived previously \citep{wang2013lasso}.
+Below, we extend these results to the adaptive case tend them to it the adaptive EDPP rule for group lasso.
 
 \begin{theorem}[Adaptive EDPP for group lasso]
-For the group lasso problem \eqref{eq:glasso}, let $\lambda_0:=\max_j\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$.
-Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$.
-Under condition \eqref{eq:std} and \eqref{eq:stdg}
+  For the group lasso problem \eqref{eq:glasso}, suppose $\lambda_0>\lambda_1>...>\lambda_K$, with $\lambda_0:= \max_j ||X_g^Ty||_2 / (n\sqrt{p_g})$.
+Under conditions \eqref{eq:std} and \eqref{eq:stdg},
     \begin{enumerate}
@@
                 &\left|\left|2\lambda_{k+b}X_g^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( X_g^Ty-\frac{y^T\hat{y}(\lambda_k)X_g^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\right|_2\\
-                &<2n\lambda_k\lambda_{k+b}\sqrt{p_g}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
+                &<2n\lambda_k\lambda_{k+b}\sqrt{p_g}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}.
             \end{split}
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=argmax_{X_g}\frac{||X_g^Ty||_2}{n\sqrt{p_g}}$ with dimension $n\times p_*$, then for some next update point $B$ and any $b$ s.t.
+        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=\arg \max_{X_g} ||X_g^Ty||_2 / (n\sqrt{p_g})$ with dimension $n\times p_*$, then for some next update point $B$ and any $b$ s.t.
 $0<b\leq B\leq K$, $\hat{\beta}_g(\lambda_{b})=0$ if
@@
 
-Similar to Adaptive EDPP rule, three expensive computations are $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$ and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
-The first and second only need to be computed once for the whole solution path.
-The last only needs to be computed at the time of each update with cost $O(np)$.
+Similar to the Adaptive EDPP rule, there are three expensive computations: $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$, and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
+The first two only need to be computed once for the whole solution path.
+The final term needs to be computed only when the reference solution is updated, with cost $O(np)$.
 The adaptive EDPP for group lasso, combined with the previous SSR, forms the Ada-SSR-EDPP for group lasso.

### 2021-01-19 main.tex
Updates from Overleaf

--- 2021-01-15 main.tex
@@
 A similar idea would be to use the reference solution in batches, each one being used for a fixed number of $\lam$ steps.
-However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better.
+However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better as we will show in \ref{sec:complexity}.
 \pb{Do we have evidence for this?}
@@
 \subsubsection{Complexity analysis}
+\label{sec:complexity}
 

### 2021-01-19 main.tex

--- 2021-01-18 main.tex
@@
 A similar idea would be to use the reference solution in batches, each one being used for a fixed number of $\lam$ steps.
-However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better (see Section~\ref{sec:adaptive}).
-
+However, since an appropriate batch size is difficult to determine ahead of time, and also because the ideal size changes along the path, we find that an adaptive approach is better as we will show in \ref{sec:complexity}.
 The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+1}, \ldots, \lam_{k+B}$.

### 2021-01-19 main.tex
Fix merge.

--- 2021-01-18 main.tex
@@
 We combine adaptive EDPP and SSR to form Ada-SSR-EDPP as follows. Let $\lambda_k$ denote the point in the path at which the EDPP reference has been most recently updated, and
-%$x_j^Tr(\lambda_k)$ computed and
 we want the solution at $\lambda_{k+b}$.
@@
 This decision is guided by evaluating screening power at previous $\lambda$ values, and is therefore adaptive, updating the reference more or less frequently as we continue along the solution path.
-Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm 1.
+Our goal is to minimize the computation cost, so we will first analyse computation complexity for each part in Algorithm~\ref{alg:path}.
 Then we will propose an adaptive algorithm that can minimize the entire computation cost.
@@
 Adaptive EDPP can strike a balance between BEDPP and SEDPP.
-In this example, simply using a fixed batch size $B=10$ can reduce the safe screening cost by 90\% compared to SEDPP and reduce the KKT checking cost by 50\% to more than 90\% compared BEDPP \pb{I find this confusing \ldots by 50\% to more than 90\%?
-What does that mean?}.
+In this example, simply using a fixed batch size $B=10$ can reduce the safe rule updating cost by 90\% compared to SEDPP and reduce the KKT checking cost by about 80\% compared to BEDPP.
 
@@
 It was proposed as a one-step rule but can be extended to an adaptive rule with minimal changes.
-%Let $\Tilde{y}=2y-1\in\{-1,1\}^n$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
 
@@
   \begin{equation}
-    \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))
+    \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))<n\lambda_{k+b}
   \end{equation}
-  \pb{This appears to be missing something. This is not a true/false expression, it's just a number.}
 \end{theorem}

### 2021-01-19 main.tex
Edits to 5.1

@@
     \item A new feature screening framework (Section 3.1,3.2), which updates the reference for screening along the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
-    \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section 3.4,4.1,4.2).
+    \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP \pb{do we need these abbreviations?
+We never really use them.
+We just use AHS in the figures/tables} for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section 3.4,4.1,4.2).
     \item An algorithm to determine when to update to a new reference $\lambda$ value for best efficiency (Section \ref{sec:adaptive}).
@@
 
-In this section conduct experiments solving lasso model on both simulated data sets and real data sets, to show our proposed adaptive hybrid rule screening method outperforms previous screening method such as SSR, SEDPP, HSSR and Slores.
-Active-set cycling in \ref{sec:active} is always used with all screening methods because it can be easily combined with any screening methods with no extra cost.
+In this section, we demonstrate that our proposed adaptive hybrid screening method outperforms other methods through numerical experiments involving both simulated and real dats.
+Active-set cycling (Section~\ref{sec:active}) is used in combination with all methods because it can be easily combined with any screening method at no extra cost.
 
-The adaptive hybrid rule screening is implemented in the \textbf{R} package \textbf{biglasso} and we will use this package for our experiment.
-Compared to traditional packages that solve lasso problem, such as \textbf{glmnet}, \textbf{biglasso} focuses on efficiently solving lasso problem with high-dimensional data sets that have a large number of features.
-First, it utilized the memory-mapping techniques that stores the data set on the disk and reads in only the part of the data necessary for model solving.
-Second, it applied screening rules to reduce both the computation cost and memory cost as we have discussed.
-These two features together help \textbf{biglasso} to outperform other packages.
-We will show that our new screening method will result in a new version of the package that shows significant improvement compared to previous version.
+The proposed adaptive hybrid screening approach is implemented in the R package \textbf{biglasso} and we use this package in our experiments.
+Compared to other packages that fit lasso models, such as \textbf{glmnet}, \textbf{biglasso} focuses on data sets that are too large to fit into memory.
+In particular, it utilizes memory-mapping techniques that store the data on disk and read in only the portion necessary for model solving.
+Furthermore, its screening rules emphasize both the computation and memory costs as we have discussed.
+The adaptive screening approach proposed in this manuscript led to the development of a new version of the package, \textbf{biglasso} 1.4, that is significantly faster than previous versions.
 
-For all the following experiments, we will solve the lasso model along a path of $100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_K=0.05\lambda_0$ and the rest $\lambda$-values equally spaced between on log scale.
+For all the following experiments, we solve the lasso model along a path of $100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_L=0.05\lambda_0$ and the intermediate values equally spaced on a log scale.
+Note that $L$ denotes the number of $\lam$ points that the lasso problem is solved along the coefficient path.
+\pb{is this inconsistent?
+Don't we use K everywhere else in the paper?}
 
@@
 
-In this part, we will solve the standard lasso problem \eqref{eq:lasso} with different screening methods: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive hybrid rule (AHR).
-The AHR is Ada-SSR-EDPP which uses EDPP as the safe rule.
-Note that AC is always incorporated with all other screening rules, so using AC alone can be considered as a baseline for this comparison.
+We begin by comparing screening methods for solving the standard lasso problem \eqref{eq:lasso}: Active-set Cycling (AC) alone, SSR, SEDPP, HSSR and adaptive hybrid rule (AHR; referred to as Ada-SSR-EDPP earlier in the paper).
+Note that because AC is incorporated into all of the other screening rules, AC alone can be considered as the baseline for this comparison.
 
-The data will be simulated from the model: $y=X\beta+0.1\epsilon$.
-$X$ and $\epsilon$ are sampled i.i.d from $N(0,1)$.
-$\beta$ will have $s$ randomly selected elements equally spaced between $[-\beta_{max},\beta_{max}]$ and the rest $p-s$ elements are zeros.
-The lasso model is solved along a grid of $L$ $\lambda$-values equally spaced on the log scale between $[\lambda_{\max},\lambda_{\min}]$.
-Each setting is replicated $10$ times to calculate the average time cost.
-By default we set $p=10,000$, $n=1,000$, $s=20$, $\beta_{max}=1$, $L=100$, $\lambda_{\min}/\lambda_{\max}=0.05$.
+The data is simulated from the model: $y=X\beta+0.1\epsilon$.
+The elements of $X$ and $\epsilon$ are sampled i.i.d from $N(0,1)$.
+The coefficient vector $\beta$ contains $s$ randomly selected elements equally spaced between $[-\beta_{\max},\beta_{\max}]$, with the remaining $p-s$ elements equal to zero.
+Each setting is replicated $10$ times to calculate the average time needed to solve the coefficient path.
+By default we set $p=10,000$, $n=1,000$, $s=20$, $\beta_{\max}=1$, $L=100$, $\lambda_{\min}/\lambda_{\max}=0.05$.
 We consider the following cases where one of the variables above is varying at a time:
@@
     \item \textbf{Varying sample size:} $n$ from $200$ to $10,000$.
-    \item \textbf{Varying signal strength:} $\beta_{max}$ from $0.05$ to $1$.
-    \item \textbf{Varying sparsity:} $s$ from $10$ to $300$ while controlling total signal size $\beta_{max}\times s=20$.
+    \item \textbf{Varying signal strength:} $\beta_{\max}$ from $0.05$ to $1$.
+    \item \textbf{Varying sparsity:} $s$ from $10$ to $300$ while controlling total signal size $\beta_{\max}\times s=20$.
     \item \textbf{Varying number of grid points:}  $L$ from $20$ to $1000$.
@@
 Second column: varying sample size $n$.
-Third column: varying signal strength $\beta_{max}$.
+Third column: varying signal strength $\beta_{\max}$.
 Fourth column: varying sparsity $s$.}
@@
 Figure 2 and Figure 3 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
-The AHR is uniformly the fastest under all settings.
-Most of the time it is 2-8 times faster than any other screening methods.
-It outperforms other methods especially when the data set is large (large $n$ or large $p$), the active features are sparse among all features (small $s$) or the grid of $\lambda$-value is fine (large $L$ or $\lambda_{\min}/\lambda_{\max}$).
+AHR is uniformly the fastest under all settings, typically 2-8 times faster than any other screening method.
+The difference is largest when the data set is large (large $n$ or large $p$), the active features are highly sparse (small $s$) or the grid of $\lambda$-value is fine (large $L$ or $\lambda_{\min}/\lambda_{\max}$).
+\pb{For example, when $L=1000$, AHR is XXXX times faster than any other approach.}
 
-There are several atypical cases when AHR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
-This corresponds a small data set and computation will be less challenging.
-(2) $\beta_{max}$ is close to zero.
-This means all the nonzero coefficients are close to zero and are hard to be distinguished from zero coefficients.
-This can cause problem for any statistical learning methods.
+There are, however, cases when AHR's advantage over other methods is not as significant: (1) $p$ or $n$ is small.
+For small data sets, computation is less challenging and screening rules play a smaller role.
+(2) $\beta_{\max}$ is close to zero.
+When the nonzero coefficients are close to zero, they are hard to distinguish from each other.
+This tends to cause problems for any statistical learning method.
 (3) $s$ is large.
-In this case, the underlying model that generate the data set is not sparse in the sense that proportion of nonzero coefficients is not small.
-Lasso model would not be the optimal model to analyse such an data set.
+In this case, the solution is ``dense'' and screening rules have less ability to leverage sparsity to computational advantage.
 (4) $L$ is small.
-In this case, only a coarse grid of $\lambda$-values are considered.
-The $\lambda$-value selected in this case may be far from optimal.
+In this case, only a coarse grid of $\lambda$-values are considered, providing less information for an adaptive approach to use.
+A practical downside to choosing a small $L$ is that the selected $\lam$ may be far from optimal.
 
-We also tried varying other factors, for example, varying the correlation among features in $X$, varying the sparsity with fixed signal strength or varying the minimum $\lambda$-value $\lambda_K$.
-The AHR also shows uniform advantage over other method when those factors vary in reasonable ranges.
+We also tried varying other factors, for example: the correlation among features in $X$, sparsity with fixed signal strength, and the minimum value $\lambda_K$.
+The results of these experiments were very similar, with AHR continuing to show a uniform advantage over other methods.
 
@@
 
-In this part, we will replicate the previous experiment, expect that now we will solve the sparse logistic regression model with the following screening methods: SSR, HSSR with Slores as the safe rule (HSlores), and the adaptive method Ada-SSR-Slores with Slores as the safe rule (ASlores).
-SSR is implemented in all of the three screening methods so it will be considered as the baseline.
+We now turn our attention to the sparse logistic regression model, comparing sequential strong rules (SSR), hybrid rules using Slores as the safe rule (HSlores), and adaptive screening using Slores as the safe rule (ASlores).
+SSR is implemented in all three methods and will be considered the baseline.
 
-The data will be simulated from the model: $y=\mathbf{1}\{X\beta+0.1\epsilon >0\}$.
-$X$ and $\epsilon$ are sampled i.i.d from $N(0,1)$.
-$\beta$ will have $s$ randomly selected elements equally spaced between $[-\beta_{max},\beta_{max}]$ and the rest $p-s$ elements are zeros.
+The data are simulated from the model: $y=\mathbf{1}\{X\beta+0.1\epsilon >0\}$.
+As before, $X$ and $\epsilon$ are sampled i.i.d from $N(0,1)$, while $\beta$ has $s$ randomly selected elements equally spaced between $[-\beta_{\max},\beta_{\max}]$.
 Each setting is replicated $10$ times to calculate the average time cost.
-We consider the same 7 cases we have considered in the previous experiment.
+We consider the same 7 cases as in the previous experiment.
 
@@
 Figure 4 and 5 show the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
-ASlores is also uniformly faster than other methods and this improvement is significant except for some atypical cases motioned before.
+The overall pattern is the same as for sparse linear regression, with adaptive screening uniformly faster than all other methods.
+The speedup is smaller in magnitude than for linear regression because the Slores rule is less powerful than EDPP.
+Nevertheless, the improvement in speed is still dramatic in many cases \pb{provide number here for, say, $L=500$}.
 

### 2021-01-20 main.tex
Updates from Overleaf

@@
     \item A new feature screening framework (Section 3.1,3.2), which updates the reference for screening along the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
-    \item Three specific applications of this framework, Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR-EDPP \pb{do we need these abbreviations?
-We never really use them.
-We just use AHS in the figures/tables} for group lasso, for fitting lasso-penalized linear regression and logistic regression models, respectively (Section 3.4,4.1,4.2).
+    \item Three specific applications of this framework, for fitting lasso-penalized linear regression, lasso-penalized logistic regression and group lasso models, respectively (Section~\ref{sec:method},~\ref{sec:logis},~\ref{sec:group}).
     \item An algorithm to determine when to update to a new reference $\lambda$ value for best efficiency (Section \ref{sec:adaptive}).
     \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
-    \item The Ada-SSR-SEDPP and Ada-SSR-Slores were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso} \citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
+    \item The new feature screening methods for lasso-penalized linear regression and logistic regression were implemented and added as new options to the publicly accessible \textbf{R} package \textbf{biglasso} \citep{zeng2017biglasso}, which was used to carry out the analyses in this manuscript.
 \end{itemize}
@@
 
-Typical practice when fitting lasso models is to solve for $\hat{\beta}(\lambda)$ along a decreasing sequence of $K+1$ values of $\lambda$: $\lambda_0 > \lambda_1 > \cdots > \lambda_K$.
+Typical practice when fitting lasso models is to solve for $\hat{\beta}(\lambda)$ along a decreasing sequence of $L+1$ values of $\lambda$: $\lambda_0 > \lambda_1 > \cdots > \lambda_L$.
 As we discuss shortly, we set $\lambda_0=\max_j|x_j^Ty/n|$ throughout; this ensures that $\hat{\beta}(\lambda_0)=0$, making it a natural point from which to start.
@@
 This can be done efficiently by using ``warm starts'': using previous points on the path as initial values, as these are likely to be relatively close to the solution.
-For the model at any $\lambda$-value $\lambda_{k+1}$, letting $r(\lambda_{k+1}) \equiv y-X\hat{\beta}(\lambda_{k+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{k+1})$ can be computed using the previous solution $\hat{\beta}(\lambda_k)$ as the initial value in the algorithm.
+For the model at any $\lambda$-value $\lambda_{l+1}$, letting $r(\lambda_{l+1}) \equiv y-X\hat{\beta}(\lambda_{l+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{l+1})$ can be computed using the previous solution $\hat{\beta}(\lambda_l)$ as the initial value in the algorithm.
 Pathwise coordinate descent is a algorithm that takes advantage of this idea and will be used as the lasso algorithm for the rest of the paper.
@@
 It can be implemented on top of any lasso algorithm with no additional cost.
-When solving the coefficients for at $\lambda_{k+1}$, AC considers only features whose coefficients were non-zero at $\lambda_k$ and discards the other features.
+When solving the coefficients for at $\lambda_{l+1}$, AC considers only features whose coefficients were non-zero at $\lambda_l$ and discards the other features.
 The lasso problem is then solved over this reduced number of coefficients.
@@
 
-Given the solution $\hat{\beta}(\lambda_k)$ and residual vector $r(\lambda_k)=y-X\hat{\beta}(\lambda_k)$ at $\lambda_k$, the SSR discards the $j$-th feature at $\lambda_{k+1}$ if:
+Given the solution $\hat{\beta}(\lambda_l)$ and residual vector $r(\lambda_l)=y-X\hat{\beta}(\lambda_l)$ at $\lambda_l$, the SSR discards the $j$-th feature at $\lambda_{l+1}$ if:
 \begin{equation}
   \label{eq:ssr}
-  |x_j^Tr(\lambda_k)/n|<2\lambda_{k+1}-\lambda_k.
+  |x_j^Tr(\lambda_l)/n|<2\lambda_{l+1}-\lambda_l.
 \end{equation}
@@
 
-SSR possesses the nice property that the quantity $x_j^Tr(\lambda_k)/n$ needed for SSR screening \eqref{eq:ssr} at $\lambda_{k+1}$ has already been calculated during post-convergence checking at $\lambda_k$ in \eqref{eq:kkt}.
-As this is the only computationally intensive aspect of SSR screening, and SSR violations are rare, its computational cost is roughly $O(npK)$.
+SSR possesses the nice property that the quantity $x_j^Tr(\lambda_l)/n$ needed for SSR screening \eqref{eq:ssr} at $\lambda_{l+1}$ has already been calculated during post-convergence checking at $\lambda_l$ in \eqref{eq:kkt}.
+As this is the only computationally intensive aspect of SSR screening, and SSR violations are rare, its computational cost is roughly $O(npL)$.
 
@@
 \begin{theorem}[SEDPP]
-    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$. Under condition \eqref{eq:std}
+    For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$. Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_L$. Under condition \eqref{eq:std}
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then $\hat{\beta}_j(\lambda_{k+1})=0$ if
+        \item For any $l=1,2,...,L-1$, given $\hat{\beta}(\lambda_l)$, $r(\lambda_l)$ and $\hat{y}(\lambda_l):=X\hat{\beta}(\lambda_l)$, then $\hat{\beta}_j(\lambda_{l+1})=0$ if
         \begin{equation}
@@
             \begin{split}
-                &\left|2\lambda_{k+1}x_j^Tr(\lambda_k)+(\lambda_k-\lambda_{k+1})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_k)x_j^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\\&<2n\lambda_k\lambda_{k+1}-(\lambda_k-\lambda_{k+1})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
+                &\left|2\lambda_{l+1}x_j^Tr(\lambda_l)+(\lambda_l-\lambda_{l+1})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_l)x_j^T\hat{y}(\lambda_l)}{||\hat{y}(\lambda_l)||_2^2}\right)\right|\\&<2n\lambda_l\lambda_{l+1}-(\lambda_l-\lambda_{l+1})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_l))^2}{||\hat{y}(\lambda_l)||_2^2}}
             \end{split}
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, SEDPP rule reduces to BEDPP rule. $\hat{\beta}_j(\lambda_1)=0$ if \eqref{eq:bedpp} holds with $\lambda=\lambda_1$.
+        \item For l=0, i.e., $\lambda_l=\lambda_0$, SEDPP rule reduces to BEDPP rule. $\hat{\beta}_j(\lambda_1)=0$ if \eqref{eq:bedpp} holds with $\lambda=\lambda_1$.
     \end{enumerate}
@@
 In BEDPP rule \eqref{eq:bedpp}, the most costly parts of computation that take $O(np)$ time are the computation of $\{x_j^Ty\}_{j=1}^p$ and $\{x_j^Tx_*\}_{j=1}^p$ ($x_*^Ty$ is an element of $\{x_j^Ty\}_{j=1}^p$).
-These quantities do not depend on $\lambda_k$ and thus only need to be computed once at the beginning and stored.
+These quantities do not depend on $\lambda_l$ and thus only need to be computed once at the beginning and stored.
 After this step, other computation of the rule takes almost zero time, so BEDPP rule can be viewed as an one-step rule with $O(np)$ cost.
 
-In contrast, the SEDPP rule \eqref{eq:sedpp} requires $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which must be recomputed at every $\lam$.
-This is the primary source of computational burden, as the other terms in the rule are $\{x_j^Ty\}_{j=1}^p$, which only needs to be calculated once, and $x_j^T\hat{y}(\lambda_k)$, which can be computed as $x_j^Ty-x_j^Tr(\lambda_k)$.
-Thus, the sequential safe rule SEDPP requires $O(npK)$ operations.
+In contrast, the SEDPP rule \eqref{eq:sedpp} requires $\{x_j^Tr(\lambda_l)\}_{j=1}^p$, which must be recomputed at every $\lam$.
+This is the primary source of computational burden, as the other terms in the rule are $\{x_j^Ty\}_{j=1}^p$, which only needs to be calculated once, and $x_j^T\hat{y}(\lambda_l)$, which can be computed as $x_j^Ty-x_j^Tr(\lambda_l)$.
+Thus, the sequential safe rule SEDPP requires $O(npL)$ operations.
 
-Comparing the two, BEDPP is much faster, but at each $\lambda_k$, it is bounding $r(\lambda_k)$ using $r(\lambda_0)=y$ as a reference.
-As $\lambda_k$ gets further away from $\lambda_0$, this bound becomes less precise and the screening rule becomes less powerful.
-SEDPP is slower, but at each $\lambda_{k+1}$, it uses $r(\lambda_{k})$ as the reference.
-Because $\lambda_{k+1}$ and $\lambda_k$ are close, the bound remains tight and screening continues to be powerful over the entire path.
+Comparing the two, BEDPP is much faster, but at each $\lambda_l$, it is bounding $r(\lambda_l)$ using $r(\lambda_0)=y$ as a reference.
+As $\lambda_l$ gets further away from $\lambda_0$, this bound becomes less precise and the screening rule becomes less powerful.
+SEDPP is slower, but at each $\lambda_{l+1}$, it uses $r(\lambda_{l})$ as the reference.
+Because $\lambda_{l+1}$ and $\lambda_l$ are close, the bound remains tight and screening continues to be powerful over the entire path.
 
@@
 Batch screening iterative lasso (BASIL) \citep{qian2019fast} was proposed to carry out SSR screening and post-convergence checking in batches.
-Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at.
-First, screening is carried out for each $\lambda_{k+b}$ in the batch based $r(\lambda_k$ by discarding the $j$th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Suppose we have a previous solution $\hat{\beta}(\lambda_l)$ and $r(\lambda_l)$ and the batch of $\{\lambda_{l+1},\lambda_{l+2},...,\lambda_{l+B}\}$ values we are going to solve at.
+First, screening is carried out for each $\lambda_{l+b}$ in the batch based $r(\lambda_l$ by discarding the $j$th feature if $|x_j^Tr(\lambda_l)/n|<2\lambda_{l+b}-\lambda_l$.
 The lasso problem is then solved for $\lam$ values in the batch using only features that are not discarded.
-Finally, during post-convergence checking, we search for last $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that the KKT conditions hold at $\lambda_{k+b}$ and accept only the solutions from $\lambda_{k+1}$ to $\lambda_{k+b}$.
-Next, we move to a new batch by replacing the batch head $k$ with $k+b$ and repeat the same procedure again.
+Finally, during post-convergence checking, we search for last $l+b$ in the batch $\{l+1,l+2,...,l+B\}$ such that the KKT conditions hold at $\lambda_{l+b}$ and accept only the solutions from $\lambda_{l+1}$ to $\lambda_{l+b}$.
+Next, we move to a new batch by replacing the batch head $l$ with $l+b$ and repeat the same procedure again.
 
 BASIL is most beneficial when $X$ is to large to be fit into the RAM, as it minimizes the amount of time spent reading from disk.
-During post-convergence checking, each $x_j$ only needs to be read in once for the entire batch and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$.
-Moreover, similar to SSR, the $x_j^Tr(\lambda_{x+b})$ values computed at BASIL's post-convergence check can be reused for screening at next batch.
+During post-convergence checking, each $x_j$ only needs to be read in once for the entire batch and can be used multiple times for $\{\lambda_{l+1},\lambda_{l+2},...,\lambda_{l+B}\}$.
+Moreover, similar to SSR, the $x_j^Tr(\lambda_{l+b})$ values computed at BASIL's post-convergence check can be reused for screening at next batch.
 
@@
 
-The SEDPP rule \eqref{eq:sedpp} from Theorem 2.2 allows us to screen features at $\lambda_{k+1}$ using the solution at $\lambda_k$ as a reference.
-However, since the grid of $\lam$ values is arbitrary, the rule with the same reference can be just as easily applied to screen solutions at $\lam_{k+2}, \lam_{k+3}, \ldots$, until some $\lam_{k+B}$, where we update the reference to the current solution at $\lam_{k+B}$ and screen the following $\lam$ values.
+The SEDPP rule \eqref{eq:sedpp} from Theorem 2.2 allows us to screen features at $\lambda_{l+1}$ using the solution at $\lambda_l$ as a reference.
+However, since the grid of $\lam$ values is arbitrary, the rule with the same reference can be just as easily applied to screen solutions at $\lam_{l+2}, \lam_{l+3}, \ldots$, until some $\lam_{l+B}$, where we update the reference to the current solution at $\lam_{l+B}$ and screen the following $\lam$ values.
 The difference is that in typical SEDPP usage, we would update the reference solution at every step of path; here, we are proposing to re-use solutions for several values of $\lam$, only updating the reference when it is computationally beneficial to do so.
@@
 
-The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_k$ is used to calculate screening rules at $\lam_{k+1}, \ldots, \lam_{k+B}$.
+The Adaptive EDPP rule can be stated in the following theorem, which simply restates the theorems from Section~\ref{sec:safe} in terms of this new paradigm in which a single reference solution at $\lam_l$ is used to calculate screening rules at $\lam_{l+1}, \ldots, \lam_{l+B}$.
 
@@
     For the lasso problem \eqref{eq:lasso}, let $\lambda_0:=\max_j|x_j^Ty/n|$.
-Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_K$ and the last updated reference point is $\lambda_k$.
+Suppose we have a sequence of $\lambda$ values $\lambda_0>\lambda_1>...>\lambda_L$ and the last updated reference point is $\lambda_l$.
 Under condition \eqref{eq:std}
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=X\hat{\beta}(\lambda_k)$, then for some next update point $k+B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \item For any $l=1,2,...,L-1$, given $\hat{\beta}(\lambda_l)$, $r(\lambda_l)$ and $\hat{y}(\lambda_l):=X\hat{\beta}(\lambda_l)$, then for some next update point $l+B$ and any $b$ s.t.
+$l<l+b\leq l+B\leq L$, $\hat{\beta}_j(\lambda_{l+b})=0$ if
         \begin{equation}
@@
             \begin{split}
-                &\left|2\lambda_{k+b}x_j^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_k)x_j^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\\&<2n\lambda_k\lambda_{k+b}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}
+                &\left|2\lambda_{l+b}x_j^Tr(\lambda_l)+(\lambda_l-\lambda_{l+b})\left( x_j^Ty-\frac{y^T\hat{y}(\lambda_l)x_j^T\hat{y}(\lambda_l)}{||\hat{y}(\lambda_l)||_2^2}\right)\right|\\&<2n\lambda_l\lambda_{l+b}-(\lambda_l-\lambda_{l+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_l))^2}{||\hat{y}(\lambda_l)||_2^2}}
             \end{split}
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, then for some next update point $B$ and any $b$ s.t. $0<b\leq B\leq K$, $\hat{\beta}_j(\lambda_{k+b})=0$ if
+        \item For l=0, i.e., $\lambda_l=\lambda_0$, then for some next update point $B$ and any $b$ s.t. $0<b\leq B\leq L$, $\hat{\beta}_j(\lambda_{b})=0$ if
         \begin{equation}
@@
 
-For each $\lambda$ value in $\lambda_{k+1},...,\lambda_{k+B}$, the computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} is the same, except for the quantity $\lambda_{k+b}$ ($\lambda_b$ in the case $k=0$).
-The expensive computations in calculating these rules are $x_j^Tr(\lambda_k)$, $x_j^Tx_*$ and $x_j^Ty$, all of which must be calculated for $j=1,2,...,p$ and thus require $O(np)$ operations; all other computations require at most $O(p)$ operations.
-However, since $x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$ values and $x_j^Tr(\lambda_k)$ is the same for all $\lambda$ values within the block, once they have been calculated once, they can be stored and reused to avoid additional computation for all remaining steps in the block.
-Note that $x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)$, so this term also can be calculated efficiently.
+For each $\lambda$ value in $\lambda_{l+1},...,\lambda_{l+B}$, the computation in \eqref{eq:aedpp1} or \eqref{eq:aedpp2} is the same, except for the quantity $\lambda_{l+b}$ ($\lambda_b$ in the case $l=0$).
+The expensive computations in calculating these rules are $x_j^Tr(\lambda_l)$, $x_j^Tx_*$ and $x_j^Ty$, all of which must be calculated for $j=1,2,...,p$ and thus require $O(np)$ operations; all other computations require at most $O(p)$ operations.
+However, since $x_j^Ty$ and $x_j^Tx_*$ are the same for all $\lambda$ values and $x_j^Tr(\lambda_l)$ is the same for all $\lambda$ values within the block, once they have been calculated once, they can be stored and reused to avoid additional computation for all remaining steps in the block.
+Note that $x_j^T\hat{y}(\lambda_l)=x_j^Ty-x_j^Tr(\lambda_l)$, so this term also can be calculated efficiently.
 
 Compared to one-step methods like BEDPP, the reference solutions are continually updated.
-As a result, the reference is always relatively close to the solution, and screening remains powerful over the entire path, unlike one-step methods where screening power drops drastically as $\lambda_k$ gets further away from $\lambda_0$.
+As a result, the reference is always relatively close to the solution, and screening remains powerful over the entire path, unlike one-step methods where screening power drops drastically as $\lambda_l$ gets further away from $\lambda_0$.
 Compared to sequential methods like SEDPP, the adaptive method only requires $O(np)$ computations per update, while SEDPP requires $O(np)$ computations for each $\lambda$ value.
@@
 Since HSSR \citep{Zeng2021} have been shown to provide significant speedup compared to safe rules alone, we also consider incorporating strong rules into adaptive EDPP screening.
-We refer to the adaptive hybrid rule formed by combining SSR and adaptive EDPP as Ada-SSR-EDPP.
+We form an adaptive hybrid rule combining SSR and adaptive EDPP.
 
 This combination is not trivial.
-For ordinary SSR, the quantity $x_j^Tr(\lambda_k)$ used in \eqref{eq:ssr} is already computed in the previous post-convergence check in \eqref{eq:kkt}.
+For ordinary SSR, the quantity $x_j^Tr(\lambda_l)$ used in \eqref{eq:ssr} is already computed in the previous post-convergence check in \eqref{eq:kkt}.
 However, when combined with safe rules, the post-convergence check is not applied to all features.
-For any feature that was safely discarded at the previous $\lambda$, but not the current $\lambda$, the quantity $x_j^Tr(\lambda_k)$ has not been computed yet and thus cannot be used without additional cost.
-Similar to the idea of BASIL \citep{qian2019fast}, we can also do the strong rule screening adaptively by using the latest $x_j^Tr(\lambda_k)$ available, which is computed by adaptive EDPP rule at the latest update, to reduce the number of required computations.
+For any feature that was safely discarded at the previous $\lambda$, but not the current $\lambda$, the quantity $x_j^Tr(\lambda_l)$ has not been computed yet and thus cannot be used without additional cost.
+Similar to the idea of BASIL \citep{qian2019fast}, we can also do the strong rule screening adaptively by using the latest $x_j^Tr(\lambda_l)$ available, which is computed by adaptive EDPP rule at the latest update, to reduce the number of required computations.
 
-We combine adaptive EDPP and SSR to form Ada-SSR-EDPP as follows. Let $\lambda_k$ denote the point in the path at which the EDPP reference has been most recently updated, and
-we want the solution at $\lambda_{k+b}$.
+We combine adaptive EDPP and SSR to form the adaptive hybrid rule as follows.
+Let $\lambda_l$ denote the point in the path at which the EDPP reference has been most recently updated, and we want the solution at $\lambda_{l+b}$.
 First, carry out adaptive EDPP screening.
-Second, apply adaptive SSR screening to the features that have not been discarded by adaptive EDPP and discard any feature that satisfies $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$.
+Second, apply adaptive SSR screening to the features that have not been discarded by adaptive EDPP and discard any feature that satisfies $|x_j^Tr(\lambda_l)/n|<2\lambda_{l+b}-\lambda_l$.
 Third, conduct a post-convergence check on the features that were discarded by adaptive SSR but not discarded by adaptive EDPP.
-This procedure is then repeated for $\lambda_{k+b+1}$ (unless an EDPP update is applied).
+This procedure is then repeated for $\lambda_{l+b+1}$ (unless an EDPP update is applied).
 
-By choosing the same reference for adaptive EDPP rule and adaptive SSR, the quantity $x_j^Tr(\lambda_k)$ only needs to be computed once and can be used by both rules.
+By choosing the same reference for adaptive EDPP rule and adaptive SSR, the quantity $x_j^Tr(\lambda_l)$ only needs to be computed once and can be used by both rules.
 Also, because the adaptive EDPP rule remains powerful, the set of features that require post-convergence checking remains small.
@@
     \SetAlgoLined
-    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p,  \lambda_{0},...,\lambda_{K}$}
+    \Input{$\{x_j\}_{j=1}^p, \{x_j^Ty\}_{j=1}^p,  \lambda_{0},...,\lambda_{L}$}
     \BlankLine
@@
 
-    \For{$k\xleftarrow{}$ 1 \KwTo K}{
-        Safe Screening: $\mathcal{S}_{k}\xleftarrow{}\{j:x_j$ not discarded by adaptive EDPP rule given the reference$\}$.
+    \For{$l\xleftarrow{}$ 1 \KwTo L}{
+        Safe Screening: $\mathcal{S}_{l}\xleftarrow{}\{j:x_j$ not discarded by adaptive EDPP rule given the reference$\}$.
 
-        Strong Screening: $\mathcal{R}_{k}\xleftarrow{}\{j\in \mathcal{S}_{k}:x_j$ not discarded by adaptive SSR given the reference$\}$.
+        Strong Screening: $\mathcal{R}_{l}\xleftarrow{}\{j\in \mathcal{S}_{l}:x_j$ not discarded by adaptive SSR given the reference$\}$.
 
-        \Initialize{$\hat{\beta}(\lambda_{k})=\hat{\beta}(\lambda_{k-1}), r(\lambda_{k})=r(\lambda_{k-1})$}
+        \Initialize{$\hat{\beta}(\lambda_{l})=\hat{\beta}(\lambda_{l-1}), r(\lambda_{l})=r(\lambda_{l-1})$}
 
         \Repeat{Post-convergence check passes}{
-            Solve lasso problem using only features in $\mathcal{R}_{k}$, with warm start $\hat{\beta}(\lambda_{k}), r(\lambda_{k})$.
+            Solve lasso problem using only features in $\mathcal{R}_{l}$, with warm start $\hat{\beta}(\lambda_{l}), r(\lambda_{l})$.
 
-            Save new $\hat{\beta}(\lambda_{k}), r(\lambda_{k})$.
+            Save new $\hat{\beta}(\lambda_{l}), r(\lambda_{l})$.
 
-            Post-convergence check for all $j\in \mathcal{S}_{k}\setminus\mathcal{R}_{k}$,
+            Post-convergence check for all $j\in \mathcal{S}_{l}\setminus\mathcal{R}_{l}$,
 
             \uIf{Post-convergence check does not pass}{
-                Add violating features to $\mathcal{R}_{k}$\;
+                Add violating features to $\mathcal{R}_{l}$\;
             }
@@
         \uIf{Update conditions met}{
-            Reference = $\lambda_{k}$
+            Reference = $\lambda_{l}$
 
-            Compute and save: $\{x_j^Tr(\lambda_k)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_k)=x_j^Ty-x_j^Tr(\lambda_k)\}_{j=1}^p, \hat{y}(\lambda_k)=y-r(\lambda_k)$.}
+            Compute and save: $\{x_j^Tr(\lambda_l)\}_{j=1}^p, \{x_j^T\hat{y}(\lambda_l)=x_j^Ty-x_j^Tr(\lambda_l)\}_{j=1}^p, \hat{y}(\lambda_l)=y-r(\lambda_l)$.}
 
     }
-    \Output{$\{\hat{\beta}(\lambda_{k})\}_{k=1}^K$}
+    \Output{$\{\hat{\beta}(\lambda_{l})\}_{l=1}^L$}
     \caption{Pathwise lasso algorithm with adaptive hybrid rule screening}
@@
 Calculation of $\{x_j^Ty\}_{j=1}^p$ is needed only once for the whole solution path; we ignore this as well as its computational cost is the same across all approaches.
-We assume that strong rule screening is always powerful in the sense that its set of non-discarded features, $\mathcal{R}_{k+b}$, satisfies $|\mathcal{R}_{k+b}|=o(p) \approx 0$, but that safe rule screening, with corresponding set $\mathcal{S}_{k+b}$, may not be.
+We assume that strong rule screening is always powerful in the sense that its set of non-discarded features, $\mathcal{R}_{l+b}$, satisfies $|\mathcal{R}_{l+b}|=o(p) \approx 0$, but that safe rule screening, with corresponding set $\mathcal{S}_{l+b}$, may not be.
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
@@
 Under these assumptions, there are two dominating parts in the algorithm within each update.
-First, the computation of $\{x_j^Tr(\lambda_k)\}_{j=1}^p$ at the time of updating the reference, which requires $np$ multiplications.
-Then, for each $\lambda_{k+b}$, the post-convergence check requires approximately $|\mathcal{S}_{k+b} \setminus \mathcal{R}_{k+b}| \approx |\mathcal{S}_{k+b}|$ KKT condition checks, each of which requires $n$ multiplications.
-These sum to $n\sum_{i=k}^{k+B}|\mathcal{S}_k|$ multiplications, where $k+B$ is the start of the next update.
-Combining these two parts, the average cost per $\lambda$ in the block $\lambda_{k+1},...,\lambda_{k+B}$ is
+First, the computation of $\{x_j^Tr(\lambda_l)\}_{j=1}^p$ at the time of updating the reference, which requires $np$ multiplications.
+Then, for each $\lambda_{l+b}$, the post-convergence check requires approximately $|\mathcal{S}_{l+b} \setminus \mathcal{R}_{l+b}| \approx |\mathcal{S}_{l+b}|$ KKT condition checks, each of which requires $n$ multiplications.
+These sum to $n\sum_{b=1}^{B}|\mathcal{S}_{l=b}|$ multiplications, where $l+B$ is the start of the next update.
+Combining these two parts, the average cost per $\lambda$ in the block $\lambda_{l+1},...,\lambda_{l+B}$ is
 \begin{equation}
     \label{eq:cost}
-    \bar{T}_k(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_{k+b}|}{B},
+    \bar{T}_l(B) \approx n\frac{p}{B}+n\frac{\sum_{b=1}^B|\mathcal{S}_{l+b}|}{B},
 \end{equation}
@@
 To better illustrate these two effects, we considered a simple updating scheme: update the reference after every batch of $B$ $\lambda$ values.
-Figure~\ref{fig:batchsizes} illustrates the effect of the batch size $B$ on $|\mathcal{S}_{k+b}|$ in a real data set solved over a path of $K=100$ $\lambda$-values.
-The vertical axis is the proportion of discarded features, $1-|\mathcal{S}_{k+b}|/p$.
+Figure~\ref{fig:batchsizes} illustrates the effect of the batch size $B$ on $|\mathcal{S}_{l+b}|$ in a real data set solved over a path of $L=100$ $\lambda$-values.
+The vertical axis is the proportion of discarded features, $1-|\mathcal{S}_{l+b}|/p$.
 
@@
 
-BEDPP is the special case of adaptive EDPP that never updates ($B=K$).
+BEDPP is the special case of adaptive EDPP that never updates ($B=L$).
 When the reference is not updated, safe rule screening will eventually fail to discard any features and the KKT condition checking cost will increase to its maximum, $np$.
@@
 A reasonable approach to minimizing the average cost, therefore, is to update the reference at the point where reusing it one additional time would increase the average cost.
-That is, we should update the reference at $\lambda_{k+B}$ if $\bar{T}_k(B+1)>\bar{T}_k(B)$.
-In practice, we will instead update the reference to $\lambda_{k+B}$ when $\bar{T}_k(B)>\bar{T}_k(B-1)$, because $\bar{T}_k(B+1)$ cannot be calculated without having already carried out screening at $\lambda_{k+B+1}$.
+That is, we should update the reference at $\lambda_{l+B}$ if $\bar{T}_l(B+1)>\bar{T}_l(B)$.
+In practice, we will instead update the reference to $\lambda_{l+B}$ when $\bar{T}_l(B)>\bar{T}_l(B-1)$, because $\bar{T}_l(B+1)$ cannot be calculated without having already carried out screening at $\lambda_{l+B+1}$.
 The two conditions should be close and thus this substitution should be near optimal.
@@
     \label{eq:crit}
-    (B-1)|\mathcal{S}_{k+B}|-\sum_{b=1}^{B-1}|\mathcal{S}_{k+b}|>p.
+    (B-1)|\mathcal{S}_{l+B}|-\sum_{b=1}^{B-1}|\mathcal{S}_{l+b}|>p.
 \end{equation}
@@
 The resulting adaptive rule, \eqref{eq:crit}, provides a robust strategy that addresses the three most common scenarios.
-First, if the screening power stays high, meaning $\mathcal{S}_{k+b}$ is small for all $b$, then the left-hand-side of \eqref{eq:crit} will be small and thus at this point we will not update to further exploit the old reference.
-Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{k+B}$ is large but $\mathcal{S}_{k+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of \eqref{eq:crit} will be large and we will update the useless old reference to a helpful new one.
-Last, if the screening power drops dramatically immediately after the last update, meaning $\mathcal{S}_{k+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of \eqref{eq:crit} will be approximately $p-|\mathcal{S}_1|$.
+First, if the screening power stays high, meaning $\mathcal{S}_{l+b}$ is small for all $b$, then the left-hand-side of \eqref{eq:crit} will be small and thus at this point we will not update to further exploit the old reference.
+Second, if the screening power has been high for a while but dropped suddenly, meaning $\mathcal{S}_{l+B}$ is large but $\mathcal{S}_{l+b}$ are mostly small for $b=1,2,...,B-1$, then the left-hand-side of \eqref{eq:crit} will be large and we will update the useless old reference to a helpful new one.
+Last, if the screening power drops dramatically immediately after the last update, meaning $\mathcal{S}_{l+b}$ are close to $p$ for $b=2,3,...,B$, then the left-hand-side of \eqref{eq:crit} will be approximately $p-|\mathcal{S}_1|$.
 This is less than $p$, so we will again not update.
@@
 \section{Extension to other lasso type problems}
-\label{sec:4}
+\label{sec:extension}
 
@@
 \subsection{Adaptive safe rule for sparse logistic regression}
+\label{sec:logis}
 
@@
 Sequential strong rules require only a small change for logistic regression.
-The residual vector now is $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$.
-Then the SSR discards the $j$-th feature at $\lambda_{k+1}$ if \eqref{eq:ssr} holds.
+The residual vector now is $r(\lambda_l)=y-\pi(\hat{\beta}(\lambda_l))$.
+Then the SSR discards the $j$-th feature at $\lambda_{l+1}$ if \eqref{eq:ssr} holds.
 
@@
 \begin{theorem}[Adaptive Slores]
-For the sparse logistic regression model \eqref{eq:logis}, let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$, and suppose $\lambda_0>\lambda_1>...>\lambda_K$.
+For the sparse logistic regression model \eqref{eq:logis}, let $\lambda_0:=\max_j|x_j^Ty/n|$, $\Tilde{y}=2y-1\in\{-1,1\}^n$, and suppose $\lambda_0>\lambda_1>...>\lambda_L$.
 For all $\theta\in(0,1)^n$, let
@@
 
-Under the conditions on $X$ given in \eqref{eq:std}, for any $k=1,2,...,K-1$, assume $\hat{\beta}(\lambda_k)$, $r(\lambda_k)=y-\pi(\hat{\beta}(\lambda_k))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_k)\neq0\} $, $\theta(\lambda_k)=\{r_i(\lambda_k)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_k):=\pi(\hat{\beta}(\lambda_k))$ are known.
-For some next update point $k+B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, let
+Under the conditions on $X$ given in \eqref{eq:std}, for any $l=1,2,...,L-1$, assume $\hat{\beta}(\lambda_l)$, $r(\lambda_l)=y-\pi(\hat{\beta}(\lambda_l))$, $x_*\in\{x_j:\hat{\beta}_j(\lambda_l)\neq0\} $, $\theta(\lambda_l)=\{r_i(\lambda_l)\Tilde{y}_i\}_{i=1}^n$ and $\hat{y}(\lambda_l):=\pi(\hat{\beta}(\lambda_l))$ are known.
+For some next update point $l+B$ and any $b$ s.t.
+$l<l+b\leq l+B\leq L$, let
 \begin{equation}
-  R(\lambda_{k+b}) = \sqrt{\frac{n}{2} \bigg[g\bigg(\frac{\lambda_{k+b}}{\lambda_k}\theta(\lambda_k)\bigg) - g\bigg(\theta(\lambda_k)\bigg) + \bigg(1 - \frac{\lambda_{k+b}}{\lambda_k}\bigg) \bigg(\nabla g\big(\theta(\lambda_k)\big)\bigg)^T\theta(\lambda_k)\bigg]},
+  R(\lambda_{l+b}) = \sqrt{\frac{n}{2} \bigg[g\bigg(\frac{\lambda_{l+b}}{\lambda_l}\theta(\lambda_l)\bigg) - g\bigg(\theta(\lambda_l)\bigg) + \bigg(1 - \frac{\lambda_{l+b}}{\lambda_l}\bigg) \bigg(\nabla g\big(\theta(\lambda_l)\big)\bigg)^T\theta(\lambda_l)\bigg]},
 \end{equation}
-and $d(\lambda_{k+b})=\sqrt{n}(\lambda_k-\lambda_{k+b})/R(\lambda_{k+b})$. For $\xi = -1,1$ and $j=1,2,...,p$,
+and $d(\lambda_{l+b})=\sqrt{n}(\lambda_l-\lambda_{l+b})/R(\lambda_{l+b})$. For $\xi = -1,1$ and $j=1,2,...,p$,
 
 \begin{enumerate}
-    \item If $-\xi \sign(x_*^Ty)x_j^Tx_*\geq nd(\lambda_{k+b})$, then
+    \item If $-\xi \sign(x_*^Ty)x_j^Tx_*\geq nd(\lambda_{l+b})$, then
 
     \begin{equation}
-        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=\sqrt{n}R(\lambda_{k+b})-\xi x_j^Tr(\lambda_k);
+        T_\xi(\lambda_{l+b},x_j;r(\lambda_l))=\sqrt{n}R(\lambda_{l+b})-\xi x_j^Tr(\lambda_l);
     \end{equation}
 
-    \item If $-\xi \sign(x_*^Ty)x_j^Tx_*< nd(\lambda_{k+b})$, then
+    \item If $-\xi \sign(x_*^Ty)x_j^Tx_*< nd(\lambda_{l+b})$, then
 
     \begin{equation}
-        T_\xi(\lambda_{k+b},x_j;r(\lambda_k))=R(\lambda_{k+b})\sqrt{n+nu_\xi^2-2\xi u_\xi \sign(x_*^Ty)x_j^Tx_*}-nu_\xi(\lambda_k-\lambda_{k+b})-\xi x_j^Tr(\lambda_k),
+        T_\xi(\lambda_{l+b},x_j;r(\lambda_l))=R(\lambda_{l+b})\sqrt{n+nu_\xi^2-2\xi u_\xi \sign(x_*^Ty)x_j^Tx_*}-nu_\xi(\lambda_l-\lambda_{l+b})-\xi x_j^Tr(\lambda_l),
     \end{equation}
@@
         u_\xi&=\frac{-\xi a_1+\sqrt{\Delta}}{2a_2},\\
-        a_0&=(x_j^Tx_*)^2-n^2d^2(\lambda_{k+b}),\nonumber\\
-        a_1&=-2n\,\sign(x_*^Ty)x_j^Tx_*\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
-        a_2&=n^2\big(1-d^2(\lambda_{k+b})\big),\nonumber\\
+        a_0&=(x_j^Tx_*)^2-n^2d^2(\lambda_{l+b}),\nonumber\\
+        a_1&=-2n\,\sign(x_*^Ty)x_j^Tx_*\big(1-d^2(\lambda_{l+b})\big),\nonumber\\
+        a_2&=n^2\big(1-d^2(\lambda_{l+b})\big),\nonumber\\
         \Delta&=a_1^2-4a_0a_1.\nonumber
@@
 
-Then $\hat{\beta}_j(\lambda_{k+b})=0$ if
+Then $\hat{\beta}_j(\lambda_{l+b})=0$ if
   \begin{equation}
-    \max_{\xi=\pm1} T_\xi(\lambda_{k+b},x_j;r(\lambda_k))<n\lambda_{k+b}
+    \max_{\xi=\pm1} T_\xi(\lambda_{l+b},x_j;r(\lambda_l))<n\lambda_{l+b}
   \end{equation}
@@
 The quantity $\{x_j^Tx_*\}_{j=1}^p$ can be similarly reused unless $x_*$ changes, which happens if the corresponding regression coefficient drops out of the model; this is relatively rare, but can happen.
-Other than those two terms, the only term that requires expensive $O(np)$ computations is $\{x_j^Tr(\lambda_k)\}_{j=1}^p$, which needs to be computed only when we update the reference solution.
-Thus Algorithm~\ref{alg:path} can be applies to the sparse logistic model, with Slores replacing EDPP.
-We refer to the resulting algorithm as Ada-SSR-Slores.
+Other than those two terms, the only term that requires expensive $O(np)$ computations is $\{x_j^Tr(\lambda_l)\}_{j=1}^p$, which needs to be computed only when we update the reference solution.
+Thus Algorithm~\ref{alg:path} can be applies to the sparse logistic model, with Slores replacing EDPP, to form the adaptive hybrid rule algorithm for sparse logistic regression.
 
 \subsection{Adaptive safe rule for group lasso}
+\label{sec:group}
 
@@
 
-We can again use the KKT conditions to derive sequential strong rules. Given $r(\lambda_k)=y-\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, we discard features in the $g$-th group at $\lambda_{k+1}$ if
-\begin{equation} \bigg|\bigg|\frac{1}{n}X_g^Tr(\lambda_k)\bigg|\bigg|_2<\sqrt{p_g}(2\lambda_{k+1}-\lambda_k).
+We can again use the KKT conditions to derive sequential strong rules. Given $r(\lambda_l)=y-\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_l)$, we discard features in the $g$-th group at $\lambda_{l+1}$ if
+\begin{equation} \bigg|\bigg|\frac{1}{n}X_g^Tr(\lambda_l)\bigg|\bigg|_2<\sqrt{p_g}(2\lambda_{l+1}-\lambda_l).
 \end{equation}
@@
 \begin{theorem}[Adaptive EDPP for group lasso]
-  For the group lasso problem \eqref{eq:glasso}, suppose $\lambda_0>\lambda_1>...>\lambda_K$, with $\lambda_0:= \max_j ||X_g^Ty||_2 / (n\sqrt{p_g})$.
+  For the group lasso problem \eqref{eq:glasso}, suppose $\lambda_0>\lambda_1>...>\lambda_L$, with $\lambda_0:= \max_j ||X_g^Ty||_2 / (n\sqrt{p_g})$.
 Under conditions \eqref{eq:std} and \eqref{eq:stdg},
     \begin{enumerate}
-        \item For any $k=1,2,...,K-1$, given $\hat{\beta}(\lambda_k)$, $r(\lambda_k)$ and $\hat{y}(\lambda_k):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_k)$, then for some next update point $k+B$ and any $b$ s.t.
-$k<k+b\leq k+B\leq K$, $\hat{\beta}_g(\lambda_{k+b})=0$ if
+        \item For any $l=1,2,...,L-1$, given $\hat{\beta}(\lambda_l)$, $r(\lambda_l)$ and $\hat{y}(\lambda_l):=\sum_{g=1}^GX_g\hat{\beta}_g(\lambda_l)$, then for some next update point $l+B$ and any $b$ s.t.
+$l<l+b\leq l+B\leq L$, $\hat{\beta}_g(\lambda_{l+b})=0$ if
         \begin{equation}
             \begin{split}
-                &\left|\left|2\lambda_{k+b}X_g^Tr(\lambda_k)+(\lambda_k-\lambda_{k+b})\left( X_g^Ty-\frac{y^T\hat{y}(\lambda_k)X_g^T\hat{y}(\lambda_k)}{||\hat{y}(\lambda_k)||_2^2}\right)\right|\right|_2\\
-                &<2n\lambda_k\lambda_{k+b}\sqrt{p_g}-(\lambda_k-\lambda_{k+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_k))^2}{||\hat{y}(\lambda_k)||_2^2}}.
+                &\left|\left|2\lambda_{l+b}X_g^Tr(\lambda_l)+(\lambda_l-\lambda_{l+b})\left( X_g^Ty-\frac{y^T\hat{y}(\lambda_l)X_g^T\hat{y}(\lambda_l)}{||\hat{y}(\lambda_l)||_2^2}\right)\right|\right|_2\\
+                &<2n\lambda_l\lambda_{l+b}\sqrt{p_g}-(\lambda_l-\lambda_{l+b})\sqrt{n||y||_2^2-\frac{n(y^T\hat{y}(\lambda_l))^2}{||\hat{y}(\lambda_l)||_2^2}}.
             \end{split}
         \end{equation}
-        \item For k=0, i.e., $\lambda_k=\lambda_0$, let $X_*=\arg \max_{X_g} ||X_g^Ty||_2 / (n\sqrt{p_g})$ with dimension $n\times p_*$, then for some next update point $B$ and any $b$ s.t.
-$0<b\leq B\leq K$, $\hat{\beta}_g(\lambda_{b})=0$ if
+        \item For l=0, i.e., $\lambda_l=\lambda_0$, let $X_*=\arg \max_{X_g} ||X_g^Ty||_2 / (n\sqrt{p_g})$ with dimension $n\times p_*$, then for some next update point $B$ and any $b$ s.t.
+$0<b\leq B\leq L$, $\hat{\beta}_g(\lambda_{b})=0$ if
         \begin{equation}
@@
 
-Similar to the Adaptive EDPP rule, there are three expensive computations: $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$, and $\{X_g^Tr(\lambda_k)\}_{g=1}^G$.
+Similar to the Adaptive EDPP rule, there are three expensive computations: $\{X_g^Ty\}_{g=1}^G$, $\{X_g^TX_*\}_{g=1}^G$, and $\{X_g^Tr(\lambda_l)\}_{g=1}^G$.
 The first two only need to be computed once for the whole solution path.
 The final term needs to be computed only when the reference solution is updated, with cost $O(np)$.
-The adaptive EDPP for group lasso, combined with the previous SSR, forms the Ada-SSR-EDPP for group lasso.
+The adaptive EDPP for group lasso, combined with the previous SSR, forms adaptive hybrid rule for group lasso.
 
@@
 Furthermore, its screening rules emphasize both the computation and memory costs as we have discussed.
-The adaptive screening approach proposed in this manuscript led to the development of a new version of the package, \textbf{biglasso} 1.4, that is significantly faster than previous versions.
+The adaptive screening approach proposed in this manuscript led to the development of a new version of the package, \textbf{biglasso} 1.4-0, that is significantly faster than previous versions.
 
-For all the following experiments, we solve the lasso model along a path of $100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_L=0.05\lambda_0$ and the intermediate values equally spaced on a log scale.
-Note that $L$ denotes the number of $\lam$ points that the lasso problem is solved along the coefficient path.
-\pb{is this inconsistent?
-Don't we use K everywhere else in the paper?}
+For all the following experiments, unless otherwise specified, we solve the lasso model along a path of $L=100$ $\lambda$-values with the maximum $\lambda_0=\max_j|x_j^Ty/n|$ determined by the data, the minimum $\lambda_L=0.05\lambda_0$ and the intermediate values equally spaced on a log scale.
 
@@
 The difference is largest when the data set is large (large $n$ or large $p$), the active features are highly sparse (small $s$) or the grid of $\lambda$-value is fine (large $L$ or $\lambda_{\min}/\lambda_{\max}$).
-\pb{For example, when $L=1000$, AHR is XXXX times faster than any other approach.}
+For example, when $L=1000$, AHR is 18 times faster than any other approach.
 
@@
 
-We also tried varying other factors, for example: the correlation among features in $X$, sparsity with fixed signal strength, and the minimum value $\lambda_K$.
+We also tried varying other factors, for example: the correlation among features in $X$, sparsity with fixed signal strength, and the minimum value $\lambda_L$.
 The results of these experiments were very similar, with AHR continuing to show a uniform advantage over other methods.
@@
 The speedup is smaller in magnitude than for linear regression because the Slores rule is less powerful than EDPP.
-Nevertheless, the improvement in speed is still dramatic in many cases \pb{provide number here for, say, $L=500$}.
+Nevertheless, the improvement in speed is still dramatic in many cases, for example, 4 times faster than any other methods when $L=1,000$.
 

### 2021-01-27 TaylorFrancisStyle.tex
Add a version of Taylor&Francis style

\documentclass[]{interact}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
%\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled

\usepackage[numbers,sort&compress]{natbib}% Citation support using natbib.sty
\bibpunct[, ]{[}{]}{,}{n}{,}{,}% Citation support using natbib.sty
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
\makeatletter% @ becomes a letter
\def\NAT@def@citea{\def\@citea{\NAT@separator}}% Suppress spaces between citations using natbib.sty
\makeatother% @ becomes a symbol again

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ruled,vlined, linesnumbered]{algorithm2e}
\usepackage[english]{babel}
\usepackage[nottoc]{tocbibind}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=black, linkcolor=., urlcolor=cyan}
% Custom commands / shortcuts
\providecommand{\sign}{\textrm{sign}}
\providecommand{\pb}[1]{\textcolor{red}{#1}}
\providecommand{\lam}{\lambda}

\title{Adaptive Hybrid Screening for Efficient Lasso Optimization}
%\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
%  \and
%  Patrick Breheny\\Department of Biostatistics\\University of Iowa}

\author{
\name{Chuyi Wang\textsuperscript{a}\thanks{CONTACT Chuyi Wang. Email: chuyi-wang@uiowa.edu} and Patrick Breheny\textsuperscript{b}}
\affil{\textsuperscript{a}Department of Statistics and Actuarial Sciences, University of Iowa, USA; \\\textsuperscript{b}Department of Biostatistics, University of Iowa, USA}
}
\date{}

\begin{document}

\maketitle

\begin{abstract}
Lasso type models are popular in statistics, especially for high-dimensional data. Typical practice is to tune the size of lasso penalty along a path of values. Due to modern data collection techniques, researchers need to analyse data with millions of features, which brings a great need for an efficient lasso optimization algorithm. Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features. In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values. It reuses previous solutions in the path and reduces unhelpful heavy computations. It is a flexible framework that can be easily extended to different types of lasso models. Two applications for the standard lasso model and the sparse logistic model are shown as examples. We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
\end{abstract}

\begin{keywords}
Lasso; feature Screening; safe screening; solution path; large-scale sparse learning
\end{keywords}

\input{main}

\renewcommand\bibname{References}
\bibliographystyle{tfnlm}
\bibliography{ref}

\end{document}

### 2021-01-27 main.tex
Add a version of Taylor&Francis style

@@
 
-\section{Existing feature screening rules}
+\section{Existing Feature Screening Rules}
 \label{sec:existing}
@@
 
-\subsection{Strong rules}
+\subsection{Strong Rules}
 
@@
 
-\subsection{Safe rules}
+\subsection{Safe Rules}
 \label{sec:safe}
@@
 
-\subsection{Other approaches to screening}
+\subsection{Other Approaches to Screening}
 
@@
 
-\section{Adaptive screening}
+\section{Adaptive Screening}
 \label{sec:method}
@@
 
-\subsection{Adaptive safe rules}
+\subsection{Adaptive Safe Rules}
 
@@
 
-\subsection{Adaptive hybrid rules}
+\subsection{Adaptive Hybrid Rules}
 
@@
 
-\subsection{Pathwise lasso algorithm with adaptive hybrid rule}
+\subsection{Pathwise Lasso Algorithm with Adaptive Hybrid Rule}
 
@@
 
-\subsection{Adaptive update algorithm}
+\subsection{Adaptive Update Algorithm}
 \label{sec:adaptive}
@@
 
-\subsubsection{Complexity analysis}
+\subsubsection{Complexity Analysis}
 \label{sec:complexity}
@@
     \centering
-    \includegraphics[scale = 0.6]{plots/batchsizes.pdf}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
+    \includegraphics[width=0.6\textwidth]{plots/batchsizes.pdf}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
     \label{fig:batchsizes}
@@
 
-\subsubsection{Efficient updating algorithm}
+\subsubsection{Efficient Updating Algorithm}
 
@@
 
-\section{Extension to other lasso type problems}
+\section{Extension to other Lasso Type Problems}
 \label{sec:extension}
@@
 
-\subsection{Adaptive safe rule for sparse logistic regression}
+\subsection{Adaptive Safe Rule for Sparse Logistic Regression}
 \label{sec:logis}
@@
 
-\subsection{Adaptive safe rule for group lasso}
+\subsection{Adaptive Safe Rule for Group Lasso}
 \label{sec:group}
@@
 
-\subsection{Simulation study}
+\subsection{Simulation Study}
 \label{sec:sim}
 
-\subsubsection{Lasso model}
+\subsubsection{Lasso Model}
 
@@
     \centering
-    \includegraphics[scale = 0.59]{plots/511.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[width=\textwidth]{plots/511.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[scale = 0.59]{plots/511b.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[width=0.82\textwidth]{plots/511b.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
 
-Figure 2 and Figure 3 shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
+Figure~\ref{fig:5.1.1a} and~\ref{fig:5.1.1b} shows the computation time (top row) and relative computation time compared to AC (bottom row) of solving lasso problem with different screening methods.
 AHR is uniformly the fastest under all settings, typically 2-8 times faster than any other screening method.
@@
 
-\subsubsection{Sparse logistic regression model}
+\subsubsection{Sparse logistic Regression Model}
 
@@
     \centering
-    \includegraphics[scale = 0.59]{plots/512.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[width=\textwidth]{plots/512.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[scale = 0.59]{plots/512b.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[width=0.82\textwidth]{plots/512b.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.
@@
 
-Figure 4 and 5 show the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
+Figure~\ref{fig:5.1.2a} and~\ref{fig:5.1.2b} show the computation time (top row) and relative computation time compared to SSR (bottom row) of solving sparse logistic regression problem with different screening methods.
 The overall pattern is the same as for sparse linear regression, with adaptive screening uniformly faster than all other methods.
@@
 
-\subsection{Real data analysis}
+\subsection{Real Data Analysis}
 \label{sec:real-data}
@@
 For 2 and 4, since in each experiment the response is randomly selected, we replicate the experiment 50 times to get an accurate estimate.
-Table 1 compares the average computation time for different screening methods in these data sets.
+Table~\ref{Tab:real} compares the average computation time for different screening methods in these data sets.
 
@@
 \caption{Average computing time in second (standard error) for solving the lasso model}
+\label{Tab:real}
 \end{table}
@@
 
-\subsection{Big data performance}
+\subsection{Big Data Performance}
 
@@
 $n=973$ out of 1,080 subjects have this measurement and they will be considered as the sample for this analysis.
-The experiment is replicated 5 times to take the average, shown in the Table 2.
+The experiment is replicated 5 times to take the average, shown in the Table~\ref{Tab:big1}.
 
@@
 \caption{Average computing time in minute and standard error for solving the lasso model on big data}
+\label{Tab:big1}
 \end{table}
@@
 $n=1008$ out of 1,080 subjects have this measurement and they will be considered as the sample for this analysis.
-The experiment is replicated 5 times to take the average, shown in the Table 3.
+The experiment is replicated 5 times to take the average, shown in the Table~\ref{Tab:big2}.
 
@@
 \caption{Average computing time in minute and standard error for solving the sparse logistic model on big data}
+\label{Tab:big2}
 \end{table}

### 2021-01-28 main.tex
Edits to 5.3 and 6

--- 2021-01-20 main.tex
@@
 
-Since HSSR \citep{Zeng2021} have been shown to provide significant speedup compared to safe rules alone, we also consider incorporating strong rules into adaptive EDPP screening.
-We form an adaptive hybrid rule combining SSR and adaptive EDPP.
+Since HSSR \citep{Zeng2021} has been shown to provide significant speedup compared to safe rules alone, we also consider incorporating strong rules into adaptive EDPP screening, forming an adaptive hybrid rule combining SSR and adaptive EDPP.
 
@@
 The final term needs to be computed only when the reference solution is updated, with cost $O(np)$.
-The adaptive EDPP for group lasso, combined with the previous SSR, forms adaptive hybrid rule for group lasso.
+The adaptive EDPP for group lasso, combined with the previous SSR, forms our adaptive hybrid rule for group lasso.
 
@@
 The speedup is smaller in magnitude than for linear regression because the Slores rule is less powerful than EDPP.
-Nevertheless, the improvement in speed is still dramatic in many cases, for example, 4 times faster than any other methods when $L=1,000$.
+Nevertheless, the improvement in speed is still dramatic in many cases.
+For example, when $L=1,000$, AHR was 4 times faster than any other method.
 
@@
 
-In previous sections, we used simulation to compare the screening methods under different scenario.
-In real world, data may be generated from different complicated models that cannot be covered by a simulation study, so in this section we are going to test the screening methods for lasso model on some real data sets to make sure our comparison conclusion is representative in real world.
-Following the studies of \citep{wang2013lasso, xiang2016screening, Zeng2021}, we will test the lasso screening methods on the following data sets:
+The previous section compared screening methods under different scenarios using simulated data.
+Data generating mechanisms in the real world, however, are much more complex than those of a simulation.
+In this section, we compare screening methods for lasso models on a variety of real data sets to ensure the conclusions of the previous section are representative of real world data.
+Following the studies of \citep{wang2013lasso, xiang2016screening, Zeng2021}, we test the lasso screening methods on the following data sets:
 
@@
 
-For 1 and 3, we replicate the experiment 10 times to take the average.
-For 2 and 4, since in each experiment the response is randomly selected, we replicate the experiment 50 times to get an accurate estimate.
+For GENE and GWAS, we replicate the experiment 10 times to take the average.
+For data sets MNIST and NYT, because the response is randomly selected, we replicate the experiment 50 times to get an accurate estimate.
 Table 1 compares the average computation time for different screening methods in these data sets.
@@
 
-AHR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\%.
-Also note that the performance of SEDPP varies a lot in MNIST and NYT data sets, where the response is randomly selected in each replication, suggesting that the speed of SEDPP is sensitive to the data.
-AHR is built with SEDPP as the safe rule but does not have the problem of instability, because it can adaptively adjust itself according the performance of the safe rule.
+AHR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\% \pb{how about ``faster than other methods by factor ranging from 70\% to 630\%''?
+To me, ``faster than the fastest of the rest'' seems more complicated than necessary}.
+Also note that the performance of SEDPP varies considerably for the MNIST and NYT data sets, where the response is randomly selected in each replication, indicating that the speed of SEDPP is sensitive to the data.
+AHR is built with SEDPP as the safe rule but does not share this issue of instability because it can adaptively adjust itself according the performance of the safe rule.
 
@@
 
-Ultra high dimensional big data that is too large to be fit into the memory is the real challenge and is the place where the help of a good screening method is wanted most.
-We test the screening methods on a data from a genome-wide association study on 1,080 subjects with heart conditions.
-We want to identify genetic factors that are associated with some heart condition severity measurements.
-After imputing and filtering, there are $p=11,830,470$ SNP measurements used as the features.
+Ultra high dimensional big data that is too large to fit into memory represents the greatest challenge and the scenario where the help of a good screening method is needed most.
+To test the screening methods described in this paper, we used data from the Genetic Risk Assessment of Defibrillator Events study (GRADE, \url{https://www.clinicaltrials.gov/ct2/show/NCT02045043}).
+Genome-wide genetic data were collected for 1,080 subjects diagnosed with cardiomyopathy and who had undergone surgery to receive an implantable cardioverter defibrillator in the past 5 years.
+After imputation using the Haplotype Reference Consortium as a reference genome and filtering for quality control \citep{Das2016}, there were $p=11,830,470$ SNPs which used as features.
 The size of the file storing the feature matrix is 96G and we conduct the test on a machine with 32G RAM.
-We choose a larger $\lambda_{\min} =0.5\lambda_{\max}$ to avoid having more features selected than the number of observations, where the solution becomes not unique.
+We chose a relatively large $\lambda_{\min} =0.5\lambda_{\max}$ to avoid having more features selected than the number of observations, at which point the solution is no longer unique.
 
-For the lasso model, we choose the Left ventricular ejection fraction (LVEF) as the response.
-It measures the proportion of blood being pumped out of the left ventricle of the heart (the main pumping chamber) with each contraction.
-Lower value means severer heart failure.
-$n=973$ out of 1,080 subjects have this measurement and they will be considered as the sample for this analysis.
-The experiment is replicated 5 times to take the average, shown in the Table 2.
+A variety of clinical data was collected on these individuals.
+To examine the performance of screening rules for linear regression, we focused on left ventricular ejection fraction (LVEF) as the response.
+LVEF measures the proportion of blood being pumped out of the left ventricle of the heart with each contraction.
+Lower values are associated with more severe heart disease.
+LVEF data was available for $n=973$ subjects and they will be considered as the sample for this analysis.
+The experiment is replicated 5 times, and results are shown in Table~\ref{Tab:lvef}.
 
@@
 \hline
-
 Screening method & AC\,\,\,\,\,\,\,\,\,    & SSR\,\,\,\,\,\,   & SEDPP & HSSR\,\,\,  & AHR\,\,\,\,\,\,  \\
@@
 \end{tabular}
-\caption{Average computing time in minute and standard error for solving the lasso model on big data}
+\caption{Average computing time in minutes and standard error for the LVEF analysis (lasso-penalized linear regression).\label{Tab:lvef}}
 \end{table}
 
-For the sparse logistic model, we choose the New York Heart Association (NYHA) Functional Classification as the response.
-It classifies patients by how much they are limited during physical activity.
-The classes range from 1 to 4 so we combine class 1 and 2 as the negative class with no or slight limitation of physical activity and class 3 and 4 as the positive class with substantial limitation.
-$n=1008$ out of 1,080 subjects have this measurement and they will be considered as the sample for this analysis.
-The experiment is replicated 5 times to take the average, shown in the Table 3.
+For the sparse logistic model, we choose the New York Heart Association (NYHA) Functional Classification as the response, which classifies patients on the basis of limitations to their physical activity.
+The classes range from 1 to 4, which we dichotomize into patients with no or slight limitation of physical activity (classes 1 and 2) and patients with substantial limitations (classes 3 and 4).
+The NYHA classification was available for $n=1008$ subjects, who form the sample for the logistic regression analysis.
+The experiment is replicated 5 times to take the average and results are shown in Table~\ref{Tab:nyha}.
 
@@
 \end{tabular}
-\caption{Average computing time in minute and standard error for solving the sparse logistic model on big data}
+\caption{Average computing time in minutes and standard error for the NYHA analysis (lasso-penalized logistic regression).\label{Tab:nyha}}
 \end{table}
 
-For both the lasso model and the sparse logistic model, the purposed adaptive hybrid methods outperforms other methods with great reduction in computation time.
-On the lasso model, the adaptive hybrid method achieves 6 times speedup.
+For both analyses, the proposed adaptive hybrid methods result in substantial reductions in computation time.
+In particular, for the lasso analysis of LVEF, the adaptive hybrid method reduces computation time from nearly an hour and a half to under 15 minutes, a 6-fold speedup.
 
@@
 
-In this paper, we proposed the novel adaptive hybrid screening framework for efficient lasso type problem optimization over the solution path.
-The key idea is cleverly reusing the reference for screening along the path until updating to a new reference is beneficial for computation cost.
-We developed three instances in this framework: Ada-SSR-EDPP, Ada-SSR-Slores and Ada-SSR EDPP for group lasso, for 3 different types of lasso problems.
-We tested the first two in extensive numeric experiments on both simulated data and real data, including a ultra big data that does not fit into the memory.
-Our proposed rules outperformed other state-of-the-art screening methods uniformly, especially in the most challenging scenarios.
+In this paper, we have proposed a novel adaptive hybrid screening framework for efficient lasso-type optimization over the solution path.
+The key idea is to judiciously reuse the reference for screening along the path until the point where updating to a new reference is beneficial.
+We developed three instances of algorithms using this framework, for standard lasso-penalized linear regression, for sparse logistic regression, and for the group lasso.
+Extensive numeric experiments on both simulated and real data, including a very large data set that cannot fit into memory, demonstrate that our proposed algorithms outperform other state-of-the-art screening methods uniformly, in many cases several times faster that competing approaches.
 
-Ada-SSR-EDPP and Ada-SSR-Slores have been implemented in  publicly accessible \textbf{R} packages \textbf{biglasso}\citep{zeng2017biglasso}, which was used to carry out the numeric experiments.
+The algorithms for lasso-penalized linear and logistic regression have been implemented in the publicly accessible R package \textbf{biglasso} \citep{zeng2017biglasso}, which was used to carry out the numeric experiments.
 
-Our adaptive hybrid screening framework also has great flexibility for extensions.
-It can substitute coordinate descent with any other faster lasso problem optimizer, SSR with any other stronger strong rules and the adaptive updating algorithm with any other cleverer algorithm.
-Most importantly, most sequential safe rules can be modified as adaptive safe rules and fit into our framework.
-This lead to several future extensions.
-First, if a stronger safe rule is developed, our framework can better exploit its power and lead to an even faster algorithm.
-Second, there are still many lasso type problems that do not have corresponding sequential safe rules, such as sparse Cox regression, sparse Poisson regression and sparse SVM.
-Once they are developed, they can be fit into our framework to produce efficient algorithm for other types of lasso problem.
+The proposed adaptive hybrid screening framework is flexible and can be extended in several ways.
+The framework is general and does not require a specific algorithm, strong rule, or safe rule.
+As faster algorithms to solve the lasso problem, better safe rules, or improved strong rules are developed, these can be directly plugged into the adaptive hybrid framework with a corresponding improvement in computational efficiency.
+Nevertheless, there are still several lasso type problems without sequential safe rules, such as sparse Cox regression, sparse Poisson regression, and sparse support vector machines.
+As safe rules for these problems are developed, they can be readily fit into our framework to produce efficient algorithms as well.

### 2021-01-28 batch-hssr.tex
Updates from Overleaf
Edits to 3.1

@@
 \usepackage[nottoc]{tocbibind}
-\usepackage{color}
+\usepackage{xcolor}
 \usepackage{natbib}
@@
 \usepackage{float}
+\usepackage{hyperref}
+\hypersetup{colorlinks=true, citecolor=black, linkcolor=., urlcolor=cyan}
 \newtheorem{theorem}{Theorem}[section]
@@
 In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
-It reuses previous solutions in the path and avoids unhelpful heavy computations.
+It reuses previous solutions in the path and reduces unhelpful heavy computations.
 It is a flexible framework that can be easily extended to different types of lasso models.
-The Ada-SSR-EDPP for the standard lasso model and the Ada-SSR-Slores for the sparse logistic model are shown as examples.
+Two applications for the standard lasso model and the sparse logistic model are shown as examples.
 We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.

### 2021-01-28 main.tex

@@
 For data sets MNIST and NYT, because the response is randomly selected, we replicate the experiment 50 times to get an accurate estimate.
-Table 1 compares the average computation time for different screening methods in these data sets.
+Table~\ref{Tab:real} compares the average computation time for different screening methods in these data sets.
 

### 2021-01-28 main.tex
Reformatting tables, fixing references

@@
 
-There are two important categories of feature screening rules: ``strong'' rules \citep{tibshirani2011regression, qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules \citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
+There are two important categories of feature screening rules: ``strong'' rules \citep{Tibshirani2012, qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules \citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
 As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
@@
 These violations are inevitable in active-set cycling, as they occur every time a feature is added to the model.
-Sequential strong rules (SSR) \citep{tibshirani2011regression} have the basic idea of active-set cycling, but reduce violations by retaining features that are ``close'' to entering the model.
+Sequential strong rules (SSR) \citep{Tibshirani2012} have the basic idea of active-set cycling, but reduce violations by retaining features that are ``close'' to entering the model.
 
@@
 \centering
-\begin{tabular}{l|l|l|l|l}
-\hline
+\begin{tabular}{lllll}
+\toprule
  & GENE & MNIST & GWAS & NYT \\
 Screening method & n=536 & n=784 & n=313 & n=5,500 \\
- & p=17,322 & p=60,000 & p=660,496 & p=55,000 \\ \hline
+       & p=17,322 & p=60,000 & p=660,496 & p=55,000 \\
+\midrule
 AC & 2.14 (0.03) & 6.82 (0.07) & 46.67 (0.13) & 59.20 (1.89) \\
@@
 HSSR & 1.21 (0.01) & 3.44 (0.07) & 23.85 (0.06) & 31.05 (0.80) \\
-AHR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\\hline
+AHR & \textbf{0.71 (0.01)} & \textbf{1.15 (0.02)} & \textbf{8.80 (0.03)} & \textbf{12.71 (1.05)} \\
+\bottomrule
 \end{tabular}
@@
 \centering
-\begin{tabular}{l|l|l|l|l|l}
-\hline
+\begin{tabular}{llllll}
+\toprule
 Screening method & AC\,\,\,\,\,\,\,\,\,    & SSR\,\,\,\,\,\,   & SEDPP & HSSR\,\,\,  & AHR\,\,\,\,\,\,  \\
-\hline
-Time & 183.6 & 78.6 & 78.6 & 84.9 & 13.6\\
-Standard error & 0.43 & 0.65 & 0.20 & 0.48 & 0.15
- \\\hline
+\midrule
+Time & 183.6 & 78.6 & 78.6 & 84.9 & 13.6 \\
+Standard error & 0.43 & 0.65 & 0.20 & 0.48 & 0.15 \\
+\bottomrule
 \end{tabular}
@@
 \centering
-\begin{tabular}{l|l|l|l}
-\hline
-
+\begin{tabular}{llll}
+\toprule
 Screening method & SSR\,\,\,\,\,\,\,\,\,    & HSlores\,\,\,\,\,\,   & ASlores \\
-\hline
+\midrule
 Time & 82.7 & 107.5 & 51.7 \\
-Standard error & 0.10 & 0.67 & 0.17 
- \\\hline
+Standard error & 0.10 & 0.67 & 0.17 \\
+\bottomrule
 \end{tabular}

### 2021-01-28 main.tex
Formatting

@@
 One promising technique to address this challenge is feature screening.
-The lasso model solution is sparse in the sense that most coefficients will be exactly zero; for these ``inactive'' coefficients we do not need their associated features.
+The lasso model solution is sparse in the sense that most coefficients will be exactly zero; for these \quotes{inactive} coefficients we do not need their associated features.
 In theory, if we knew which coefficients were nonzero at each value of $\lambda$, we could read into memory only those features and leave the remaining features on disk.
@@
 There are many screening techniques where the solution obtained after screening is guaranteed to be the global optimum if one exists, and in this paper we focus only on this type of screening.
-In what follows, we refer to features left on disk as ``discarded'' features, although it is worth clarifying that this is not a permanent decision.
+In what follows, we refer to features left on disk as \quotes{discarded} features, although it is worth clarifying that this is not a permanent decision.
 In particular, a feature can be discarded at one value of $\lambda$ but included in the list of potentially active features at other values of $\lambda$.
 
-There are two important categories of feature screening rules: ``strong'' rules \citep{Tibshirani2012, qian2019fast}, which occasionally incorrectly discard some active features, and ``safe'' rules \citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
+There are two important categories of feature screening rules: \quotes{strong} rules \citep{Tibshirani2012, qian2019fast}, which occasionally incorrectly discard some active features, and \quotes{safe} rules \citep{ghaoui2010safe,wang2013lasso,xiang2012fast, xiang2011learning}, which are guaranteed never to do so.
 As one might expect, strong rules tend to be easier to calculate; however, because mistakes are possible, one must add a post-convergence check to ensure that no features were incorrectly discarded.
@@
 The goal of pathwise algorithms is to solve for this entire solution path.
-This can be done efficiently by using ``warm starts'': using previous points on the path as initial values, as these are likely to be relatively close to the solution.
+This can be done efficiently by using \quotes{warm starts}: using previous points on the path as initial values, as these are likely to be relatively close to the solution.
 For the model at any $\lambda$-value $\lambda_{l+1}$, letting $r(\lambda_{l+1}) \equiv y-X\hat{\beta}(\lambda_{l+1})$ denote the vector of residuals, the solution $\hat{\beta}(\lambda_{l+1})$ can be computed using the previous solution $\hat{\beta}(\lambda_l)$ as the initial value in the algorithm.
@@
 These violations are inevitable in active-set cycling, as they occur every time a feature is added to the model.
-Sequential strong rules (SSR) \citep{Tibshirani2012} have the basic idea of active-set cycling, but reduce violations by retaining features that are ``close'' to entering the model.
+Sequential strong rules (SSR) \citep{Tibshirani2012} have the basic idea of active-set cycling, but reduce violations by retaining features that are \quotes{close} to entering the model.
 
@@
 \end{equation}
-The SSR is derived from the KKT condition and the ``unit-slope'' assumption that the size of the slope of $x_j^Tr(\lambda)/n$ over $\lambda$ is bounded by 1.
+The SSR is derived from the KKT condition and the \quotes{unit-slope} assumption that the size of the slope of $x_j^Tr(\lambda)/n$ over $\lambda$ is bounded by 1.
 
-The biggest problem of SSR is that the ``unit-slope'' assumption may not hold and thus discarded features are not guaranteed to have zero coefficients.
+The biggest problem of SSR is that the \quotes{unit-slope} assumption may not hold and thus discarded features are not guaranteed to have zero coefficients.
 As with AC, a post-convergence KKT check is therefore needed for the discarded features to make sure their coefficients are truly zero.
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{plots/batchsizes.pdf}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
+    \includegraphics[width=0.6\textwidth]{plots/batchsizes.eps}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
     \label{fig:batchsizes}
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/511.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[width=\textwidth]{plots/511.eps}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[width=0.82\textwidth]{plots/511b.pdf}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[width=0.82\textwidth]{plots/511b.eps}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
 (3) $s$ is large.
-In this case, the solution is ``dense'' and screening rules have less ability to leverage sparsity to computational advantage.
+In this case, the solution is \quotes{dense} and screening rules have less ability to leverage sparsity to computational advantage.
 (4) $L$ is small.
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/512.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[width=\textwidth]{plots/512.eps}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[width=0.82\textwidth]{plots/512b.pdf}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[width=0.82\textwidth]{plots/512b.eps}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.
@@
     \item \textbf{Breast cancer gene expression data
-(GENE):} this data has expression measurements of $p=17,322$ genes from $n=536$ patients.
+(GENE, \url{https://myweb.uiowa.edu/pbreheny/data/bcTCGA.html}):} this data has expression measurements of $p=17,322$ genes from $n=536$ patients.
 The response is the expression measurement of the gene BRCA1, which has been identified to be related to risk of breast cancer.
     \item \textbf{MNIST handwritten image data
-(MNIST):} this data set has $60,000$ images in the training set and $10,000$ images in the testing set.
+(MNIST, \url{http://yann.lecun.com/exdb/mnist}):} this data set has $60,000$ images in the training set and $10,000$ images in the testing set.
 Each image is a $28\times 28=784$ pixels image of handwritten digits.
@@
 Then an image from the testing set is randomly selected as the response.
-    \item \textbf{ Cardiac fibrosis genome-wide association data
-(GWAS):} this data set has $p=660,496$ single nucleotide
+    \item \textbf{Cardiac fibrosis genome-wide association data
+(GWAS, \url{https://arxiv.org/abs/1607.05636}):} this data set has $p=660,496$ single nucleotide
 polymorphisms (SNPs) collected from $n=313$ human hearts. The response is the log of the ratio of cardiomyocytes to fibroblasts in the heart tissue, which is associated with heart failure.
     \item \textbf{Subset of New York Times bag-of-words data
-(NYT):} the raw data set is a $300,000\times 102,660$ matrix, each row being a document and each column being number of occurrence of a specific word in those documents.
+(NYT, \url{https://archive.ics.uci.edu/ml/datasets/Bag+of+Words}):} the raw data set is a $300,000\times 102,660$ matrix, each row being a document and each column being number of occurrence of a specific word in those documents.
 We selected $n=5,500$ documents by removing documents with low word counts.
@@
 
-AHR again outperforms other screening methods on all data sets, faster than the fastest of the rest by 70\% to 200\% \pb{how about ``faster than other methods by factor ranging from 70\% to 630\%''?
-To me, ``faster than the fastest of the rest'' seems more complicated than necessary}.
+AHR again outperforms other screening methods on all data sets, faster than other methods by factor ranging from 70\% to 630\%.
 Also note that the performance of SEDPP varies considerably for the MNIST and NYT data sets, where the response is randomly selected in each replication, indicating that the speed of SEDPP is sensitive to the data.

### 2021-01-29 TFStyleAnonymous.tex
TF style anonymous submission

--- 2021-01-27 TaylorFrancisStyle.tex
@@
 \providecommand{\lam}{\lambda}
+\newcommand{\quotes}[1]{`#1'}
 
 \title{Adaptive Hybrid Screening for Efficient Lasso Optimization}
-%\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
-%  \and
-%  Patrick Breheny\\Department of Biostatistics\\University of Iowa}
 
-\author{
-\name{Chuyi Wang\textsuperscript{a}\thanks{CONTACT Chuyi Wang. Email: chuyi-wang@uiowa.edu} and Patrick Breheny\textsuperscript{b}}
-\affil{\textsuperscript{a}Department of Statistics and Actuarial Sciences, University of Iowa, USA; \\\textsuperscript{b}Department of Biostatistics, University of Iowa, USA}
-}
+\author{Word count: 8899.}
+
 \date{}
@@
 Typical practice is to tune the size of lasso penalty along a path of values.
-Due to modern data collection techniques, researchers need to analyse data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
+Due to modern data collection techniques, researchers need to analyze data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
 Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.

### 2021-01-29 TFStyleTitle.tex
TF style anonymous submission

--- 2021-01-27 TaylorFrancisStyle.tex
@@
 \providecommand{\lam}{\lambda}
+\newcommand{\quotes}[1]{`#1'}
 
 \title{Adaptive Hybrid Screening for Efficient Lasso Optimization}
-%\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
-%  \and
-%  Patrick Breheny\\Department of Biostatistics\\University of Iowa}
 
 \author{
-\name{Chuyi Wang\textsuperscript{a}\thanks{CONTACT Chuyi Wang. Email: chuyi-wang@uiowa.edu} and Patrick Breheny\textsuperscript{b}}
+\name{Chuyi Wang\textsuperscript{a}\thanks{CONTACT Chuyi Wang. Email: chuyi-wang@uiowa.edu} and Patrick Breheny\textsuperscript{b}\thanks{CONTACT Patrick Breheny. Email: patrick-breheny@uiowa.edu}}
 \affil{\textsuperscript{a}Department of Statistics and Actuarial Sciences, University of Iowa, USA; \\\textsuperscript{b}Department of Biostatistics, University of Iowa, USA}
@@
 
-\begin{abstract}
-Lasso type models are popular in statistics, especially for high-dimensional data.
-Typical practice is to tune the size of lasso penalty along a path of values.
-Due to modern data collection techniques, researchers need to analyse data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
-Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.
-In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
-It reuses previous solutions in the path and reduces unhelpful heavy computations.
-It is a flexible framework that can be easily extended to different types of lasso models.
-Two applications for the standard lasso model and the sparse logistic model are shown as examples.
-We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
-\end{abstract}
-
-\begin{keywords}
-Lasso; feature Screening; safe screening; solution path; large-scale sparse learning
-\end{keywords}
-
-\input{main}
-
-\renewcommand\bibname{References}
-\bibliographystyle{tfnlm}
-\bibliography{ref}
-
 \end{document}

### 2021-01-29 jscs/TFStyle.tex
Moving journal files to jscs directory

--- 2021-01-27 TaylorFrancisStyle.tex
@@
 \providecommand{\lam}{\lambda}
+\newcommand{\quotes}[1]{`#1'}
 
 \title{Adaptive Hybrid Screening for Efficient Lasso Optimization}
-%\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
-%  \and
-%  Patrick Breheny\\Department of Biostatistics\\University of Iowa}
 

### 2021-01-29 jscs/adaptive-hssr.tex
Moving journal files to jscs directory

--- 2021-01-28 main.tex
@@
+\documentclass[]{interact}
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
+%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
+%\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
+%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled
+
+\usepackage[numbers,sort&compress]{natbib}% Citation support using natbib.sty
+\bibpunct[, ]{[}{]}{,}{n}{,}{,}% Citation support using natbib.sty
+\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
+\makeatletter% @ becomes a letter
+\def\NAT@def@citea{\def\@citea{\NAT@separator}}% Suppress spaces between citations using natbib.sty
+\makeatother% @ becomes a symbol again
+
+\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\newtheorem{notation}{Notation}
+
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage[ruled,vlined, linesnumbered]{algorithm2e}
+\usepackage[english]{babel}
+\usepackage[nottoc]{tocbibind}
+\usepackage{xcolor}
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage{hyperref}
+\hypersetup{colorlinks=true, citecolor=black, linkcolor=., urlcolor=cyan}
+\graphicspath{{../plots/}}
+
+% Custom commands / shortcuts
+\providecommand{\sign}{\textrm{sign}}
+\providecommand{\pb}[1]{\textcolor{red}{#1}}
+\providecommand{\lam}{\lambda}
+\newcommand{\quotes}[1]{`#1'}
+
+\title{Adaptive Hybrid Screening for Efficient Lasso Optimization}
+
+\author{Word count: 8899.}
+
+\date{}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
+Lasso type models are popular in statistics, especially for high-dimensional data.
+Typical practice is to tune the size of lasso penalty along a path of values.
+Due to modern data collection techniques, researchers need to analyze data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
+Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.
+In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
+It reuses previous solutions in the path and reduces unhelpful heavy computations.
+It is a flexible framework that can be easily extended to different types of lasso models.
+Two applications for the standard lasso model and the sparse logistic model are shown as examples.
+We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
+\end{abstract}
+
+\begin{keywords}
+Lasso; feature Screening; safe screening; solution path; large-scale sparse learning
+\end{keywords}
+
 \section{Introduction}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{plots/batchsizes.eps}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
+    \includegraphics[width=0.6\textwidth]{batchsizes.eps}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
     \label{fig:batchsizes}
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/511.eps}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[width=\textwidth]{511.eps}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[width=0.82\textwidth]{plots/511b.eps}    \caption{Comparing speed of screening methods for lasso model under different settings.
+    \includegraphics[width=0.82\textwidth]{511b.eps}    \caption{Comparing speed of screening methods for lasso model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[width=\textwidth]{plots/512.eps}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[width=\textwidth]{512.eps}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.
@@
     \centering
-    \includegraphics[width=0.82\textwidth]{plots/512b.eps}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
+    \includegraphics[width=0.82\textwidth]{512b.eps}    \caption{Comparing speed of screening methods for sparse logistic regression model under different settings.
 Top row: computation time in second.
@@
 As safe rules for these problems are developed, they can be readily fit into our framework to produce efficient algorithms as well.
+
+\renewcommand\bibname{References}
+\bibliographystyle{tfnlm}
+\begin{thebibliography}{10}
+\providecommand{\url}[1]{\normalfont{#1}}
+\providecommand{\urlprefix}{Available from: }
+
+\bibitem{tibshirani1996regression}
+Tibshirani~R. Regression shrinkage and selection via the lasso. Journal of the
+  Royal Statistical Society: Series B (Methodological).
+  1996;\hspace{0pt}58(1):267--288.
+
+\bibitem{yuan2006model}
+Yuan~M, Lin~Y. Model selection and estimation in regression with grouped
+  variables. Journal of the Royal Statistical Society: Series B (Statistical
+  Methodology). 2006;\hspace{0pt}68(1):49--67.
+
+\bibitem{zou2005regularization}
+Zou~H, Hastie~T. Regularization and variable selection via the elastic net.
+  Journal of the Royal Statistical Society: Series B (Statistical Methodology).
+  2005;\hspace{0pt}67(2):301--320.
+
+\bibitem{friedman2007pathwise}
+Friedman~J, Hastie~T, H{\"o}fling~H, et~al. Pathwise coordinate optimization.
+  The Annals of Applied Statistics. 2007;\hspace{0pt}1(2):302--332.
+
+\bibitem{Tibshirani2012}
+Tibshirani~R, Bien~J, Friedman~J, et~al. Strong rules for discarding predictors
+  in lasso-type problems. Journal of the Royal Statistical Society Series B.
+  2012;\hspace{0pt}74(2):245--266.
+
+\bibitem{qian2019fast}
+Qian~J, Du~W, Tanigawa~Y, et~al. A fast and flexible algorithm for solving the
+  lasso in large-scale and ultrahigh-dimensional problems. BioRxiv.
+  2019;\hspace{0pt}:630079.
+
+\bibitem{ghaoui2010safe}
+Ghaoui~LE, Viallon~V, Rabbani~T. Safe feature elimination for the lasso and
+  sparse supervised learning problems. arXiv:10094219. 2010;\hspace{0pt}.
+
+\bibitem{wang2013lasso}
+Wang~J, Zhou~J, Wonka~P, et~al. Lasso screening rules via dual polytope
+  projection. In: Advances in Neural Information Processing Systems; 2013. p.
+  1070--1078.
+
+\bibitem{xiang2012fast}
+Xiang~ZJ, Ramadge~PJ. Fast lasso screening tests based on correlations. In:
+  International Conference on Acoustics, Speech and Signal Processing; IEEE;
+  2012. p. 2137--2140.
+
+\bibitem{xiang2011learning}
+Xiang~ZJ, Xu~H, Ramadge~PJ. Learning sparse representations of high dimensional
+  data on large scale dictionaries. In: Advances in Neural Information
+  Processing Systems; 2011. p. 900--908.
+
+\bibitem{Zeng2021}
+Zeng~Y, Yang~T, Breheny~P. Hybrid safe–strong rules for efficient
+  optimization in lasso-type problems. Computational Statistics \& Data
+  Analysis. 2021;\hspace{0pt}153:107063.
+
+\bibitem{zeng2017biglasso}
+Zeng~Y, Breheny~P. The biglasso package: a memory-and computation-efficient
+  solver for lasso model fitting with big data in {R}. arXiv:170105936.
+  2017;\hspace{0pt}.
+
+\bibitem{lee2007efficient}
+Lee~H, Battle~A, Raina~R, et~al. Efficient sparse coding algorithms. In:
+  Advances in neural information processing systems; 2007. p. 801--808.
+
+\bibitem{Fan2008}
+Fan~J, Lv~J. Sure independence screening for ultrahigh dimensional feature
+  space. Journal of the Royal Statistical Society Series B.
+  2008;\hspace{0pt}70(5):849--911.
+
+\bibitem{wang2014safe}
+Wang~J, Zhou~J, Liu~J, et~al. A safe screening rule for sparse logistic
+  regression. In: Advances in Neural Information Processing Systems; 2014. p.
+  1053--1061.
+
+\bibitem{breheny2015group}
+Breheny~P, Huang~J. Group descent algorithms for nonconvex penalized linear and
+  logistic regression models with grouped predictors. Statistics and Computing.
+  2015;\hspace{0pt}25(2):173--187.
+
+\bibitem{xiang2016screening}
+Xiang~ZJ, Wang~Y, Ramadge~PJ. Screening tests for lasso problems. IEEE
+  Transactions on Pattern Analysis and Machine Intelligence.
+  2016;\hspace{0pt}39(5):1008--1027.
+
+\bibitem{Das2016}
+Das~S, Forer~L, Sch{\"o}nherr~S, et~al. Next-generation genotype imputation
+  service and methods. Nature Genetics. 2016 Oct;\hspace{0pt}48(10):1284--1287.
+
+\end{thebibliography}
+
+\end{document}

### 2021-01-29 batch-hssr.tex
Reformatting tables, fixing references
Formatting
Moving journal files to jscs directory
Edits to abstract

--- 2020-09-18 batch-hssr.tex
@@
 \usepackage{float}
+\usepackage{booktabs}
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage{hyperref}
+\hypersetup{colorlinks=true, citecolor=black, linkcolor=., urlcolor=cyan}
 \newtheorem{theorem}{Theorem}[section]
 \bibliographystyle{ims}
+\graphicspath{{plots/}}
+
 % Custom commands / shortcuts
 \providecommand{\sign}{\textrm{sign}}
-\providecommand{\note}[1]{\textcolor{red}{#1}}
+\providecommand{\pb}[1]{\textcolor{red}{#1}}
 \providecommand{\lam}{\lambda}
+\newcommand{\quotes}[1]{``#1''}
 
@@
 
+\begin{abstract}
+Lasso type models are a popular approach for analyzing high-dimensional data.
+The size of modern data sets can be quite large, so developing efficient algorithms is important.
+Feature screening techniques have proven to be effective at increasing efficiency, as they allow for considerable dimension reduction during the optimization process.
+In this paper, we develop an adaptive hybrid screening framework where screening is carried out adaptively along the path of tuning parameter values, reusing previous solutions to reduce heavy screening computations if they fail to significantly reduce dimensionality.
+We focus on the standard lasso model and sparse logistic model, but the proposed framework is flexible and can be easily extended to different types of lasso models.
+Through experiments involving a wide variety of simulated and real data sets, we show that the adaptive hybrid methods significantly outperform other state-of-the-art methods, with the greatest speedup occurring in the most challenging scenarios.
+\end{abstract}
+
 \input{main}

### 2021-01-29 jscs/TFStyleAnonymous.tex
Moving journal files to jscs directory
Edits to abstract

--- 2021-01-29 TFStyleAnonymous.tex
@@
 \hypersetup{colorlinks=true, citecolor=black, linkcolor=., urlcolor=cyan}
+\graphicspath{{../plots/}}
+
 % Custom commands / shortcuts
@@
 \begin{abstract}
-Lasso type models are popular in statistics, especially for high-dimensional data.
-Typical practice is to tune the size of lasso penalty along a path of values.
-Due to modern data collection techniques, researchers need to analyze data with millions of features, which brings a great need for an efficient lasso optimization algorithm.
-Feature screening techniques have proven to be powerful for this need, because they can discard features and lead to a model with much less features.
-In this paper, we develop an adaptive hybrid screening framework where screening is carried out adpatively along the path of tuning parameter values.
-It reuses previous solutions in the path and reduces unhelpful heavy computations.
-It is a flexible framework that can be easily extended to different types of lasso models.
-Two applications for the standard lasso model and the sparse logistic model are shown as examples.
-We perform simulation study and real data study in a wide range of scenarios and the adaptive hybrid methods outperform other state-of-the-art method significantly and uniformly, with the greatest speedup in the most challenging scenarios.
+Lasso type models are a popular approach for analyzing high-dimensional data.
+The size of modern data sets can be quite large, so developing efficient algorithms is important.
+Feature screening techniques have proven to be effective at increasing efficiency, as they allow for considerable dimension reduction during the optimization process.
+In this paper, we develop an adaptive hybrid screening framework where screening is carried out adaptively along the path of tuning parameter values, reusing previous solutions to reduce heavy screening computations if they fail to significantly reduce dimensionality.
+We focus on the standard lasso model and sparse logistic model, but the proposed framework is flexible and can be easily extended to different types of lasso models.
+Through experiments involving a wide variety of simulated and real data sets, we show that the adaptive hybrid methods significantly outperform other state-of-the-art methods, with the greatest speedup occurring in the most challenging scenarios.
 \end{abstract}
@@
 
-\input{main}
+\input{../main}
 
@@
 \bibliographystyle{tfnlm}
-\bibliography{ref}
+\bibliography{../ref}
 

### 2021-06-23 main.tex
Address reviewer issues except 1

@@
 
-Throughout this paper, it will be assumed that $y$ is centered and $\{x_j\}_{j=1}^p$ are centered and standardized:
+Throughout this paper, it will be assumed for simplicity that $y$ is centered and $\{x_j\}_{j=1}^p$ are centered and standardized:
 \begin{equation}
@@
 Furthermore, this can be done without loss of generality as one can always obtain the solution on the original scale through a simple linear transformation of the standardized solution.
+Nevertheless, the methods proposed in this paper also work without standardization.
 
@@
 Then using the KKT conditions, some features can be guaranteed to have zero coefficients and be discarded safely.
-Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed and under the standardization \eqref{eq:std} can be simplified in the following theorems \citep{Zeng2021}:
+Two forms of the EDPP rule, basic EDPP (BEDPP) and sequential EDPP (SEDPP)\citep{wang2013lasso}, were proposed without standardization and under the standardization \eqref{eq:std} can be simplified in the following theorems \citep{Zeng2021}:
 
@@
 
-Compared to one-step methods like BEDPP, the reference solutions are continually updated.
+Compared to one-step methods like BEDPP, the reference solutions are updated systematically.
 As a result, the reference is always relatively close to the solution, and screening remains powerful over the entire path, unlike one-step methods where screening power drops drastically as $\lambda_l$ gets further away from $\lambda_0$.
@@
         }
-        \uIf{Update conditions met}{
+        \uIf{Update conditions met\label{line:upcond}}{
             Reference = $\lambda_{l}$
@@
 
-In this section we will fill in line 11 in Algorithm~\ref{alg:path}.
+In this section we will fill in line \ref{line:upcond} in Algorithm~\ref{alg:path}.
 We develop an algorithm to determine when to update the reference for screening.
@@
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
+These two assumptions are supported by experiments from both the origin paper of SSR \citep{Tibshirani2012} and many other papers studying feature screening.
 
@@
 Then, for each $\lambda_{l+b}$, the post-convergence check requires approximately $|\mathcal{S}_{l+b} \setminus \mathcal{R}_{l+b}| \approx |\mathcal{S}_{l+b}|$ KKT condition checks, each of which requires $n$ multiplications.
-These sum to $n\sum_{b=1}^{B}|\mathcal{S}_{l=b}|$ multiplications, where $l+B$ is the start of the next update.
+These sum to $n\sum_{b=1}^{B}|\mathcal{S}_{l+b}|$ multiplications, where $l+B$ is the start of the next update.
 Combining these two parts, the average cost per $\lambda$ in the block $\lambda_{l+1},...,\lambda_{l+B}$ is
@@
 Adaptive EDPP can strike a balance between BEDPP and SEDPP.
+The screening power drops as the same reference keeps being reused, indicated by the decreasing part of the green line.
+However, the reference gets updated periodically and at those points screening regains strength, indicated by the upward jumps on the green line.
+The overall screening power is kept relative high with only a few updates.
 In this example, simply using a fixed batch size $B=10$ can reduce the safe rule updating cost by 90\% compared to SEDPP and reduce the KKT checking cost by about 80\% compared to BEDPP.
@@
 
-We use this updating condition at line 11 in Algorithm~\ref{alg:path} to form a complete pathwise lasso algorithm with adaptive hybrid screening.
+We use this updating condition at line \ref{line:upcond} in Algorithm~\ref{alg:path} to form a complete pathwise lasso algorithm with adaptive hybrid screening.
 
@@
     \label{eq:logis}
-    %\hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}-
-  \frac{1}{n} \sum_{i=1}^n \big\{y_i\log\pi_i(\beta) + (1-y_i)\log(1 -\pi_i(\beta))\big\} + \lambda||\beta||_1,
+    %\hat{\beta}(\lambda)=\underset{(\beta,\beta_0)\in \mathbb{R}^p\times\mathbb{R}^1}{\mathrm{argmin}}
+  -\frac{1}{n} \sum_{i=1}^n \big\{y_i\log\pi_i(\beta) + (1-y_i)\log(1 -\pi_i(\beta))\big\} + \lambda||\beta||_1,
 \end{equation}
@@
 When computing the adaptive Slores, $\{x_j^Ty\}_{j=1}^p$ needs to be computed only once, after which it can be stored and reused for the whole solution path.
-The quantity $\{x_j^Tx_*\}_{j=1}^p$ can be similarly reused unless $x_*$ changes, which happens if the corresponding regression coefficient drops out of the model; this is relatively rare, but can happen.
+The vector $x_*$ can be chosen arbitrarily from features that has non-zero coefficients at the reference $\lambda_l$, for example, the feature whose coefficient that first enters the model.
+The quantity $\{x_j^Tx_*\}_{j=1}^p$ can be similarly reused unless the corresponding regression coefficient drops out of the model; this can happen but is relatively rare.
 Other than those two terms, the only term that requires expensive $O(np)$ computations is $\{x_j^Tr(\lambda_l)\}_{j=1}^p$, which needs to be computed only when we update the reference solution.
@@
 \begin{theorem}[Adaptive EDPP for group lasso]
-  For the group lasso problem \eqref{eq:glasso}, suppose $\lambda_0>\lambda_1>...>\lambda_L$, with $\lambda_0:= \max_j ||X_g^Ty||_2 / (n\sqrt{p_g})$.
+  For the group lasso problem \eqref{eq:glasso}, suppose $\lambda_0>\lambda_1>...>\lambda_L$, with $\lambda_0:= \max_g ||X_g^Ty||_2 / (n\sqrt{p_g})$.
 Under conditions \eqref{eq:std} and \eqref{eq:stdg},
@@
 For example, when $L=1000$, AHR is 18 times faster than any other approach.
+When $\lambda_{\min}/\lambda_{\max}$ is large, both AHR and HSSR can take advantage because all the $\lam$ values in the path are close to the first reference $\lambda_{\max}$.
 
@@
 As faster algorithms to solve the lasso problem, better safe rules, or improved strong rules are developed, these can be directly plugged into the adaptive hybrid framework with a corresponding improvement in computational efficiency.
+As a result of the flexibility, the standardization conditions required in this paper can also be removed if we substitute the underlying sequential safe rules with the forms in their original papers that do not require standardization.
 Nevertheless, there are still several lasso type problems without sequential safe rules, such as sparse Cox regression, sparse Poisson regression, and sparse support vector machines.
-As safe rules for these problems are developed, they can be readily fit into our framework to produce efficient algorithms as well.
+The sequential strong rule can address these problems, but as safe rules for these problems are developed, our framework can readily fit both strong rules and safe rules in to produce an even more efficient algorithms.

### 2021-08-17 appendix.tex
Add appendix

\appendix
\appendixpage

\section{Supplementary Real Data Analysis Results}
\label{sec:ap}

At the first replication on each of the 4 data sets, we first record the number of features discarded by each screening method at each $\lambda$ value along the path of $L=100$ values. Features discarded by SEDPP are safely discarded and features discarded by SSR are not safely discarded and require additional checks. For the adaptive hybrid rule, we use AHR\_Safe to denote the features that are safely discarded first by adaptive EDPP and AHR\_Strong to denote features that discarded afterward by adaptive SSR and require additional checks. The results are summarized in Figure \ref{fig:ap1}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.82\textwidth]{app1.eps}    \caption{Comparing number of discards by screening methods for lasso model along $\lambda$ values.}
    \label{fig:ap1}
\end{figure}

Note each jump of the number of discards for AHR method indicates an update of reference because a newer reference leads to higher screening power. Our adaptive updating algorithm determines the timing of update dynamically depending on the screening performance. For all four data sets, with about only 10 updates, the adaptive hybrid screening can safely discard a great number of features at most $\lambda$ values.

Next we compare the number of rounds of KKT conditions checks and the number of KKT conditions checks on individual features, needed for AHR and SSR respectively, as shown in Table \ref{Tab:kkt1} and Table \ref{Tab:kkt2}. In a round of KKT conditions check, all features that are not discarded by the safe rule are checked, and a round a KKT conditions check potentially include a large number of KKT conditions checks on individual features.

\begin{table}[H]
\centering
\begin{tabular}{lllll}
\toprule
Screening method & GENE & MNIST & GWAS & NYT \\
\midrule
SSR & 99 & 99 & 99 & 99 \\
AHR & 99 & 99 & 99 & 99 \\
\bottomrule
\end{tabular}
\caption{Number of rounds of KKT conditions checks required for the whole path}
\label{Tab:kkt1}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{lllll}
\toprule
Screening method & GENE & MNIST & GWAS & NYT \\
\midrule
SSR & 1,712 & 5,943 & 60,986 & 5,429 \\
AHR & 172 & 286 & 2,353 & 622 \\
\bottomrule
\end{tabular}
\caption{Number of KKT conditions checks on individual features ($\times10^3$) required for the whole path}
\label{Tab:kkt2}
\end{table}

Although a path include $L=100$ $\lambda$ values, the solution at the first value $\lambda_{0}$ is trivially $\hat{\beta}(\lambda_0)=0$ so we are essentially solving along $99$ $\lam$ values. If the strong rule does not make a violation, the minimal number of rounds of KKT conditions checks required will be $99$. In all four data sets, neither SSR nor the adaptive SSR in AHR ever makes a violation. However two methods are very different in terms of the number of KKT conditions checks on individual features, which proportionally increases the computational cost. AHR requires much less checks on individual features because the adaptive EDPP narrows down the set of features that need to be checked by a magnitude.

### 2021-08-17 jscs/adaptive-hssr.tex
Fix reference style
Add appendix

@@
 \usepackage[utf8]{inputenc}
+\usepackage{appendix}
 \usepackage{amsmath}
@@
 \usepackage[english]{babel}
-\usepackage[nottoc]{tocbibind}
+%\usepackage[nottoc]{tocbibind}
 \usepackage{xcolor}
@@
 \hypersetup{colorlinks=true, citecolor=black, linkcolor=., urlcolor=cyan}
+\usepackage{breakurl}
 \graphicspath{{../plots/}}
@@
 AHR is built with SEDPP as the safe rule but does not share this issue of instability because it can adaptively adjust itself according the performance of the safe rule.
+Besides the computation time, we also look at a variaty of other statistics in the experiments, as discussed in the Appendix \ref{sec:ap}.
 
@@
 
-\renewcommand\bibname{References}
 \bibliographystyle{tfnlm}
@@
 
+\appendix
+\appendixpage
+
+\section{Supplementary Real Data Analysis Results}
+\label{sec:ap}
+
+At the first replication on each of the 4 data sets, we first record the number of features discarded by each screening method at each $\lambda$ value along the path of $L=100$ values.
+Features discarded by SEDPP are safely discarded and features discarded by SSR are not safely discarded and require additional checks.
+For the adaptive hybrid rule, we use AHR\_Safe to denote the features that are safely discarded first by adaptive EDPP and AHR\_Strong to denote features that discarded afterward by adaptive SSR and require additional checks.
+The results are summarized in Figure \ref{fig:ap1}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.82\textwidth]{app1.eps}    \caption{Comparing number of discards by screening methods for lasso model along $\lambda$ values.}
+    \label{fig:ap1}
+\end{figure}
+
+Note each jump of the number of discards for AHR method indicates an update of reference because a newer reference leads to higher screening power.
+Our adaptive updating algorithm determines the timing of update dynamically depending on the screening performance.
+For all four data sets, with about only 10 updates, the adaptive hybrid screening can safely discard a great number of features at most $\lambda$ values.
+
+Next we compare the number of rounds of KKT conditions checks and the number of KKT conditions checks on individual features, needed for AHR and SSR respectively, as shown in Table \ref{Tab:kkt1} and Table \ref{Tab:kkt2}.
+In a round of KKT conditions check, all features that are not discarded by the safe rule are checked, and a round a KKT conditions check potentially include a large number of KKT conditions checks on individual features.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{lllll}
+\toprule
+Screening method & GENE & MNIST & GWAS & NYT \\
+\midrule
+SSR & 99 & 99 & 99 & 99 \\
+AHR & 99 & 99 & 99 & 99 \\
+\bottomrule
+\end{tabular}
+\caption{Number of rounds of KKT conditions checks required for the whole path}
+\label{Tab:kkt1}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{lllll}
+\toprule
+Screening method & GENE & MNIST & GWAS & NYT \\
+\midrule
+SSR & 1,712 & 5,943 & 60,986 & 5,429 \\
+AHR & 172 & 286 & 2,353 & 622 \\
+\bottomrule
+\end{tabular}
+\caption{Number of KKT conditions checks on individual features ($\times10^3$) required for the whole path}
+\label{Tab:kkt2}
+\end{table}
+
+Although a path include $L=100$ $\lambda$ values, the solution at the first value $\lambda_{0}$ is trivially $\hat{\beta}(\lambda_0)=0$ so we are essentially solving along $99$ $\lam$ values.
+If the strong rule does not make a violation, the minimal number of rounds of KKT conditions checks required will be $99$.
+In all four data sets, neither SSR nor the adaptive SSR in AHR ever makes a violation.
+However two methods are very different in terms of the number of KKT conditions checks on individual features, which proportionally increases the computational cost.
+AHR requires much less checks on individual features because the adaptive EDPP narrows down the set of features that need to be checked by a magnitude.
+
 \end{document}

### 2021-08-17 main.tex
Add appendix

@@
 Compared to strong rules, safe rules are never violated.
-Features can be discarded safely, with no need for post-covergence checking, as the coefficients are guaranteed to be zero by the rule.
+Features can be discarded safely, with no need for post-convergence checking, as the coefficients are guaranteed to be zero by the rule.
 We mainly focus on enhanced dual polytope projections (EDPP) rules\citep{wang2013lasso} because they outperform other known safe rules and are easy to incorporate into our method.
@@
 Combined with \eqref{eq:cost}, the latter condition is approximately
-
 \begin{equation}
@@
 In addition to the standardization conditions given in \eqref{eq:std}, we apply an additional standardization at the group level \citep{breheny2015group}:
-
 \begin{equation}

### 2021-08-17 jscs/adaptive-hssr.tex
Arguments on SSR

@@
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
+These two assumptions are supported by experiments from the origin paper of SSR \citep{Tibshirani2012}, many other papers studying feature screening, and our manuscript as discussed in the Appendix \ref{sec:ap}.
 
@@
 As faster algorithms to solve the lasso problem, better safe rules, or improved strong rules are developed, these can be directly plugged into the adaptive hybrid framework with a corresponding improvement in computational efficiency.
+As a result of the flexibility, the standardization conditions required in this paper can also be removed if we substitute the underlying sequential safe rules with the forms in their original papers that do not require standardization.
 Nevertheless, there are still several lasso type problems without sequential safe rules, such as sparse Cox regression, sparse Poisson regression, and sparse support vector machines.
-As safe rules for these problems are developed, they can be readily fit into our framework to produce efficient algorithms as well.
+The sequential strong rule can address these problems, but as safe rules for these problems are developed, our framework can readily fit both strong rules and safe rules in to produce an even more efficient algorithms.
 

### 2021-08-17 main.tex
Arguments on SSR

@@
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
-These two assumptions are supported by experiments from both the origin paper of SSR \citep{Tibshirani2012} and many other papers studying feature screening.
+These two assumptions are supported by experiments from the origin paper of SSR \citep{Tibshirani2012}, many other papers studying feature screening, and our manuscript as discussed in the Appendix \ref{sec:ap}.
 

### 2021-09-08 appendix.tex
Edits to appendix

@@
-\appendix
-\appendixpage
+%\appendix
+%\appendixpage
 
-\section{Supplementary Real Data Analysis Results}
-\label{sec:ap}
+\section*{Appendix}
+%\label{sec:ap}
 
-At the first replication on each of the 4 data sets, we first record the number of features discarded by each screening method at each $\lambda$ value along the path of $L=100$ values.
-Features discarded by SEDPP are safely discarded and features discarded by SSR are not safely discarded and require additional checks.
+To illustrate the inner workings of the proposed algorithm on a variety of problems, for a single replication of each of the four data sets in Section~\ref{sec:real-data} we recorded the number of features discarded by each screening method at each $\lambda$ value along the path of $L=100$ values.
+Features discarded by SEDPP are safely discarded, while features discarded by SSR are not necessarily safe and require additional checks.
 For the adaptive hybrid rule, we use AHR\_Safe to denote the features that are safely discarded first by adaptive EDPP and AHR\_Strong to denote features that discarded afterward by adaptive SSR and require additional checks.
@@
 
-Note each jump of the number of discards for AHR method indicates an update of reference because a newer reference leads to higher screening power.
+Note that the AHR method is rather ``jumpy''; this is by design, and these spikes represent moments along the path that triggered an update of the reference solution to gain more screening power.
 Our adaptive updating algorithm determines the timing of update dynamically depending on the screening performance.
@@
 
-Next we compare the number of rounds of KKT conditions checks and the number of KKT conditions checks on individual features, needed for AHR and SSR respectively, as shown in Table \ref{Tab:kkt1} and Table \ref{Tab:kkt2}.
-In a round of KKT conditions check, all features that are not discarded by the safe rule are checked, and a round a KKT conditions check potentially include a large number of KKT conditions checks on individual features.
+Next we compare the number of rounds of KKT condition checks and the number of KKT condition checks on individual features needed for AHR and SSR respectively, as shown in Table \ref{Tab:kkt1} and Table \ref{Tab:kkt2}.
+In a round of KKT condition checking, all features that are not discarded by the safe rule are checked, which potentially includes a large number of individual feature checks.
 
@@
 
-Although a path include $L=100$ $\lambda$ values, the solution at the first value $\lambda_{0}$ is trivially $\hat{\beta}(\lambda_0)=0$ so we are essentially solving along $99$ $\lam$ values.
-If the strong rule does not make a violation, the minimal number of rounds of KKT conditions checks required will be $99$.
-In all four data sets, neither SSR nor the adaptive SSR in AHR ever makes a violation.
-However two methods are very different in terms of the number of KKT conditions checks on individual features, which proportionally increases the computational cost.
-AHR requires much less checks on individual features because the adaptive EDPP narrows down the set of features that need to be checked by a magnitude.
+Although all paths includes $L=100$ $\lambda$ values, the solution at the first value is exactly $\hat{\beta}(\lambda_0)=0$ and does not require any checking.
+Thus, if no violations occur in the application of the strong rule, the number of rounds of KKT condition checking required will attain its minimum value of $99$.
+In all four data sets, neither SSR nor the adaptive SSR in AHR is ever violated (as other authors have discussed, violations are rare but possible).
+However, the two methods are very different in terms of the number of individual features involved in these condition checks.
+AHR requires far fewer checks on individual features because the adaptive EDPP narrows down the set of features that need to be checked by an order of magnitude, which is how it achieves greater computational efficiency.

### 2021-09-08 main.tex
Edits to appendix

--- 2021-08-17 main.tex
@@
 
-This manuscript provides a brief review of existing feature screening rules in Section\ref{sec:existing} as well as the following novel contributions:
+This manuscript provides a brief review of existing feature screening rules in Section~\ref{sec:existing} as well as the following novel contributions:
 
 \begin{itemize}
-    \item A new feature screening framework (Section 3.1,3.2), which updates the reference for screening along the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
-    \item Three specific applications of this framework, for fitting lasso-penalized linear regression, lasso-penalized logistic regression and group lasso models, respectively (Section~\ref{sec:method},~\ref{sec:logis},~\ref{sec:group}).
-    \item An algorithm to determine when to update to a new reference $\lambda$ value for best efficiency (Section \ref{sec:adaptive}).
+    \item A new feature screening framework (Sections~\ref{sec:asr}, \ref{sec:ahr}), which updates the reference for screening along the grid of $\lambda$ values on any combination of strong screening rules and safe screening rules, which can generate a family of more efficient and scalable screening rules, compared to previous screening rules that are either sequential or one-step.
+    \item Three specific applications of this framework for fitting lasso penalized linear regression, lasso penalized logistic regression, and group lasso models (Sections~\ref{sec:method},~\ref{sec:logis},~\ref{sec:group}).
+    \item An algorithm to determine when to update the reference $\lambda$ value for best efficiency (Section \ref{sec:adaptive}).
     \item Simulation studies (Section~\ref{sec:sim}) and real data analysis (Section~\ref{sec:real-data}) under a variety of scenarios, including testing data sets larger than memory, which showed that the proposed algorithms outperform other approaches in all cases, with substantial speed up.
@@
 \subsection{Adaptive Safe Rules}
+\label{sec:asr}
 
@@
 \subsection{Adaptive Hybrid Rules}
+\label{sec:ahr}
 
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[ht]
   \label{alg:path}
@@
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
-These two assumptions are supported by experiments from both the origin paper of SSR \citep{Tibshirani2012} and many other papers studying feature screening.
+These two assumptions are supported by experiments from the original SSR paper \citep{Tibshirani2012} as well as our own investigations as discussed in the Appendix.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 
-\begin{table}[H]
+\begin{table}[ht]
 \centering
@@
 \end{tabular}
-\caption{Average computing time in second (standard error) for solving the lasso model}
+\caption{Average computing time in seconds (standard error) for solving the lasso model}
 \label{Tab:real}
@@
 
-AHR again outperforms other screening methods on all data sets, faster than other methods by factor ranging from 70\% to 630\%.
+AHR again outperforms other screening methods on all data sets, faster than other methods by a factor ranging from 70\% to 630\%.
 Also note that the performance of SEDPP varies considerably for the MNIST and NYT data sets, where the response is randomly selected in each replication, indicating that the speed of SEDPP is sensitive to the data.
-AHR is built with SEDPP as the safe rule but does not share this issue of instability because it can adaptively adjust itself according the performance of the safe rule.
-Besides the computation time, we also look at a variaty of other statistics in the experiments, as discussed in the Appendix \ref{sec:ap}.
+AHR is built with SEDPP as the safe rule but does not share this issue of instability because it adaptively adjusts itself according the performance of the safe rule.
+A more detailed investigation of the algorithms' performance on these data sets including information on the number of rejections and KKT checks required is provided in the Appendix.
 

### 2021-09-08 jscs/response/response.tex
response: Draft started

\documentclass{article}
\usepackage[left=1in,right=1in,bottom=1in,top=1in]{geometry}
\usepackage{amsmath}

\begin{document}

\subsubsection*{Response to comments by Reviewer 1}

Thank you very much for your detailed reading of the paper and your insightful comments and questions. You raise a number of good points and we have modified the manuscript in several places based upon your feedback.  In our opinion, these revisions have nicely improved upon the original submission.

\begin{enumerate}

\item \emph{Numerical studies only focus on the computational performances of the algorithms. One may be interested in some details in the proposed algorithm: the size of variables remaining from the safe or strong rules, the number of KKT condition checks, the adaptive batch sizes, etc. It would be good to add the numerical studies for details in the algorithm.}

\item \emph{The paper assumes that the predictive variables are standardized for linear and logistic regression models. For group lasso, the additional orthogonal assumption are required for the proposed method. I’m just wondering if the proposed method is applicable without the standardization assumptions. Specifically, is it possible to develop (or exist) the sequential safe and strong rules without the standardization assumptions.}

\item \emph{In page 10, line 13, ``We also assume that post-convergence check will usually pass in the first iterations''. I’m not sure it is reasonable.}

\item \emph{In page 8, line 19, ``the reference solutions are continually updated''. The reference solutions are not always updated. So, I’m not sure the term ``continually'' is appropriate.}

\item \emph{In Figure 3, the green line (HSSR) pattern is quite different with others. Could you explain it?}

\item \emph{In Section 6(Conclusion), there does not exist the sequential safe rules for sparse Cox regression, Poisson regression, and support vector machines. It would be good to explain the existence of the sequential strong rules for each problem.}

\item \emph{In Theorem 4.1, $x_* \in \{ x_j : \hat{\beta}_j(\lambda_l) \ne 0 \}$. Is the $x_*$ arbitrary? It seems that further explanation for $x_*$ is needed.}

\item \emph{Minor corrections:} These have all been made. Thank you very much for pointing them out.

\end{enumerate}

\end{document}

### 2021-09-08 jscs/adaptive-hssr.tex
response: Draft started

@@
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
-These two assumptions are supported by experiments from the origin paper of SSR \citep{Tibshirani2012}, many other papers studying feature screening, and our manuscript as discussed in the Appendix \ref{sec:ap}.
+These two assumptions are supported by experiments from the origin paper of SSR \citep{Tibshirani2012}, many other papers studying feature screening, and our manuscript as discussed in the Appendix.
 
@@
 AHR is built with SEDPP as the safe rule but does not share this issue of instability because it can adaptively adjust itself according the performance of the safe rule.
-Besides the computation time, we also look at a variaty of other statistics in the experiments, as discussed in the Appendix \ref{sec:ap}.
+Besides the computation time, we also look at a variaty of other statistics in the experiments, as discussed in the Appendix.
 
@@
 
-\appendix
-\appendixpage
-
-\section{Supplementary Real Data Analysis Results}
-\label{sec:ap}
-
-At the first replication on each of the 4 data sets, we first record the number of features discarded by each screening method at each $\lambda$ value along the path of $L=100$ values.
-Features discarded by SEDPP are safely discarded and features discarded by SSR are not safely discarded and require additional checks.
-For the adaptive hybrid rule, we use AHR\_Safe to denote the features that are safely discarded first by adaptive EDPP and AHR\_Strong to denote features that discarded afterward by adaptive SSR and require additional checks.
-The results are summarized in Figure \ref{fig:ap1}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.82\textwidth]{app1.eps}    \caption{Comparing number of discards by screening methods for lasso model along $\lambda$ values.}
-    \label{fig:ap1}
-\end{figure}
-
-Note each jump of the number of discards for AHR method indicates an update of reference because a newer reference leads to higher screening power.
-Our adaptive updating algorithm determines the timing of update dynamically depending on the screening performance.
-For all four data sets, with about only 10 updates, the adaptive hybrid screening can safely discard a great number of features at most $\lambda$ values.
-
-Next we compare the number of rounds of KKT conditions checks and the number of KKT conditions checks on individual features, needed for AHR and SSR respectively, as shown in Table \ref{Tab:kkt1} and Table \ref{Tab:kkt2}.
-In a round of KKT conditions check, all features that are not discarded by the safe rule are checked, and a round a KKT conditions check potentially include a large number of KKT conditions checks on individual features.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{lllll}
-\toprule
-Screening method & GENE & MNIST & GWAS & NYT \\
-\midrule
-SSR & 99 & 99 & 99 & 99 \\
-AHR & 99 & 99 & 99 & 99 \\
-\bottomrule
-\end{tabular}
-\caption{Number of rounds of KKT conditions checks required for the whole path}
-\label{Tab:kkt1}
-\end{table}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{lllll}
-\toprule
-Screening method & GENE & MNIST & GWAS & NYT \\
-\midrule
-SSR & 1,712 & 5,943 & 60,986 & 5,429 \\
-AHR & 172 & 286 & 2,353 & 622 \\
-\bottomrule
-\end{tabular}
-\caption{Number of KKT conditions checks on individual features ($\times10^3$) required for the whole path}
-\label{Tab:kkt2}
-\end{table}
-
-Although a path include $L=100$ $\lambda$ values, the solution at the first value $\lambda_{0}$ is trivially $\hat{\beta}(\lambda_0)=0$ so we are essentially solving along $99$ $\lam$ values.
-If the strong rule does not make a violation, the minimal number of rounds of KKT conditions checks required will be $99$.
-In all four data sets, neither SSR nor the adaptive SSR in AHR ever makes a violation.
-However two methods are very different in terms of the number of KKT conditions checks on individual features, which proportionally increases the computational cost.
-AHR requires much less checks on individual features because the adaptive EDPP narrows down the set of features that need to be checked by a magnitude.
-
 \end{document}

### 2021-09-08 jscs/response/response.tex
Adding some responses to reviewer comments

@@
 
+  This is an excellent point.
+We felt that some readers would definitely want to know this additional information, while others might just care that the algorithm is faster.
+So, in the revised manuscript we have created an appendix that presents these additional details, which do indeed lend insight into how all of the algorithms are working and how the proposed method manages to achieve efficiency gains.
+
 \item \emph{The paper assumes that the predictive variables are standardized for linear and logistic regression models.
@@
 
+  We now provide both a citation and our own investigations (in the appendix) to support this assumption.
+
 \item \emph{In page 8, line 19, ``the reference solutions are continually updated''. The reference solutions are not always updated. So, I’m not sure the term ``continually'' is appropriate.}
+
+  Very good point. In the revised manuscript, we have changed this to ``the reference gets updated periodically'', which is a more accurate description.
 
@@
 
-\item \emph{Minor corrections:} These have all been made. Thank you very much for pointing them out.
+\end{enumerate}
+
+\textbf{Minor corrections:}
+
+\begin{enumerate}
+
+\item \emph{In Theorem 4.1, $\lambda_0 := \max_j |x^T_j y/n|$ may be incorrect.
+It would be the maximum gradient value at $\hat{\beta} = 0$ of the negative log-likelihood in logistic regression model.}
+
+\item \emph{In page 10, line 20, $|S_{l=b}|$ should be $|S_{l+b}|$.}
+
+\item \emph{In Figure 1, the green line is not continuous. It would be better to modify Figure 1.}
+
+\item \emph{In page 9, line 50, the ’line 12’ is better than ’line 11’ in Algorithm 1.}
+
+\item \emph{In Theorem 4.2, $\lambda_0 := \max_j \lVert \ldots \rVert$. The $j$ should be $g$.}
 

### 2021-09-09 jscs/response/response.tex
Fix appendix and add responses

@@
 
+    Most of the sequential safe or strong rules does not require standardization, including the rules mentioned in our manuscript.
+As a result, our method does not require standardization and we introduce the standardization assumption mainly for simplicity.
+We also add this clarification to the manuscript in the end of the first paragraph in Section 2.
+
 \item \emph{In page 10, line 13, ``We also assume that post-convergence check will usually pass in the first iterations''. I’m not sure it is reasonable.}
@@
 
-  Very good point. In the revised manuscript, we have changed this to ``the reference gets updated periodically'', which is a more accurate description.
+  Very good point. In the revised manuscript, we have changed this to ``the reference gets updated systematically'', which is a more accurate description.
 
 \item \emph{In Figure 3, the green line (HSSR) pattern is quite different with others. Could you explain it?}
+
+    We add a brief explanation that HSSR works better when $\lambda$ values in the path are closer to $\lambda_{\max}$ but we decide not to go deeper as HSSR is not our main interest.
 
@@
 
+    Thanks for this good suggestion. We explain their existence in the last sentence in this section.
+
 \item \emph{In Theorem 4.1, $x_* \in \{ x_j : \hat{\beta}_j(\lambda_l) \ne 0 \}$. Is the $x_*$ arbitrary? It seems that further explanation for $x_*$ is needed.}
+
+    It is a good question. In the second sentence in the last paragraph after the theorem, we clarify that $x_*$ can be chosen arbitrarily and add more explanation for it.
 
@@
 
+    Under the standardization assumption, the gradient will be $|x^T_j y/n|$ and this expression is correct.
+
 \item \emph{In page 10, line 20, $|S_{l=b}|$ should be $|S_{l+b}|$.}
+
+    Thanks for the good observation and it is fixed.
 
@@
 
+    The green line should have jumps that represent updates of reference that increase screening power. We add an explanation of the jumps in the 7th sentence in the paragraph after the figure.
+
 \item \emph{In page 9, line 50, the ’line 12’ is better than ’line 11’ in Algorithm 1.}
 
+    Good suggestion. It is updated.
+
 \item \emph{In Theorem 4.2, $\lambda_0 := \max_j \lVert \ldots \rVert$. The $j$ should be $g$.}
+
+    Thanks. It is fixed.
 

### 2021-09-09 jscs/adaptive-hssr.tex
Fix appendix and add responses

@@
 
+\section*{Appendix}
+%\label{sec:ap}
+
+To illustrate the inner workings of the proposed algorithm on a variety of problems, for a single replication of each of the four data sets in Section~\ref{sec:real-data} we recorded the number of features discarded by each screening method at each $\lambda$ value along the path of $L=100$ values.
+Features discarded by SEDPP are safely discarded, while features discarded by SSR are not necessarily safe and require additional checks.
+For the adaptive hybrid rule, we use AHR\_Safe to denote the features that are safely discarded first by adaptive EDPP and AHR\_Strong to denote features that discarded afterward by adaptive SSR and require additional checks.
+The results are summarized in Figure \ref{fig:ap1}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.82\textwidth]{app1.eps}    \caption{Comparing number of discards by screening methods for lasso model along $\lambda$ values.}
+    \label{fig:ap1}
+\end{figure}
+
+Note that the AHR method is rather ``jumpy''; this is by design, and these spikes represent moments along the path that triggered an update of the reference solution to gain more screening power.
+Our adaptive updating algorithm determines the timing of update dynamically depending on the screening performance.
+For all four data sets, with about only 10 updates, the adaptive hybrid screening can safely discard a great number of features at most $\lambda$ values.
+
+Next we compare the number of rounds of KKT condition checks and the number of KKT condition checks on individual features needed for AHR and SSR respectively, as shown in Table \ref{Tab:kkt1} and Table \ref{Tab:kkt2}.
+In a round of KKT condition checking, all features that are not discarded by the safe rule are checked, which potentially includes a large number of individual feature checks.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{lllll}
+\toprule
+Screening method & GENE & MNIST & GWAS & NYT \\
+\midrule
+SSR & 99 & 99 & 99 & 99 \\
+AHR & 99 & 99 & 99 & 99 \\
+\bottomrule
+\end{tabular}
+\caption{Number of rounds of KKT conditions checks required for the whole path}
+\label{Tab:kkt1}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{lllll}
+\toprule
+Screening method & GENE & MNIST & GWAS & NYT \\
+\midrule
+SSR & 1,712 & 5,943 & 60,986 & 5,429 \\
+AHR & 172 & 286 & 2,353 & 622 \\
+\bottomrule
+\end{tabular}
+\caption{Number of KKT conditions checks on individual features ($\times10^3$) required for the whole path}
+\label{Tab:kkt2}
+\end{table}
+
+Although all paths includes $L=100$ $\lambda$ values, the solution at the first value is exactly $\hat{\beta}(\lambda_0)=0$ and does not require any checking.
+Thus, if no violations occur in the application of the strong rule, the number of rounds of KKT condition checking required will attain its minimum value of $99$.
+In all four data sets, neither SSR nor the adaptive SSR in AHR is ever violated (as other authors have discussed, violations are rare but possible).
+However, the two methods are very different in terms of the number of individual features involved in these condition checks.
+AHR requires far fewer checks on individual features because the adaptive EDPP narrows down the set of features that need to be checked by an order of magnitude, which is how it achieves greater computational efficiency.
+
 \end{document}

### 2021-09-11 jscs/response/response.tex
Some edits to responses; new cover letter

--- 2021-09-08 jscs/response/response.tex
@@
 We felt that some readers would definitely want to know this additional information, while others might just care that the algorithm is faster.
-So, in the revised manuscript we have created an appendix that presents these additional details, which do indeed lend insight into how all of the algorithms are working and how the proposed method manages to achieve efficiency gains.
+So, in the revised manuscript we present these additional details in an appendix, which does indeed lend insight into how all of the algorithms are working and how the proposed method manages to achieve efficiency gains.
 
@@
 Specifically, is it possible to develop (or exist) the sequential safe and strong rules without the standardization assumptions.}
+
+  Most sequential safe or strong rules do not require standardization, including the rules that we describe in our manuscript.
+As a result, our method does not require standardization.
+We introduce the standardization assumption mainly for simplicity.
+In the revised manuscript, we have clarified this point at the end of the first paragraph in Section 2.
 
@@
 
-  Very good point. In the revised manuscript, we have changed this to ``the reference gets updated periodically'', which is a more accurate description.
+  Very good point. In the revised manuscript, we have changed this to ``the reference gets updated systematically'', which is a more accurate description.
 
 \item \emph{In Figure 3, the green line (HSSR) pattern is quite different with others. Could you explain it?}
+
+  We have added a short explanation in Section 5.1.1 that HSSR works better when $\lambda$ values in the path are closer to $\lambda_{\max}$.
+Further exploration and discussion of the performance of hybrid rules compared to safe/strong rules may be found in Zeng et al.~(2021) paper in which they are proposed.
 
@@
 
+  Thank you for this good suggestion. In the final paragraph of the conclusion section, we now discuss the existence of strong rules for various models.
+
 \item \emph{In Theorem 4.1, $x_* \in \{ x_j : \hat{\beta}_j(\lambda_l) \ne 0 \}$. Is the $x_*$ arbitrary? It seems that further explanation for $x_*$ is needed.}
+
+  This is a good question.
+We have added further clarification of this point in paragraph following the theorem.
+The feature $x_*$ is indeed arbitrary -- any feature with non-zero coefficient at the reference $\lambda_l$ suffices.
 
@@
 
-\textbf{Minor corrections:}
+\subsubsection*{Minor corrections:}
 
@@
 
+  You are correct that $\lambda_0$ should be the maximum gradient of the negative log-likelihood.
+However, under the standardization assumption, this gradient is $|x^T_j y/n|$ at $\hat{\beta} = 0$.
+Thus, the expression is correct, albeit not immediately obvious.
+
 \item \emph{In page 10, line 20, $|S_{l=b}|$ should be $|S_{l+b}|$.}
+
+  Thank you very much for pointing this out. We have corrected this in the revised submission.
 
@@
 
+  Thank you for directing our attention to the fact that this may be confusing to the reader.
+The discontinuities are correct -- every time the reference is updated, this causes a ``jump'' as the screening power is greatly increased every time this happens.
+In the revised manuscript, we have added an explanation for this phenomenon in the paragraph following Figure 1.
+
 \item \emph{In page 9, line 50, the ’line 12’ is better than ’line 11’ in Algorithm 1.}
 
+  Thank you very much for pointing this out. We have adopted this suggestion in the revised submission.
+
 \item \emph{In Theorem 4.2, $\lambda_0 := \max_j \lVert \ldots \rVert$. The $j$ should be $g$.}
+
+  Thank you very much for pointing this out. We have corrected this in the revised submission.
 

### 2021-09-11 jscs/adaptive-hssr.tex
Some edits to responses; new cover letter

@@
 We also assume that post-convergence check will usually pass in the first iteration and thus is only needed approximately once per $\lambda$.
-These two assumptions are supported by experiments from the origin paper of SSR \citep{Tibshirani2012}, many other papers studying feature screening, and our manuscript as discussed in the Appendix.
+These two assumptions are supported by experiments from the original SSR paper \citep{Tibshirani2012} as well as our own investigations as discussed in the Appendix.
 
@@
 When computing the adaptive Slores, $\{x_j^Ty\}_{j=1}^p$ needs to be computed only once, after which it can be stored and reused for the whole solution path.
-The vector $x_*$ can be chosen arbitrarily from features that has non-zero coefficients at the reference $\lambda_l$, for example, the feature whose coefficient that first enters the model.
+The vector $x_*$ can be chosen arbitrarily -- any feature with non-zero coefficient at the reference $\lambda_l$ suffices.
 The quantity $\{x_j^Tx_*\}_{j=1}^p$ can be similarly reused unless the corresponding regression coefficient drops out of the model; this can happen but is relatively rare.
@@
 
-AHR again outperforms other screening methods on all data sets, faster than other methods by factor ranging from 70\% to 630\%.
+AHR again outperforms other screening methods on all data sets, faster than other methods by a factor ranging from 70\% to 630\%.
 Also note that the performance of SEDPP varies considerably for the MNIST and NYT data sets, where the response is randomly selected in each replication, indicating that the speed of SEDPP is sensitive to the data.
-AHR is built with SEDPP as the safe rule but does not share this issue of instability because it can adaptively adjust itself according the performance of the safe rule.
-Besides the computation time, we also look at a variaty of other statistics in the experiments, as discussed in the Appendix.
+AHR is built with SEDPP as the safe rule but does not share this issue of instability because it adaptively adjusts itself according the performance of the safe rule.
+A more detailed investigation of the algorithms' performance on these data sets including information on the number of rejections and KKT checks required is provided in the Appendix.
 
@@
 
+%\appendix
+%\appendixpage
+
 \section*{Appendix}
